### 2021-12-08 inst/report/proposal/proposal.Rmd
First commit

---
title: "Implication of overestimation of connectance predicted by the ADBM on the stability of food web"
output: 
  pdf_document:
    number_sections: true
    toc: yes

header-includes:
  - \usepackage{setspace}\linespread{1.25}
bibliography: references.bib
---

## Key points:

-   Overestimation of connectance in food web model [@gravelInferringFoodWeb2013]
-   Undersampling in food web
-   Implications of above on food web stability
-   Effect of intervality on the stability of food web

## Preliminary work

### Implication of overestimation of connectance in the ADBM

#### Benguela Pelagic food web

-   Removal of most connected node

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_1} Most connected"}
knitr::include_graphics("../../../results/plot_dd_mc.png")
```

-   Removal of random nodes

```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_2} Random extinctions"}
knitr::include_graphics("../../../results/plot_dd_rand.png")
```

# References

### 2021-12-08 manuscript/ms_C3.Rmd
First commit

---
title: "Structural stability of ADBM predicted food webs"
authors:
- name: Anubhav Gupta
  thanks: Corresponding author
  department: Department of Evolutionary Biology and Environmental Studies
  affiliation: University of Zurich
  location: 8057 Zurich, Switzerland
  email: anubhav.gupta@ieu.uzh.ch
- name: Owen L. Petchey
  department: Department of Evolutionary Biology and Environmental Studies
  affiliation: University of Zurich
  location: 8057 Zurich, Switzerland
  email: owen.petchey@ieu.uzh.ch
geometry: margin=1in
output:
  pdf_document:
    number_sections: true
  rticles::arxiv_article:
    keep_tex: yes

keywords:
- connectance
- ABC
- ADBM
- food web
- extinction
- uncertainty
header-includes:
- \usepackage{lineno}
- \linenumbers
- \usepackage {amsmath}
- \setlength\parindent{24pt}
- \usepackage{setspace}\doublespacing
mainfont: Times New Roman
bibliography: bibliography.bib
abstract: |
  Some text here.
---

# Introduction

<!-- Paragraph: Anthropogenic changes and trophic cascading extinctions-->

Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity and can lead to food web collapse. Climate change can lead to the collapse of a food web [@ullah2018]. Primary extinctions in a food web can give rise to further secondary extinctions in a food web resulting in collapse of the food web. Depending upon the food web, removal of few species from a food web can result in the food web collapse.

A loss of species in an ecosystem can lead to secondary extinction of species that feed on the species. The effect of these losses would depend upon the complexity of the food web.

Simulation study has been used to understand the robustness of food webs predicted using food web models [@dunneCascadingExtinctionsCommunity2009]. As food web models can be used to predicting interactions to understanding the mechanism behind interactions in a food web, it is important to know how robust these predicted food webs are.

<!-- Paragraph: ADBM predicted food webs -->

The allometric diet breadth model (ADBM) was the first model able to predict food web connectance (i.e. the number of realised links divided by total number of possible links) and structure (i.e. the arrangement of those links). ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.

In Gupta et al. (2021), the connectance (number of realised links divided by the total number of possible links) was overestimated by the allometric diet breadth model (ADBM) when compared with observed food webs. The study used approximate Bayesian computation to parameterise the ADBM and true skill statistics as the goodness of fit. It is crucial to understand the robustness of these food webs predicted using the ADBM.

-   Canonical experiments not possible

-   Community viability analysis

-   How diversity and complexity influence the susceptibility of communities to secondary extinctions

<!-- Paragraph: Robustness of ADBM predicted food webs -->

Theoretical studies have simulated primary extinctions to check the robustness of food webs [@dunneCascadingExtinctionsCommunity2009]. @dunne had shown that the robustness of a food web increases with connectance.

# Materials and methods

## Allometric Diet Breadth Model (ADBM)

The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966]. The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008]. The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.

## Food web data

The observed food webs that we fit the ADBM to belong to marine, freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). The observed connectance of these food webs is from 0.03 to 0.24 and there are 29 to 239 species. The food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids. They also contain various types of feeding interactions, including predation, herbivory, bacterivory, parasitism, pathogenic, and parasitoid.

## Species removal

We used the primary species removal method used in @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species. The most-connected and least-connected criteria are based on the degree (i.e. total number of links to resource and links from consumer for each species) of species. Given a primary removal if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are dropped from the web and were recorded as a secondary extinction. Then the next appropriate species are removed determining the most- and least-connected species based on the web remaining after all prior primary removals and secondary extinctions had occurred. This process was carried out until all species were extinct from the web.

Robustness (R) of food web was quantified as the proportion of species subjected to primary removals that resulted in a total loss (i.e. primary removals plus secondary extinctions) of some specified proportion of the species. In our study, we use $R_{50}$, primary extinctions that result in at least 50 per cent of total species loss [@dunne2002; @dunne2004; @dunne2009]. Therefore, there is no secondary extinction in a maximally robust community ($R_{50} = 0.50$), whereas in a minimally robust community ($R_{50} = 1/S$) there is extensive secondary extinctions (i.e. at least $S/2 - 1$)

# Results

# Discussion

# References

### 2021-12-08 Bioenergetic_model/test.jl

@@ -1,0 +1,37 @@
+using DifferentialEquations
+using Plots
+
+function LV_model(du,u,p,t)
+    # growth rate of the resource (modelled as a logistic growth function)
+    GrowthR = p.growthrate * u[1] * (1 - u[1]/p.K)
+    # rate of resource ingestion by consumer (modelled as a type I functional response)
+    IngestC = p.ingestrate * u[1] * u[2]
+    # mortality of consumer (modelled as density independent) 
+    MortC = p.mortrate * u[2]
+    # calculate and store changes in abundance (du/dt):
+    # change in resource abundance
+    du[1] = GrowthR - IngestC
+    # change in consumer abundance
+    du[2] = p.assimeff * IngestC - MortC
+end
+
+# Parameters
+p = (growthrate = 1.0, ingestrate = 0.2, mortrate = 0.2, assimeff = 0.5, K = 10)
+
+# Initial values
+u0 = [1.0, 1.0]
+
+# Timespan
+tspan = (0.0, 100.0)
+
+prob = ODEProblem(LV_model, u0, tspan, p)
+
+sol = solve(prob)
+
+plot(sol,
+    ylabel = "Abundance",
+    xlabel = "Time",
+    title = "Lotka-Volterra",
+    label = ["prey" "predator"], 
+    linestyle = [:dash :dot],
+    lw=2)

### 2021-12-08 R/ADBM_ABC_fw.R

@@ -1,0 +1,34 @@
+ADBM_ABC_fw <- function(fw_name, fw_tol){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".RDS"))
+  
+  sel_ind <- which.min(ADBM_fw_all$dist)
+  ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}

### 2021-12-08 R/intervality.R

@@ -1,0 +1,36 @@
+# 14.10.2021
+# We compute the intervality of food webs using the approach defined in Stouffer et al. (2006) and written in Cheddar package
+
+library(cheddar)
+
+## Converts predation matrix into an object which cheddar can use
+mat.to.comm <- function(pred.mat, fw_title){
+  append_n <- function(n){
+    append_n <- paste(c('n',n), collapse='')
+  }
+  
+  dm <- dim(pred.mat)[1]
+  nod <- data.frame(node = sapply(1:dm, append_n), stringsAsFactors = FALSE)
+  prop <- list(title = fw_title)
+  trop <- data.frame(resource = character(), consumer = character())
+  
+  for(i in 1:dm){
+    for(j in 1:dm){
+      if(pred.mat[i,j] == 1){
+        temp <- data.frame(resource = append_n(i), consumer = append_n(j), stringsAsFactors = FALSE)
+        trop = rbind(trop, temp)
+      }
+    }
+  }
+  mat.to.comm <- Community(nod, prop, trop)
+}
+
+
+intervality <- function(pred_mat){
+  title <- "foodweb"
+  community <- mat.to.comm(pred_mat, title)
+ 
+  sdg <- SumDietGaps(community = community)
+   
+  return(sdg)
+}

### 2021-12-08 R/most_connected_ext.R

@@ -1,0 +1,41 @@
+# 23.11.2021
+# Simulating extinction for most connected nodes
+
+most_connected_ext <- function(net){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  # Stop when all the species is extinct
+  while(all(is.na(new_net)) == FALSE ! sum(new_net) != 0){
+    indeg <- rowSums(new_net)
+    outdeg <- colSums(new_net)
+    totdeg <- indeg + outdeg
+    
+    max_totdeg <- which.max(totdeg)
+    node <- names(max_totdeg)
+    
+    ext_list[[k]] <- sim_single_ext(net = new_net, node = node)
+    new_net <- ext_list[[k]]$net
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    } else {
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+                  )
+    }
+    
+    k <- k + 1
+    print(k)
+  }
+  
+  return(dd)
+
+}

### 2021-12-08 R/random_ext.R

@@ -1,0 +1,44 @@
+# 24.11.2021
+# Simulating extinctions for random nodes
+
+random_ext <- function(net, nsim){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+  
+  for(sim_ind in 1:nsim){
+      dd_temp <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+      new_net <- net
+      k <- 1
+      ext_list <- list()
+    
+    while(all(is.na(new_net)) == FALSE | sum(new_net) != 0){
+      pool_node <- rownames(new_net)
+      
+      node <- sample(x = pool_node, size = 1)
+      
+      ext_list[[k]] <- sim_single_ext(net = new_net, node = node)
+      new_net <- ext_list[[k]]$net
+      
+      if(k != 1){
+        dd_temp <- rbind(dd_temp, 
+                    data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                               acc_sec_ext = ext_list[[k]][[2]] + dd_temp$acc_sec_ext[k-1], nsim = sim_ind)
+        )
+      } else {
+        dd_temp <- rbind(dd_temp, 
+                    data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                               acc_sec_ext = ext_list[[k]][[2]], nsim = sim_ind)
+        )
+      }
+      
+      k <- k + 1
+      print(k)
+    }
+    dd <- rbind(dd, dd_temp)
+  }
+  
+  
+  sim_ind <- sim_ind + 1
+  
+  return(dd)
+}

### 2021-12-08 R/random_ext_parallel.R

@@ -1,0 +1,30 @@
+# 25.11.2021
+
+
+random_ext_parallel <- function(net, nsim, n_cores){
+  
+  nsim_pcore <- nsim/n_cores
+  registerDoParallel(cores = n_cores)
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+      result <- random_ext(net = net, nsim = nsim_pcore)
+      list(result)
+    }
+  
+  result_all <- res_pcores[[1]]
+  
+  for(i in 2:n_cores){
+    result_all <- rbind(result_all, 
+                        res_pcores[[i]] %>%
+                          mutate(nsim = (i-1)*nsim_pcore + nsim)
+    ) 
+  }
+
+  return(result_all)  
+}
+
+
+
+

### 2021-12-08 R/random_ext_summary.R

@@ -1,0 +1,11 @@
+# 25.11.2021
+
+random_ext_summary <- function(ext_seq){
+  
+  ext_seq_smry <- ext_seq %>%
+    group_by(acc_pri_ext) %>%
+    summarise(mean_acc_sec_ext = mean(acc_sec_ext), l_acc_sec_ext = min(acc_sec_ext), u_acc_sec_ext = max(acc_sec_ext),
+              count_n = n())
+  
+  return(ext_seq_smry)
+}

### 2021-12-08 inst/main/comp_mc.R

@@ -1,0 +1,84 @@
+# 22.10.2021
+# We compute how the secondary extinctions vary when we remove the most connected species in the food web predicted by ADBM
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing most connected nodes
+dd_mc <- data.frame(sec_ext = double(),
+                    n_ext = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/ADBM_2008_Petchey_par.xlsx")
+n_fw <- dim(metadata_fw_tol)[1]
+n_fw <- 11
+fw_ind <- c(1:7, 9, 10, 11)
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  ADBM_ABC_fw_calc <- ADBM_ABC_fw(fw_name = fw_name, fw_tol = fw_tol)
+  
+  real_pred_mat <- ADBM_ABC_fw_calc$real_pred_mat
+  ADBM_ABC_pred_mat <- ADBM_ABC_fw_calc$ADBM_pred_mat
+  ADBM_2008_pred_mat <- ADBM_2008_fw(fw_name = fw_name)$ADBM_pred_mat
+  
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
+  L_ADBM_2008 <- sum(ADBM_2008_pred_mat)
+  
+  
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  ADBM_ABC_conn <- sum(ADBM_ABC_pred_mat)/(dim(ADBM_ABC_pred_mat)[1]^2)
+  ADBM_2008_conn <- sum(ADBM_2008_pred_mat)/(dim(ADBM_2008_pred_mat)[1]^2)
+  
+  real_net <- as.network(real_pred_mat, loops = TRUE)
[…]

### 2021-12-08 inst/main/comp_rand.R

@@ -1,0 +1,107 @@
+# 22.10.2021
+# We compute how the secondary extinctions vary when we remove random species in the food web predicted by ADBM
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+
+# For removing random nodes
+dd_rand <- data.frame(mean_ext = double(),
+                      CI_lower = double(),
+                      CI_upper = double(),
+                      n_ext = integer(),
+                      type = character(),
+                      fw_name = character(),
+                      S = integer(),
+                      L = integer())
+
+
+ext_vs_n <- function(fw_name, fw_tol){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".RDS"))
+  
+  sel_ind <- which.min(ADBM_fw_all$dist)
+  ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}
+
+# Getting the foodweb name and tolerance
[…]

### 2021-12-08 inst/main/comp_rand_v2.R

@@ -1,0 +1,132 @@
+# 25.11.2021
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly = FALSE)
+
+dd_raw <- data.frame(acc_pri_ext = integer(), acc_sec_ext = integer(),
+                     nsim = integer(), type = character(), fw_name = character(),
+                     S = integer(), L = integer())
+  
+dd_rand <- data.frame(acc_pri_ext = integer(),
+                      mean_acc_sec_ext = double(),
+                      l_acc_sec_ext = double(),
+                      u_acc_sec_ext = double(),
+                      type = character(),
+                      fw_name = character(),
+                      S = integer(),
+                      L = integer(),
+                      count_n = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  Nsim <- 1000
+  
+  ADBM_ABC_fw_calc <- ADBM_ABC_fw(fw_name = fw_name, fw_tol = fw_tol)
+  
+  real_pred_mat <- ADBM_ABC_fw_calc$real_pred_mat
+  
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  ADBM_ABC_pred_mat <- ADBM_ABC_fw_calc$ADBM_pred_mat
+  ADBM_2008_pred_mat <- ADBM_2008_fw(fw_name = fw_name)$ADBM_pred_mat
+  
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
+  L_ADBM_2008 <- sum(ADBM_2008_pred_mat)
+  
+  
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
[…]

### 2021-12-08 inst/main/degree_distn.R

@@ -1,0 +1,14 @@
+# 25.11.2021
+
+
+##### Investigating degree distribution of Skipwith Pond
+
+skip_emp <- readRDS("../C1_method_v2/data/Skipwith Pond.web.RDS")$predation.matrix
+skip_ABC <- readRDS("data/ADBM_ABC_predicted_foodwebs/Skipwith Pond.pred_mat.RDS")
+
+skip_emp_net <- as.network(skip_emp)
+skip_ABC_net <- as.network(skip_ABC)
+
+NetworkExtinction::DegreeDistribution(skip_emp_net)
+
+NetworkExtinction::DegreeDistribution(skip_ABC_net)

### 2021-12-08 inst/main/diagnosis.R

@@ -1,0 +1,84 @@
+# 13.10.2021
+# We investigate the reasons for the differences in the secondary extinctions from ADBM predicted food webs and that of 
+# empirical food webs
+
+library(dplyr)
+library(tidyverse)
+
+dd_mc <- readRDS("results/dd_mc.RDS")
+rob_all <- readRDS("results/rob_all.RDS")
+dd <- data.frame(diff_rob = double(), conn_ADBM = double(), conn_emp = double(), diff_conn = double(),
+                 foodweb = character(), diff_intervality = double(), L_ADBM = integer(),
+                 L_emp = integer(), diff_L = integer(), rob_emp = double())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method/results/check/check_TSS_a.xlsx")
+
+for(fw_name in unique(dd_mc$fw_name)){
+  
+  pred_mat_ADBM <- readRDS(paste0("data/ADBM_2008_predicted_foodwebs/", fw_name, ".pred_mat.RDS"))
+  pred_mat_emp <- readRDS(paste0("../C1_method/data_new/", fw_name, ".web.Rdata"))$predation.matrix
+  
+  conn_ADBM <- sum(pred_mat_ADBM)/(dim(pred_mat_ADBM)[1]^2)
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  
+  L_ADBM <- sum(pred_mat_ADBM)
+  L_emp <- sum(pred_mat_emp)
+  
+  fw_name_f <- fw_name
+  
+  rob_ADBM <- filter(rob_all, type == "ADBM", fw_name == fw_name_f)$robustness
+  rob_emp <- filter(rob_all, type == "Empirical", fw_name == fw_name_f)$robustness
+  
+  dd <- rbind(dd,
+              data.frame(diff_rob = rob_ADBM - rob_emp, conn_ADBM = conn_ADBM, 
+                         conn_emp = conn_emp, diff_conn = conn_ADBM - conn_emp,
+                         foodweb = fw_name, 
+                         diff_intervality = intervality(pred_mat_emp) - intervality(pred_mat_ADBM),
+                         L_ADBM = L_ADBM, L_emp = L_emp, diff_L = L_ADBM - L_emp, rob_emp = rob_emp)
+  )
[…]

### 2021-12-08 inst/main/investigate_broadstone.R

@@ -1,0 +1,15 @@
+# 07.12.2021
+# We investigate the Broadstone Stream food web here
+
+### Empirical Broadstone Stream
+broad2008 <- readRDS("../C1_data/data/Broadstone Stream.web.RDS")
+broad2008 <- broad2008$predation.matrix
+broad2008_comm <- mat.to.comm(pred.mat = broad2008, fw_title = "Broadstone Stream")
+
+ext_seq_2008 <- most_connected_ext(net = broad2008)
+Plot.matrix(web = broad2008, title = "Broadstone Stream")
+PlotWebByLevel(community = broad2008_comm)
+
+
+
+

### 2021-12-08 inst/main/investigate_caricaie_lakes.R

@@ -1,0 +1,35 @@
+# 27.10.2021
+# Investigate Secondary extinctions in Caricaie Lakes food web
+
+caricaie_emp <- readRDS("../C1_method_v2/data/Caricaie Lakes.web.RDS")$predation.matrix
+caricaie_2008 <-readRDS("../C3_overestimation/data/ADBM_2008_predicted_foodwebs/Caricaie Lakes.pred_mat.RDS")
+caricaie_ABC <- readRDS("../C3_overestimation/data/ADBM_ABC_predicted_foodwebs/Caricaie Lakes.pred_mat.RDS")
+
+Plot.matrix(caricaie_emp)
+Plot.matrix(caricaie_2008)
+Plot.matrix(caricaie_ABC)
+
+conn_emp <- sum(caricaie_emp)/(dim(caricaie_emp)[1]^2)
+conn_2008 <- sum(caricaie_2008)/(dim(caricaie_2008)[1]^2)
+conn_ABC <- sum(caricaie_ABC)/(dim(caricaie_ABC)[1]^2)
+
+net_caricaie_emp <- as.network(caricaie_emp)
+net_caricaie_2008 <- as.network(caricaie_2008)
+
+comm_caricaie_emp <- mat.to.comm(pred.mat = caricaie_emp, fw_title = "blabla")
+comm_caricaie_2008 <- mat.to.comm(pred.mat = caricaie_2008, fw_title = "blabla")
+
+indeg_caricaie_emp <- InDegree(community = comm_caricaie_emp)
+indeg_caricaie_2008 <- InDegree(community = comm_caricaie_2008)
+
+outdeg_caricaie_emp <- OutDegree(community = comm_caricaie_emp)
+outdeg_caricaie_2008 <- OutDegree(community = comm_caricaie_2008)
+
+hist(indeg_caricaie_emp, breaks = 50)
+hist(indeg_caricaie_2008, breaks = 50)
+
+hist(outdeg_caricaie_emp, breaks = 50)
+hist(outdeg_caricaie_2008, breaks = 50)
+
+emp <- DegreeDistribution(net_caricaie_emp)
+DegreeDistribution(net_caricaie_2008)

### 2021-12-08 inst/main/investigate_skipwith.R

@@ -1,0 +1,25 @@
+# 06.12.2021
+# We investigate the skipwtih pond food web here
+
+
+### Empirical Skipwith Pond
+skip2008 <- readRDS("../C1_data/data/Skipwith Pond.web.RDS")
+skip2008 <- skip2008$predation.matrix
+skip2008_comm <- mat.to.comm(pred.mat = skip2008, fw_title = "Skipwith Pond")
+
+ext_seq_2008 <- most_connected_ext(net = skip2008)
+Plot.matrix(web = skip2008, title = "Skipwith Pond")
+PlotWebByLevel(community = skip2008_comm)
+
+
+### ADBM_ABC Skipwith Pond
+skip_ADBM_ABC <- readRDS("data/ADBM_ABC_predicted_foodwebs/Skipwith Pond.pred_mat.RDS")
+skip_ADBM_ABC_comm <- mat.to.comm(pred.mat = skip_ADBM_ABC, fw_title = "Skipwith Pond")
+
+ext_seq_ADBM_ABC <- most_connected_ext(net = skip_ADBM_ABC)
+Plot.matrix(web = skip_ADBM_ABC, title = "Skipwith Pond")
+
+PlotWebByLevel(community = skip_ADBM_ABC_comm)
+
+
+

### 2021-12-08 inst/main/investigate_small_reef.R

@@ -1,0 +1,15 @@
+# 27.10.2021
+# Investigate Secondary extinctions in Small Reef food web
+
+reef_emp <- readRDS("../C1_method_v2/data/Small Reef.web.RDS")$predation.matrix
+reef_2008 <-readRDS("../C3_overestimation/data/ADBM_2008_predicted_foodwebs/Small Reef.pred_mat.RDS")
+reef_ABC <- readRDS("../C3_overestimation/data/ADBM_ABC_predicted_foodwebs/Small Reef.pred_mat.RDS")
+
+
+Plot.matrix(reef_emp)
+Plot.matrix(reef_2008)
+Plot.matrix(reef_ABC)
+
+conn_emp <- sum(ythan_emp)/(dim(ythan_emp)[1]^2)
+conn_2008 <- sum(reef_2008)/(dim(reef_2008)[1]^2)
+

### 2021-12-08 inst/main/investigate_ythan.R

@@ -1,0 +1,15 @@
+# 26.10.2021
+# Investigate Secondary extinctions in Ythan food web
+
+ythan_emp <- readRDS("../C1_method_v2/data/Ythan.web.RDS")$predation.matrix
+ythan_2008 <-readRDS("../C3_overestimation/data/ADBM_2008_predicted_foodwebs/Ythan.pred_mat.RDS")
+ythan_ABC <- readRDS("../C3_overestimation/data/ADBM_ABC_predicted_foodwebs/Ythan.pred_mat.RDS")
+
+
+Plot.matrix(ythan_emp)
+Plot.matrix(ythan_2008)
+Plot.matrix(ythan_ABC)
+
+conn_emp <- sum(ythan_emp)/(dim(ythan_emp)[1]^2)
+conn_2008 <- sum(ythan_2008)/(dim(ythan_2008)[1]^2)
+

### 2021-12-08 inst/main/overestimation.R

@@ -1,0 +1,100 @@
+# 07.09.2021
+
+# We investigate the effect of overestimation of connectance in the stability
+library(R.utils)
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+
+######### Benguela Pelagic food web
+
+fw_name <- "Benguela Pelagic"
+# fw_name <- "Broadstone Stream size_agg"
+# fw_name <- "Coachella"
+
+real_fw <- readRDS(paste("../C1_method/data_new/", fw_name, ".web.Rdata", sep = ""))
+real_pred_mat <- real_fw$predation.matrix
+
+ADBM_fw_all <- readRDS(paste0("../C1_method/results/rejection/", fw_name, "/rN=1000_tol=0.6_TSS_lower_a/", fw_name, ".Rdata"))
+
+sel_ind <- which.min(ADBM_fw_all$dist)
+
+ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+
+## Generating the ADBM predicted food web
+
+fw_data <- real_fw
+
+n_species <- length(fw_data$species.sizes)
+
+M <- fw_data$species.sizes
+M <- sort(M)
+
+sim_a <- 10^ADBM_fw_par$a
+sim_ai <- ADBM_fw_par$ai
+sim_aj <- ADBM_fw_par$aj
+sim_r.b <- 10^ADBM_fw_par$r.b
+
+local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+rownames(pred_mat) <- as.character(seq(1, n_species))
+colnames(pred_mat) <- as.character(seq(1, n_species))
+
+ADBM_pred_mat <- pred_mat
+
+real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+ADBM_conn <- sum(ADBM_pred_mat)/(dim(ADBM_pred_mat)[1]^2)
+
+### Using the package NetworkExtinction to simulate extinction
+
+library(NetworkExtinction)
+library(network)
+
+real_net <- as.network(real_pred_mat, loops = TRUE)
+ADBM_net <- as.network(ADBM_pred_mat, loops = TRUE)
+
[…]

### 2021-12-08 inst/main/overestimation_v2.R

@@ -1,0 +1,144 @@
+# 24.09.2021
+# We put the script of overestimation.R in function
+# We use the NetworkExtinction package from https://derek-corcoran-barrios.github.io/NetworkExtinction/index.html
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+
+
+# For removing most connected nodes
+dd_mc <- data.frame(sec_ext = double(),
+                    n_ext = integer(),
+                    type = character(),
+                    fw_name = character())
+  
+# For removing random nodes
+dd_rand <- data.frame(mean_ext = double(),
+                      CI_lower = double(),
+                      CI_upper = double(),
+                      n_ext = integer(),
+                      type = character(),
+                      fw_name = character())
+
+ext_vs_n <- function(fw_name, fw_tol){
+  
+  real_fw <- readRDS(paste("../C1_method/data_new/", fw_name, ".web.Rdata", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".Rdata"))
+  
+  sel_ind <- which.min(ADBM_fw_all$dist)
+  ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
[…]

### 2021-12-08 inst/main/plot_mc.R

@@ -1,0 +1,56 @@
+# 22.10.2021
+# Plot how secondary extinctions vary when number of species removed is increased
+
+dd_mc <- readRDS("results/dd_mc_v2.RDS")
+
+library(ggplot2)
+library(dplyr)
+library(latex2exp)
+
+dd_mc_mod <- dd_mc %>%
+  mutate(n_ext_by_S = n_ext/S, sec_ext_by_S = sec_ext/S)
+
+plot_dd_mc_mod <- ggplot(dd_mc_mod) +
+  geom_point(aes(x = n_ext_by_S, y = sec_ext_by_S, color = type), size = 2) +
+  facet_wrap(~fw_name, scales = "free") +
+  theme_classic() +
+  xlab("Species removed/S") +
+  ylab("Cumulative secondary extinction/S") +
+  scale_color_discrete(name = "Type")
+
+# ggsave(plot = plot_dd_mc_mod, filename = "results/plot_dd_mc.png", width = 10, height = 6)
+
+# ggsave(plot = plot_dd_mc_mod, filename = "results/plot_dd_mc_2008_ABC_emp.png", width = 9, height = 6)
+
+dd_rand_mod <- dd_rand %>%
+  mutate(n_ext_by_S = n_ext/S, mean_ext_by_S = mean_ext/S)
+
+plot_dd_rand_mod <- ggplot(dd_rand_mod) +
+  geom_point(aes(x = n_ext_by_S, y = mean_ext_by_S, color = type), size = 2) +
+  facet_wrap(~fw_name, scales = "free") +
+  theme_classic() +
+  xlab("Species removed/S") +
+  ylab("Cumulative secondary extinction/S") +
+  scale_color_discrete(name = "Type")
+
+
+# ggsave(plot = plot_dd_rand_mod, filename = "results/plot_dd_rand.png", width = 10, height = 6)
+
+
+
+dd_rand_mod_1 <- dd_rand %>%
+  mutate(n_ext_by_S = n_ext/S, mean_ext_by_S = mean_ext/S, CI_lower_by_S = CI_lower/S, CI_upper_by_S = CI_upper/S)
+
+plot_dd_rand_mod_1 <- ggplot(dd_rand_mod_1) +
+  geom_point(aes(x = n_ext_by_S, y = mean_ext_by_S, color = type), size = 2) +
+  geom_line(aes(x = n_ext_by_S, y = mean_ext_by_S, color = type)) +
[…]

### 2021-12-08 inst/main/robustness_mc.R

@@ -1,0 +1,169 @@
+# 25.10.2021
+# We investigate how the robustness vary across food webs
+
+library(cheddar)
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mc <- readRDS("results/dd_mc_v2.RDS")
+
+fw_list <- unique(dd_mc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double(), intervality = double())
+
+for(foodweb in fw_list){
+
+  #### ADBM ABC predicted food web first ####
+  dd_mc_ADBM_ABC <- dd_mc %>%
+    filter(fw_name == foodweb, type == "ADBM_ABC") %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  N_row <- dim(dd_mc_ADBM_ABC)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_mc_ADBM_ABC[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  
+  pred_mat_ADBM_ABC <- readRDS(paste0("data/ADBM_ABC_predicted_foodwebs/", foodweb, ".pred_mat.RDS"))
+  S <- dim(pred_mat_ADBM_ABC)[1]
+  conn_ADBM_ABC <- sum(pred_mat_ADBM_ABC)/(dim(pred_mat_ADBM_ABC)[1]^2)
+  intervality_ADBM_ABC <- intervality(pred_mat_ADBM_ABC)
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "ADBM_ABC", connectance = conn_ADBM_ABC,
+                              S = S, intervality = intervality_ADBM_ABC)
+                   )
+  
+  #### ADBM 2008 predicted food web second ####
+  dd_mc_ADBM_2008 <- dd_mc %>%
+    filter(fw_name == foodweb, type == "ADBM_2008") %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  N_row <- dim(dd_mc_ADBM_2008)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_mc_ADBM_2008[i,]
[…]

### 2021-12-08 inst/main/robustness_rand.R

@@ -1,0 +1,119 @@
+# 25.11.2021
+
+library(cheddar)
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_rand_raw <- readRDS("results/dd_rand_raw.RDS")
+
+fw_list <- unique(dd_rand_raw$fw_name)
+sim_ind <- unique(dd_rand_raw$nsim)
+list_all <- expand.grid(nsim = sim_ind, fw_name = fw_list)
+N <- dim(list_all)[1]
+
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double())
+
+for(i in 1:N){
+  
+  row_sel <- list_all[i,]
+  foodweb <- as.character(row_sel$fw_name)
+  
+  
+  ###### ADBM_ABC #######
+  type_fw = "ADBM_ABC"
+  dd_fil <- dd_rand_raw %>%
+    filter(fw_name == row_sel$fw_name, nsim == row_sel$nsim, type == type_fw) %>%
+    mutate(acc_tot_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  
+  N_row <- dim(dd_fil)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_fil[i,]
+    if(ith_row$acc_tot_ext >= 0.5){
+      robustness <- ith_row$acc_pri_ext/ith_row$S
+      break
+    }
+  }
+  
+  pred_mat <- readRDS(paste0("data/", type_fw, "_predicted_foodwebs/", foodweb, ".pred_mat.RDS"))
+  S <- dim(pred_mat)[1]
+  conn <- sum(pred_mat)/(dim(pred_mat)[1]^2)
+
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = type_fw, connectance = conn,
+                              S = S)
+  )
+  
+  ###### ADBM_2008 #######
+  type_fw = "ADBM_2008"
+  dd_fil <- dd_rand_raw %>%
+    filter(fw_name == row_sel$fw_name, nsim == row_sel$nsim, type == type_fw) %>%
+    mutate(acc_tot_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  
+  N_row <- dim(dd_fil)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_fil[i,]
[…]

### 2021-12-27 manuscript/ms_C3.Rmd
first commit
updated manuscript

@@
 ---
-title: "Structural stability of ADBM predicted food webs"
+title: "Robustness of ADBM predicted food webs"
 authors:
@@
 
-<!-- Paragraph: Anthropogenic changes and trophic cascading extinctions-->
+## Background on anthropogenic changes and its impact on food web
 
@@
 Primary extinctions in a food web can give rise to further secondary extinctions in a food web resulting in collapse of the food web.
-Depending upon the food web, removal of few species from a food web can result in the food web collapse.
+The impact of this extinction is dependent on the complexity and structure of the food web (reference).
 
-A loss of species in an ecosystem can lead to secondary extinction of species that feed on the species. The effect of these losses would depend upon the complexity of the food web.
+## Briefly explain work done by Jennifer Dunne on species extinctions
 
-Simulation study has been used to understand the robustness of food webs predicted using food web models [@dunneCascadingExtinctionsCommunity2009].
-As food web models can be used to predicting interactions to understanding the mechanism behind interactions in a food web, it is important to know how robust these predicted food webs are.
+Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+These studies showed that the robustness of the food webs increases with food web connectance.
+When canonical experiments in natural ecosystems are not possible, this provides an alternate solution to investigate the impact of primary extinctions in a food web.
 
-<!-- Paragraph: ADBM predicted food webs -->
+## ADBM predicted food webs
 
@@
 the number of realised links divided by total number of possible links) and structure (i.e.
-the arrangement of those links).
+the arrangement of those links) [@beckerman2006; @petchey2008].
 ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.
 
+## Robustness of ADBM predicted food webs
+
 In Gupta et al.
-(2021), the connectance (number of realised links divided by the total number of possible links) was overestimated by the allometric diet breadth model (ADBM) when compared with observed food webs.
-The study used approximate Bayesian computation to parameterise the ADBM and true skill statistics as the goodness of fit.
-It is crucial to understand the robustness of these food webs predicted using the ADBM.
+(2021), the ADBM parameterised with approximate Bayesian computation overestimated the food web connectance when compared with the observed connectance.
+It is crucial to investigate the implication of this overestimation in the robustness of predicted food webs.
+We suspect that the ADBM predicted food webs would be more robust as compared to the observed food webs.
 
--   Canonical experiments not possible
+## What we do in this study
 
--   Community viability analysis
-
--   How diversity and complexity influence the susceptibility of communities to secondary extinctions
-
-<!-- Paragraph: Robustness of ADBM predicted food webs -->
-
-Theoretical studies have simulated primary extinctions to check the robustness of food webs [@dunneCascadingExtinctionsCommunity2009].
-@dunne had shown that the robustness of a food web increases with connectance.
+In this study, we simulate primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
+We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand how the outcome varies among these approaches.
 
@@
 
-The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthurOptimalUsePatchy1966].
-The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petcheySizeForagingFood2008].
+The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthur1966].
+The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
 The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
@@
 
+```{r echo=FALSE, warning=FALSE}
+library(readxl)
+library(knitr)
+library(kableExtra)
+fw_table <- read_excel("table/fw_table.xlsx")
+kable(fw_table, format = "latex",
+      caption = "\\label{fig:tab_1}Information about the food webs predicted using the ADBM.", escape = FALSE, align = "l") %>%
+  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
+  landscape(margin = "1cm") %>%
+  column_spec(1, width = "3cm") %>%
+  column_spec(2, width = "8em") %>%
+  column_spec(7, width = "8em") %>%
+  column_spec(8, width = "8em") %>%
+  column_spec(9, width = "8em")
+
+```
+
 ## Species removal
 
-We used the primary species removal method used in @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species.
+We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species.
 The most-connected and least-connected criteria are based on the degree (i.e.
@@
 primary removals plus secondary extinctions) of some specified proportion of the species.
-In our study, we use $R_{50}$, primary extinctions that result in at least 50 per cent of total species loss [@dunne2002; @dunne2004; @dunne2009].
+In our study, we use $R_{50}$, primary extinctions that result in at least 50 per cent of total species loss [@dunne2002network; @dunne2004; @dunneCascadingExtinctionsCommunity2009].
 Therefore, there is no secondary extinction in a maximally robust community ($R_{50} = 0.50$), whereas in a minimally robust community ($R_{50} = 1/S$) there is extensive secondary extinctions (i.e.
-at least $S/2 - 1$)
+at least $S/2 - 1$).
 
@@
 
+## Explain the secondary extinction curves
+
+```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions for 12 food webs across different ecosystems."}
+knitr::include_graphics("../results/plot_dd_mc_mod.png")
+```
+
+### Compare the results from the different methods
+
+## Explain the outlier food webs: where the stability of ADBM predicted food webs is lower than empirical food webs
+
+## Explain the robustness plots
+
+### Compare the results from the different methods
+
 # Discussion
 
+## What does overestimation of connectance imply in terms of stability?
+
+## Discuss how the robustness is dependent on the TSS of the predicted food web
+
+* Would a higher TSS imply a higher difference in the robustness between predicted and observed food web?
+
+## Compare the results from our study with results from other food web models (Jennifer A. Dunne and Williams (2009))
+
+## Explain that the ADBM can only predicts contiguous diets
+
+## Future prospect of using a dynamical model to model the temporal dynamics of the ADBM predicted food web
+
 # References

### 2021-12-27 inst/main/comp_mc_v3.R

@@ -1,0 +1,90 @@
+# 13.12.2021
+# Modified version of comp_mc_v2.R
+# We consider all the 1000 predicted food webs from ADBM
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing most connected nodes
+dd_mc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+ 
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_mc <- most_connected_ext(net = real_pred_mat)
+  
+  dd_mc <- rbind(dd_mc, 
+                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
+                            acc_sec_ext = real_ext_mc$acc_sec_ext,
+                            nsim = 1,
+                            type = "Empirical",
+                            fw_name = fw_name,
+                            S = S,
+                            L = L_real))
+  
+  for(j in 1:1000){
[…]

### 2021-12-27 inst/main/robustness_mc_v3.R

@@ -1,0 +1,14 @@
+# 14.12.2021
+# We investigate how the robustness vary across food webs 
+# We use the output produced by using the script comp_mc_v3.R
+
+library(cheddar)
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mc <- readRDS("results/dd_mc_v3.RDS")
+
+fw_list <- unique(dd_mc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double(), intervality = double())
+

### 2022-02-28 manuscript/ms_C3.Rmd
ms updated

@@
 ---
-title: "Robustness of ADBM predicted food webs"
+title: Missing links, false positives, and the topological robustness of predicted food webs
 authors:
-- name: Anubhav Gupta
+- affiliation: University of Zurich
+  department: Department of Evolutionary Biology and Environmental Studies
+  email: anubhav.gupta@ieu.uzh.ch
+  location: 8057 Zurich, Switzerland
+  name: Anubhav Gupta
   thanks: Corresponding author
+- affiliation: University of Zurich
   department: Department of Evolutionary Biology and Environmental Studies
-  affiliation: University of Zurich
+  email: owen.petchey@ieu.uzh.ch
   location: 8057 Zurich, Switzerland
-  email: anubhav.gupta@ieu.uzh.ch
-- name: Owen L. Petchey
-  department: Department of Evolutionary Biology and Environmental Studies
-  affiliation: University of Zurich
-  location: 8057 Zurich, Switzerland
-  email: owen.petchey@ieu.uzh.ch
+  name: Owen L. Petchey
 geometry: margin=1in
-output:
-  pdf_document:
-    number_sections: true
-  rticles::arxiv_article:
-    keep_tex: yes
+abstract: |
 
+  1)  Undersampling of species in a food web can lead to missing trophic interactions in the food web.
+This can be compensated by using food web models such as allometric diet breadth model (ADBM) to predict those missing links.
+At the same time, these models might predict links which are probably not true i.e.
+false positives.
+So, it is cruicial to understand how this affects the stability of predicted food webs when compared with the observed food webs.
+  2)  In our study, we compare the number of secondary extinctions when there is a primary extinction of species in food webs predicted by the ADBM to that in the observed food webs, and compute the robustness across 12 different food webs from a wide variety of ecosystems.
+  3)  We found that the ADBM predicted food webs were more robust than the observed food webs, and this can be attributed to connectance of the ADBM predicted food webs being higher than that of the observed food webs.
+  4)  These results suggest that real food webs might be more robust as compared to the food webs constructed using observed data.
 keywords:
@@
   - \usepackage{setspace}\doublespacing
+# indent: true
 mainfont: Times New Roman
 bibliography: bibliography.bib
-abstract: |
-  Some text here.
+biblio-style: biblatex
+output:
+  rticles::arxiv_article:
+    keep_tex: true
 ---
+
+# Alternate titles
+
+* Robustness of ADBM predicted food webs
 
@@
 
-Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity and can lead to food web collapse.
-Climate change can lead to the collapse of a food web [@ullah2018].
-Primary extinctions in a food web can give rise to further secondary extinctions in a food web resulting in collapse of the food web.
-The impact of this extinction is dependent on the complexity and structure of the food web (reference).
+Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity, and can lead to food web collapse [@ullah2018].
+Primary extinctions in a food web can give rise to further secondary extinctions in a food web which can result in collapse of the food web (reference).
+The rate at which a primary extinctions can lead to secondary extinctions is dependent on the structure and complexity of that food web (reference).
+Understanding this can help to implement conservation efforts tailored to a given food web structure (reference).
 
-## Briefly explain work done by Jennifer Dunne on species extinctions
+## Briefly explain work done by Jennifer Dunne on food web [OP] robustness to primary extinctions, and also what has been done since, particularly concerning the importance of connectance
 
@@
 These studies showed that the robustness of the food webs increases with food web connectance.
-When canonical experiments in natural ecosystems are not possible, this provides an alternate solution to investigate the impact of primary extinctions in a food web.
+Also, the removal of the most connected species cause considerably more secondary extinctions than random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
+These studies provide an alternate solution to investigate the impact of primary extinctions in a food web when canonical experiments in natural ecosystems are not possible.
 
-## ADBM predicted food webs
+Along with robustness based on topological structure of a food web, robustness based on the food web dynamics has been studied as well (reference).
+Topological approaches only require the food web structure whereas dynamical approaches also require the temporal dynamics of the food web along with the food web structure.
+For example: @williamsEffectsNetworkDynamical2008 combined models of network structure with models of bionergetic dynamics to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
 
-The allometric diet breadth model (ADBM) was the first model able to predict food web connectance (i.e.
-the number of realised links divided by total number of possible links) and structure (i.e.
-the arrangement of those links) [@beckerman2006; @petchey2008].
-ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.
+[OP] Explain (either here or in the methods) difference between topological and abundance (given by dynamics) based criteria for a secondary extinction occurring.
 
-## Robustness of ADBM predicted food webs
+## [OP] State what is the problem...
+
+A key assumption of this work is that food webs are very well sampled, so that all links that in reality can occur are represented.
+Yet it is known that not all food webs are very well sampled, and then do not represent all of the feeding links that occur (reference).
+One solution to this problem is to use a food web model to predict which are the missing links, and to then measure the robustness of the predicted food web.
+This solution is not fool proof, however, as it is likely that the food web model is not perfect, and so may still miss some links, and also may predict some links that could not, in fact occur.
+
+## In previous work...
 
 In Gupta et al.
-(2021), the ADBM parameterised with approximate Bayesian computation overestimated the food web connectance when compared with the observed connectance.
-It is crucial to investigate the implication of this overestimation in the robustness of predicted food webs.
-We suspect that the ADBM predicted food webs would be more robust as compared to the observed food webs.
+(2022) we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) by fitting it to empirical data using approximate Bayesian computation, and the goodness of fit of the ADBM was measured using the true skill statistics which takes into account the presence of links as well as the absence of links.
+(ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.) A key finding of Gupta et al.
+(2022) was that the predicted food web connectance was consistently higher as compared to the observed connectance.
+This means that there were some trophic links (false positives) predicted by the ADBM which are not observed in the empirical food web data.
+Simultaneously there were some trophic links (false negatives) that were not predicted by the ADBM but were observed in the empirical food web.
+In that work there was no attempt to estimate the importance of these findings on computing the robustness of these food webs to species extinctions.
 
@@
 
+It is crucial to investigate the implication of this consistent overestimation of connectance in the robustness of predicted food webs.
+We expect that the ADBM predicted food webs would be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
 In this study, we simulate primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
-We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand how the outcome varies among these approaches.
+We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
 
 # Materials and methods
+
+[OP] ## Provide overview of the methods
+
+In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different scenarios on 12 food webs predicted by the ADBM from wide variety of ecosystems, and compute the resultant secondary extinctions.
+We then compute a robustness metric to quantify the robustness of those predicted food webs.
 
@@
 
-## Species removal
+## Primary and secondary extinctions
 
@@
 
+## Calculating robustness
+
 Robustness (R) of food web was quantified as the proportion of species subjected to primary removals that resulted in a total loss (i.e.
 primary removals plus secondary extinctions) of some specified proportion of the species.
-In our study, we use $R_{50}$, primary extinctions that result in at least 50 per cent of total species loss [@dunne2002network; @dunne2004; @dunneCascadingExtinctionsCommunity2009].
+In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, that result in at least 50 per cent of total species loss [@dunne2002network; @dunne2004; @dunneCascadingExtinctionsCommunity2009].
 Therefore, there is no secondary extinction in a maximally robust community ($R_{50} = 0.50$), whereas in a minimally robust community ($R_{50} = 1/S$) there is extensive secondary extinctions (i.e.
@@
 
-## Explain the secondary extinction curves
+We first present the cumulative secondary extinctions in the food webs for three different extinction scenarios.
+We also computed the robustness metric for the food webs where the robustness metric quantifies the number of species extinctions required to have at least 50% of total number of species extinctions in a food web.
 
-```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions for 12 food webs across different ecosystems."}
-knitr::include_graphics("../results/plot_dd_mc_mod.png")
+## Show and describe the secondary extinction curves
+
+In Fig.
+\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show the secondary extinction curves of ADBM predicted food webs and observed food webs for 12 different food webs under three different extinction scenarios.
+In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs.
+
+In the most connected extinction scenario, the cumulative secondary extinction curve for the observed food webs rose quickly as compared to the ADBM predicted food webs, and then reach saturation after a certain number of primary removal of species.
+In some of the food webs (Fig.
+\ref{fig:fig_r1} (f, g, h, i, j, k)), there were intersection between the cumulative secondary extinction curves of ADBM predicted food webs and that of the observed food webs.
+In case of the Broadstone Stream (taxonomic aggregation) food web and the Tuesday Lake food web (Fig.
+\ref{fig:fig_r1} (b and k)), the secondary extinction curves for the ADBM food webs were higher than the observed food webs, whereas in case of the Skipwith Pond food web (Fig.
+\ref{fig:fig_r1} (i)), there were no secondary extinctions for any given number of primary removal of species.
+
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the most connected species for 12 food webs.
+S denotes the number of species in a food web.
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
+knitr::include_graphics("../results/plot_mostconnected.png")
 ```
 
-### Compare the results from the different methods
+Except Broadstone Stream (taxonomic aggregation), Broadstone Stream (size aggregation) and Tuesday Lake food webs (Fig.
+\ref{fig:fig_r2} (b, c and k)), the mean cumulative secondary extinction curves for all the other food webs predicted by the ADBM were always lower than that of the observed food webs in the random extinction scenario.
+The shape of the cumulative secondary extinctions curves varied across the food webs.
 
-## Explain the outlier food webs: where the stability of ADBM predicted food webs is lower than empirical food webs
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary removals of random species for 12 food webs.
+S denotes the number of species in a food web.
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
+knitr::include_graphics("../results/plot_random.png")
+```
 
-## Explain the robustness plots
+Compared to the most connected and random extinction scenarios, the cumulative extinction curves in the least connected extinction scenario had very low values and were flat for most of the food webs (Fig.
+\ref{fig:fig_r3}) compared to the most connected extinction and random extinction scenarios.
+In most of the food webs, there was a lot of overlap between the extinction curves of the ADBM predicted foof webs and the observed food webs.
 
-### Compare the results from the different methods
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the least connected species for 12 food webs.
+S denotes the number of species in a food web.
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
+knitr::include_graphics("../results/plot_leastconnected.png")
+```
+
+## Show and describe the following:
+
+I suggest to focus on the relationship between (difference in robustness between observed and predicted connectance) and (difference in robustness between the observed and predicted food web).
+
+The ADBM predicted food webs were more robust than the observed food web with some exceptions (Fig.
+\ref{fig:fig_r4}).
+The food webs were more robust to least connected and random extinction scenarios than the primary deletion of the most connected species.
+The difference in the robustness values between the ADBM predicted food webs and observed food webs was higher in the most connected extinction scenario as compared to the least connected extinction and random extinction scenarios.
+
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
+Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions)."}
+knitr::include_graphics("../results/plot_robustness_all_uncertainty.png")
+```
+
+AG: I will also add robustness plot for random extinction. It takes more time to compute.
 
@@
 
+The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs, and the shape of the robustness extinction curves varies between food webs.
+The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios.
+A future development would be to understand the stability of the dynamics of the ADBM predicted food webs and compare it with our study.
+
+...
+
 ## What does overestimation of connectance imply in terms of stability?
 
-## Discuss how the robustness is dependent on the TSS of the predicted food web
+For most of the food webs, the primary removals of species resulted in a higher secondary extinction in the ADBM predicted food webs than that of the observed food webs (Fig.
+\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}).
+This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a high connectance has on average more number of trophic links as compared to the food webs with low connectance.
 
-* Would a higher TSS imply a higher difference in the robustness between predicted and observed food web?
+It would be intriguing to know if this difference in connectance has a similar influence in the dynamical stability of the food webs as well.
+Hence, a future prospect could be to use a dynamical model (for example: bionergetic food web model [@broseAllometricScalingEnhances2006]) to model the temporal dynamics of the ADBM predicted food webs.
+It would be interesting to know the temporal stability of these ADBM predicted food webs compared to the observed food webs because it has been known that food webs with increasing connectance stability diminishes [@mayWillLargeComplex1972].
+
+...
+
+Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability.
+
+## Explain that the ADBM can only predicts contiguous diets [OP] and the implications of this
+
+Using only body size as a trait, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
+I.e.
+it cannot predict that a predator will consume prey of size 1 and 3, and not consume prey of size 2.
+Also, it is important to note that the observed diets were not contiguous when prey are ordered by their size, and this is due to some ecological differences in how predator group choose their prey [@caronAddressingEltonianShortfall].
+So, the parameterisation process lead to a greater number of predicted links than observed.
+
+This higher connectance in the ADBM predicted food webs has lead to a higher robustness of the ADBM predicted food webs.
+An important question to ask here is how reliable are these results.
+We suspect that this is because the model and the observed data are wrong to some extent.
+We expect that some of the links that do in reality occur are not present in the observed datasets, which is quite possible because of low sampling effort or rare prey-predator interactions even when there is intensive sampling.
+This would mean that the false positives may actually be a correctly predicted link.
+
+We suspect that the model is also predicting links which actually do not occur.
+This is because the current ADBM model only takes body size trait, and therefore only predicts contiguous diet.
+That would mean any interaction that is not possible because of some other traits not correlated with the body size would still be predicted by the model.
+For example, a species might have a defensive trait that could result in the predator species not predating on that species at all.
+
+AG: (Caution) Some of the texts might be very similar to or same as in C1 MS.
+With multiple iterations of the current ms, the current text would be altered.
+Also, the current ms would be checked using a plagiarism software before submission.
+
+...
+
+<!-- ## Discuss how the robustness is dependent on the TSS of the predicted food web -->
+
+<!-- * Would a higher TSS imply a higher difference in the robustness between predicted and observed food web? -->
+
+<!-- OP: This (TSS and robustness relationship) would need to be presented in the Results, if this is to be included. -->
+
+<!-- AG: I will present TSS and robustness relationship in the next version of the ms, and add relevant text here. -->
 
@@
 
-## Explain that the ADBM can only predicts contiguous diets
+The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased.
+A future study could be to understand the robustness of other food web models [@InferringFoodWeb] and compare it with our study.
+We expect similar results.
 
-## Future prospect of using a dynamical model to model the temporal dynamics of the ADBM predicted food web
+[OP] Including if and why we expect our findings to be replicated with those other models. Include some of Gravel and Poissot's models
+
+...
+
+Need to coordinate this content with what I proposed on line 141.
+
+Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability."
 

### 2022-02-28 manuscript/ms_C3.Rmd
minor changes

@@
 
-AG: I will also add robustness plot for random extinction. It takes more time to compute.
+AG: I will also update the robustness plot for random extinction (Fig.
+4 (b)) once the simulation is completed.
+The one shown here is only for few simulations and as a placeholder.
+It takes more time to compute.
 
@@
 The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased.
-A future study could be to understand the robustness of other food web models [@InferringFoodWeb] and compare it with our study.
+A future study could be to understand the robustness of other food web models [@gravelInferringFoodWeb2013a] and compare it with our study.
 We expect similar results.
@@
 
-Need to coordinate this content with what I proposed on line 141.
+<!-- Need to coordinate this content with what I proposed on line 141. -->
 
-Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability."
+<!-- Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability." -->
 

### 2022-03-21 manuscript/ms_C3.Rmd
owen's comments

@@
 ---
-title: Missing links, false positives, and the topological robustness of predicted food webs
+title: Missing links, forbidden links, and the topological robustness of food webs
 authors:
@@
 
-  1)  Undersampling of species in a food web can lead to missing trophic interactions in the food web.
-This can be compensated by using food web models such as allometric diet breadth model (ADBM) to predict those missing links.
-At the same time, these models might predict links which are probably not true i.e.
-false positives.
-So, it is cruicial to understand how this affects the stability of predicted food webs when compared with the observed food webs.
-  2)  In our study, we compare the number of secondary extinctions when there is a primary extinction of species in food webs predicted by the ADBM to that in the observed food webs, and compute the robustness across 12 different food webs from a wide variety of ecosystems.
-  3)  We found that the ADBM predicted food webs were more robust than the observed food webs, and this can be attributed to connectance of the ADBM predicted food webs being higher than that of the observed food webs.
-  4)  These results suggest that real food webs might be more robust as compared to the food webs constructed using observed data.
+  1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food web.
+Undersampling can be compensated for by using food web models such as allometric diet breadth model (ADBM) to predict missing links.
+At the same time, models might predict links which cannot occur, i.e., false positives.
+  2) Previous research shows that (i) food web robustness (the inverse of number of secondary extinctions occuring due to a primary extinction) increases with connectance (the number of tophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
+Thus we expect that predicted food webs are more robust than observed ones.
+This expectation has never, to our knowledge, been tested, nor has the quantative size of any effect.
+  2) We fill this gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though can also make false positives.
+We did this for 12 different food webs from a wide variety of ecosystems.
+  3)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
+**OP: Here something about the effect size.**
+  4)  These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
+Nevertheless, increased connectance may contribute to lower dynamical stability, and so it would be interesting to compare the dynamical stability of observed and predicted food webs, as well as the topological stability that we have focused on.
+
 keywords:
@@
 
-Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity, and can lead to food web collapse [@ullah2018].
+Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity, and can lead to food web collapse [@ullah2018].
 Primary extinctions in a food web can give rise to further secondary extinctions in a food web which can result in collapse of the food web (reference).
@@
 In Gupta et al.
-(2022) we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) by fitting it to empirical data using approximate Bayesian computation, and the goodness of fit of the ADBM was measured using the true skill statistics which takes into account the presence of links as well as the absence of links.
-(ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.) A key finding of Gupta et al.
+(2022) we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) by fitting it to empirical data using approximate Bayesian computation.
+The goodness of fit of the ADBM was measured using the true skill statistic, which takes into account the presence of links as well as the absence of links.
+The ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.
+A key finding of Gupta et al.
 (2022) was that the predicted food web connectance was consistently higher as compared to the observed connectance.
@@
 In that work there was no attempt to estimate the importance of these findings on computing the robustness of these food webs to species extinctions.
+**OP: here mention the other study (not ours) that also found this result--that predicted food webs had higher connectance than the observed ones they modelled.
 
@@
 
-The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency foraging model [@macarthur1966].
+The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966].
 The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
-The foraging variables in the model: energy content of the resources, handling times of the prey, space clearance rate and prey densities are allometrically scaled to the body sizes of the species.
+The foraging variables in the model are: energy content of prey, handling times of the predator on prey, space clearance rate of predator on prey, and prey densities.
+All are derived from the body sizes of the species via allometries.
 
@@
 
+## **OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution.
+
 ## Primary and secondary extinctions
@@
 The most-connected and least-connected criteria are based on the degree (i.e.
-total number of links to resource and links from consumer for each species) of species.
-Given a primary removal if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are dropped from the web and were recorded as a secondary extinction.
-Then the next appropriate species are removed determining the most- and least-connected species based on the web remaining after all prior primary removals and secondary extinctions had occurred.
+total number of links to resources and from consumers) of species.
+Given a primary removal if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
+Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
+One no more secondary extinctions occured, then another primary extinctions was made, of the next appropriate species.
 This process was carried out until all species were extinct from the web.
@@
 
-Robustness (R) of food web was quantified as the proportion of species subjected to primary removals that resulted in a total loss (i.e.
+Robustness (R) of food web was quantified as the proportion of species subjected to primary removals that resulted in a loss (i.e.
 primary removals plus secondary extinctions) of some specified proportion of the species.
 In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, that result in at least 50 per cent of total species loss [@dunne2002network; @dunne2004; @dunneCascadingExtinctionsCommunity2009].
-Therefore, there is no secondary extinction in a maximally robust community ($R_{50} = 0.50$), whereas in a minimally robust community ($R_{50} = 1/S$) there is extensive secondary extinctions (i.e.
+Therefore, if primary extinctions never cause any secondary extinctions, the food web is maximally robust and ($R_{50} = 0.50$).
+Whereas in a minimally robust community ($R_{50} = 1/S$), since the first primary extinction causes as cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
 at least $S/2 - 1$).
@@
 # Results
-
-We first present the cumulative secondary extinctions in the food webs for three different extinction scenarios.
-We also computed the robustness metric for the food webs where the robustness metric quantifies the number of species extinctions required to have at least 50% of total number of species extinctions in a food web.
 
@@
 \ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show the secondary extinction curves of ADBM predicted food webs and observed food webs for 12 different food webs under three different extinction scenarios.
-In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs.
+In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs **OP: this is not so clear to me.
+State how many cases?
+It seems there are many cases where secondary extinctions are more numerous in the observed food web: blue line above the red.**.
 
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the most connected species for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs.
 S denotes the number of species in a food web.
@@
 Except Broadstone Stream (taxonomic aggregation), Broadstone Stream (size aggregation) and Tuesday Lake food webs (Fig.
-\ref{fig:fig_r2} (b, c and k)), the mean cumulative secondary extinction curves for all the other food webs predicted by the ADBM were always lower than that of the observed food webs in the random extinction scenario.
+\ref{fig:fig_r2} (b, c and k)), the **mean cumulative secondary extinction curves** **OP: must be explained somewhere how/why this is a mean** for all the other food webs predicted by the ADBM were always lower than that of the observed food webs in the random extinction scenario.
 The shape of the cumulative secondary extinctions curves varied across the food webs.
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary removals of random species for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs.
 S denotes the number of species in a food web.
@@
 \ref{fig:fig_r3}) compared to the most connected extinction and random extinction scenarios.
-In most of the food webs, there was a lot of overlap between the extinction curves of the ADBM predicted foof webs and the observed food webs.
+In most of the food webs, there was a lot of overlap between the extinction curves of the ADBM predicted food webs and the observed food webs.
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the least connected species for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary **removals of the least connected species** for 12 food webs.
 S denotes the number of species in a food web.
@@
 
+**OP: write text describing the effect sizes, e.g. how big is the difference between observed and ADBM webs.**
+
 ## Show and describe the following:
@@
 I suggest to focus on the relationship between (difference in robustness between observed and predicted connectance) and (difference in robustness between the observed and predicted food web).
+**OP: I miss text describing this relationship.** **OP: Allow the panels in the figure to have different y-axis scales.**
 
+**OP: This paragraph should go in the previous section**.
 The ADBM predicted food webs were more robust than the observed food web with some exceptions (Fig.
@@
 The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs, and the shape of the robustness extinction curves varies between food webs.
+
 The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios.
@@
 This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a high connectance has on average more number of trophic links as compared to the food webs with low connectance.
+**OP: should here cite figure 4.**
 
@@
 An important question to ask here is how reliable are these results.
-We suspect that this is because the model and the observed data are wrong to some extent.
+We suspect that both the model and the observed data are wrong to some extent.
 We expect that some of the links that do in reality occur are not present in the observed datasets, which is quite possible because of low sampling effort or rare prey-predator interactions even when there is intensive sampling.

### 2022-03-21 manuscript/ms_C3.Rmd
minor

--- 2022-02-28 manuscript/ms_C3.Rmd
@@
 
-  1)  Undersampling of species in a food web can lead to missing trophic interactions in the food web.
-This can be compensated by using food web models such as allometric diet breadth model (ADBM) to predict those missing links.
-At the same time, these models might predict links which are probably not true i.e.
+  1)  Undersampling of species in a food web can lead to missing trophic interactions in the food web which could be compensated by using food web models such as allometric diet breadth model (ADBM) to predict those missing links.
+However, these models might predict links which are probably not true i.e.
 false positives.
 So, it is cruicial to understand how this affects the stability of predicted food webs when compared with the observed food webs.
-  2)  In our study, we compare the number of secondary extinctions when there is a primary extinction of species in food webs predicted by the ADBM to that in the observed food webs, and compute the robustness across 12 different food webs from a wide variety of ecosystems.
+  2)  In our study, we compare the number of secondary extinctions resulting from the  primary extinction of species in food webs predicted by the ADBM to that in the observed food webs, and compute the robustness across 12 different food webs from a wide variety of ecosystems.
   3)  We found that the ADBM predicted food webs were more robust than the observed food webs, and this can be attributed to connectance of the ADBM predicted food webs being higher than that of the observed food webs.

### 2022-07-06 inst/main/justincase/extinct_seq_issue.Rmd

---
title: "Duplicate extinction"
author: "Anubhav Gupta"
date: "11/22/2021"
output: pdf_document
---
```{r warning = FALSE, message = FALSE}

library(NetworkExtinction)
library(network)

data("net")
ch_data <- net

net_sim <- SimulateExtinctions(Network = net, Order = c(3, 4, 7, 10, 1, 5, 8, 2, 6, 9), Method = "Ordered")

net_sim

plot.network(x = ch_data, label = network.vertex.names(ch_data))
```

It can be seen that the extinction of node 4 and node 3 results in secondary extinction of node 7. However, the function SimulateExtinctions does not check if node 7 is already extinct or not when it is asked for primary extinction of node 7 as can be seen from the result above. In the above case, node 7 is extinct twice: once in secondary extinction and next time in primary extinction. This eventually results in a total extinction of 13 nodes, however there are only 10 nodes in the network.

```{r}
sessionInfo()
```

### 2022-07-06 manuscript/ms_C3.Rmd

--- 2022-03-21 manuscript/ms_C3.Rmd
@@
 Undersampling can be compensated for by using food web models such as allometric diet breadth model (ADBM) to predict missing links.
-At the same time, models might predict links which cannot occur, i.e., false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of number of secondary extinctions occuring due to a primary extinction) increases with connectance (the number of tophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
+Simultaneously, models might predict links which cannot occur, i.e., false positives.
+  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of trophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
 Thus we expect that predicted food webs are more robust than observed ones.
-This expectation has never, to our knowledge, been tested, nor has the quantative size of any effect.
-  2) We fill this gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though can also make false positives.
+This expectation has never, to our knowledge, been tested, nor has the effect size been quantified.
+  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though can also make false positives.
 We did this for 12 different food webs from a wide variety of ecosystems.
-  3)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
-**OP: Here something about the effect size.**
-  4)  These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
+  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
+On average, for every X unit of increase in connectance, we found the food webs to be robust by YY units for random extinction scenario.**OP: Here something about the effect size.**
+  5)  These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
 Nevertheless, increased connectance may contribute to lower dynamical stability, and so it would be interesting to compare the dynamical stability of observed and predicted food webs, as well as the topological stability that we have focused on.
@@
 
-# Alternate titles
-
-* Robustness of ADBM predicted food webs
-
 # Introduction
@@
 Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity, and can lead to food web collapse [@ullah2018].
-Primary extinctions in a food web can give rise to further secondary extinctions in a food web which can result in collapse of the food web (reference).
-The rate at which a primary extinctions can lead to secondary extinctions is dependent on the structure and complexity of that food web (reference).
-Understanding this can help to implement conservation efforts tailored to a given food web structure (reference).
+This collapse in the food web is due to cascades of secondary extinctions in a food web because of primary loss of species, for example due to habitat destruction.
+The rate of collapse of these predicted food webs is dependent on the structure and complexity of those food webs [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+Therefore, research focused on cascading secondary extinctions also known as 'community viability analysis' have been performed extensively in the past few decades [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
 
@@
 
-A key assumption of this work is that food webs are very well sampled, so that all links that in reality can occur are represented.
-Yet it is known that not all food webs are very well sampled, and then do not represent all of the feeding links that occur (reference).
-One solution to this problem is to use a food web model to predict which are the missing links, and to then measure the robustness of the predicted food web.
-This solution is not fool proof, however, as it is likely that the food web model is not perfect, and so may still miss some links, and also may predict some links that could not, in fact occur.
-
-## In previous work...
-
-In Gupta et al.
-(2022) we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) by fitting it to empirical data using approximate Bayesian computation.
-The goodness of fit of the ADBM was measured using the true skill statistic, which takes into account the presence of links as well as the absence of links.
-The ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.
-A key finding of Gupta et al.
-(2022) was that the predicted food web connectance was consistently higher as compared to the observed connectance.
-This means that there were some trophic links (false positives) predicted by the ADBM which are not observed in the empirical food web data.
-Simultaneously there were some trophic links (false negatives) that were not predicted by the ADBM but were observed in the empirical food web.
-In that work there was no attempt to estimate the importance of these findings on computing the robustness of these food webs to species extinctions.
-**OP: here mention the other study (not ours) that also found this result--that predicted food webs had higher connectance than the observed ones they modelled.
+A key assumption of the observed food webs is that the food webs are very well sampled i.e.
+all the links that in reality can occur are represented.
+However, it is known that not all food webs are very well sampled and then do not represent all of the feeding links that occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
+Some rare trophic links require more sampling effort as compared to others whereas some trophic links remain unobserved because of linkage constraints irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
+One solution to this problem is to use a food web model such as Allometric Diet Breadth Model (ADBM) to predict which are the missing links, and to then measure the robustness of the predicted food web.
+ADBM is a mechanistic model constructed using rules based on body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which at the same time are perhaps not observed because those interactions are rare.
+However, this solution is not infallible, as it is likely that the food web model might still miss some links, and also may predict some links that could not, in fact occur.
 
 ## What we do in this study
+
+In our study, we investigate the robustness of the ADBM predicted food webs as compared to the observed food webs and quantify the effect of overestimation of connectance on the robustness of these predicted food webs.
+We do this by simulating primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
+We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
 
@@
 
-## **OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution.
+## \*\*OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution.
 
@@
 \ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show the secondary extinction curves of ADBM predicted food webs and observed food webs for 12 different food webs under three different extinction scenarios.
+We found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for nine, nine and seven food webs.
+
 In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs **OP: this is not so clear to me.

### 2022-07-06 manuscript/ms_C3.tex

\documentclass{article}

\usepackage{arxiv}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{graphicx}

\title{Missing links, forbidden links, and the topological robustness of
food webs}

\author{
    Anubhav Gupta
    \thanks{Corresponding author}
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:anubhav.gupta@ieu.uzh.ch}{\nolinkurl{anubhav.gupta@ieu.uzh.ch}}} \\
   \And
    Owen L. Petchey
   \\
    Department of Evolutionary Biology and Environmental Studies \\
    University of Zurich \\
  8057 Zurich, Switzerland \\
  \texttt{\href{mailto:owen.petchey@ieu.uzh.ch}{\nolinkurl{owen.petchey@ieu.uzh.ch}}} \\
  }

% tightlist command for lists without linebreak
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Pandoc citation processing
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{lineno}
\linenumbers
\usepackage {amsmath}
\setlength\parindent{24pt}
\usepackage{setspace}\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\begin{document}
\maketitle

\begin{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Undersampling can lead to missing trophic interactions in recorded
  food webs, with potential consequences for the perceived functioning
  and stability of the food web. Undersampling can be compensated for by
  using food web models such as allometric diet breadth model (ADBM) to
  predict missing links. Simultaneously, models might predict links
  which cannot occur, i.e., false positives.
\item
  Previous research shows that (i) food web robustness (the inverse of
  the number of secondary extinctions occuring due to primary
  extinctions) increases with connectance (the number of trophic links
  divided by the number of possible links), and (ii) that predicted food
  webs usually have greater connectance than observed ones. Thus we
  expect that predicted food webs are more robust than observed ones.
  This expectation has never, to our knowledge, been tested, nor has the
  effect size been quantified.
\item
  We fill this research gap by comparing the robustness of observed food
  webs to the robustness of food webs predicted by a model (the ADBM)
  that can account for missing links, though can also make false
  positives. We did this for 12 different food webs from a wide variety
  of ecosystems.
\item
  We found, as expected, that the predicted food webs were more robust
  than the observed food webs, and this can be attributed to the higher
  connectance of the predicted food webs. On average, for every X unit
  of increase in connectance, we found the food webs to be robust by YY
  units for random extinction scenario.\textbf{OP: Here something about
  the effect size.}
\item
  These results show that undersampling can lead to large underestimates
  of food web robustness that can be compensated for by filling in
  missing links with food web models. Nevertheless, increased
  connectance may contribute to lower dynamical stability, and so it
  would be interesting to compare the dynamical stability of observed
  and predicted food webs, as well as the topological stability that we
  have focused on.
\end{enumerate}
\end{abstract}

\keywords{
    connectance
   \and
    ABC
   \and
    ADBM
   \and
    food web
   \and
    extinction
   \and
    uncertainty
  }

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{background-on-anthropogenic-changes-and-its-impact-on-food-web}{%
\subsection{Background on anthropogenic changes and its impact on food
web}\label{background-on-anthropogenic-changes-and-its-impact-on-food-web}}

Anthropogenic changes such as climate change and habitat destruction are
a threat to biodiversity, and can lead to food web collapse (Ullah et
al. 2018). This collapse in the food web is due to cascades of secondary
extinctions in a food web because of primary loss of species, for
example due to habitat destruction. The rate of collapse of these
predicted food webs is dependent on the structure and complexity of
those food webs (Jennifer A. Dunne, Williams, and Martinez 2002b;
Jennifer A. Dunne and Williams 2009). Therefore, research focused on
cascading secondary extinctions also known as `community viability
analysis' have been performed extensively in the past few decades
(Jennifer A. Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and
Williams 2009; Berg et al. 2011; Ebenman, Law, and Borrvall 2004;
Ebenman and Jonsson 2005).

\hypertarget{briefly-explain-work-done-by-jennifer-dunne-on-food-web-op-robustness-to-primary-extinctions-and-also-what-has-been-done-since-particularly-concerning-the-importance-of-connectance}{%
\subsection{Briefly explain work done by Jennifer Dunne on food web
{[}OP{]} robustness to primary extinctions, and also what has been done
since, particularly concerning the importance of
connectance}\label{briefly-explain-work-done-by-jennifer-dunne-on-food-web-op-robustness-to-primary-extinctions-and-also-what-has-been-done-since-particularly-concerning-the-importance-of-connectance}}

Simulation of primary species loss has been conducted in observed food
webs and model food webs from terrestrial and aquatic ecosystems where
robustness was measured in terms of secondary extinctions (Jennifer A.
Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
2009). These studies showed that the robustness \textbf{of the food
webs} increases with food web connectance. Also, the removal of the most
connected species cause considerably more secondary extinctions than
random removals of species (Jennifer A. Dunne, Williams, and Martinez
2002a; Sol'e and Montoya 2001). These studies provide an alternate
solution to investigate the impact of primary extinctions in a food web
when canonical experiments in natural ecosystems are not possible.

Along with robustness based on topological structure of a food web,
robustness based on the food web dynamics has been studied as well
(reference). Topological approaches only require the food web structure
whereas dynamical approaches also require the temporal dynamics of the
food web along with the food web structure. For example: Williams (2008)
combined models of network structure with models of bionergetic dynamics
to study the role of food web topology and nonlinear dynamics on species
coexistence in complex ecological networks.

{[}OP{]} Explain (either here or in the methods) difference between
topological and abundance (given by dynamics) based criteria for a
secondary extinction occurring.

\hypertarget{op-state-what-is-the-problem}{%
\subsection{{[}OP{]} State what is the
problem\ldots{}}\label{op-state-what-is-the-problem}}

A key assumption of the observed food webs is that the food webs are
very well sampled i.e.~all the links that in reality can occur are
represented. However, it is known that not all food webs are very well
sampled and then do not represent all of the feeding links that occur
(Caron et al. 2022; Patonai and Jord'an 2017; Jordano 2016). Some rare
trophic links require more sampling effort as compared to others whereas
some trophic links remain unobserved because of linkage constraints
irrespective of sufficient sampling effort (Jordano 2016). One solution
to this problem is to use a food web model such as Allometric Diet
Breadth Model (ADBM) to predict which are the missing links, and to then
measure the robustness of the predicted food web. ADBM is a mechanistic
model constructed using rules based on body sizes of prey and predator
where trophic interactions satisfying those rules would be predicted by
the model which at the same time are perhaps not observed because those
interactions are rare. However, this solution is not infallible, as it
is likely that the food web model might still miss some links, and also
may predict some links that could not, in fact occur.

\hypertarget{what-we-do-in-this-study}{%
\subsection{What we do in this study}\label{what-we-do-in-this-study}}

In our study, we investigate the robustness of the ADBM predicted food
webs as compared to the observed food webs and quantify the effect of
overestimation of connectance on the robustness of these predicted food
webs. We do this by simulating primary species loss in 12 food webs
predicted from the ADBM to quantify the secondary loss of extinctions.
We use three different approaches of species removal: (i) most connected
species, (ii) random species and (iii) least connected species to
understand if the outcome varies among these approaches.

It is crucial to investigate the implication of this consistent
overestimation of connectance in the robustness of predicted food webs.
We expect that the ADBM predicted food webs would be more robust as
compared to the observed food webs, and for the greater robustness to be
related to the amount by which the ADBM overestimates connectance. In
this study, we simulate primary species loss in 12 food webs predicted
from the ADBM to quantify the secondary loss of extinctions. We use
three different approaches of species removal: (i) most connected
species, (ii) random species and (iii) least connected species to
understand if the outcome varies among these approaches.

\hypertarget{materials-and-methods}{%
\section{Materials and methods}\label{materials-and-methods}}

{[}OP{]} \#\# Provide overview of the methods

In the upcoming sections, we present a detailed account of the
implementation of simulation of primary extinctions for three different
scenarios on 12 food webs predicted by the ADBM from wide variety of
ecosystems, and compute the resultant secondary extinctions. We then
compute a robustness metric to quantify the robustness of those
predicted food webs.

\hypertarget{allometric-diet-breadth-model-adbm}{%
\subsection{Allometric Diet Breadth Model
(ADBM)}\label{allometric-diet-breadth-model-adbm}}

The allometric diet breadth model (ADBM) is based on optimal foraging
theory, specifically the contingency model (MacArthur and Pianka 1966).
The ADBM predicts the set of prey species a consumer should feed upon to
maximise its rate of energy intake (Petchey et al. 2008). The foraging
variables in the model are: energy content of prey, handling times of
the predator on prey, space clearance rate of predator on prey, and prey
densities. All are derived from the body sizes of the species via
allometries.

\hypertarget{food-web-data}{%
\subsection{Food web data}\label{food-web-data}}

The observed food webs that we fit the ADBM to belong to marine,
freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). The
observed connectance of these food webs is from 0.03 to 0.24 and there
are 29 to 239 species. The food webs contain primary producers,
herbivores, carnivores, parasites, and parasitoids. They also contain
various types of feeding interactions, including predation, herbivory,
bacterivory, parasitism, pathogenic, and parasitoid.

\newgeometry{margin=1cm}
\begin{landscape}\begin{table}

\caption{\label{tab:unnamed-chunk-1}\label{fig:tab_1}Information about the food webs predicted using the ADBM.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{7}{9}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{8em}|l|l|l|l|>{}p{8em}|>{}p{8em}|>{}p{8em}}
\hline
Common food web name (Original Publication) & Predation matrix source & General ecosystem & Number of species & Observed connectance & 95\% prediction interval of predicted connectance  (Gupta et al. (2022))\\
\hline
Benguela Pelagic (Yodzis 1998) & Brose et al. (2005) & Marine & 30 & 0.21 & 0.26 - 0.59\\
\hline
Broadstone Stream (taxonomic aggregation) (Woodward and Hildrew 2001; Woodward
et al. 2005) & Brose et al. (2005) & Freshwater & 29 & 0.19 & 0.18 - 0.72\\
\hline
Broom (Memmott et al. 2000) & Brose et al. (2005) & Terrestrial & 60 & 0.03 & 0.12 - 0.89\\
\hline
Capinteria (Lafferty et al. 2006) & Hechinger et al. (2011) & Marine (Salt Marsh) & 88 & 0.08 & 0.11 - 0.80\\
\hline
Caricaie Lakes (Cattin et al. 2004) & Brose et al. (2005) & Freshwater & 158 & 0.05 & 0.11 - 0.81\\
\hline
Grasslands (Dawah et al. 1995) & Brose et al. (2005) & Terrestrial & 65 & 0.03 & 0.03 - 0.44\\
\hline
Mill Stream (Ledger, Edwards, Woodward unpublished) & Brose et al. (2005) & Freshwater & 80 & 0.06 & 0.08 - 0.60\\
\hline
Skipwith Pond (Warren 1989) & Brose et al. (2005) & Freshwater & 71 & 0.07 & 0.17 - 0.90\\
\hline
Small Reef (Opitz 1996 Table 8.6.2) & Alyssa R. Cirtwill and Anna Eklöf (2018) & Marine (Reef) & 239 & 0.06 & 0.07 - 0.66\\
\hline
Tuesday Lake (Jonsson et al. 2005) & Brose et al. (2005) & Freshwater & 73 & 0.08 & 0.09 - 0.57\\
\hline
Ythan (Emmerson and Raffaelli 2004) & Alyssa R. Cirtwill and Anna Eklöf (2018) & Marine (Estuarine) & 85 & 0.04 & 0.13 - 0.84\\
\hline
Broadstone Stream (size aggregation) (Woodward
et al. 2010) & Guy Woodward. (2021) & Freshwater & 29 & 0.24 & 0.25 - 0.47\\
\hline
\end{tabular}}
\end{table}
\end{landscape}
\restoregeometry

\hypertarget{op-need-a-section-on-how-the-food-web-model-was-fit-to-the-data.-also-should-state-how-we-deal-with-use-the-uncertainty-contained-in-the-posterior-joint-distribution.}{%
\subsection{**OP: need a section on how the food web model was fit to
the data. Also should state how we deal with / use the uncertainty
contained in the posterior joint
distribution.}\label{op-need-a-section-on-how-the-food-web-model-was-fit-to-the-data.-also-should-state-how-we-deal-with-use-the-uncertainty-contained-in-the-posterior-joint-distribution.}}

\hypertarget{primary-and-secondary-extinctions}{%
\subsection{Primary and secondary
extinctions}\label{primary-and-secondary-extinctions}}

We implemented the primary species removal method from Jennifer A. Dunne
and Williams (2009) by sequentially removing species using one of three
criteria: removal of (i) the most-connected species, (ii) the
least-connected species and (iii) randomly chosen species. The
most-connected and least-connected criteria are based on the degree
(i.e.~total number of links to resources and from consumers) of species.
Given a primary removal if any remaining species lost all of their
resource species, or any cannibalistic species lost all of their
resource species except the cannibalistic links, they are removed from
the web and a secondary extinction was recorded. Secondary extinctions
may cause further secondary extinctions, which were also checked for and
recorded. One no more secondary extinctions occured, then another
primary extinctions was made, of the next appropriate species. This
process was carried out until all species were extinct from the web.

\hypertarget{calculating-robustness}{%
\subsection{Calculating robustness}\label{calculating-robustness}}

Robustness (R) of food web was quantified as the proportion of species
subjected to primary removals that resulted in a loss (i.e.~primary
removals plus secondary extinctions) of some specified proportion of the
species. In our study, we use \(R_{50}\), the number of primary
extinctions divided by the total number of species, that result in at
least 50 per cent of total species loss (Jennifer A. Dunne, Williams,
and Martinez 2002b; J. Dunne, Williams, and Martinez 2004; Jennifer A.
Dunne and Williams 2009). Therefore, if primary extinctions never cause
any secondary extinctions, the food web is maximally robust and
(\(R_{50} = 0.50\)). Whereas in a minimally robust community
(\(R_{50} = 1/S\)), since the first primary extinction causes as cascade
of secondary extinctions of at least nearly half of the species in the
food web (i.e.~at least \(S/2 - 1\)).

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{show-and-describe-the-secondary-extinction-curves}{%
\subsection{Show and describe the secondary extinction
curves}\label{show-and-describe-the-secondary-extinction-curves}}

In Fig. \ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show
the secondary extinction curves of ADBM predicted food webs and observed
food webs for 12 different food webs under three different extinction
scenarios. We found that the cumulative secondary extinction was higher
for the ADBM predicted food webs as compared to the observed food webs
for nine, nine and seven food webs.

In general, irrespective of the extinction scenarios, we found that the
cumulative secondary extinction was higher for the ADBM predicted food
webs as compared to the observed food webs for most of the food webs
\textbf{OP: this is not so clear to me. State how many cases? It seems
there are many cases where secondary extinctions are more numerous in
the observed food web: blue line above the red.}.

In the most connected extinction scenario, the cumulative secondary
extinction curve for the observed food webs rose quickly as compared to
the ADBM predicted food webs, and then reach saturation after a certain
number of primary removal of species. In some of the food webs (Fig.
\ref{fig:fig_r1} (f, g, h, i, j, k)), there were intersection between
the cumulative secondary extinction curves of ADBM predicted food webs
and that of the observed food webs. In case of the Broadstone Stream
(taxonomic aggregation) food web and the Tuesday Lake food web (Fig.
\ref{fig:fig_r1} (b and k)), the secondary extinction curves for the
ADBM food webs were higher than the observed food webs, whereas in case
of the Skipwith Pond food web (Fig. \ref{fig:fig_r1} (i)), there were no
secondary extinctions for any given number of primary removal of
species.

\begin{figure}

{\centering \includegraphics[width=400px]{../results/plot_mostconnected}

}

\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-2}
\end{figure}

Except Broadstone Stream (taxonomic aggregation), Broadstone Stream
(size aggregation) and Tuesday Lake food webs (Fig. \ref{fig:fig_r2} (b,
c and k)), the \textbf{mean cumulative secondary extinction curves}
\textbf{OP: must be explained somewhere how/why this is a mean} for all
the other food webs predicted by the ADBM were always lower than that of
the observed food webs in the random extinction scenario. The shape of
the cumulative secondary extinctions curves varied across the food webs.

\begin{figure}

{\centering \includegraphics[width=400px]{../results/plot_random}

}

\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-3}
\end{figure}

Compared to the most connected and random extinction scenarios, the
cumulative extinction curves in the least connected extinction scenario
had very low values and were flat for most of the food webs (Fig.
\ref{fig:fig_r3}) compared to the most connected extinction and random
extinction scenarios. In most of the food webs, there was a lot of
overlap between the extinction curves of the ADBM predicted food webs
and the observed food webs.

\begin{figure}

{\centering \includegraphics[width=400px]{../results/plot_leastconnected}

}

\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary **removals of the least connected species** for 12 food webs. S denotes the number of species in a food web. The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-4}
\end{figure}

\textbf{OP: write text describing the effect sizes, e.g.~how big is the
difference between observed and ADBM webs.}

\hypertarget{show-and-describe-the-following}{%
\subsection{Show and describe the
following:}\label{show-and-describe-the-following}}

I suggest to focus on the relationship between (difference in robustness
between observed and predicted connectance) and (difference in
robustness between the observed and predicted food web). \textbf{OP: I
miss text describing this relationship.} \textbf{OP: Allow the panels in
the figure to have different y-axis scales.}

\textbf{OP: This paragraph should go in the previous section}. The ADBM
predicted food webs were more robust than the observed food web with
some exceptions (Fig. \ref{fig:fig_r4}). The food webs were more robust
to least connected and random extinction scenarios than the primary
deletion of the most connected species. The difference in the robustness
values between the ADBM predicted food webs and observed food webs was
higher in the most connected extinction scenario as compared to the
least connected extinction and random extinction scenarios.

\begin{figure}

{\centering \includegraphics[width=400px]{../results/plot_robustness_all_uncertainty}

}

\caption{\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems. Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).}\label{fig:unnamed-chunk-5}
\end{figure}

AG: I will also update the robustness plot for random extinction (Fig. 4
(b)) once the simulation is completed. The one shown here is only for
few simulations and as a placeholder. It takes more time to compute.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The primary removal of species revealed that the ADBM predicted food
webs are more robust than the observed food webs, and the shape of the
robustness extinction curves varies between food webs.

The food webs are least robust to primary extinction of the most
connected species scenario compared to that of least connected and
random extinction scenarios. A future development would be to understand
the stability of the dynamics of the ADBM predicted food webs and
compare it with our study.

\ldots{}

\hypertarget{what-does-overestimation-of-connectance-imply-in-terms-of-stability}{%
\subsection{What does overestimation of connectance imply in terms of
stability?}\label{what-does-overestimation-of-connectance-imply-in-terms-of-stability}}

For most of the food webs, the primary removals of species resulted in a
higher secondary extinction in the ADBM predicted food webs than that of
the observed food webs (Fig. \ref{fig:fig_r1}, \ref{fig:fig_r2} and
\ref{fig:fig_r3}). This can be attributed to the higher connectance of
the ADBM predicted food webs as compared to that of the observed food
webs because a species in a food web with a high connectance has on
average more number of trophic links as compared to the food webs with
low connectance. \textbf{OP: should here cite figure 4.}

It would be intriguing to know if this difference in connectance has a
similar influence in the dynamical stability of the food webs as well.
Hence, a future prospect could be to use a dynamical model (for example:
bionergetic food web model (Brose, Williams, and Martinez 2006)) to
model the temporal dynamics of the ADBM predicted food webs. It would be
interesting to know the temporal stability of these ADBM predicted food
webs compared to the observed food webs because it has been known that
food webs with increasing connectance stability diminishes (May 1972).

\ldots{}

Include here the possibility that the increased connectance would
influence dynamical stability, and state if and why this may increase or
decrease stability.

\hypertarget{explain-that-the-adbm-can-only-predicts-contiguous-diets-op-and-the-implications-of-this}{%
\subsection{Explain that the ADBM can only predicts contiguous diets
{[}OP{]} and the implications of
this}\label{explain-that-the-adbm-can-only-predicts-contiguous-diets-op-and-the-implications-of-this}}

Using only body size as a trait, the ADBM can only predict diets that
are contiguous with respect to the size of the prey. I.e. it cannot
predict that a predator will consume prey of size 1 and 3, and not
consume prey of size 2. Also, it is important to note that the observed
diets were not contiguous when prey are ordered by their size, and this
is due to some ecological differences in how predator group choose their
prey (Caron et al. 2022). So, the parameterisation process lead to a
greater number of predicted links than observed.

This higher connectance in the ADBM predicted food webs has lead to a
higher robustness of the ADBM predicted food webs. An important question
to ask here is how reliable are these results. We suspect that both the
model and the observed data are wrong to some extent. We expect that
some of the links that do in reality occur are not present in the
observed datasets, which is quite possible because of low sampling
effort or rare prey-predator interactions even when there is intensive
sampling. This would mean that the false positives may actually be a
correctly predicted link.

We suspect that the model is also predicting links which actually do not
occur. This is because the current ADBM model only takes body size
trait, and therefore only predicts contiguous diet. That would mean any
interaction that is not possible because of some other traits not
correlated with the body size would still be predicted by the model. For
example, a species might have a defensive trait that could result in the
predator species not predating on that species at all.

AG: (Caution) Some of the texts might be very similar to or same as in
C1 MS. With multiple iterations of the current ms, the current text
would be altered. Also, the current ms would be checked using a
plagiarism software before submission.

\ldots{}

\hypertarget{compare-the-results-from-our-study-with-results-from-other-food-web-models-jennifer-a.-dunne-and-williams-2009}{%
\subsection{Compare the results from our study with results from other
food web models (Jennifer A. Dunne and Williams
(2009))}\label{compare-the-results-from-our-study-with-results-from-other-food-web-models-jennifer-a.-dunne-and-williams-2009}}

The findings from our study is similar to what had been documented for
other food web models (Jennifer A. Dunne and Williams 2009), in terms of
increase in the robustness when the connectance of the food web is
increased. A future study could be to understand the robustness of other
food web models (Gravel et al. 2013) and compare it with our study. We
expect similar results.

{[}OP{]} Including if and why we expect our findings to be replicated
with those other models. Include some of Gravel and Poissot's models

\ldots{}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bergUsingSensitivityAnalysis2011}{}}%
Berg, Sofia, Maria Christianou, Tomas Jonsson, and Bo Ebenman. 2011.
{``Using Sensitivity Analysis to Identify Keystone Species and Keystone
Links in Size-Based Food Webs.''} \emph{Oikos} 120 (4): 510--19.
\url{https://doi.org/10.1111/j.1600-0706.2010.18864.x}.

\leavevmode\vadjust pre{\hypertarget{ref-broseAllometricScalingEnhances2006}{}}%
Brose, Ulrich, Richard J. Williams, and Neo D. Martinez. 2006.
{``Allometric Scaling Enhances Stability in Complex Food Webs.''}
\emph{Ecology Letters} 9 (11): 1228--36.
\url{https://doi.org/10.1111/j.1461-0248.2006.00978.x}.

\leavevmode\vadjust pre{\hypertarget{ref-caronAddressingEltonianShortfall}{}}%
Caron, Dominique, Luigi Maiorano, Wilfried Thuiller, and Laura J.
Pollock. 2022. {``Addressing the {Eltonian} Shortfall with Trait-Based
Interaction Models.''} \emph{Ecology Letters} n/a (n/a).
\url{https://doi.org/10.1111/ele.13966}.

\leavevmode\vadjust pre{\hypertarget{ref-dunne2004}{}}%
Dunne, Ja, Rj Williams, and Nd Martinez. 2004. {``Network Structure and
Robustness of Marine Food Webs.''} \emph{Marine Ecology Progress Series}
273: 291--302. \url{https://doi.org/10.3354/meps273291}.

\leavevmode\vadjust pre{\hypertarget{ref-dunneCascadingExtinctionsCommunity2009}{}}%
Dunne, Jennifer A., and Richard J. Williams. 2009. {``Cascading
Extinctions and Community Collapse in Model Food Webs.''}
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences} 364 (1524): 1711--23.
\url{https://doi.org/10.1098/rstb.2008.0219}.

\leavevmode\vadjust pre{\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}}%
Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002a.
{``Network Structure and Biodiversity Loss in Food Webs: Robustness
Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.
\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}.

\leavevmode\vadjust pre{\hypertarget{ref-dunne2002network}{}}%
Dunne, Jennifer A, Richard J Williams, and Neo D Martinez. 2002b.
{``Network Structure and Biodiversity Loss in Food Webs: Robustness
Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.

\leavevmode\vadjust pre{\hypertarget{ref-ebenmanUsingCommunityViability2005}{}}%
Ebenman, Bo, and Tomas Jonsson. 2005. {``Using Community Viability
Analysis to Identify Fragile Systems and Keystone Species.''}
\emph{Trends in Ecology \& Evolution} 20 (10): 568--75.
\url{https://doi.org/10.1016/j.tree.2005.06.011}.

\leavevmode\vadjust pre{\hypertarget{ref-ebenmanCOMMUNITYVIABILITYANALYSIS2004}{}}%
Ebenman, Bo, Richard Law, and Charlotte Borrvall. 2004. {``{COMMUNITY
VIABILITY ANALYSIS}: {THE RESPONSE OF ECOLOGICAL COMMUNITIES TO SPECIES
LOSS}.''} \emph{Ecology} 85 (9): 2591--2600.
\url{https://doi.org/10.1890/03-8018}.

\leavevmode\vadjust pre{\hypertarget{ref-gravelInferringFoodWeb2013a}{}}%
Gravel, Dominique, Timoth'ee Poisot, Camille Albouy, Laure Velez, and
David Mouillot. 2013. {``Inferring Food Web Structure from
Predator--Prey Body Size Relationships.''} \emph{Methods in Ecology and
Evolution} 4 (11): 1083--90.
\url{https://doi.org/10.1111/2041-210X.12103}.

\leavevmode\vadjust pre{\hypertarget{ref-jordanoSamplingNetworksEcological2016}{}}%
Jordano, Pedro. 2016. {``Sampling Networks of Ecological
Interactions.''} \emph{Functional Ecology} 30 (12): 1883--93.
\url{https://doi.org/10.1111/1365-2435.12763}.

\leavevmode\vadjust pre{\hypertarget{ref-macarthur1966}{}}%
MacArthur, Robert H., and Eric R. Pianka. 1966. {``On Optimal Use of a
Patchy Environment.''} \emph{The American Naturalist} 100 (916): 603--9.
\url{https://www.jstor.org/stable/2459298}.

\leavevmode\vadjust pre{\hypertarget{ref-mayWillLargeComplex1972}{}}%
May, Robert M. 1972. {``Will a {Large Complex System} Be {Stable}?''}
\emph{Nature} 238 (5364): 413. \url{https://doi.org/10.1038/238413a0}.

\leavevmode\vadjust pre{\hypertarget{ref-patonaiAggregationIncompleteFood2017}{}}%
Patonai, Katalin, and Ferenc Jord'an. 2017. {``Aggregation of Incomplete
Food Web Data May Help to Suggest Sampling Strategies.''}
\emph{Ecological Modelling} 352 (May): 77--89.
\url{https://doi.org/10.1016/j.ecolmodel.2017.02.024}.

\leavevmode\vadjust pre{\hypertarget{ref-petchey2008}{}}%
Petchey, Owen L., A. P. Beckerman, J. O. Riede, and P. H. Warren. 2008.
{``Size, Foraging, and Food Web Structure.''} \emph{Proceedings of the
National Academy of Sciences} 105 (11): 4191--96.
\url{https://doi.org/10.1073/pnas.0710672105}.

\leavevmode\vadjust pre{\hypertarget{ref-soleComplexityFragilityEcological2001}{}}%
Sol'e, Ricard V., and M. Montoya. 2001. {``Complexity and Fragility in
Ecological Networks.''} \emph{Proceedings of the Royal Society of
London. Series B: Biological Sciences} 268 (1480): 2039--45.
\url{https://doi.org/10.1098/rspb.2001.1767}.

\leavevmode\vadjust pre{\hypertarget{ref-ullah2018}{}}%
Ullah, Hadayet, Ivan Nagelkerken, Silvan U. Goldenberg, and Damien A.
Fordham. 2018. {``Climate Change Could Drive Marine Food Web Collapse
Through Altered Trophic Flows and Cyanobacterial Proliferation.''}
Edited by Michel Loreau. \emph{PLOS Biology} 16 (1): e2003446.
\url{https://doi.org/10.1371/journal.pbio.2003446}.

\leavevmode\vadjust pre{\hypertarget{ref-williamsEffectsNetworkDynamical2008}{}}%
Williams, Richard J. 2008. {``Effects of Network and Dynamical Model
Structure on Species Persistence in Large Model Food Webs.''}
\emph{Theoretical Ecology} 1 (3): 141--51.
\url{https://doi.org/10.1007/s12080-008-0013-5}.

\end{CSLReferences}

\bibliographystyle{biblatex}
\bibliography{bibliography.bib}

\end{document}

### 2022-07-06 manuscript/ms_C3_OP.Rmd

--- 2022-03-21 manuscript/ms_C3.Rmd
@@
 ---
-title: Missing links, false positives, and the topological robustness of predicted food webs
+title: "Robustness of ADBM predicted food webs OR [OP] Missing links, false positives, and the topological robustness of predicted food webs."
 authors:
-- affiliation: University of Zurich
+- name: Anubhav Gupta
+  thanks: Corresponding author
   department: Department of Evolutionary Biology and Environmental Studies
+  affiliation: University of Zurich
+  location: 8057 Zurich, Switzerland
   email: anubhav.gupta@ieu.uzh.ch
+- name: Owen L. Petchey
+  department: Department of Evolutionary Biology and Environmental Studies
+  affiliation: University of Zurich
   location: 8057 Zurich, Switzerland
-  name: Anubhav Gupta
-  thanks: Corresponding author
-- affiliation: University of Zurich
-  department: Department of Evolutionary Biology and Environmental Studies
   email: owen.petchey@ieu.uzh.ch
-  location: 8057 Zurich, Switzerland
-  name: Owen L. Petchey
 geometry: margin=1in
-abstract: |
+output:
+  pdf_document:
+    number_sections: true
+  rticles::arxiv_article:
+    keep_tex: yes
 
-  1)  Undersampling of species in a food web can lead to missing trophic interactions in the food web which could be compensated by using food web models such as allometric diet breadth model (ADBM) to predict those missing links.
-However, these models might predict links which are probably not true i.e.
-false positives.
-So, it is cruicial to understand how this affects the stability of predicted food webs when compared with the observed food webs.
-  2)  In our study, we compare the number of secondary extinctions resulting from the  primary extinction of species in food webs predicted by the ADBM to that in the observed food webs, and compute the robustness across 12 different food webs from a wide variety of ecosystems.
-  3)  We found that the ADBM predicted food webs were more robust than the observed food webs, and this can be attributed to connectance of the ADBM predicted food webs being higher than that of the observed food webs.
-  4)  These results suggest that real food webs might be more robust as compared to the food webs constructed using observed data.
 keywords:
@@
 - \usepackage{setspace}\doublespacing
-# indent: true
 mainfont: Times New Roman
 bibliography: bibliography.bib
-biblio-style: biblatex
-output:
-  rticles::arxiv_article:
-    keep_tex: true
+abstract: |
+  Some text here.
 ---
-
-# Alternate titles
-
-* Robustness of ADBM predicted food webs
 
@@
 
-Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity, and can lead to food web collapse [@ullah2018].
-Primary extinctions in a food web can give rise to further secondary extinctions in a food web which can result in collapse of the food web (reference).
-The rate at which a primary extinctions can lead to secondary extinctions is dependent on the structure and complexity of that food web (reference).
-Understanding this can help to implement conservation efforts tailored to a given food web structure (reference).
+Anthropogenic changes such as climate change and habitat destruction is a threat to biodiversity, and can lead to food web collapse.
+Climate change can lead to the collapse of a food web [@ullah2018].
+Primary extinctions in a food web can give rise to further secondary extinctions in a food web resulting in collapse of the food web.
+The impact of this extinction is dependent on the complexity and structure of the food web (reference).
 
@@
 These studies showed that the robustness of the food webs increases with food web connectance.
-Also, the removal of the most connected species cause considerably more secondary extinctions than random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
-These studies provide an alternate solution to investigate the impact of primary extinctions in a food web when canonical experiments in natural ecosystems are not possible.
+When canonical experiments in natural ecosystems are not possible, this provides an alternate solution to investigate the impact of primary extinctions in a food web.
 
-Along with robustness based on topological structure of a food web, robustness based on the food web dynamics has been studied as well (reference).
-Topological approaches only require the food web structure whereas dynamical approaches also require the temporal dynamics of the food web along with the food web structure.
-For example: @williamsEffectsNetworkDynamical2008 combined models of network structure with models of bionergetic dynamics to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
+Connectance of a food web plays a key role in determining the robustness of the predicted food webs.
 
@@
 A key assumption of this work is that food webs are very well sampled, so that all links that in reality can occur are represented.
-Yet it is known that not all food webs are very well sampled, and then do not represent all of the feeding links that occur (reference).
+Yet it is know that not all food webs are very well sampled, and then do not represent all of the feeding links that occur.
 One solution to this problem is to use a food web model to predict which are the missing links, and to then measure the robustness of the predicted food web.
@@
 
-In Gupta et al.
-(2022) we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) by fitting it to empirical data using approximate Bayesian computation, and the goodness of fit of the ADBM was measured using the true skill statistics which takes into account the presence of links as well as the absence of links.
-(ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.) A key finding of Gupta et al.
-(2022) was that the predicted food web connectance was consistently higher as compared to the observed connectance.
-This means that there were some trophic links (false positives) predicted by the ADBM which are not observed in the empirical food web data.
-Simultaneously there were some trophic links (false negatives) that were not predicted by the ADBM but were observed in the empirical food web.
-In that work there was no attempt to estimate the importance of these findings on computing the robustness of these food webs to species extinctions.
+In previous work we made predictions of food web structure using the allometric diet breadth model (ADBM, [@beckerman2006; @petchey2008]) fit to empirical data using ABC.
+(ADBM uses foraging theory specifically the contingency model [@macarthur1966] to predict the diet of each potential consumer and thereby the food web structure.) A key finding of this work was...
+overestimated the food web connectance when compared with the observed connectance.
+[State interpretation]: false positives, false negatives.
+In that work there was no attempt to estimate the importance of these findings for food web robustness to extinctions.
 
@@
 
-It is crucial to investigate the implication of this consistent overestimation of connectance in the robustness of predicted food webs.
+It is crucial to investigate the implication of this overestimation in the robustness of predicted food webs.
 We expect that the ADBM predicted food webs would be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
@@
 
-In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different scenarios on 12 food webs predicted by the ADBM from wide variety of ecosystems, and compute the resultant secondary extinctions.
-We then compute a robustness metric to quantify the robustness of those predicted food webs.
+...
 
@@
 
-We first present the cumulative secondary extinctions in the food webs for three different extinction scenarios.
-We also computed the robustness metric for the food webs where the robustness metric quantifies the number of species extinctions required to have at least 50% of total number of species extinctions in a food web.
-
 ## Show and describe the secondary extinction curves
 
-In Fig.
-\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show the secondary extinction curves of ADBM predicted food webs and observed food webs for 12 different food webs under three different extinction scenarios.
-In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs.
-
-In the most connected extinction scenario, the cumulative secondary extinction curve for the observed food webs rose quickly as compared to the ADBM predicted food webs, and then reach saturation after a certain number of primary removal of species.
-In some of the food webs (Fig.
-\ref{fig:fig_r1} (f, g, h, i, j, k)), there were intersection between the cumulative secondary extinction curves of ADBM predicted food webs and that of the observed food webs.
-In case of the Broadstone Stream (taxonomic aggregation) food web and the Tuesday Lake food web (Fig.
-\ref{fig:fig_r1} (b and k)), the secondary extinction curves for the ADBM food webs were higher than the observed food webs, whereas in case of the Skipwith Pond food web (Fig.
-\ref{fig:fig_r1} (i)), there were no secondary extinctions for any given number of primary removal of species.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the most connected species for 12 food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_mostconnected.png")
-```
-
-Except Broadstone Stream (taxonomic aggregation), Broadstone Stream (size aggregation) and Tuesday Lake food webs (Fig.
-\ref{fig:fig_r2} (b, c and k)), the mean cumulative secondary extinction curves for all the other food webs predicted by the ADBM were always lower than that of the observed food webs in the random extinction scenario.
-The shape of the cumulative secondary extinctions curves varied across the food webs.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary removals of random species for 12 food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_random.png")
-```
-
-Compared to the most connected and random extinction scenarios, the cumulative extinction curves in the least connected extinction scenario had very low values and were flat for most of the food webs (Fig.
-\ref{fig:fig_r3}) compared to the most connected extinction and random extinction scenarios.
-In most of the food webs, there was a lot of overlap between the extinction curves of the ADBM predicted foof webs and the observed food webs.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the least connected species for 12 food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_leastconnected.png")
+```{r, echo=FALSE, fig.align='center', out.width="500px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions for 12 food webs across different ecosystems."}
+knitr::include_graphics("../results/plot_dd_mc_mod.png")
 ```
@@
 
-I suggest to focus on the relationship between (difference in robustness between observed and predicted connectance) and (difference in robustness between the observed and predicted food web).
+I suggest to focus on the relationship between (difference in robustness between observed and predicted food web) and (difference in robustness between the observed and predicted food web).
 
-The ADBM predicted food webs were more robust than the observed food web with some exceptions (Fig.
-\ref{fig:fig_r4}).
-The food webs were more robust to least connected and random extinction scenarios than the primary deletion of the most connected species.
-The difference in the robustness values between the ADBM predicted food webs and observed food webs was higher in the most connected extinction scenario as compared to the least connected extinction and random extinction scenarios.
+Show differences between the methods.
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions)."}
-knitr::include_graphics("../results/plot_robustness_all_uncertainty.png")
-```
+Mention the outlier food webs: where the stability of ADBM predicted food webs is lower than empirical food webs
 
-AG: I will also update the robustness plot for random extinction (Fig.
-4 (b)) once the simulation is completed.
-The one shown here is only for few simulations and as a placeholder.
-It takes more time to compute.
+## Explain the robustness plots
+
+[OP] I'm not too sure what is meant by this.
+
+### Compare the results from the different methods
 
@@
 
-The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs, and the shape of the robustness extinction curves varies between food webs.
-The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios.
-A future development would be to understand the stability of the dynamics of the ADBM predicted food webs and compare it with our study.
+## [OP] Briefly summarise the findings
 
@@
 
-For most of the food webs, the primary removals of species resulted in a higher secondary extinction in the ADBM predicted food webs than that of the observed food webs (Fig.
-\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}).
-This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a high connectance has on average more number of trophic links as compared to the food webs with low connectance.
-
-It would be intriguing to know if this difference in connectance has a similar influence in the dynamical stability of the food webs as well.
-Hence, a future prospect could be to use a dynamical model (for example: bionergetic food web model [@broseAllometricScalingEnhances2006]) to model the temporal dynamics of the ADBM predicted food webs.
-It would be interesting to know the temporal stability of these ADBM predicted food webs compared to the observed food webs because it has been known that food webs with increasing connectance stability diminishes [@mayWillLargeComplex1972].
-
 ...
@@
 
+## Discuss how the robustness is dependent on the TSS of the predicted food web
+
+* Would a higher TSS imply a higher difference in the robustness between predicted and observed food web?
+
+OP: This (TSS and robustness relationship) would need to be presented in the Results, if this is to be included.
+
+## Compare the results from our study with results from other food web models (Jennifer A. Dunne and Williams (2009))
+
+[OP] Including if and why we expect our findings to be replicated with those other models. Include some of Gravel and Poissot's models
+
 ## Explain that the ADBM can only predicts contiguous diets [OP] and the implications of this
-
-Using only body size as a trait, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
-I.e.
-it cannot predict that a predator will consume prey of size 1 and 3, and not consume prey of size 2.
-Also, it is important to note that the observed diets were not contiguous when prey are ordered by their size, and this is due to some ecological differences in how predator group choose their prey [@caronAddressingEltonianShortfall].
-So, the parameterisation process lead to a greater number of predicted links than observed.
-
-This higher connectance in the ADBM predicted food webs has lead to a higher robustness of the ADBM predicted food webs.
-An important question to ask here is how reliable are these results.
-We suspect that this is because the model and the observed data are wrong to some extent.
-We expect that some of the links that do in reality occur are not present in the observed datasets, which is quite possible because of low sampling effort or rare prey-predator interactions even when there is intensive sampling.
-This would mean that the false positives may actually be a correctly predicted link.
-
-We suspect that the model is also predicting links which actually do not occur.
-This is because the current ADBM model only takes body size trait, and therefore only predicts contiguous diet.
-That would mean any interaction that is not possible because of some other traits not correlated with the body size would still be predicted by the model.
-For example, a species might have a defensive trait that could result in the predator species not predating on that species at all.
-
-AG: (Caution) Some of the texts might be very similar to or same as in C1 MS.
-With multiple iterations of the current ms, the current text would be altered.
-Also, the current ms would be checked using a plagiarism software before submission.
 
@@
 
-<!-- ## Discuss how the robustness is dependent on the TSS of the predicted food web -->
+## Future prospect of using a dynamical model to model the temporal dynamics of the ADBM predicted food web
 
-<!-- * Would a higher TSS imply a higher difference in the robustness between predicted and observed food web? -->
-
-<!-- OP: This (TSS and robustness relationship) would need to be presented in the Results, if this is to be included. -->
-
-<!-- AG: I will present TSS and robustness relationship in the next version of the ms, and add relevant text here. -->
-
-## Compare the results from our study with results from other food web models (Jennifer A. Dunne and Williams (2009))
-
-The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased.
-A future study could be to understand the robustness of other food web models [@gravelInferringFoodWeb2013a] and compare it with our study.
-We expect similar results.
-
-[OP] Including if and why we expect our findings to be replicated with those other models. Include some of Gravel and Poissot's models
-
-...
-
-<!-- Need to coordinate this content with what I proposed on line 141. -->
-
-<!-- Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability." -->
+Need to coordinate this content with what I proposed on line 141.
 

### 2022-07-06 manuscript/ms_C3_v2.Rmd

--- 2022-07-06 manuscript/ms_C3.Rmd
@@
 
-In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different scenarios on 12 food webs predicted by the ADBM from wide variety of ecosystems, and compute the resultant secondary extinctions.
+In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems, and compute the resultant secondary extinctions.
 We then compute a robustness metric to quantify the robustness of those predicted food webs.
@@
 ## \*\*OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution.
+
+## Model parameterisation using approximate Bayesian computation
+
+The ADBM was parameterised using approximate Bayesian computation (ABC) where a set of parameter values were sampled from the prior distributions.
+That set of parameter values parameter values were either accepted and or rejected based on close the predicted is to the observed food web using a accuracy metric -- True skill statistic.
+The accepted parameter values formed a posterior distribution.
+Further prediction intervals of the true skill statistic and connectance of the predicted food webs were calculated.
+In our study, we considered food webs where the predicted connectance lies in the 95% prediction interval of the predicted connectance.
 
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary \\texrbf{removals of the most connected species} for 12 food webs.
 S denotes the number of species in a food web.
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary \\textbf{removals of random species} for 12 food webs.
 S denotes the number of species in a food web.
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary **removals of the least connected species** for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of the least connected species} for 12 food webs.
 S denotes the number of species in a food web.
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions)."}
-knitr::include_graphics("../results/plot_robustness_all_uncertainty.png")
+knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
+```
+
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e ratio of relative difference in robustness between ADBM predicted food webs and observed food webs to relative difference in their connectance) shown for the 12 food webs.
+Red filled circles represent means.
+Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits."}
+knitr::include_graphics("../results/plot_R50_slope.png")
 ```

### 2022-07-06 manuscript/ms_C3_v2.tex

--- 2022-07-06 manuscript/ms_C3.tex
@@
 Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
-2009). These studies showed that the robustness \textbf{of the food
-webs} increases with food web connectance. Also, the removal of the most
+2009). These studies showed that the robustness of the food webs
+increases with food web connectance. Also, the removal of the most
 connected species cause considerably more secondary extinctions than
@@
 implementation of simulation of primary extinctions for three different
-scenarios on 12 food webs predicted by the ADBM from wide variety of
+scenarios on 12 food webs predicted by the ADBM from a wide variety of
 ecosystems, and compute the resultant secondary extinctions. We then
@@
 distribution.}\label{op-need-a-section-on-how-the-food-web-model-was-fit-to-the-data.-also-should-state-how-we-deal-with-use-the-uncertainty-contained-in-the-posterior-joint-distribution.}}
+
+\hypertarget{model-parameterisation-using-approximate-bayesian-computation}{%
+\subsection{Model parameterisation using approximate Bayesian
+computation}\label{model-parameterisation-using-approximate-bayesian-computation}}
+
+The ADBM was parameterised using approximate Bayesian computation (ABC)
+where a set of parameter values were sampled from the prior
+distributions. That set of parameter values parameter values were either
+accepted and or rejected based on close the predicted is to the observed
+food web using a accuracy metric -- True skill statistic. The accepted
+parameter values formed a posterior distribution. Further prediction
+intervals of the true skill statistic and connectance of the predicted
+food webs were calculated. In our study, we considered food webs where
+the predicted connectance lies in the 95\% prediction interval of the
+predicted connectance.
 
@@
 
-\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs.
+\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the most connected species** for 12 food webs.
 S denotes the number of species in a food web.
@@
 
-\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs.
+\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary \textbf{removals of random species} for 12 food webs.
 S denotes the number of species in a food web.
@@
 
-{\centering \includegraphics[width=400px]{../results/plot_robustness_all_uncertainty}
+{\centering \includegraphics[width=450px]{../results/plot_R50_ADBM_vs_obs}
 
@@
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).}\label{fig:unnamed-chunk-5}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=450px]{../results/plot_R50_slope}
+
+}
+
+\caption{\label{fig:fig_r5} Effect size (i.e ratio of relative difference in robustness between ADBM predicted food webs and observed food webs to relative difference in their connectance) shown for the 12 food webs.
+Red filled circles represent means.
+Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits.}\label{fig:unnamed-chunk-6}
 \end{figure}

### 2022-09-20 manuscript/ms_C3_v2.Rmd
Manuscript for feedback to Owen

--- 2022-07-06 manuscript/ms_C3.Rmd
@@
 ---
-title: Missing links, forbidden links, and the topological robustness of food webs
+title: Missing links and the topological robustness of food webs
 authors:
@@
 
-  1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food web.
-Undersampling can be compensated for by using food web models such as allometric diet breadth model (ADBM) to predict missing links.
+  1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs.
+Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links.
 Simultaneously, models might predict links which cannot occur, i.e., false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of trophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
+  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
 Thus we expect that predicted food webs are more robust than observed ones.
@@
   4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
-On average, for every X unit of increase in connectance, we found the food webs to be robust by YY units for random extinction scenario.**OP: Here something about the effect size.**
+On average, for every one unit of increase in connectance, we found the food webs to be robust by 0.52 units and 0.04 units for the most connected and the random species extinction scenarios respectively while no effect in the least connected species extinction scenario.
   5)  These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
@@
 
-## Background on anthropogenic changes and its impact on food web
+<!-- ## Background on anthropogenic changes and its impact on food web -->
 
 Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity, and can lead to food web collapse [@ullah2018].
-This collapse in the food web is due to cascades of secondary extinctions in a food web because of primary loss of species, for example due to habitat destruction.
-The rate of collapse of these predicted food webs is dependent on the structure and complexity of those food webs [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-Therefore, research focused on cascading secondary extinctions also known as 'community viability analysis' have been performed extensively in the past few decades [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
-
-## Briefly explain work done by Jennifer Dunne on food web [OP] robustness to primary extinctions, and also what has been done since, particularly concerning the importance of connectance
+This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species, for example due to habitat destruction and climate change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
+Therefore, research focused on cascading secondary extinctions also known as 'community viability analysis' have been performed extensively in the past few decades to quantify how robust are food webs to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
+And it has been shown that the rate of collapse of a food web is dependent on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
 
 Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-These studies showed that the robustness of the food webs increases with food web connectance.
-Also, the removal of the most connected species cause considerably more secondary extinctions than random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
-These studies provide an alternate solution to investigate the impact of primary extinctions in a food web when canonical experiments in natural ecosystems are not possible.
+These studies have shown that the robustness of the food webs increases with food web connectance.
+Also, the removal of the most connected species cause considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
+Simulation studies like these which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure provide an alternate solution to canonical experiments in natural ecosystems which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
 
-Along with robustness based on topological structure of a food web, robustness based on the food web dynamics has been studied as well (reference).
-Topological approaches only require the food web structure whereas dynamical approaches also require the temporal dynamics of the food web along with the food web structure.
-For example: @williamsEffectsNetworkDynamical2008 combined models of network structure with models of bionergetic dynamics to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
+Along with quantifying food web robustness based on its topological structure, studies such as @williamsEffectsNetworkDynamical2008, @broseAllometricScalingEnhances2006 and @martinezDiversityComplexityPersistence have quantified robustness based on the abundance dynamics of a food web.
+The topological approach of quantifying a food web robustness only requires the food web structure whereas the dynamical approach not only requires the food web structure but also the temporal dynamics of abundance of species in that food web.
+For example: @williamsEffectsNetworkDynamical2008 combined models of network structure with models of bioenergetic dynamics to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
 
-[OP] Explain (either here or in the methods) difference between topological and abundance (given by dynamics) based criteria for a secondary extinction occurring.
+<!-- ## [OP] State what is the problem... -->
 
-## [OP] State what is the problem...
-
-A key assumption of the observed food webs is that the food webs are very well sampled i.e.
+A key assumption of the observed food webs is that they are very well sampled i.e.
 all the links that in reality can occur are represented.
@@
 Some rare trophic links require more sampling effort as compared to others whereas some trophic links remain unobserved because of linkage constraints irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
-One solution to this problem is to use a food web model such as Allometric Diet Breadth Model (ADBM) to predict which are the missing links, and to then measure the robustness of the predicted food web.
-ADBM is a mechanistic model constructed using rules based on body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which at the same time are perhaps not observed because those interactions are rare.
+Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
+Therefore, one solution to compensate for undersampling is to use a food web model such as the Allometric Diet Breadth Model (ADBM) to predict the missing links, and to then measure the robustness of the predicted food web.
+ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which are perhaps not observed because those interactions are rare.
 However, this solution is not infallible, as it is likely that the food web model might still miss some links, and also may predict some links that could not, in fact occur.
 
-## What we do in this study
+<!-- ## What we do in this study -->
 
-In our study, we investigate the robustness of the ADBM predicted food webs as compared to the observed food webs and quantify the effect of overestimation of connectance on the robustness of these predicted food webs.
+In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs, and quantify the effect of undersampling i.e overestimation of connectance on the robustness of these predicted food webs.
+We expect that the ADBM predicted food webs to be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
 We do this by simulating primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
-We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
-
-It is crucial to investigate the implication of this consistent overestimation of connectance in the robustness of predicted food webs.
-We expect that the ADBM predicted food webs would be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
-In this study, we simulate primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
 We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
@@
 
-[OP] ## Provide overview of the methods
+<!-- [OP] ## Provide overview of the methods -->
 
-In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different scenarios on 12 food webs predicted by the ADBM from wide variety of ecosystems, and compute the resultant secondary extinctions.
-We then compute a robustness metric to quantify the robustness of those predicted food webs.
+In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different extinction scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems and compute the resultant secondary extinctions.
+We then compute a robustness metric to quantify the robustness of those predicted food webs and compare them against that of the observed food webs.
 
@@
 The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966].
+We chose this model because the ADBM can likely predict missing links in the predicted food webs because it consistently overestimated connectance in the predicted food webs as shown by our study in @guptaSimultaneouslyEstimatingFood2022.
 The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
-The foraging variables in the model are: energy content of prey, handling times of the predator on prey, space clearance rate of predator on prey, and prey densities.
-All are derived from the body sizes of the species via allometries.
+The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate i.e.
+how fast a predator searches space, and prey densities.
+All of these variables are derived from the allometric scaling relationship using the body sizes of species.
+More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petchey2008.
 
@@
 The observed food webs that we fit the ADBM to belong to marine, freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}).
-The observed connectance of these food webs is from 0.03 to 0.24 and there are 29 to 239 species.
-The food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids.
-They also contain various types of feeding interactions, including predation, herbivory, bacterivory, parasitism, pathogenic, and parasitoid.
+These food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids and also contain various types of feeding interactions, including predation, herbivory, bacterivory, parasitism and pathogenic.
+The observed connectance of these food webs varies from 0.03 to 0.24 and the number of species varies from 29 to 239 species.
+
+The goodness of fit of the ADBM's predictions depends on the interaction types in the food webs with predictions that are more size-structured such as aquatic and herbivory interactions being better predicted when compared to less size-structured ones such as parasitoid and terrestrial herbivory ones [@petchey2008].
 
@@
 
-## \*\*OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution.
+<!-- ## \*\*OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution. -->
 
-## Primary and secondary extinctions
+## Model parameterisation using approximate Bayesian computation
 
-We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species.
+The ADBM was parameterised using approximate Bayesian computation (ABC) where a set of parameter values were sampled from the prior distributions.
+That set of parameter values was either accepted or rejected based on how close the predicted food web is to the observed food web using an accuracy metric -- true skill statistic (TSS).
+The accepted parameter values then formed a posterior distribution.
+Further, prediction intervals of the true skill statistic and connectance of the predicted food webs were computed.
+In our study, we considered food webs where the predicted connectance lay within the 95% prediction interval.
+A detailed explanation of the parameterisation method can be found in @guptaSimultaneouslyEstimatingFood2022.
+
+## Extinction scenarios and robustness
+
+We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of the three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species.
 The most-connected and least-connected criteria are based on the degree (i.e.
-total number of links to resources and from consumers) of species.
-Given a primary removal if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
+the total number of links to resources and from consumers) of species.
+We considered these mentioned criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web and the extinction of most-connected species and least-connected species takes into account the two opposite extreme scenarios.
+These extinction scenarios have been widely used in studying species extinctions and collapse of food webs and other networks [@dunne2002network; @soleComplexityFragilityEcological2001; @dunne2004; @dunneCascadingExtinctionsCommunity2009; @albertStatisticalMechanicsComplex2002].
+
+Given a primary removal of species in a food web if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
 Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
-One no more secondary extinctions occured, then another primary extinctions was made, of the next appropriate species.
-This process was carried out until all species were extinct from the web.
+Once no more secondary extinctions occurred, then another primary extinction was made, of the next appropriate species depending on the extinction scenario.
+This process was carried out until all the species were extinct from the food web.
 
-## Calculating robustness
+The robustness (R) of a food web was defined as the proportion of species subjected to primary removals that resulted in a set of extinction (i.e.
+primary removals plus secondary extinctions) of some specified proportion of the species.
+In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, which results in at least 50% of total species loss [@dunne2002network; @dunne2004; @jonssonReliabilityR50Measure2015; @dunneCascadingExtinctionsCommunity2009].
+Therefore, if primary extinctions never cause any secondary extinctions, the food web is maximally robust and ($R_{50} = 0.50$).
+Whereas in a minimally robust community ($R_{50} = 1/S$), the first primary extinction causes a cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
+at least $S/2 - 1$).
 
-Robustness (R) of food web was quantified as the proportion of species subjected to primary removals that resulted in a loss (i.e.
-primary removals plus secondary extinctions) of some specified proportion of the species.
-In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, that result in at least 50 per cent of total species loss [@dunne2002network; @dunne2004; @dunneCascadingExtinctionsCommunity2009].
-Therefore, if primary extinctions never cause any secondary extinctions, the food web is maximally robust and ($R_{50} = 0.50$).
-Whereas in a minimally robust community ($R_{50} = 1/S$), since the first primary extinction causes as cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
-at least $S/2 - 1$).
+## Simulating species extinctions
+
+First, we simulated primary species loss in food webs predicted by the ADBM which had the maximum true skill statistics and compared it to primary species loss in observed food webs.
+Second, to take into account the uncertainty in robustness in the ADBM predicted food webs we simulated primary species loss and thereby computed robustness for all the ADBM predicted food webs corresponding to the 95% prediction interval of the predicted connectance.
+In the case of the random extinction scenario, we simulated 1000 random extinction sequences in a single ADBM predicted food web.
+
+## Statistical analysis
+
+In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web.
+To quantify the effect of undersampling i.e.
+overestimation of connectance we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (I.e 0.5 for $R_{50}$ and 1 for connectance).
+However, we did not perform any statistical significance test because we work with simulated food webs and therefore the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].
 
@@
 
-## Show and describe the secondary extinction curves
+We first present the secondary extinction curves of the ADBM predicted food webs which had the maximum true skill statistics and the observed food webs for 12 food webs under three different extinction scenarios.
+We then compare the robustness of all the ADBM predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
+Finally we quantify the effect of overestimation of connectance on the difference in their robustness estimates.
+
+## Secondary extinctions
+
+In the most-connected extinction scenario, the cumulative secondary extinction curves started to rise steeply at a lower number of primary species removal in the observed food webs as compared to the ADBM predicted food webs for nine food webs (Fig.
+\ref{fig:fig_r1} (a, c, d, e, f, g, h, j, l)).
+However there were higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal (Fig.
+\ref{fig:fig_r1} (a, f, g, h, k)).
+In the Skipwith Pond food web, there were no secondary extinctions for any number of primary removal of species (Fig.
+\ref{fig:fig_r1} (i)), whereas in the Broadstone Stream (taxonomic aggregation) food web the same was true only for the observed food web but in the ADBM predicted food web there was a steep rise in the cumulative secondary extinctions (Fig.
+\ref{fig:fig_r1} (b)).
+
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of the most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+S denotes the number of species in a food web.
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
+knitr::include_graphics("../results/plot_mostconnected_maxTSS.png")
+```
 
 In Fig.
-\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show the secondary extinction curves of ADBM predicted food webs and observed food webs for 12 different food webs under three different extinction scenarios.
-We found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for nine, nine and seven food webs.
+\ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show qualitative differences between their secondary extinction curves.
+The secondary extinctions in the ADBM predicted food webs were more abrupt than that in the observed food webs.
 
-In general, irrespective of the extinction scenarios, we found that the cumulative secondary extinction was higher for the ADBM predicted food webs as compared to the observed food webs for most of the food webs **OP: this is not so clear to me.
-State how many cases?
-It seems there are many cases where secondary extinctions are more numerous in the observed food web: blue line above the red.**.
-
-In the most connected extinction scenario, the cumulative secondary extinction curve for the observed food webs rose quickly as compared to the ADBM predicted food webs, and then reach saturation after a certain number of primary removal of species.
-In some of the food webs (Fig.
-\ref{fig:fig_r1} (f, g, h, i, j, k)), there were intersection between the cumulative secondary extinction curves of ADBM predicted food webs and that of the observed food webs.
-In case of the Broadstone Stream (taxonomic aggregation) food web and the Tuesday Lake food web (Fig.
-\ref{fig:fig_r1} (b and k)), the secondary extinction curves for the ADBM food webs were higher than the observed food webs, whereas in case of the Skipwith Pond food web (Fig.
-\ref{fig:fig_r1} (i)), there were no secondary extinctions for any given number of primary removal of species.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
 S denotes the number of species in a food web.
 The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_mostconnected.png")
+knitr::include_graphics("../results/plot_ra_extlines_maxTSS.png")
 ```
 
-Except Broadstone Stream (taxonomic aggregation), Broadstone Stream (size aggregation) and Tuesday Lake food webs (Fig.
-\ref{fig:fig_r2} (b, c and k)), the **mean cumulative secondary extinction curves** **OP: must be explained somewhere how/why this is a mean** for all the other food webs predicted by the ADBM were always lower than that of the observed food webs in the random extinction scenario.
-The shape of the cumulative secondary extinctions curves varied across the food webs.
+Compared to the most-connected and random extinction scenarios, there were fewer secondary extinctions in the least-connected extinction scenario and therefore the secondary extinction curves were flat for most of the food webs (Fig.
+\ref{fig:fig_r3}).
+In some of the food webs, the extinction curves of the ADBM predicted food webs overlapped with the observed food webs (Fig.
+\ref{fig:fig_r3} (b, c, g, h, i, k, l)}).
+Contrary to the most-connected scenario, there was a very high number of secondary extinctions occurring at very low number of primary species removal (Fig.
+\ref{fig:fig_r3} (a, d, e, f, j)).
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of the least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
 The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_random.png")
+knitr::include_graphics("../results/plot_leastconnected_maxTSS.png")
 ```
 
-Compared to the most connected and random extinction scenarios, the cumulative extinction curves in the least connected extinction scenario had very low values and were flat for most of the food webs (Fig.
-\ref{fig:fig_r3}) compared to the most connected extinction and random extinction scenarios.
-In most of the food webs, there was a lot of overlap between the extinction curves of the ADBM predicted food webs and the observed food webs.
+## Robustness
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary **removals of the least connected species** for 12 food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_leastconnected.png")
+The ADBM predicted food webs were more robust than the observed food webs on average in the most-connected and random extinction scenarios (Fig.
+\ref{fig:fig_r4} (a, b)).
+However, there were large variations in the robustness within the ADBM predicted food webs in the most-connected extinction scenario (Fig.
+\ref{fig:fig_r4} (a)).
+For example, the ADBM predicted Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the ADBM predicted food webs compared to other food webs.
+
+The food webs were more robust to the random extinction scenario than the most-connected scenario (Fig.
+\ref{fig:fig_r4} (a, b)).
+Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
+\ref{fig:fig_r4} (b)).
+Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
+Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
+
+In the least-connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig.
+\ref{fig:fig_r4} (c)), however there were some exceptions.
+The ADBM predicted food webs for Small Reef and Benguela Pelagic had very low median robustness.
+Benguela Pelagic, Broom and Capinteria food webs from the ADBM had larger variations in robustness when compared to that of the others.
+
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems.
+Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
+Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.
+Some points are not visible due to perfect overlap in b and c.
+Refer to Fig.
+7 in the Supplementary Information for a faceted visualisation."}
+knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
 ```
 
-**OP: write text describing the effect sizes, e.g. how big is the difference between observed and ADBM webs.**
+In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size was positive on average in the most-connected extinction scenario (Fig.
+\ref{fig:fig_r5} (a)) i.e.
+overestimation of connectance had a positive effect on the robustness.
+In the random extinction scenario, there was a positive effect of overestimation of connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig.
+\ref{fig:fig_r5} (b)).
+However, the effect size varied across the food webs.
+In the least-connected extinction scenario, the overestimation of connectance had little effect on average on the difference in the robustness (Fig.
+\ref{fig:fig_r5} (c)).
 
-## Show and describe the following:
-
-I suggest to focus on the relationship between (difference in robustness between observed and predicted connectance) and (difference in robustness between the observed and predicted food web).
-**OP: I miss text describing this relationship.** **OP: Allow the panels in the figure to have different y-axis scales.**
-
-**OP: This paragraph should go in the previous section**.
-The ADBM predicted food webs were more robust than the observed food web with some exceptions (Fig.
-\ref{fig:fig_r4}).
-The food webs were more robust to least connected and random extinction scenarios than the primary deletion of the most connected species.
-The difference in the robustness values between the ADBM predicted food webs and observed food webs was higher in the most connected extinction scenario as compared to the least connected extinction and random extinction scenarios.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions)."}
-knitr::include_graphics("../results/plot_robustness_all_uncertainty.png")
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e ratio of difference in normalised robustness between ADBM predicted food webs and observed food webs to difference in their normalised connectance) shown for the 12 food webs.
+Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+knitr::include_graphics("../results/plot_R50_slope.png")
 ```
-
-AG: I will also update the robustness plot for random extinction (Fig.
-4 (b)) once the simulation is completed.
-The one shown here is only for few simulations and as a placeholder.
-It takes more time to compute.
 
@@
 
-The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs, and the shape of the robustness extinction curves varies between food webs.
+The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs on average, with variation within the robustness of the ADBM predicted food webs in the 12 food web ecosystems suggesting that undersampling in food webs can lead to differences in the estimates of food web robustness.
+The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios on average.
+A future development would be to understand how undersampling i.e.
+overestimation of connectance influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs, and compare it with our study.
 
-The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios.
-A future development would be to understand the stability of the dynamics of the ADBM predicted food webs and compare it with our study.
+<!-- ## What does overestimation of connectance imply in terms of stability? -->
 
-...
+The robustness of the ADBM predicted food webs were higher than that of the observed food webs on average (Fig.
+\ref{fig:fig_r4}) for all of the 12 food web ecosystems with some exceptions.
+This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has on average more trophic links as compared to a food web with a lower connectance (Fig.
+\ref{fig:fig_r5}).
+Our study suggests that it is important to consider undersampling in observed food webs when computing their robustness.
 
-## What does overestimation of connectance imply in terms of stability?
+The findings from our study are similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of an increase in the robustness when the connectance of a food web is increased.
+However, contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig.
+\ref{fig:fig_r5}).
+The ADBM consistently predicted higher connectance than that of the observed food webs however, in some cases an increase in connectance resulted in lower robustness (Fig.
+\ref{fig:fig_r5}) in the predicted food web.
+For example: the Benguela Pelagic and Small Reef food webs were surprisingly less robust to primary extinctions on average in the least-connected extinction scenario (Fig.
+\ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
+We suspect this is because the ADBM is underestimating the proportion of basal species in the predicted food webs when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
+As a result, these low degree basal species are the ones to be removed at an early stage in the deletion sequence thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
+This suggests that the overestimation of connectance by the ADBM resulted in a more robust food web on average but differences in the predicted food web properties such as underestimation of the proportion of basal species and overestimation of the maximum trophic level (Fig: \ref{fig:fig_a1}) counteracted that effect and led to reduced robustness.
+This suggests that food web properties other than connectance play an important role in determining the robustness of a food web and therefore should be also taken into account.
 
-For most of the food webs, the primary removals of species resulted in a higher secondary extinction in the ADBM predicted food webs than that of the observed food webs (Fig.
-\ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}).
-This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a high connectance has on average more number of trophic links as compared to the food webs with low connectance.
-**OP: should here cite figure 4.**
+<!-- ## Explain how ADBM predicts diet, that the ADBM can only predicts contiguous diets [OP] and the implications of this -->
 
-It would be intriguing to know if this difference in connectance has a similar influence in the dynamical stability of the food webs as well.
-Hence, a future prospect could be to use a dynamical model (for example: bionergetic food web model [@broseAllometricScalingEnhances2006]) to model the temporal dynamics of the ADBM predicted food webs.
-It would be interesting to know the temporal stability of these ADBM predicted food webs compared to the observed food webs because it has been known that food webs with increasing connectance stability diminishes [@mayWillLargeComplex1972].
+The ADBM based on its size-based rules predicts the diet of a consumer and hence is able to predict some links in the predicted food webs which do in reality occur but are actually not observed in the observed food webs perhaps because of low sampling effort.
+<!-- This could also be possible because of rare prey-predator interactions even when sampling is extensive [@grayJoiningDotsAutomated2015; @woodwardChapterIndividualBasedFood2010; @jordanoSamplingNetworksEcological2016].
+-->
+A future study could be to extend our study to use other food webs models based on size-based rules such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021 and compare them with our study.
+We expect similar results because these food webs are also based on body size rules.
 
-...
+As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM.
+Firstly this may be because the ADBM uses only body size as a trait.
+A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022].
+Secondly, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
+I.e.
+it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2.
+However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall].
+Therefore a future study could extend our study with other food web models which are not based on body size such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008.
+We expect to have a difference in results based on whether the trophic interactions in the food webs are governed by size-structured rules or not.
 
-Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability.
+It would be intriguing to know if this difference in connectance has a similar influence on the dynamical stability of the food webs as well.
+Hence, a prospect could be to use a dynamical model (for example bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
+We expect that the difference in dynamical robustness of the ADBM predicted and the observed food webs would be similar to differences in their topological robustness because the dynamical robustness of the ADBM predicted and the observed food webs would be both underestimated when compared to their topological robustness [@curtsdotterRobustnessSecondaryExtinctions2011a].
 
-## Explain that the ADBM can only predicts contiguous diets [OP] and the implications of this
+<!-- ## Incorporate trait-based deletions sequences -->
 
-Using only body size as a trait, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
-I.e.
-it cannot predict that a predator will consume prey of size 1 and 3, and not consume prey of size 2.
-Also, it is important to note that the observed diets were not contiguous when prey are ordered by their size, and this is due to some ecological differences in how predator group choose their prey [@caronAddressingEltonianShortfall].
-So, the parameterisation process lead to a greater number of predicted links than observed.
+<!-- Although our study takes into account all the theoretically possible extinction sequences of species in a food web, a future development could be to specifically consider extinction sequences which are more realistic based on species traits which are more realistic than the others [@bergEcologicalCommunitiesAre2015; @jacobRoleBodySize2011].
+This can help to understand which extinction sequences results in a greater difference in robustness of the ADBM predicted food webs and that of the observed food webs.
+-->
 
-This higher connectance in the ADBM predicted food webs has lead to a higher robustness of the ADBM predicted food webs.
-An important question to ask here is how reliable are these results.
-We suspect that both the model and the observed data are wrong to some extent.
-We expect that some of the links that do in reality occur are not present in the observed datasets, which is quite possible because of low sampling effort or rare prey-predator interactions even when there is intensive sampling.
-This would mean that the false positives may actually be a correctly predicted link.
+<!-- ## Use food web properties to parameterise the ADBM via ABC -->
 
-We suspect that the model is also predicting links which actually do not occur.
-This is because the current ADBM model only takes body size trait, and therefore only predicts contiguous diet.
-That would mean any interaction that is not possible because of some other traits not correlated with the body size would still be predicted by the model.
-For example, a species might have a defensive trait that could result in the predator species not predating on that species at all.
+Since the ADBM underestimates the proportion of basal species and overestimates the maximum trophic level in the predicted food webs compared to that of the observed food webs, it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
 
-AG: (Caution) Some of the texts might be very similar to or same as in C1 MS.
-With multiple iterations of the current ms, the current text would be altered.
-Also, the current ms would be checked using a plagiarism software before submission.
+<!-- ## Conclusion -->
 
-...
+We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links i.e.
+overestimation of connectance on the topological robustness of 12 food webs from various ecosystems.
+We found that the overestimation of connectance can have large impacts on the robustness of the food webs with variation in robustness among the predicted food webs which have also been influenced by differences in the structural food web properties between the ADBM predicted food webs and the observed food webs.
 
-<!-- ## Discuss how the robustness is dependent on the TSS of the predicted food web -->
+# Acknowledgements
 
-<!-- * Would a higher TSS imply a higher difference in the robustness between predicted and observed food web? -->
+This work was supported by the University Research Priority Program Global Change and Biodiversity (Grant number: U-704-04-11) of the University of Zurich.
 
-<!-- OP: This (TSS and robustness relationship) would need to be presented in the Results, if this is to be included. -->
+# Conflict of interest
 
-<!-- AG: I will present TSS and robustness relationship in the next version of the ms, and add relevant text here. -->
+None declared
 
-## Compare the results from our study with results from other food web models (Jennifer A. Dunne and Williams (2009))
+# Author contributions
 
-The findings from our study is similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of increase in the robustness when the connectance of the food web is increased.
-A future study could be to understand the robustness of other food web models [@gravelInferringFoodWeb2013a] and compare it with our study.
-We expect similar results.
+**Anubhav Gupta:** Conceptualisation; Data curation; Formal analysis; Investigation; Methodology; Project administration; Software; Validation; Writing -- original draft; Writing -- review and editing.
+**Owen L.
+Petchey:**
+**AG:** Owen, Could you please add your contributions here?
 
-[OP] Including if and why we expect our findings to be replicated with those other models. Include some of Gravel and Poissot's models
+# Data Accessibility Statement
 
-...
+To be added
+<!-- All the data used in this study was collected in other studies and is openly available.
+We list those studies and the open access source in Table \ref{fig:tab_1}.
+The complete code used in the analysis is available in the repository <XXX>.
+-->
 
-<!-- Need to coordinate this content with what I proposed on line 141. -->
+# Supplementary Information
 
-<!-- Line 141 is "Include here the possibility that the increased connectance would influence dynamical stability, and state if and why this may increase or decrease stability." -->
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_a1} Maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
+Box represent 25th and 75th percentile; bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+knitr::include_graphics("../results/plot_max_tl_ADBM_vs_emp.png")
+```
+
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
+Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
+Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+knitr::include_graphics("../results/plot_R50_ADBM_vs_obs_ra_lc_facet.png")
+```
 

### 2022-09-20 manuscript/ms_C3_v2.Rmd
Update ms_C3_v2.Rmd

@@
 Simultaneously, models might predict links which cannot occur, i.e., false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that predicted food webs usually have greater connectance than observed ones.
+  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
 Thus we expect that predicted food webs are more robust than observed ones.
 This expectation has never, to our knowledge, been tested, nor has the effect size been quantified.
-  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though can also make false positives.
+  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though which does not predict all links correctly.
 We did this for 12 different food webs from a wide variety of ecosystems.
+We used three extinction scenarios: random, most connected, and least connected.
   4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
@@
 This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species, for example due to habitat destruction and climate change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
+An example of a secondary extinction is when a consumer goes extinction because its sole resource species goes extinct.
 Therefore, research focused on cascading secondary extinctions also known as 'community viability analysis' have been performed extensively in the past few decades to quantify how robust are food webs to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
-And it has been shown that the rate of collapse of a food web is dependent on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+This research revealed that the rate of collapse of a food web is dependent on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
 
-Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-These studies have shown that the robustness of the food webs increases with food web connectance.
-Also, the removal of the most connected species cause considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
-Simulation studies like these which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure provide an alternate solution to canonical experiments in natural ecosystems which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
+Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+Primary species loss is considered to be extinction of a species due to causes external to the food web.
+In research with models, the specific cause or causes are usually not specified.
+Overharvesting of a population which causes extinction could be considered a driver of a primary extinction.
+A secondary extinction is an extinction caused by a previous extinction (either primary or secondary).
+Numerous studies have used a topological criteria for assigning a secondary extinction to a species, i.e., if an extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction because it has no resources.
+
+When there are few primary extinctions, and these cause many secondary extinctions, a food web is said to be fragile or not robust.
+When there are few secondary extinctions, a food web is said to be robust.
+Several studies have shown that the robustness of the food webs increases with food web connectance.
+Also, the removal (primary extinction) of the most connected species cause considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
+Simulation studies like these, which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure, provide an alternate solution to canonical experiments in natural ecosystems which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
 
@@
 all the links that in reality can occur are represented.
-However, it is known that not all food webs are very well sampled and then do not represent all of the feeding links that occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
-Some rare trophic links require more sampling effort as compared to others whereas some trophic links remain unobserved because of linkage constraints irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
+However, it is known that not all food webs are very well sampled and then do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
+Some rare trophic links require more sampling effort as compared to others, whereas some trophic links remain unobserved because of linkage constraints irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
 Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
 Therefore, one solution to compensate for undersampling is to use a food web model such as the Allometric Diet Breadth Model (ADBM) to predict the missing links, and to then measure the robustness of the predicted food web.
-ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which are perhaps not observed because those interactions are rare.
+The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which are perhaps not observed because those interactions are rare.
 However, this solution is not infallible, as it is likely that the food web model might still miss some links, and also may predict some links that could not, in fact occur.
@@
 
-In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs, and quantify the effect of undersampling i.e overestimation of connectance on the robustness of these predicted food webs.
-We expect that the ADBM predicted food webs to be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
+In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs.
+We expect the ADBM predicted food webs to be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
 We do this by simulating primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
-We use three different approaches of species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
+We use three different approaches of primary species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
 
@@
 In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different extinction scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems and compute the resultant secondary extinctions.
-We then compute a robustness metric to quantify the robustness of those predicted food webs and compare them against that of the observed food webs.
+We then describe a robustness metric of those predicted food webs and how we compare to properties of the food webs.
 
@@
 The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966].
-We chose this model because the ADBM can likely predict missing links in the predicted food webs because it consistently overestimated connectance in the predicted food webs as shown by our study in @guptaSimultaneouslyEstimatingFood2022.
+We chose this model because we have already used it to predict missing links in the predicted food webs, whereby it consistently overestimated connectance  @guptaSimultaneouslyEstimatingFood2022.
 The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
@@
 how fast a predator searches space, and prey densities.
-All of these variables are derived from the allometric scaling relationship using the body sizes of species.
+Each of these variables is derived from the allometric scaling relationship using the body sizes of species.
 More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petchey2008.
@@
 
-The goodness of fit of the ADBM's predictions depends on the interaction types in the food webs with predictions that are more size-structured such as aquatic and herbivory interactions being better predicted when compared to less size-structured ones such as parasitoid and terrestrial herbivory ones [@petchey2008].
+**OP: reduce the width of the final column of table 1.**
+**OP: state how and why these set of 12 food webs were chosen to study by us.**
+
+The goodness of fit of the ADBM's predictions depends on the interaction types in the food webs.
+Those with size-structured interactions, such as herbivory in aquatic ecosystems interactions being better predicted when compared to less size-structured ones such as parasitoids and terrestrial herbivory ones [@petchey2008].
 
@@
 the total number of links to resources and from consumers) of species.
-We considered these mentioned criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web and the extinction of most-connected species and least-connected species takes into account the two opposite extreme scenarios.
+We considered these three criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web and the extinction of most-connected species and least-connected species takes into account the two opposite extreme scenarios.
 These extinction scenarios have been widely used in studying species extinctions and collapse of food webs and other networks [@dunne2002network; @soleComplexityFragilityEcological2001; @dunne2004; @dunneCascadingExtinctionsCommunity2009; @albertStatisticalMechanicsComplex2002].
 
-Given a primary removal of species in a food web if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
+Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
 Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
@@
 
-The robustness (R) of a food web was defined as the proportion of species subjected to primary removals that resulted in a set of extinction (i.e.
-primary removals plus secondary extinctions) of some specified proportion of the species.
+The robustness (R) of a food web was defined as the proportion of species subjected to primary removals that resulted in extinction (primary and secondary extinctions) of some specified proportion of the species.
 In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, which results in at least 50% of total species loss [@dunne2002network; @dunne2004; @jonssonReliabilityR50Measure2015; @dunneCascadingExtinctionsCommunity2009].
@@
 Second, to take into account the uncertainty in robustness in the ADBM predicted food webs we simulated primary species loss and thereby computed robustness for all the ADBM predicted food webs corresponding to the 95% prediction interval of the predicted connectance.
-In the case of the random extinction scenario, we simulated 1000 random extinction sequences in a single ADBM predicted food web.
+Furthermore, in the case of the random extinction scenario, we simulated 1000 random extinction sequences in a single ADBM predicted food web.
 
-## Statistical analysis
+## Analysis
 
-In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web.
-To quantify the effect of undersampling i.e.
-overestimation of connectance we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (I.e 0.5 for $R_{50}$ and 1 for connectance).
+In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web to random extinction.
+To quantify the effect of undersampling, i.e.
+overestimation of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (I.e 0.5 for $R_{50}$ and 1 for connectance).
 However, we did not perform any statistical significance test because we work with simulated food webs and therefore the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].
@@
 
-We first present the secondary extinction curves of the ADBM predicted food webs which had the maximum true skill statistics and the observed food webs for 12 food webs under three different extinction scenarios.
+We first present the secondary extinction curves of the ADBM predicted food webs which had the maximum true skill statistics and of the observed food webs for 12 food webs under three different extinction scenarios.
 We then compare the robustness of all the ADBM predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
@@
 \ref{fig:fig_r1} (a, c, d, e, f, g, h, j, l)).
-However there were higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal (Fig.
+However there were higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal in five food webs (Fig.
 \ref{fig:fig_r1} (a, f, g, h, k)).
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of the most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 In Fig.
-\ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show qualitative differences between their secondary extinction curves.
+\ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show example variation caused by different random primary extinction orders.
 The secondary extinctions in the ADBM predicted food webs were more abrupt than that in the observed food webs.
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
+**OP: expand and clarify what is meant by abrupt... describe this in a sentence. (Abrupt could mean different things to different people, so clarification would be good.)
+
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
 S denotes the number of species in a food web.
@@
 
-Compared to the most-connected and random extinction scenarios, there were fewer secondary extinctions in the least-connected extinction scenario and therefore the secondary extinction curves were flat for most of the food webs (Fig.
+Compared to the most-connected and random extinction scenarios, there were fewer secondary extinctions in the least-connected extinction scenario and therefore the secondary extinction curves were flat for many of the food webs (Fig.
 \ref{fig:fig_r3}).
@@
 \ref{fig:fig_r3} (b, c, g, h, i, k, l)}).
-Contrary to the most-connected scenario, there was a very high number of secondary extinctions occurring at very low number of primary species removal (Fig.
+In five of the food webs, a very high number of secondary extinctions occurred at very low number of primary species removal (Fig.
 \ref{fig:fig_r3} (a, d, e, f, j)).
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary \\textbf{removals of the least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 
-In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size was positive on average in the most-connected extinction scenario (Fig.
+**OP: "Box" in the figure caption is stated, but it is not clear where boxes are in the figure.
+
+In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size of connectance on robustness was positive on average in the most-connected extinction scenario (Fig.
 \ref{fig:fig_r5} (a)) i.e.
@@
 
+**OP: In figure 5c it looks like most of the data is less than zero, i.e. higher connectance is associated with lower robustness.**
+
 ```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e ratio of difference in normalised robustness between ADBM predicted food webs and observed food webs to difference in their normalised connectance) shown for the 12 food webs.
@@
 
-The primary removal of species revealed that the ADBM predicted food webs are more robust than the observed food webs on average, with variation within the robustness of the ADBM predicted food webs in the 12 food web ecosystems suggesting that undersampling in food webs can lead to differences in the estimates of food web robustness.
-The food webs are least robust to primary extinction of the most connected species scenario compared to that of least connected and random extinction scenarios on average.
-A future development would be to understand how undersampling i.e.
-overestimation of connectance influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs, and compare it with our study.
+As expected, the ADBM predicted food webs were more robust than the observed food webs on average.
+The considerable variation of the robustness of the ADBM predicted food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling.
+As was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average.
+A future development would be to understand how undersampling, i.e.
+overestimation of connectance, influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs, and compare it with the patterns in our study in which extinction occur only by topological criteria.
+**OP: what might one expect, based on previous work/evidence/results?*
 
@@
 
-The robustness of the ADBM predicted food webs were higher than that of the observed food webs on average (Fig.
-\ref{fig:fig_r4}) for all of the 12 food web ecosystems with some exceptions.
-This can be attributed to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has on average more trophic links as compared to a food web with a lower connectance (Fig.
+As mentioned, the robustness of the ADBM predicted food webs was higher than that of the observed food webs on average (Fig.
+\ref{fig:fig_r4}) for all of the 12 food web ecosystems (with some exceptions).
+This is likely due to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has on average more trophic links as compared to a food web with a lower connectance (Fig.
 \ref{fig:fig_r5}).
@@
 \ref{fig:fig_r5}).
-The ADBM consistently predicted higher connectance than that of the observed food webs however, in some cases an increase in connectance resulted in lower robustness (Fig.
+**OP: the next sentence seems to be repeating the previous two, rather than adding some content.
+Please clarify what development is provided in the next sentence** The ADBM usually predicted higher connectance than that of the observed food webs however, in some cases an increase in connectance resulted in lower robustness (Fig.
 \ref{fig:fig_r5}) in the predicted food web.
@@
 \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
+**OP.
+next sentence is my suggestion, please check it is accurate** In these two food webs, extinction of the least connected species could cause an almost complete, or complete collapse of the food web.
 We suspect this is because the ADBM is underestimating the proportion of basal species in the predicted food webs when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
@@
 This suggests that the overestimation of connectance by the ADBM resulted in a more robust food web on average but differences in the predicted food web properties such as underestimation of the proportion of basal species and overestimation of the maximum trophic level (Fig: \ref{fig:fig_a1}) counteracted that effect and led to reduced robustness.
-This suggests that food web properties other than connectance play an important role in determining the robustness of a food web and therefore should be also taken into account.
+This suggests that food web properties other than connectance play an important role in determining the robustness of a food web and therefore should be also taken into account (**OP: add a citation to one or more of the published studies that have shown this.).
 
@@
 
-The ADBM based on its size-based rules predicts the diet of a consumer and hence is able to predict some links in the predicted food webs which do in reality occur but are actually not observed in the observed food webs perhaps because of low sampling effort.
+**OP: the next sentence does not add any value, which is not so good in a two sentence paragraph.
+You could delete the first sentence and replace it with some sentences along the lines of: One of the choices we made was to use the ADBM, whereas we could have chosed to use other models.
+Alternative include modelX, modelY,...
+And then describe those models in some detail and the continue what remains here.** The ADBM based on its size-based rules predicts the diet of a consumer and hence is able to predict some links in the predicted food webs which do in reality occur but are actually not observed in the observed food webs perhaps because of low sampling effort.
 <!-- This could also be possible because of rare prey-predator interactions even when sampling is extensive [@grayJoiningDotsAutomated2015; @woodwardChapterIndividualBasedFood2010; @jordanoSamplingNetworksEcological2016].
@@
 A future study could be to extend our study to use other food webs models based on size-based rules such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021 and compare them with our study.
-We expect similar results because these food webs are also based on body size rules.
+We expect, however, similar results because these food webs are also based on body size rules.
 
 As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM.
-Firstly this may be because the ADBM uses only body size as a trait.
+Real false positive means that the food web model predicts a link between two species that can never interact.
+(The other type of false positive is when the model predicts a link that was not observed, but when it could have been observed.
+In this case, further sampling should result in the link being observed and a change from false positive to true positive.) Firstly this may be because the ADBM uses only body size as a trait.
 A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022].
@@
 Hence, a prospect could be to use a dynamical model (for example bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
-We expect that the difference in dynamical robustness of the ADBM predicted and the observed food webs would be similar to differences in their topological robustness because the dynamical robustness of the ADBM predicted and the observed food webs would be both underestimated when compared to their topological robustness [@curtsdotterRobustnessSecondaryExtinctions2011a].
+**OP: please try to clarify/futher explain the following sentence, as I don't quite understand it.** We expect that the difference in dynamical robustness of the ADBM predicted and the observed food webs would be similar to differences in their topological robustness because the dynamical robustness of the ADBM predicted and the observed food webs would be both underestimated when compared to their topological robustness [@curtsdotterRobustnessSecondaryExtinctions2011a].
 
@@
 
-Since the ADBM underestimates the proportion of basal species and overestimates the maximum trophic level in the predicted food webs compared to that of the observed food webs, it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
+Since the ADBM underestimates the proportion of basal species and overestimates the maximum trophic level in the predicted food webs compared to that of the observed food webs **OP: you/ we must give evidence for this new assertion**, it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
+We would explain more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.
 
@@
 overestimation of connectance on the topological robustness of 12 food webs from various ecosystems.
-We found that the overestimation of connectance can have large impacts on the robustness of the food webs with variation in robustness among the predicted food webs which have also been influenced by differences in the structural food web properties between the ADBM predicted food webs and the observed food webs.
+We found that the overestimation of connectance can have large impacts on the robustness of the food webs, while at the same time producing large variation in robustness among the predicted food webs.
+Differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are responsible.
 
@@
 **Owen L.
-Petchey:**
-**AG:** Owen, Could you please add your contributions here?
+Petchey:** Conceptualization, Funding acquisition, Resources, Supervision, Writing -- review & editing.
+**AG:** Owen, Could you please add your contributions here? **OP: done**
 

### 2022-09-20 manuscript/ms_C3_v2.Rmd
update

--- 2022-09-20 manuscript/ms_C3_v2.Rmd
@@
   - \usepackage{lineno}
-  - \linenumbers
+  # - \linenumbers
   - \usepackage {amsmath}

### 2022-09-20 manuscript/ms_C3_v2.tex
update

--- 2022-07-06 manuscript/ms_C3.tex
@@
 
-\title{Missing links, forbidden links, and the topological robustness of
-food webs}
+\title{Missing links and the topological robustness of food webs}
 
@@
 \usepackage{lineno}
-\linenumbers
 \usepackage {amsmath}
@@
   food webs, with potential consequences for the perceived functioning
-  and stability of the food web. Undersampling can be compensated for by
-  using food web models such as allometric diet breadth model (ADBM) to
-  predict missing links. Simultaneously, models might predict links
-  which cannot occur, i.e., false positives.
+  and stability of the food webs. Undersampling can be compensated for
+  by using food web models such as the allometric diet breadth model
+  (ADBM) to predict missing links. Simultaneously, models might predict
+  links which cannot occur, i.e., false positives.
 \item
@@
   the number of secondary extinctions occuring due to primary
-  extinctions) increases with connectance (the number of trophic links
-  divided by the number of possible links), and (ii) that predicted food
-  webs usually have greater connectance than observed ones. Thus we
-  expect that predicted food webs are more robust than observed ones.
-  This expectation has never, to our knowledge, been tested, nor has the
-  effect size been quantified.
+  extinctions) increases with connectance (the number of realised
+  trophic links divided by the number of possible links), and (ii) that
+  predicted food webs usually have greater connectance than observed
+  ones. Thus we expect that predicted food webs are more robust than
+  observed ones. This expectation has never, to our knowledge, been
+  tested, nor has the effect size been quantified.
 \item
@@
   than the observed food webs, and this can be attributed to the higher
-  connectance of the predicted food webs. On average, for every X unit
-  of increase in connectance, we found the food webs to be robust by YY
-  units for random extinction scenario.\textbf{OP: Here something about
-  the effect size.}
+  connectance of the predicted food webs. On average, for every one unit
+  of increase in connectance, we found the food webs to be robust by
+  0.52 units and 0.04 units for the most connected and the random
+  species extinction scenarios respectively while no effect in the least
+  connected species extinction scenario.
 \item
@@
 
-\hypertarget{background-on-anthropogenic-changes-and-its-impact-on-food-web}{%
-\subsection{Background on anthropogenic changes and its impact on food
-web}\label{background-on-anthropogenic-changes-and-its-impact-on-food-web}}
-
 Anthropogenic changes such as climate change and habitat destruction are
 a threat to biodiversity, and can lead to food web collapse (Ullah et
-al. 2018). This collapse in the food web is due to cascades of secondary
-extinctions in a food web because of primary loss of species, for
-example due to habitat destruction. The rate of collapse of these
-predicted food webs is dependent on the structure and complexity of
-those food webs (Jennifer A. Dunne, Williams, and Martinez 2002b;
-Jennifer A. Dunne and Williams 2009). Therefore, research focused on
-cascading secondary extinctions also known as `community viability
-analysis' have been performed extensively in the past few decades
+al. 2018). This food web collapse is due to the cascades of secondary
+extinctions in a food web because of the primary loss of species, for
+example due to habitat destruction and climate change (Pimm et al. 2006;
+J. A. Thomas et al. 2004; C. D. Thomas et al. 2004). Therefore, research
+focused on cascading secondary extinctions also known as `community
+viability analysis' have been performed extensively in the past few
+decades to quantify how robust are food webs to species extinction
 (Jennifer A. Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and
 Williams 2009; Berg et al. 2011; Ebenman, Law, and Borrvall 2004;
-Ebenman and Jonsson 2005).
-
-\hypertarget{briefly-explain-work-done-by-jennifer-dunne-on-food-web-op-robustness-to-primary-extinctions-and-also-what-has-been-done-since-particularly-concerning-the-importance-of-connectance}{%
-\subsection{Briefly explain work done by Jennifer Dunne on food web
-{[}OP{]} robustness to primary extinctions, and also what has been done
-since, particularly concerning the importance of
-connectance}\label{briefly-explain-work-done-by-jennifer-dunne-on-food-web-op-robustness-to-primary-extinctions-and-also-what-has-been-done-since-particularly-concerning-the-importance-of-connectance}}
+Ebenman and Jonsson 2005). And it has been shown that the rate of
+collapse of a food web is dependent on its structure and complexity
+(Jennifer A. Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and
+Williams 2009).
 
@@
 Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
-2009). These studies showed that the robustness \textbf{of the food
-webs} increases with food web connectance. Also, the removal of the most
-connected species cause considerably more secondary extinctions than
+2009). These studies have shown that the robustness of the food webs
+increases with food web connectance. Also, the removal of the most
+connected species cause considerably more secondary extinctions than the
 random removals of species (Jennifer A. Dunne, Williams, and Martinez
-2002a; Sol'e and Montoya 2001). These studies provide an alternate
-solution to investigate the impact of primary extinctions in a food web
-when canonical experiments in natural ecosystems are not possible.
+2002a; Sol'e and Montoya 2001). Simulation studies like these which
+investigate the impact of primary extinctions in a food web to quantify
+robustness based on its topological structure provide an alternate
+solution to canonical experiments in natural ecosystems which are not
+possible or very difficult to conduct (Jennifer A. Dunne and Williams
+2009).
 
-Along with robustness based on topological structure of a food web,
-robustness based on the food web dynamics has been studied as well
-(reference). Topological approaches only require the food web structure
-whereas dynamical approaches also require the temporal dynamics of the
-food web along with the food web structure. For example: Williams (2008)
-combined models of network structure with models of bionergetic dynamics
-to study the role of food web topology and nonlinear dynamics on species
-coexistence in complex ecological networks.
+Along with quantifying food web robustness based on its topological
+structure, studies such as Williams (2008), Brose, Williams, and
+Martinez (2006) and Martinez, Williams, and Dunne (2006) have quantified
+robustness based on the abundance dynamics of a food web. The
+topological approach of quantifying a food web robustness only requires
+the food web structure whereas the dynamical approach not only requires
+the food web structure but also the temporal dynamics of abundance of
+species in that food web. For example: Williams (2008) combined models
+of network structure with models of bioenergetic dynamics to study the
+role of food web topology and nonlinear dynamics on species coexistence
+in complex ecological networks.
 
-{[}OP{]} Explain (either here or in the methods) difference between
-topological and abundance (given by dynamics) based criteria for a
-secondary extinction occurring.
+A key assumption of the observed food webs is that they are very well
+sampled i.e.~all the links that in reality can occur are represented.
+However, it is known that not all food webs are very well sampled and
+then do not represent all of the feeding links that occur (Caron et al.
+2022; Patonai and Jord'an 2017; Jordano 2016). Some rare trophic links
+require more sampling effort as compared to others whereas some trophic
+links remain unobserved because of linkage constraints irrespective of
+sufficient sampling effort (Jordano 2016). Previous studies such as
+Caron et al. (2022) and Gupta, Furrer, and Petchey (2022) have shown
+that the predicted food webs from these models usually have greater
+connectance than the observed ones. Therefore, one solution to
+compensate for undersampling is to use a food web model such as the
+Allometric Diet Breadth Model (ADBM) to predict the missing links, and
+to then measure the robustness of the predicted food web. ADBM is a
+mechanistic model constructed using foraging rules based on the body
+sizes of prey and predator where trophic interactions satisfying those
+rules would be predicted by the model which are perhaps not observed
+because those interactions are rare. However, this solution is not
+infallible, as it is likely that the food web model might still miss
+some links, and also may predict some links that could not, in fact
+occur.
 
-\hypertarget{op-state-what-is-the-problem}{%
-\subsection{{[}OP{]} State what is the
-problem\ldots{}}\label{op-state-what-is-the-problem}}
-
-A key assumption of the observed food webs is that the food webs are
-very well sampled i.e.~all the links that in reality can occur are
-represented. However, it is known that not all food webs are very well
-sampled and then do not represent all of the feeding links that occur
-(Caron et al. 2022; Patonai and Jord'an 2017; Jordano 2016). Some rare
-trophic links require more sampling effort as compared to others whereas
-some trophic links remain unobserved because of linkage constraints
-irrespective of sufficient sampling effort (Jordano 2016). One solution
-to this problem is to use a food web model such as Allometric Diet
-Breadth Model (ADBM) to predict which are the missing links, and to then
-measure the robustness of the predicted food web. ADBM is a mechanistic
-model constructed using rules based on body sizes of prey and predator
-where trophic interactions satisfying those rules would be predicted by
-the model which at the same time are perhaps not observed because those
-interactions are rare. However, this solution is not infallible, as it
-is likely that the food web model might still miss some links, and also
-may predict some links that could not, in fact occur.
-
-\hypertarget{what-we-do-in-this-study}{%
-\subsection{What we do in this study}\label{what-we-do-in-this-study}}
-
-In our study, we investigate the robustness of the ADBM predicted food
-webs as compared to the observed food webs and quantify the effect of
-overestimation of connectance on the robustness of these predicted food
-webs. We do this by simulating primary species loss in 12 food webs
-predicted from the ADBM to quantify the secondary loss of extinctions.
-We use three different approaches of species removal: (i) most connected
-species, (ii) random species and (iii) least connected species to
-understand if the outcome varies among these approaches.
-
-It is crucial to investigate the implication of this consistent
-overestimation of connectance in the robustness of predicted food webs.
-We expect that the ADBM predicted food webs would be more robust as
-compared to the observed food webs, and for the greater robustness to be
-related to the amount by which the ADBM overestimates connectance. In
-this study, we simulate primary species loss in 12 food webs predicted
-from the ADBM to quantify the secondary loss of extinctions. We use
-three different approaches of species removal: (i) most connected
-species, (ii) random species and (iii) least connected species to
-understand if the outcome varies among these approaches.
+In our study, we investigate the topological robustness of the ADBM
+predicted food webs and compare it to that of the observed food webs,
+and quantify the effect of undersampling i.e overestimation of
+connectance on the robustness of these predicted food webs. We expect
+that the ADBM predicted food webs to be more robust as compared to the
+observed food webs, and for the greater robustness to be related to the
+amount by which the ADBM overestimates connectance. We do this by
+simulating primary species loss in 12 food webs predicted from the ADBM
+to quantify the secondary loss of extinctions. We use three different
+approaches of species removal: (i) most connected species, (ii) random
+species and (iii) least connected species to understand if the outcome
+varies among these approaches.
 
@@
 
-{[}OP{]} \#\# Provide overview of the methods
-
 In the upcoming sections, we present a detailed account of the
 implementation of simulation of primary extinctions for three different
-scenarios on 12 food webs predicted by the ADBM from wide variety of
-ecosystems, and compute the resultant secondary extinctions. We then
-compute a robustness metric to quantify the robustness of those
-predicted food webs.
+extinction scenarios on 12 food webs predicted by the ADBM from a wide
+variety of ecosystems and compute the resultant secondary extinctions.
+We then compute a robustness metric to quantify the robustness of those
+predicted food webs and compare them against that of the observed food
+webs.
 
@@
 theory, specifically the contingency model (MacArthur and Pianka 1966).
-The ADBM predicts the set of prey species a consumer should feed upon to
-maximise its rate of energy intake (Petchey et al. 2008). The foraging
-variables in the model are: energy content of prey, handling times of
-the predator on prey, space clearance rate of predator on prey, and prey
-densities. All are derived from the body sizes of the species via
-allometries.
+We chose this model because the ADBM can likely predict missing links in
+the predicted food webs because it consistently overestimated
+connectance in the predicted food webs as shown by our study in Gupta,
+Furrer, and Petchey (2022). The ADBM predicts the set of prey species a
+consumer should feed upon to maximise its rate of energy intake (Petchey
+et al. 2008). The foraging variables used in the model are the energy
+content of prey, handling times of the predator on prey, space clearance
+rate i.e.~how fast a predator searches space, and prey densities. All of
+these variables are derived from the allometric scaling relationship
+using the body sizes of species. More details on the foraging rules
+defined in the ADBM and ADBM's predictive power across different food
+webs can be found in Petchey et al. (2008).
 
@@
 The observed food webs that we fit the ADBM to belong to marine,
-freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). The
-observed connectance of these food webs is from 0.03 to 0.24 and there
-are 29 to 239 species. The food webs contain primary producers,
-herbivores, carnivores, parasites, and parasitoids. They also contain
-various types of feeding interactions, including predation, herbivory,
-bacterivory, parasitism, pathogenic, and parasitoid.
+freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). These
+food webs contain primary producers, herbivores, carnivores, parasites,
+and parasitoids and also contain various types of feeding interactions,
+including predation, herbivory, bacterivory, parasitism and pathogenic.
+The observed connectance of these food webs varies from 0.03 to 0.24 and
+the number of species varies from 29 to 239 species.
+
+The goodness of fit of the ADBM's predictions depends on the interaction
+types in the food webs with predictions that are more size-structured
+such as aquatic and herbivory interactions being better predicted when
+compared to less size-structured ones such as parasitoid and terrestrial
+herbivory ones (Petchey et al. 2008).
 
@@
 Common food web name (Original Publication) & Predation matrix source & General ecosystem & Number of species & Observed connectance & 95\% prediction interval of predicted connectance  (Gupta et al.
-(2022))\\
+2022)\\
 \hline
@@
 
-\hypertarget{op-need-a-section-on-how-the-food-web-model-was-fit-to-the-data.-also-should-state-how-we-deal-with-use-the-uncertainty-contained-in-the-posterior-joint-distribution.}{%
-\subsection{**OP: need a section on how the food web model was fit to
-the data. Also should state how we deal with / use the uncertainty
-contained in the posterior joint
-distribution.}\label{op-need-a-section-on-how-the-food-web-model-was-fit-to-the-data.-also-should-state-how-we-deal-with-use-the-uncertainty-contained-in-the-posterior-joint-distribution.}}
+\hypertarget{model-parameterisation-using-approximate-bayesian-computation}{%
+\subsection{Model parameterisation using approximate Bayesian
+computation}\label{model-parameterisation-using-approximate-bayesian-computation}}
 
-\hypertarget{primary-and-secondary-extinctions}{%
-\subsection{Primary and secondary
-extinctions}\label{primary-and-secondary-extinctions}}
+The ADBM was parameterised using approximate Bayesian computation (ABC)
+where a set of parameter values were sampled from the prior
+distributions. That set of parameter values was either accepted or
+rejected based on how close the predicted food web is to the observed
+food web using an accuracy metric -- true skill statistic (TSS). The
+accepted parameter values then formed a posterior distribution. Further,
+prediction intervals of the true skill statistic and connectance of the
+predicted food webs were computed. In our study, we considered food webs
+where the predicted connectance lay within the 95\% prediction interval.
+A detailed explanation of the parameterisation method can be found in
+Gupta, Furrer, and Petchey (2022).
+
+\hypertarget{extinction-scenarios-and-robustness}{%
+\subsection{Extinction scenarios and
+robustness}\label{extinction-scenarios-and-robustness}}
 
 We implemented the primary species removal method from Jennifer A. Dunne
-and Williams (2009) by sequentially removing species using one of three
-criteria: removal of (i) the most-connected species, (ii) the
+and Williams (2009) by sequentially removing species using one of the
+three criteria: removal of (i) the most-connected species, (ii) the
 least-connected species and (iii) randomly chosen species. The
 most-connected and least-connected criteria are based on the degree
-(i.e.~total number of links to resources and from consumers) of species.
-Given a primary removal if any remaining species lost all of their
-resource species, or any cannibalistic species lost all of their
-resource species except the cannibalistic links, they are removed from
-the web and a secondary extinction was recorded. Secondary extinctions
-may cause further secondary extinctions, which were also checked for and
-recorded. One no more secondary extinctions occured, then another
-primary extinctions was made, of the next appropriate species. This
-process was carried out until all species were extinct from the web.
+(i.e.~the total number of links to resources and from consumers) of
+species. We considered these mentioned criteria because the random
+extinction scenario takes into account all the theoretically possible
+extinction sequences of species that can occur in a food web and the
+extinction of most-connected species and least-connected species takes
+into account the two opposite extreme scenarios. These extinction
+scenarios have been widely used in studying species extinctions and
+collapse of food webs and other networks (Jennifer A. Dunne, Williams,
+and Martinez 2002b; Sol'e and Montoya 2001; J. Dunne, Williams, and
+Martinez 2004; Jennifer A. Dunne and Williams 2009; Albert and Barab'asi
+2002).
 
-\hypertarget{calculating-robustness}{%
-\subsection{Calculating robustness}\label{calculating-robustness}}
+Given a primary removal of species in a food web if any remaining
+species lost all of their resource species, or any cannibalistic species
+lost all of their resource species except the cannibalistic links, they
+are removed from the web and a secondary extinction was recorded.
+Secondary extinctions may cause further secondary extinctions, which
+were also checked for and recorded. Once no more secondary extinctions
+occurred, then another primary extinction was made, of the next
+appropriate species depending on the extinction scenario. This process
+was carried out until all the species were extinct from the food web.
 
-Robustness (R) of food web was quantified as the proportion of species
-subjected to primary removals that resulted in a loss (i.e.~primary
-removals plus secondary extinctions) of some specified proportion of the
-species. In our study, we use \(R_{50}\), the number of primary
-extinctions divided by the total number of species, that result in at
-least 50 per cent of total species loss (Jennifer A. Dunne, Williams,
-and Martinez 2002b; J. Dunne, Williams, and Martinez 2004; Jennifer A.
-Dunne and Williams 2009). Therefore, if primary extinctions never cause
-any secondary extinctions, the food web is maximally robust and
-(\(R_{50} = 0.50\)). Whereas in a minimally robust community
-(\(R_{50} = 1/S\)), since the first primary extinction causes as cascade
-of secondary extinctions of at least nearly half of the species in the
-food web (i.e.~at least \(S/2 - 1\)).
+The robustness (R) of a food web was defined as the proportion of
+species subjected to primary removals that resulted in a set of
+extinction (i.e.~primary removals plus secondary extinctions) of some
+specified proportion of the species. In our study, we use \(R_{50}\),
+the number of primary extinctions divided by the total number of
+species, which results in at least 50\% of total species loss (Jennifer
+A. Dunne, Williams, and Martinez 2002b; J. Dunne, Williams, and Martinez
+2004; Jonsson et al. 2015; Jennifer A. Dunne and Williams 2009).
+Therefore, if primary extinctions never cause any secondary extinctions,
+the food web is maximally robust and (\(R_{50} = 0.50\)). Whereas in a
+minimally robust community (\(R_{50} = 1/S\)), the first primary
+extinction causes a cascade of secondary extinctions of at least nearly
+half of the species in the food web (i.e.~at least \(S/2 - 1\)).
+
+\hypertarget{simulating-species-extinctions}{%
+\subsection{Simulating species
+extinctions}\label{simulating-species-extinctions}}
+
+First, we simulated primary species loss in food webs predicted by the
+ADBM which had the maximum true skill statistics and compared it to
+primary species loss in observed food webs. Second, to take into account
+the uncertainty in robustness in the ADBM predicted food webs we
+simulated primary species loss and thereby computed robustness for all
+the ADBM predicted food webs corresponding to the 95\% prediction
+interval of the predicted connectance. In the case of the random
+extinction scenario, we simulated 1000 random extinction sequences in a
+single ADBM predicted food web.
+
+\hypertarget{statistical-analysis}{%
+\subsection{Statistical analysis}\label{statistical-analysis}}
+
+In the random extinction scenario, we computed robustness \(R_{50}\) for
+all 1000 independent random extinction sequences and calculated the
+median as a summary statistics to quantify the average robustness of a
+single food web. To quantify the effect of undersampling
+i.e.~overestimation of connectance we compute the ratio of the
+difference in normalised robustness between the ADBM predicted food webs
+and observed food webs to the difference in their normalised
+connectance, where normalisation was performed by dividing the variables
+by their maximum possible values (I.e 0.5 for \(R_{50}\) and 1 for
+connectance). However, we did not perform any statistical significance
+test because we work with simulated food webs and therefore the p-values
+of these tests are influenced by the number of model simulations (White
+et al. 2014).
 
@@
 
-\hypertarget{show-and-describe-the-secondary-extinction-curves}{%
-\subsection{Show and describe the secondary extinction
-curves}\label{show-and-describe-the-secondary-extinction-curves}}
+We first present the secondary extinction curves of the ADBM predicted
+food webs which had the maximum true skill statistics and the observed
+food webs for 12 food webs under three different extinction scenarios.
+We then compare the robustness of all the ADBM predicted food webs
+within the 95\% prediction interval against that of the observed food
+webs to take into account uncertainty in the robustness across food webs
+predictions. Finally we quantify the effect of overestimation of
+connectance on the difference in their robustness estimates.
 
-In Fig. \ref{fig:fig_r1}, \ref{fig:fig_r2} and \ref{fig:fig_r3}, we show
-the secondary extinction curves of ADBM predicted food webs and observed
-food webs for 12 different food webs under three different extinction
-scenarios. We found that the cumulative secondary extinction was higher
-for the ADBM predicted food webs as compared to the observed food webs
-for nine, nine and seven food webs.
+\hypertarget{secondary-extinctions}{%
+\subsection{Secondary extinctions}\label{secondary-extinctions}}
 
-In general, irrespective of the extinction scenarios, we found that the
-cumulative secondary extinction was higher for the ADBM predicted food
-webs as compared to the observed food webs for most of the food webs
-\textbf{OP: this is not so clear to me. State how many cases? It seems
-there are many cases where secondary extinctions are more numerous in
-the observed food web: blue line above the red.}.
-
-In the most connected extinction scenario, the cumulative secondary
-extinction curve for the observed food webs rose quickly as compared to
-the ADBM predicted food webs, and then reach saturation after a certain
-number of primary removal of species. In some of the food webs (Fig.
-\ref{fig:fig_r1} (f, g, h, i, j, k)), there were intersection between
-the cumulative secondary extinction curves of ADBM predicted food webs
-and that of the observed food webs. In case of the Broadstone Stream
-(taxonomic aggregation) food web and the Tuesday Lake food web (Fig.
-\ref{fig:fig_r1} (b and k)), the secondary extinction curves for the
-ADBM food webs were higher than the observed food webs, whereas in case
-of the Skipwith Pond food web (Fig. \ref{fig:fig_r1} (i)), there were no
-secondary extinctions for any given number of primary removal of
-species.
+In the most-connected extinction scenario, the cumulative secondary
+extinction curves started to rise steeply at a lower number of primary
+species removal in the observed food webs as compared to the ADBM
+predicted food webs for nine food webs (Fig. \ref{fig:fig_r1} (a, c, d,
+e, f, g, h, j, l)). However there were higher number of cumulative
+secondary extinctions occurring in the ADBM predicted food webs when
+compared to that of the observed food webs at a high number of primary
+species removal (Fig. \ref{fig:fig_r1} (a, f, g, h, k)). In the Skipwith
+Pond food web, there were no secondary extinctions for any number of
+primary removal of species (Fig. \ref{fig:fig_r1} (i)), whereas in the
+Broadstone Stream (taxonomic aggregation) food web the same was true
+only for the observed food web but in the ADBM predicted food web there
+was a steep rise in the cumulative secondary extinctions (Fig.
+\ref{fig:fig_r1} (b)).
 
@@
 
-{\centering \includegraphics[width=400px]{../results/plot_mostconnected}
+{\centering \includegraphics[width=400px]{../results/plot_mostconnected_maxTSS}
 
@@
 
-\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary **removals of the most connected species** for 12 food webs.
+\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of the most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 
-Except Broadstone Stream (taxonomic aggregation), Broadstone Stream
-(size aggregation) and Tuesday Lake food webs (Fig. \ref{fig:fig_r2} (b,
-c and k)), the \textbf{mean cumulative secondary extinction curves}
-\textbf{OP: must be explained somewhere how/why this is a mean} for all
-the other food webs predicted by the ADBM were always lower than that of
-the observed food webs in the random extinction scenario. The shape of
-the cumulative secondary extinctions curves varied across the food webs.
+In Fig. \ref{fig:fig_r2}, we present the cumulative secondary
+extinctions in the ADBM predicted and the observed food webs for five
+(out of 1000) independent random extinction sequences to show
+qualitative differences between their secondary extinction curves. The
+secondary extinctions in the ADBM predicted food webs were more abrupt
+than that in the observed food webs.
 
@@
 
-{\centering \includegraphics[width=400px]{../results/plot_random}
+{\centering \includegraphics[width=400px]{../results/plot_ra_extlines_maxTSS}
 
@@
 
-\caption{\label{fig:fig_r2} Mean cumulative secondary extinctions of species resulting from the primary **removals of random species** for 12 food webs.
+\caption{\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
 S denotes the number of species in a food web.
@@
 
-Compared to the most connected and random extinction scenarios, the
-cumulative extinction curves in the least connected extinction scenario
-had very low values and were flat for most of the food webs (Fig.
-\ref{fig:fig_r3}) compared to the most connected extinction and random
-extinction scenarios. In most of the food webs, there was a lot of
-overlap between the extinction curves of the ADBM predicted food webs
-and the observed food webs.
+Compared to the most-connected and random extinction scenarios, there
+were fewer secondary extinctions in the least-connected extinction
+scenario and therefore the secondary extinction curves were flat for
+most of the food webs (Fig. \ref{fig:fig_r3}). In some of the food webs,
+the extinction curves of the ADBM predicted food webs overlapped with
+the observed food webs (Fig. \ref{fig:fig_r3} (b, c, g, h, i, k, l)\}).
+Contrary to the most-connected scenario, there was a very high number of
+secondary extinctions occurring at very low number of primary species
+removal (Fig. \ref{fig:fig_r3} (a, d, e, f, j)).
 
@@
 
-{\centering \includegraphics[width=400px]{../results/plot_leastconnected}
+{\centering \includegraphics[width=400px]{../results/plot_leastconnected_maxTSS}
 
@@
 
-\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary **removals of the least connected species** for 12 food webs.
+\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of the least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 
-\textbf{OP: write text describing the effect sizes, e.g.~how big is the
-difference between observed and ADBM webs.}
+\hypertarget{robustness}{%
+\subsection{Robustness}\label{robustness}}
 
-\hypertarget{show-and-describe-the-following}{%
-\subsection{Show and describe the
-following:}\label{show-and-describe-the-following}}
+The ADBM predicted food webs were more robust than the observed food
+webs on average in the most-connected and random extinction scenarios
+(Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in
+the robustness within the ADBM predicted food webs in the most-connected
+extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the ADBM
+predicted Caricaie Lakes food web was more robust than the observed food
+web on average but had a larger variation in the robustness within the
+ADBM predicted food webs compared to other food webs.
 
-I suggest to focus on the relationship between (difference in robustness
-between observed and predicted connectance) and (difference in
-robustness between the observed and predicted food web). \textbf{OP: I
-miss text describing this relationship.} \textbf{OP: Allow the panels in
-the figure to have different y-axis scales.}
+The food webs were more robust to the random extinction scenario than
+the most-connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
+and Benguela Pelagic food webs had more variations in robustness within
+the ADBM predicted food webs as compared to the other food webs (Fig.
+\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
+aggregation) and Broadstone Stream (size aggregation) food webs were the
+most robust (Median \(R_{50} = 0.5\)) for both ADBM predicted and
+observed food webs. Although there were few less robust ADBM predicted
+food webs in the Broadstone Stream (size aggregation) as shown by the
+outliers.
 
-\textbf{OP: This paragraph should go in the previous section}. The ADBM
-predicted food webs were more robust than the observed food web with
-some exceptions (Fig. \ref{fig:fig_r4}). The food webs were more robust
-to least connected and random extinction scenarios than the primary
-deletion of the most connected species. The difference in the robustness
-values between the ADBM predicted food webs and observed food webs was
-higher in the most connected extinction scenario as compared to the
-least connected extinction and random extinction scenarios.
+In the least-connected extinction scenario, the food webs had a very
+high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
+(Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
+ADBM predicted food webs for Small Reef and Benguela Pelagic had very
+low median robustness. Benguela Pelagic, Broom and Capinteria food webs
+from the ADBM had larger variations in robustness when compared to that
+of the others.
 
@@
 
-\caption{\label{fig:fig_r4} Robustness plots for 12 food webs across different ecosystems.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).}\label{fig:unnamed-chunk-5}
+\caption{\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems.
+Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).
+Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.
+Some points are not visible due to perfect overlap in b and c.
+Refer to Fig.
+7 in the Supplementary Information for a faceted visualisation.}\label{fig:unnamed-chunk-5}
 \end{figure}
 
-AG: I will also update the robustness plot for random extinction (Fig. 4
-(b)) once the simulation is completed. The one shown here is only for
-few simulations and as a placeholder. It takes more time to compute.
+In all of the food webs except Small Reef and Broadstone Stream
+(taxonomic aggregation), the effect size was positive on average in the
+most-connected extinction scenario (Fig. \ref{fig:fig_r5} (a))
+i.e.~overestimation of connectance had a positive effect on the
+robustness. In the random extinction scenario, there was a positive
+effect of overestimation of connectance on the robustness for Ythan,
+Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom
+and Benguela Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect
+size varied across the food webs. In the least-connected extinction
+scenario, the overestimation of connectance had little effect on average
+on the difference in the robustness (Fig. \ref{fig:fig_r5} (c)).
+
+\begin{figure}
+
+{\centering \includegraphics[width=450px]{../results/plot_R50_slope}
+
+}
+
+\caption{\label{fig:fig_r5} Effect size (i.e ratio of difference in normalised robustness between ADBM predicted food webs and observed food webs to difference in their normalised connectance) shown for the 12 food webs.
+Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-6}
+\end{figure}
 
@@
 The primary removal of species revealed that the ADBM predicted food
-webs are more robust than the observed food webs, and the shape of the
-robustness extinction curves varies between food webs.
+webs are more robust than the observed food webs on average, with
+variation within the robustness of the ADBM predicted food webs in the
+12 food web ecosystems suggesting that undersampling in food webs can
+lead to differences in the estimates of food web robustness. The food
+webs are least robust to primary extinction of the most connected
+species scenario compared to that of least connected and random
+extinction scenarios on average. A future development would be to
+understand how undersampling i.e.~overestimation of connectance
+influences the stability of the dynamics of the ADBM predicted food webs
+against that of the observed food webs, and compare it with our study.
 
-The food webs are least robust to primary extinction of the most
-connected species scenario compared to that of least connected and
-random extinction scenarios. A future development would be to understand
-the stability of the dynamics of the ADBM predicted food webs and
-compare it with our study.
+The robustness of the ADBM predicted food webs were higher than that of
+the observed food webs on average (Fig. \ref{fig:fig_r4}) for all of the
+12 food web ecosystems with some exceptions. This can be attributed to
+the higher connectance of the ADBM predicted food webs as compared to
+that of the observed food webs because a species in a food web with a
+higher connectance has on average more trophic links as compared to a
+food web with a lower connectance (Fig. \ref{fig:fig_r5}). Our study
+suggests that it is important to consider undersampling in observed food
+webs when computing their robustness.
 
-\ldots{}
+The findings from our study are similar to what had been documented for
+other food web models (Jennifer A. Dunne and Williams 2009), in terms of
+an increase in the robustness when the connectance of a food web is
+increased. However, contrary to general expectations (Jennifer A. Dunne,
+Williams, and Martinez 2002a), food web robustness did not always
+increase with the connectance (Fig. \ref{fig:fig_r5}). The ADBM
+consistently predicted higher connectance than that of the observed food
+webs however, in some cases an increase in connectance resulted in lower
+robustness (Fig. \ref{fig:fig_r5}) in the predicted food web. For
+example: the Benguela Pelagic and Small Reef food webs were surprisingly
+less robust to primary extinctions on average in the least-connected
+extinction scenario (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5}
+(c)). We suspect this is because the ADBM is underestimating the
+proportion of basal species in the predicted food webs when compared to
+that of the observed food webs (Fig: 6 (a) in Gupta, Furrer, and Petchey
+(2022)). As a result, these low degree basal species are the ones to be
+removed at an early stage in the deletion sequence thereby resulting in
+an earlier food web collapse in the ADBM predicted food web as compared
+to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
+This suggests that the overestimation of connectance by the ADBM
+resulted in a more robust food web on average but differences in the
+predicted food web properties such as underestimation of the proportion
+of basal species and overestimation of the maximum trophic level (Fig:
+\ref{fig:fig_a1}) counteracted that effect and led to reduced
+robustness. This suggests that food web properties other than
+connectance play an important role in determining the robustness of a
+food web and therefore should be also taken into account.
 
-\hypertarget{what-does-overestimation-of-connectance-imply-in-terms-of-stability}{%
-\subsection{What does overestimation of connectance imply in terms of
-stability?}\label{what-does-overestimation-of-connectance-imply-in-terms-of-stability}}
+The ADBM based on its size-based rules predicts the diet of a consumer
+and hence is able to predict some links in the predicted food webs which
+do in reality occur but are actually not observed in the observed food
+webs perhaps because of low sampling effort. A future study could be to
+extend our study to use other food webs models based on size-based rules
+such as Gravel et al. (2013) and Vagnon et al. (2021) and compare them
+with our study. We expect similar results because these food webs are
+also based on body size rules.
 
-For most of the food webs, the primary removals of species resulted in a
-higher secondary extinction in the ADBM predicted food webs than that of
-the observed food webs (Fig. \ref{fig:fig_r1}, \ref{fig:fig_r2} and
-\ref{fig:fig_r3}). This can be attributed to the higher connectance of
-the ADBM predicted food webs as compared to that of the observed food
-webs because a species in a food web with a high connectance has on
-average more number of trophic links as compared to the food webs with
-low connectance. \textbf{OP: should here cite figure 4.}
+As with any food web model, we expect that there are real false
+positives in the food webs predicted by the ADBM. Firstly this may be
+because the ADBM uses only body size as a trait. A trait uncorrelated
+with the body size may be influential in determining the interaction
+between two species (Gupta, Furrer, and Petchey 2022). Secondly, the
+ADBM can only predict diets that are contiguous with respect to the size
+of the prey. I.e. it cannot predict that the consumer will consume prey
+of size 1 and 3, and not consume prey of size 2. However, it is
+important to note that observed diets are not always contiguous when
+prey are ordered by their size due to some ecological differences in how
+predator species choose their prey (Caron et al. 2022). Therefore a
+future study could extend our study with other food web models which are
+not based on body size such as Cattin et al. (2004) and Allesina,
+Alonso, and Pascual (2008). We expect to have a difference in results
+based on whether the trophic interactions in the food webs are governed
+by size-structured rules or not.
 
 It would be intriguing to know if this difference in connectance has a
-similar influence in the dynamical stability of the food webs as well.
-Hence, a future prospect could be to use a dynamical model (for example:
-bionergetic food web model (Brose, Williams, and Martinez 2006)) to
-model the temporal dynamics of the ADBM predicted food webs. It would be
-interesting to know the temporal stability of these ADBM predicted food
-webs compared to the observed food webs because it has been known that
-food webs with increasing connectance stability diminishes (May 1972).
+similar influence on the dynamical stability of the food webs as well.
+Hence, a prospect could be to use a dynamical model (for example
+bioenergetic food web model by Brose, Williams, and Martinez (2006)) to
+model the temporal dynamics of the ADBM predicted food webs. We expect
+that the difference in dynamical robustness of the ADBM predicted and
+the observed food webs would be similar to differences in their
+topological robustness because the dynamical robustness of the ADBM
+predicted and the observed food webs would be both underestimated when
+compared to their topological robustness (Curtsdotter et al. 2011).
 
-\ldots{}
+Since the ADBM underestimates the proportion of basal species and
+overestimates the maximum trophic level in the predicted food webs
+compared to that of the observed food webs, it would be interesting to
+use these properties as summary statistics to parameterise the ADBM and
+investigate how that influences the difference in the robustness between
+the ADBM predicted and the observed food webs.
 
-Include here the possibility that the increased connectance would
-influence dynamical stability, and state if and why this may increase or
-decrease stability.
+We have used a food web model to compensate for undersampling in
+recorded food webs and thereby quantified the influence of missing links
+i.e.~overestimation of connectance on the topological robustness of 12
+food webs from various ecosystems. We found that the overestimation of
+connectance can have large impacts on the robustness of the food webs
+with variation in robustness among the predicted food webs which have
+also been influenced by differences in the structural food web
+properties between the ADBM predicted food webs and the observed food
+webs.
 
-\hypertarget{explain-that-the-adbm-can-only-predicts-contiguous-diets-op-and-the-implications-of-this}{%
-\subsection{Explain that the ADBM can only predicts contiguous diets
-{[}OP{]} and the implications of
-this}\label{explain-that-the-adbm-can-only-predicts-contiguous-diets-op-and-the-implications-of-this}}
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
 
-Using only body size as a trait, the ADBM can only predict diets that
-are contiguous with respect to the size of the prey. I.e. it cannot
-predict that a predator will consume prey of size 1 and 3, and not
-consume prey of size 2. Also, it is important to note that the observed
-diets were not contiguous when prey are ordered by their size, and this
-is due to some ecological differences in how predator group choose their
-prey (Caron et al. 2022). So, the parameterisation process lead to a
-greater number of predicted links than observed.
+This work was supported by the University Research Priority Program
+Global Change and Biodiversity (Grant number: U-704-04-11) of the
+University of Zurich.
 
-This higher connectance in the ADBM predicted food webs has lead to a
-higher robustness of the ADBM predicted food webs. An important question
-to ask here is how reliable are these results. We suspect that both the
-model and the observed data are wrong to some extent. We expect that
-some of the links that do in reality occur are not present in the
-observed datasets, which is quite possible because of low sampling
-effort or rare prey-predator interactions even when there is intensive
-sampling. This would mean that the false positives may actually be a
-correctly predicted link.
+\hypertarget{conflict-of-interest}{%
+\section{Conflict of interest}\label{conflict-of-interest}}
 
-We suspect that the model is also predicting links which actually do not
-occur. This is because the current ADBM model only takes body size
-trait, and therefore only predicts contiguous diet. That would mean any
-interaction that is not possible because of some other traits not
-correlated with the body size would still be predicted by the model. For
-example, a species might have a defensive trait that could result in the
-predator species not predating on that species at all.
+None declared
 
-AG: (Caution) Some of the texts might be very similar to or same as in
-C1 MS. With multiple iterations of the current ms, the current text
-would be altered. Also, the current ms would be checked using a
-plagiarism software before submission.
+\hypertarget{author-contributions}{%
+\section{Author contributions}\label{author-contributions}}
 
-\ldots{}
+\textbf{Anubhav Gupta:} Conceptualisation; Data curation; Formal
+analysis; Investigation; Methodology; Project administration; Software;
+Validation; Writing -- original draft; Writing -- review and editing.
+\textbf{Owen L. Petchey:} \textbf{AG:} Owen, Could you please add your
+contributions here?
 
-\hypertarget{compare-the-results-from-our-study-with-results-from-other-food-web-models-jennifer-a.-dunne-and-williams-2009}{%
-\subsection{Compare the results from our study with results from other
-food web models (Jennifer A. Dunne and Williams
-(2009))}\label{compare-the-results-from-our-study-with-results-from-other-food-web-models-jennifer-a.-dunne-and-williams-2009}}
+\hypertarget{data-accessibility-statement}{%
+\section{Data Accessibility
+Statement}\label{data-accessibility-statement}}
 
-The findings from our study is similar to what had been documented for
-other food web models (Jennifer A. Dunne and Williams 2009), in terms of
-increase in the robustness when the connectance of the food web is
-increased. A future study could be to understand the robustness of other
-food web models (Gravel et al. 2013) and compare it with our study. We
-expect similar results.
+To be added
 
-{[}OP{]} Including if and why we expect our findings to be replicated
-with those other models. Include some of Gravel and Poissot's models
+\hypertarget{supplementary-information}{%
+\section{Supplementary Information}\label{supplementary-information}}
 
-\ldots{}
+\begin{figure}
+
+{\centering \includegraphics[width=450px]{../results/plot_max_tl_ADBM_vs_emp}
+
+}
+
+\caption{\label{fig:fig_a1} Maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
+Box represent 25th and 75th percentile; bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-7}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=450px]{../results/plot_R50_ADBM_vs_obs_ra_lc_facet}
+
+}
+
+\caption{\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
+Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).
+Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-8}
+\end{figure}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-albertStatisticalMechanicsComplex2002}{}}%
+Albert, R'eka, and Albert-L'aszl'o Barab'asi. 2002. {``Statistical
+Mechanics of Complex Networks.''} \emph{Reviews of Modern Physics} 74
+(1): 47--97. \url{https://doi.org/10.1103/RevModPhys.74.47}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-allesinaGeneralModelFood2008}{}}%
+Allesina, Stefano, David Alonso, and Mercedes Pascual. 2008. {``A
+{General Model} for {Food Web Structure}.''} \emph{Science} 320 (5876):
+658--61. \url{https://doi.org/10.1126/science.1156269}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-bergUsingSensitivityAnalysis2011}{}}%
@@
 \url{https://doi.org/10.1111/ele.13966}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cattinPhylogeneticConstraintsAdaptation2004}{}}%
+Cattin, Marie-France, Louis-F'elix Bersier, Carolin Banašek-Richter,
+Richard Baltensperger, and Jean-Pierre Gabriel. 2004. {``Phylogenetic
+Constraints and Adaptation Explain Food-Web Structure.''} \emph{Nature}
+427 (6977, 6977): 835--39. \url{https://doi.org/10.1038/nature02327}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-curtsdotterRobustnessSecondaryExtinctions2011a}{}}%
+Curtsdotter, Alva, Amrei Binzer, Ulrich Brose, Francisco de Castro, Bo
+Ebenman, Anna Eklöf, Jens O. Riede, Aaron Thierry, and Björn C. Rall.
+2011. {``Robustness to Secondary Extinctions: {Comparing} Trait-Based
+Sequential Deletions in Static and Dynamic Food Webs.''} \emph{Basic and
+Applied Ecology} 12 (7): 571--80.
+\url{https://doi.org/10.1016/j.baae.2011.09.008}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-guptaSimultaneouslyEstimatingFood2022}{}}%
+Gupta, Anubhav, Reinhard Furrer, and Owen L. Petchey. 2022.
+{``Simultaneously Estimating Food Web Connectance and Structure with
+Uncertainty.''} \emph{Ecology and Evolution} 12 (3): e8643.
+\url{https://doi.org/10.1002/ece3.8643}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-jonssonReliabilityR50Measure2015}{}}%
+Jonsson, Tomas, Sofia Berg, Alexander Pimenov, Catherine Palmer, and
+Mark Emmerson. 2015. {``The Reliability of {R50} as a Measure of
+Vulnerability of Food Webs to Sequential Species Deletions.''}
+\emph{Oikos} 124 (4): 446--57. \url{https://doi.org/10.1111/oik.01588}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-jordanoSamplingNetworksEcological2016}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-mayWillLargeComplex1972}{}}%
-May, Robert M. 1972. {``Will a {Large Complex System} Be {Stable}?''}
-\emph{Nature} 238 (5364): 413. \url{https://doi.org/10.1038/238413a0}.
+\leavevmode\vadjust pre{\hypertarget{ref-martinezDiversityComplexityPersistence}{}}%
+Martinez, Neo D, Richard J Williams, and Jennifer A Dunne. 2006.
+{``Diversity, {Complexity}, and {Persistence} in {Large Model
+Ecosystems},''} 24.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-pimmHumanImpactsRates2006}{}}%
+Pimm, Stuart, Peter Raven, Alan Peterson, Çağan H. Şekercioğlu, and Paul
+R. Ehrlich. 2006. {``Human Impacts on the Rates of Recent, Present, and
+Future Bird Extinctions.''} \emph{Proceedings of the National Academy of
+Sciences} 103 (29): 10941--46.
+\url{https://doi.org/10.1073/pnas.0604181103}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-soleComplexityFragilityEcological2001}{}}%
@@
 \url{https://doi.org/10.1098/rspb.2001.1767}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thomasExtinctionRiskClimate2004}{}}%
+Thomas, Chris D., Alison Cameron, Rhys E. Green, Michel Bakkenes, Linda
+J. Beaumont, Yvonne C. Collingham, Barend F. N. Erasmus, et al. 2004.
+{``Extinction Risk from Climate Change.''} \emph{Nature} 427 (6970,
+6970): 145--48. \url{https://doi.org/10.1038/nature02121}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-thomasComparativeLossesBritish2004}{}}%
+Thomas, J. A., M. G. Telfer, D. B. Roy, C. D. Preston, J. J. D.
+Greenwood, J. Asher, R. Fox, R. T. Clarke, and J. H. Lawton. 2004.
+{``Comparative {Losses} of {British Butterflies}, {Birds}, and {Plants}
+and the {Global Extinction Crisis}.''} \emph{Science} 303 (5665):
+1879--81. \url{https://doi.org/10.1126/science.1095046}.
 
@@
 \url{https://doi.org/10.1371/journal.pbio.2003446}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vagnonAllometricNicheModel2021}{}}%
+Vagnon, Chlo'e, Franck Cattan'eo, Chlo'e Goulon, David Grimardias, Jean
+Guillard, and Victor Frossard. 2021. {``An Allometric Niche Model for
+Species Interactions in Temperate Freshwater Ecosystems.''}
+\emph{Ecosphere} 12 (3): e03420.
+\url{https://doi.org/10.1002/ecs2.3420}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-whiteEcologistsShouldNot2014}{}}%
+White, J. Wilson, Andrew Rassweiler, Jameal F. Samhouri, Adrian C.
+Stier, and Crow White. 2014. {``Ecologists Should Not Use Statistical
+Significance Tests to Interpret Simulation Model Results.''}
+\emph{Oikos} 123 (4): 385--88.
+\url{https://doi.org/10.1111/j.1600-0706.2013.01073.x}.
 

### 2022-09-20 R/ADBM_ABC_fw_minTSS.R

@@ -1,0 +1,36 @@
+# Returns ADBM predicted food web with min TSS
+
+ADBM_ABC_fw_minTSS <- function(fw_name, fw_tol){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".RDS"))
+  
+  sel_ind <- which.max(ADBM_fw_all$dist)
+  ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}

### 2022-09-20 R/basal_species_fun.R

@@ -1,0 +1,13 @@
+# 2022.07.06
+# Returns an array of basal species
+
+basal_species_fun <- function(net){
+  
+  indeg <- rowSums(net)
+  outdeg <- colSums(net)
+  
+  basal_outdeg <- names(which(outdeg == 0))
+  indeg_zero <- names(which(indeg == 0))
+  
+  return(setdiff(basal_outdeg, indeg_zero))
+}

### 2022-09-20 R/largestbodymass_ext.R

@@ -1,0 +1,50 @@
+# 2022.08.02
+# Simulating extinction of species with largest body mass
+
+largestbodymass_ext <- function(net, bodysize){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  bodysize <- bodysize[not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  # Stop when all the species is extinct
+  while(all(is.na(new_net)) == FALSE){
+
+    node <- names(which.max(bodysize))
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    bodysize <- bodysize[rownames(new_net)]
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+      )
+    }
+    
+    k <- k + 1
+    # print(k)
+    
+  }
+  
+  return(dd)
+  
+  
+  
+}

### 2022-09-20 R/least_connected_ext.R

@@ -4,6 +4,13 @@
 least_connected_ext <- function(net){
   
   dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
   new_net <- net
   k <- 1
   ext_list <- list()
@@ -17,7 +24,7 @@ least_connected_ext <- function(net){
     min_totdeg <- which.min(totdeg)
     node <- names(min_totdeg)
     
-    ext_list[[k]] <- sim_single_ext(net = new_net, node = node)
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
     new_net <- ext_list[[k]]$net
     
     if(k != 1){

### 2022-09-20 R/least_connected_ext_wo_basal.R

@@ -1,0 +1,58 @@
+# 2022.07.22
+# Simulating extinction for least connected nodes
+# Do not remove basal nodes
+
+least_connected_ext_wo_basal <- function(net){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  wo_basal <- setdiff(rownames(new_net), basal_species)
+  net_wo_basal <- new_net[wo_basal, wo_basal]
+  
+  # Stop when all the species is extinct
+  while(all(is.na(net_wo_basal)) == FALSE){
+    indeg <- rowSums(new_net)
+    outdeg <- colSums(new_net)
+    totdeg <- indeg + outdeg
+    
+    not_basal_species <- setdiff(names(totdeg), basal_species)
+    
+    min_totdeg <- which.min(totdeg[not_basal_species])
+    node <- names(min_totdeg)
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    
+    wo_basal <- setdiff(rownames(new_net), basal_species)
+    net_wo_basal <- new_net[wo_basal, wo_basal]
+    
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+      )
+    }
+    
+    k <- k + 1
+    # print(k)
+  }
+  
+  return(dd)
+  
+}

### 2022-09-20 R/maxgenerality_ext.R

@@ -1,0 +1,47 @@
+# 2022.08.02
+# Simulating extinction for species with maximum generality
+
+maxgenerality_ext <- function(net){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  # Stop when all the species is extinct
+  while(all(is.na(new_net)) == FALSE){
+    outdeg <- colSums(new_net)
+    
+    max_outdeg <- which.max(outdeg)
+    node <- names(max_outdeg)
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+      )
+    }
+    
+    k <- k + 1
+    # print(k)
+    
+  }
+  
+  return(dd)
+  
+}

### 2022-09-20 R/most_connected_ext.R

@@ -4,6 +4,13 @@
 most_connected_ext <- function(net){
   
   dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
   new_net <- net
   k <- 1
   ext_list <- list()
@@ -17,7 +24,7 @@ most_connected_ext <- function(net){
     max_totdeg <- which.max(totdeg)
     node <- names(max_totdeg)
     
-    ext_list[[k]] <- sim_single_ext(net = new_net, node = node)
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
     new_net <- ext_list[[k]]$net
     
     if(k != 1){

### 2022-09-20 R/most_connected_ext_wo_basal.R

@@ -1,0 +1,59 @@
+# 2022.07.22
+# Simulating extinction for most connected nodes
+# Do not remove basal nodes
+
+
+most_connected_ext_wo_basal <- function(net){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  wo_basal <- setdiff(rownames(new_net), basal_species)
+  net_wo_basal <- new_net[wo_basal, wo_basal]
+  
+  # Stop when all the species is extinct
+  while(all(is.na(net_wo_basal)) == FALSE){
+    indeg <- rowSums(new_net)
+    outdeg <- colSums(new_net)
+    totdeg <- indeg + outdeg
+    
+    not_basal_species <- setdiff(names(totdeg), basal_species)
+    
+    max_totdeg <- which.max(totdeg[not_basal_species])
+    node <- names(max_totdeg)
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    
+    wo_basal <- setdiff(rownames(new_net), basal_species)
+    net_wo_basal <- new_net[wo_basal, wo_basal]
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+      )
+    }
+    
+    k <- k + 1
+    # print(k)
+    
+  }
+  
+  return(dd)
+  
+}

### 2022-09-20 R/mostabundant_ext.R

@@ -1,0 +1,51 @@
+# 2022.08.02
+# Simulating extinction of species with most abundance
+
+mostabundant_ext <- function(net, bodysize){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  bodysize <- bodysize[not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  # Stop when all the species is extinct
+  while(all(is.na(new_net)) == FALSE){
+    
+    ## Using the body mass abundance scaling
+    ## Largest body size has the lowest abundance
+    node <- names(which.min(bodysize))
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    bodysize <- bodysize[rownames(new_net)]
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+      )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+      )
+    }
+    
+    k <- k + 1
+    # print(k)
+    
+  }
+  
+  return(dd)
+  
+  
+}

### 2022-09-20 R/random_ext_parallel_wo_basal.R

@@ -1,0 +1,30 @@
+# 25.11.2021
+
+
+random_ext_parallel_wo_basal <- function(net, nsim, n_cores){
+  
+  nsim_pcore <- nsim/n_cores
+  registerDoParallel(cores = n_cores)
+  
+  res_pcores <- foreach(i = 1:n_cores, .combine = rbind) %dopar% 
+    {
+      set.seed(i)
+      result <- random_ext_wo_basal(net = net, nsim = nsim_pcore)
+      list(result)
+    }
+  
+  result_all <- res_pcores[[1]]
+  
+  for(i in 2:n_cores){
+    result_all <- rbind(result_all, 
+                        res_pcores[[i]] %>%
+                          mutate(nsim = (i-1)*nsim_pcore + nsim)
+    ) 
+  }
+  
+  return(result_all)  
+}
+
+
+
+

### 2022-09-20 R/random_ext_wo_basal.R

@@ -1,0 +1,51 @@
+# 2022.07.25
+# Simulating extinctions for random nodes (without basal species)
+
+random_ext_wo_basal <- function(net, nsim){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  for(sim_ind in 1:nsim){
+    dd_temp <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+    new_net <- net
+    k <- 1
+    ext_list <- list()
+    
+    wo_basal <- setdiff(rownames(new_net), basal_species)
+    
+    while(length(wo_basal) != 0){
+      pool_node <- wo_basal
+      
+      node <- sample(x = pool_node, size = 1)
+      
+      ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+      new_net <- ext_list[[k]]$net
+      
+      wo_basal <- setdiff(rownames(new_net), basal_species)
+      
+      if(k != 1){
+        dd_temp <- rbind(dd_temp, 
+                         data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                                    acc_sec_ext = ext_list[[k]][[2]] + dd_temp$acc_sec_ext[k-1], nsim = sim_ind)
+        )
+      } else {
+        dd_temp <- rbind(dd_temp, 
+                         data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                                    acc_sec_ext = ext_list[[k]][[2]], nsim = sim_ind)
+        )
+      }
+      
+      k <- k + 1
+      # print(k)
+    }
+    dd <- rbind(dd, dd_temp)
+  }
+  
+  return(dd)
+}

### 2022-09-20 R/sim_single_ext.R

@@ -24,6 +24,7 @@ sim_single_ext <- function(net, node){
   
   node_to_sec_ext <- which(outdeg[as.logical(node_pred)] == 1)
   
+  
   if(length(node_to_sec_ext) != 0){
     new_net_2 <- new_net[!rownames(new_net) %in% names(node_to_sec_ext), !colnames(new_net) %in% names(node_to_sec_ext)]
     if(length(new_net_2) == 1){
@@ -32,7 +33,7 @@ sim_single_ext <- function(net, node){
       rownames(new_net_2) <- lost_node
       colnames(new_net_2) <- lost_node
     }
-  } else {
+  } else { ## If there are no predator of the primary node (the one which is removed)
     new_net_2 <- new_net
   }
   

### 2022-09-20 R/sim_single_ext_v2.R

@@ -1,3 +1,58 @@
 # 2022.07.06
-# Simulating single primary extinction in a food web
+# Simulating single primary extinction in a food web i.e removing given node from a given food web
 # Calculating secondary extinction 
+# Ensure that the input network "net" does not have any isolated nodes
+
+
+sim_single_ext_v2 <- function(net, node, basal_species){
+  
+  indeg <- rowSums(net)
+  outdeg <- colSums(net)
+  
+  totdeg <- indeg + outdeg
+  
+  new_net <- net[!rownames(net) %in% node, !colnames(net) %in% node]
+  
+  if(length(new_net) == 1){
+    new_net <- as.matrix(new_net)
+    lost_node <- setdiff(rownames(net), node)
+    rownames(new_net) <- lost_node
+    colnames(new_net) <- lost_node
+  }
+  
+  sp_outdeg_zero <- names(which(colSums(new_net) == 0))
+  sp_outdeg_zero_wo_basal <- setdiff(sp_outdeg_zero, basal_species)
+  
+  count <- 1
+  n_sec_ext <- length(sp_outdeg_zero_wo_basal)
+  while(length(sp_outdeg_zero_wo_basal) != 0){
+    
+    node_to_sec_ext <- sp_outdeg_zero_wo_basal
+    new_net_2 <- new_net[!rownames(new_net) %in% node_to_sec_ext, !colnames(new_net) %in% node_to_sec_ext]
+    
+    if(length(new_net_2) == 1){
+      new_net_2 <- as.matrix(new_net_2)
+      lost_node <- setdiff(rownames(new_net), node_to_sec_ext)
+      rownames(new_net_2) <- lost_node
+      colnames(new_net_2) <- lost_node
+    }
+    
+    sp_outdeg_zero <- names(which(colSums(new_net_2) == 0))
+    sp_outdeg_zero_wo_basal <- setdiff(sp_outdeg_zero, basal_species)
+    
+    n_sec_ext <- n_sec_ext + length(sp_outdeg_zero_wo_basal)
+    # print(count)
+    count <- count + 1
+    new_net <- new_net_2
+  }
+  
+  if(count > 1){
+    list_ret <- list(net = new_net_2, n_sec_ext = n_sec_ext)
+  } else {
+    new_net_2 <- new_net
+    list_ret <- list(net = new_net_2, n_sec_ext = n_sec_ext)
+  }
+  
+  return(list_ret)
+}
+

### 2022-09-20 inst/main/calc_fw_prop.R

@@ -1,0 +1,118 @@
+## 2022.09.06
+## Calculate food web properties: Max trophic level
+
+
+max_tl_ADBM_fun <- function(foodweb){
+  
+  fw <- foodweb
+  max_tl_ADBM_all <- c()
+  
+  library(R.utils)
+  library(readxl)
+  library(cheddar)
+  
+  sourceDirectory("R", modifiedOnly = FALSE)
+  sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+
+  metadata <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+  fw_tol_loc <- metadata$dist_rej[metadata$foodweb == fw]
+  
+  for(nsim_loc in 1:1000){
+    pred_mat <- ADBM_ABC_fw_all(fw_name = fw, fw_tol = fw_tol_loc, nsim = nsim_loc)
+    
+    pred_mat_ADBM <- pred_mat$ADBM_pred_mat
+    
+    comm_ADBM <- mat.to.comm(pred.mat = pred_mat_ADBM, fw_title = fw)
+    
+    max_tl_ADBM <- max(PreyAveragedTrophicLevel(community = comm_ADBM))
+    
+    max_tl_ADBM_all <- c(max_tl_ADBM_all, max_tl_ADBM)
+  }
+  
+  return(max_tl_ADBM_all)
+}
+
+
+max_tl_emp_fun <- function(foodweb){
+  
+  fw <- foodweb
+  
+  library(R.utils)
+  library(readxl)
+  library(cheddar)
+  
+  sourceDirectory("R", modifiedOnly = FALSE)
+  sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+  
+  metadata <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+  fw_tol_loc <- metadata$dist_rej[metadata$foodweb == fw]
+  
+  for(nsim_loc in 1:10){
+    pred_mat <- ADBM_ABC_fw_all(fw_name = fw, fw_tol = fw_tol_loc, nsim = nsim_loc)
+    
+    pred_mat_emp <- pred_mat$real_pred_mat
+    
+    comm_emp <- mat.to.comm(pred.mat = pred_mat_emp, fw_title = fw)
+    
[…]

### 2022-09-20 inst/main/extinction_largestbodymass_uncertainty.R

@@ -1,0 +1,85 @@
+# 2022.02.23
+# We simulated primary extinction by removing largest body mass species in all the 1000 food web predicted by the ADBM 
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing least connected nodes
+dd_la <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  fw_data <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))
+  bodysize <- fw_data$species.sizes
+  
+  bodysize_real <- bodysize
+  names(bodysize_real) <- rownames(real_pred_mat)
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_mc <- largestbodymass_ext(net = real_pred_mat, bodysize = bodysize_real)
+  
+  
+  dd_la <- rbind(dd_la, 
+                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
+                            acc_sec_ext = real_ext_mc$acc_sec_ext,
+                            nsim = 1,
[…]

### 2022-09-20 inst/main/extinction_leastconnected.R

@@ -57,7 +57,7 @@ for(i in fw_ind){
                             L = L_real),
                  data.frame(n_ext = ADBM_ABC_ext_mc$acc_pri_ext,
                             acc_sec_ext = ADBM_ABC_ext_mc$acc_sec_ext,
-                            type = "ADBM_ABC",
+                            type = "ADBM",
                             fw_name = fw_name,
                             S = S,
                             L = L_ADBM_ABC),
@@ -65,7 +65,7 @@ for(i in fw_ind){
   print(fw_name)
 }
 
-# saveRDS(object = dd_lc, file = "results/least_connected.RDS")
+# saveRDS(object = dd_lc, file = "results/least_connected_maxTSS.RDS")
 
 
 

### 2022-09-20 inst/main/extinction_leastconnected_uncertainty.R

@@ -11,10 +11,10 @@ library(ggplot2)
 sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
 sourceDirectory("R", modifiedOnly=FALSE)
 
-# For removing least connected nodes
+# For removing most connected nodes
 dd_lc <- data.frame(n_ext = double(),
                     acc_sec_ext = integer(),
-                    nsim = integer(),
+                    nsim_fw = integer(),
                     type = character(),
                     fw_name = character(),
                     S = integer(),
@@ -40,12 +40,12 @@ for(i in fw_ind){
   S <- dim(real_pred_mat)[1]
   L_real <- sum(real_pred_mat)
   real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
-  real_ext_mc <- least_connected_ext(net = real_pred_mat)
+  real_ext_lc <- least_connected_ext(net = real_pred_mat)
   
   dd_lc <- rbind(dd_lc, 
-                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
-                            acc_sec_ext = real_ext_mc$acc_sec_ext,
-                            nsim = 1,
+                 data.frame(n_ext = real_ext_lc$acc_pri_ext,
+                            acc_sec_ext = real_ext_lc$acc_sec_ext,
+                            nsim_fw = 1,
                             type = "Empirical",
                             fw_name = fw_name,
                             S = S,
@@ -57,18 +57,18 @@ for(i in fw_ind){
     
     L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
     ADBM_ABC_conn <- sum(ADBM_ABC_pred_mat)/(dim(ADBM_ABC_pred_mat)[1]^2)
-    ADBM_ABC_ext_mc <- least_connected_ext(net = ADBM_ABC_pred_mat)
+    ADBM_ABC_ext_lc <- least_connected_ext(net = ADBM_ABC_pred_mat)
     
     dd_lc <- rbind(dd_lc,
-                   data.frame(n_ext = ADBM_ABC_ext_mc$acc_pri_ext,
-                              acc_sec_ext = ADBM_ABC_ext_mc$acc_sec_ext,
-                              nsim = j,
-                              type = "ADBM",
+                   data.frame(n_ext = ADBM_ABC_ext_lc$acc_pri_ext,
+                              acc_sec_ext = ADBM_ABC_ext_lc$acc_sec_ext,
+                              nsim_fw = j,
[…]

### 2022-09-20 inst/main/extinction_leastconnected_wo_basal.R

@@ -1,0 +1,76 @@
+# 2022.02.09
+# We simulated primary extinction by removing least connected species in food web predicted by the ADBM which had the maximum TSS
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing least connected nodes
+dd_lc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    S_wo_basal = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  ADBM_ABC_fw_calc <- ADBM_ABC_fw(fw_name = fw_name, fw_tol = fw_tol)
+  
+  real_pred_mat <- ADBM_ABC_fw_calc$real_pred_mat
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  ADBM_ABC_pred_mat <- ADBM_ABC_fw_calc$ADBM_pred_mat
+  
+  S <- dim(real_pred_mat)[1]
+  S_wo_basal_emp <- S - length(basal_species_fun(real_pred_mat))
+  L_real <- sum(real_pred_mat)
+  L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
+  S_wo_basal_ADBM <- S - length(basal_species_fun(ADBM_ABC_pred_mat))
+  
+  
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
[…]

### 2022-09-20 inst/main/extinction_leastconnected_wo_basal_uncertainty.R

@@ -1,0 +1,80 @@
+# 2022.07.22
+# We simulated primary extinction by removing least connected species in all the 1000 food web predicted by the ADBM 
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl) 
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing least connected nodes
+dd_lc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    S_wo_basal = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  S <- dim(real_pred_mat)[1]
+  S_wo_basal_emp <- S - length(basal_species_fun(real_pred_mat))
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_mc <- least_connected_ext_wo_basal(net = real_pred_mat)
+  
+  dd_lc <- rbind(dd_lc, 
+                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
+                            acc_sec_ext = real_ext_mc$acc_sec_ext,
+                            nsim = 1,
+                            type = "Empirical",
+                            fw_name = fw_name,
+                            S = S,
[…]

### 2022-09-20 inst/main/extinction_maxgenerality.R

@@ -1,0 +1,73 @@
+# 2022.08.03
+# We simulated primary extinction by removing species with max generality in food web predicted by the ADBM which had the maximum TSS
+
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing most connected nodes
+dd_mg <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  ADBM_ABC_fw_calc <- ADBM_ABC_fw(fw_name = fw_name, fw_tol = fw_tol)
+  
+  real_pred_mat <- ADBM_ABC_fw_calc$real_pred_mat
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  ADBM_ABC_pred_mat <- ADBM_ABC_fw_calc$ADBM_pred_mat
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
+  
+  
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  ADBM_ABC_conn <- sum(ADBM_ABC_pred_mat)/(dim(ADBM_ABC_pred_mat)[1]^2)
+  
+  real_ext_mc <- maxgenerality_ext(net = real_pred_mat)
+  ADBM_ABC_ext_mc <- maxgenerality_ext(net = ADBM_ABC_pred_mat)
+  
[…]

### 2022-09-20 inst/main/extinction_maxgenerality_uncertainty.R

@@ -1,0 +1,74 @@
+# 2022.02.23
+# We simulated primary extinction by removing max vulnerability species in all the 1000 food web predicted by the ADBM 
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing least connected nodes
+dd_mg <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_mc <- maxgenerality_ext(net = real_pred_mat)
+  
+  dd_mg <- rbind(dd_mg, 
+                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
+                            acc_sec_ext = real_ext_mc$acc_sec_ext,
+                            nsim = 1,
+                            type = "Empirical",
+                            fw_name = fw_name,
+                            S = S,
+                            L = L_real))
+  
+  for(j in 1:1000){
[…]

### 2022-09-20 inst/main/extinction_mostconnected_uncertainty.R

@@ -14,7 +14,7 @@ sourceDirectory("R", modifiedOnly=FALSE)
 # For removing most connected nodes
 dd_mc <- data.frame(n_ext = double(),
                     acc_sec_ext = integer(),
-                    nsim = integer(),
+                    nsim_fw = integer(),
                     type = character(),
                     fw_name = character(),
                     S = integer(),
@@ -45,7 +45,7 @@ for(i in fw_ind){
   dd_mc <- rbind(dd_mc, 
                  data.frame(n_ext = real_ext_mc$acc_pri_ext,
                             acc_sec_ext = real_ext_mc$acc_sec_ext,
-                            nsim = 1,
+                            nsim_fw = 1,
                             type = "Empirical",
                             fw_name = fw_name,
                             S = S,
@@ -62,13 +62,13 @@ for(i in fw_ind){
     dd_mc <- rbind(dd_mc,
                    data.frame(n_ext = ADBM_ABC_ext_mc$acc_pri_ext,
                               acc_sec_ext = ADBM_ABC_ext_mc$acc_sec_ext,
-                              nsim = j,
-                              type = "ADBM",
+                              nsim_fw = j,
+                              type = "ADBM_ABC",
                               fw_name = fw_name,
                               S = S,
                               L = L_ADBM_ABC))
   }
-  # print(fw_name)
+  print(fw_name)
 }
 
 # saveRDS(object = dd_mc, file = "results/most_connnected_uncertainty.RDS")

### 2022-09-20 inst/main/extinction_mostconnected_wo_basal_uncertainty.R

@@ -1,0 +1,81 @@
+# 2022.07.22
+# We simulated primary extinction by removing most connected species in all the 1000 food web predicted by the ADBM 
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing most connected nodes
+dd_mc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    S_wo_basal = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  S <- dim(real_pred_mat)[1]
+  S_wo_basal_emp <- S - length(basal_species_fun(real_pred_mat))
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_mc <- most_connected_ext_wo_basal(net = real_pred_mat)
+  
+  dd_mc <- rbind(dd_mc, 
+                 data.frame(n_ext = real_ext_mc$acc_pri_ext,
+                            acc_sec_ext = real_ext_mc$acc_sec_ext,
+                            nsim = 1,
+                            type = "Empirical",
+                            fw_name = fw_name,
+                            S = S,
[…]

### 2022-09-20 inst/main/investigate_all.R

@@ -1,0 +1,126 @@
+# 2022.09.05
+# Investigate how connectance and proportion of basal species affect robustness
+
+library(dplyr)
+library(readxl)
+library(R.utils)
+library(bipartite)
+library(cheddar)
+library(DirectedClustering)
+library(ggplot2)
+library(lme4)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+
+rob_all_raw <- readRDS("results/OP_2022_08_10/robustness_R50_random_uncertainty_sep4.RDS")
+
+fw_all <- as.character(unique(rob_all_raw$fw_name))
+
+dd_all <- data.frame(fw_name = character(), type = character(), nsim_fw = integer(),
+                     connectance = double(), robustness = double(), conn_2 = double(), prop_basal = double(),
+                     delta_rob = double(), delta_conn  = double(), delta_basal = double(),
+                     delta_sd_gen = double())
+
+for(fw in fw_all){
+  
+  rob_all_raw_ra <- rob_all_raw %>%
+    filter(fw_name == fw)
+  
+  dd <- rob_all_raw_ra %>%
+    group_by(fw_name, type, nsim_fw, connectance) %>%
+    summarise(robustness = median(robustness))
+  
+  metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+  fw_all <- metadata_fw_tol$foodweb
+  
+  fw_tol_all <- read_excel("../C1_method_v2/data/parameter_values.xlsx")
+  
+  ### Calculating proportion of basal species
+  
+  fw_tol <- fw_tol_all$dist_rej[fw_tol_all$foodweb == fw]
+  
+  ### ADBM predicted food webs
+  dd_single_ADBM <- dd %>%
+    filter(fw_name == fw & type == "ADBM_ABC")
+  
+  dd_C1_ADBM <- readRDS(paste0("../C1_method_v2/results/rejection/", fw, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw, "_prop.RDS"))
+  
+  dd_C1_ADBM <- dd_C1_ADBM$prop
+  
[…]

### 2022-09-20 inst/main/investigate_fw_random_ext.R

@@ -1,0 +1,25 @@
+# 2022.07.22
+# Investigate ADBM predicted and observed food webs corresponding to random extinction scenario
+
+library(R.utils)
+library(cheddar)
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+
+fw_name_loc <- "Tuesday Lake"
+fw_tol_loc <- 0.65
+  
+fw_pred <- ADBM_ABC_fw(fw_name = fw_name_loc, fw_tol = fw_tol_loc)
+
+fw_ADBM <- fw_pred$ADBM_pred_mat
+
+fw_real <- fw_pred$real_pred_mat
+
+
+fw_ADBM_comm <- mat.to.comm(pred.mat = fw_ADBM, fw_title = fw_name_loc)
+
+fw_real_comm <- mat.to.comm(pred.mat = fw_real, fw_title = fw_name_loc)
+
+
+PlotWebByLevel(community = fw_ADBM_comm)
+
+PlotWebByLevel(community = fw_real_comm)

### 2022-09-20 inst/main/investigate_rob_wrt_basal.R

@@ -1,0 +1,90 @@
+# 2022.07.21
+# We investigate if the difference in robustness of the ADBM predicted food webs and observed food webs is dependent
+# on food web properties such as proportion of basal species
+
+library(R.utils)
+library(dplyr)
+library(ggplot2)
+library(lme4)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+sourceDirectory("R", modifiedOnly = FALSE)
+
+fw_par_all <- readxl::read_excel("../C1_method_v2/data/parameter_values.xlsx")
+
+fw_name_loc <- "Broadstone Stream size_agg"
+fw_tol <- fw_par_all$dist_rej[fw_par_all$foodweb == fw_name_loc]
+
+
+ADBM_prop <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name_loc,"/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name_loc,"_prop.RDS"))$prop
+
+basal_ADBM <- ADBM_prop$prop_basal
+conn_ADBM <- ADBM_prop$connectance
+
+obs_fw <- readRDS(paste0("../C1_data/data/", fw_name_loc, ".web.RDS"))$predation.matrix
+
+basal_obs <- prop_basal_inter_top_herb(obs_fw)$prop_basal
+
+
+dd_rand <- readRDS("results/robustness_R50_random_uncertainty_july14.RDS")
+
+rob_fw <- dd_rand %>%
+  filter(type == "ADBM_ABC", fw_name == fw_name_loc) %>%
+  cbind(basal_ADBM = basal_ADBM)
+
+
+ggplot(rob_fw) +
+  geom_point(aes(x = basal_ADBM, y = robustness)) +
+  geom_smooth(aes(x = basal_ADBM, y = robustness), method = "lm")
+
+lm_rob_basal <- lm(robustness ~ basal_ADBM, data = rob_fw)
+summary(lm_rob_basal)
+
+
+
+ADBM_pred <- ADBM_ABC_fw_all(fw_name = fw_name_loc, fw_tol = fw_tol, nsim = 1)
+
+
+
+rob_all_raw_mc <- readRDS("results/robustness_R50_mostconnected_wo_basal_uncertainty.RDS")
+
+rob_ADBM_mc <- rob_all_raw_mc %>%
+  filter(type == "ADBM_ABC") %>%
[…]

### 2022-09-20 inst/main/investigate_small_reef.R

@@ -1,0 +1,92 @@
+# 2022.09.05
+# Investigate how connectance and proportion of basal species affect robustness
+
+library(dplyr)
+library(readxl)
+library(R.utils)
+library(bipartite)
+library(cheddar)
+library(DirectedClustering)
+library(ggplot2)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+
+
+rob_all_raw_ra <- readRDS("results/OP_2022_08_10/robustness_R50_random_uncertainty_sep4.RDS")
+
+fw <- "Small Reef"
+
+rob_all_raw_ra <- rob_all_raw_ra %>%
+  filter(fw_name == fw)
+
+dd <- rob_all_raw_ra %>%
+  group_by(fw_name, type, nsim_fw, connectance) %>%
+  summarise(robustness = median(robustness))
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+fw_all <- metadata_fw_tol$foodweb
+
+dd_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                     S = integer(), nsim = integer(), slope = double(), delta_rob = double(),
+                     delta_conn  = double(), delta_basal = double())
+
+fw_tol_all <- read_excel("../C1_method_v2/data/parameter_values.xlsx")
+
+### Calculating proportion of basal species
+
+fw_tol <- fw_tol_all$dist_rej[fw_tol_all$foodweb == fw]
+
+### ADBM predicted food webs
+dd_single_ADBM <- dd %>%
+  filter(fw_name == fw & type == "ADBM_ABC")
+
+dd_C1_ADBM <- readRDS(paste0("../C1_method_v2/results/rejection/", fw, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw, "_prop.RDS"))
+
+dd_C1_ADBM <- dd_C1_ADBM$prop
+
+dd_ADBM <- cbind(dd_single_ADBM, conn_2 = dd_C1_ADBM$connectance, prop_basal = dd_C1_ADBM$prop_basal)
+
+### Empirical food web
+
+dd_single_emp <- dd %>%
+  filter(fw_name == fw & type == "Empirical")
+
[…]

### 2022-09-20 inst/main/justincase/investigate_ythan.R

@@ -13,3 +13,9 @@ Plot.matrix(ythan_ABC)
 conn_emp <- sum(ythan_emp)/(dim(ythan_emp)[1]^2)
 conn_2008 <- sum(ythan_2008)/(dim(ythan_2008)[1]^2)
 
+
+ythan_ADBM_ABC_comm <- mat.to.comm(pred.mat = ythan_ABC, fw_title = "Ythan")
+PlotWebByLevel(community = ythan_ADBM_ABC_comm)
+
+ythan_emp_comm <- mat.to.comm(pred.mat = ythan_emp, fw_title = "Ythan Observed")
+PlotWebByLevel(community = ythan_emp_comm)

### 2022-09-20 inst/main/plot_largestbodymass.R

@@ -1,0 +1,34 @@
+# 2022.08.02
+
+# Plot how secondary extinctions vary when number of species removed is increased
+
+library(dplyr)
+library(ggplot2)
+
+dd_la <- readRDS("results/largestbodymass_maxTSS.RDS")
+
+dd_la_mod <- dd_la %>%
+  mutate(n_ext_by_S = n_ext/S, acc_sec_ext_by_S = acc_sec_ext/S)
+
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
+
+
+plot_dd_la_mod <- ggplot(dd_la_mod) +
+  geom_point(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  geom_line(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  facet_wrap(~fw_name, labeller = labeller(fw_name = fw_labs), nrow = 2) +
+  theme_classic() +
+  xlab("Species removed/S") +
+  ylab("Cumulative secondary extinctions/S") +
+  scale_color_manual(name = "Food web type", labels = c("ADBM" = "ADBM food web", "Empirical" = "Observed food web"), 
+                     values = c("ADBM" = "red", "Empirical" = "blue")) +
+  theme(legend.position="bottom", legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15))
+
+
+# ggsave(plot = plot_dd_la_mod, filename = "results/plot_largestbodymass_maxTSS.png", width = 13, height = 6)

### 2022-09-20 inst/main/plot_leastconnected_wo_basal.R

@@ -1,0 +1,34 @@
+# 2022.02.09
+
+# Plot how secondary extinctions vary when number of species removed is increased
+
+library(dplyr)
+library(ggplot2)
+
+dd_lc <- readRDS("results/least_connected_wo_basal_maxTSS.RDS")
+
+dd_lc_mod <- dd_lc %>%
+  mutate(n_ext_by_S = n_ext/S_wo_basal, acc_sec_ext_by_S = acc_sec_ext/S_wo_basal)
+
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
+
+
+plot_dd_lc_mod <- ggplot(dd_lc_mod) +
+  geom_point(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  geom_line(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  facet_wrap(~fw_name, labeller = labeller(fw_name = fw_labs), nrow = 2) +
+  theme_classic() +
+  xlab("Species removed/S") +
+  ylab("Cumulative secondary extinctions/S") +
+  scale_color_manual(name = "Food web type", labels = c("ADBM" = "ADBM food web", "Empirical" = "Observed food web"), 
+                     values = c("ADBM" = "red", "Empirical" = "blue")) +
+  theme(legend.position="bottom", legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15))
+
+
+# ggsave(plot = plot_dd_lc_mod, filename = "results/plot_leastconnected_wo_basal_maxTSS.png", width = 13, height = 6)

### 2022-09-20 inst/main/plot_maxgenerality.R

@@ -1,0 +1,33 @@
+# 2022.08.02
+
+# Plot how secondary extinctions vary when number of species removed is increased
+
+library(dplyr)
+library(ggplot2)
+
+dd_mg <- readRDS("results/maxgenerality_maxTSS.RDS")
+
+dd_mg_mod <- dd_mg %>%
+  mutate(n_ext_by_S = n_ext/S, acc_sec_ext_by_S = acc_sec_ext/S)
+
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
+
+
+plot_dd_mg_mod <- ggplot(dd_mg_mod) +
+  geom_point(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  geom_line(aes(x = n_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  facet_wrap(~fw_name, labeller = labeller(fw_name = fw_labs), nrow = 2) +
+  theme_classic() +
+  xlab("Species removed/S") +
+  ylab("Cumulative secondary extinctions/S") +
+  scale_color_manual(name = "Food web type", labels = c("ADBM" = "ADBM food web", "Empirical" = "Observed food web"), 
+                     values = c("ADBM" = "red", "Empirical" = "blue")) +
+  theme(legend.position="bottom", legend.text = element_text(size = 15),
+        legend.title = element_text(size = 15))
+
+# ggsave(plot = plot_dd_mg_mod, filename = "results/plot_maxgenerality_maxTSS.png", width = 13, height = 6)

### 2022-09-20 inst/main/plot_random_wo_basal.R

@@ -1,0 +1,58 @@
+# 2022.02.13
+
+# Plot how secondary extinctions vary when number of species removed is increased
+
+library(dplyr)
+library(ggplot2)
+
+dd_rand_raw <- readRDS("results/random_raw_wo_basal_maxTSS.RDS")
+
+dd_rand_mod <- dd_rand_raw %>%
+  group_by(fw_name, type, nsim, S_wo_basal) %>%
+  mutate(max_pri = max(acc_pri_ext)) %>%
+  group_by(fw_name, type, S_wo_basal) %>%
+  mutate(max_min_pri = min(max_pri)) %>%
+  filter(acc_pri_ext <= max_min_pri) %>%
+  group_by(fw_name, acc_pri_ext, type, S_wo_basal) %>%
+  summarise(mean_acc_sec_ext = mean(acc_sec_ext), l_acc_sec_ext = min(acc_sec_ext), u_acc_sec_ext = max(acc_sec_ext)) %>%
+  mutate(acc_pri_ext_by_S = acc_pri_ext/S_wo_basal, acc_sec_ext_by_S = mean_acc_sec_ext/S_wo_basal, l_acc_sec_ext_by_S = l_acc_sec_ext/S_wo_basal,
+         u_acc_sec_ext_by_S = u_acc_sec_ext/S_wo_basal)
+
+
+
+
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
+
+
+plot_dd_random_mod <- ggplot(dd_rand_mod) +
+  geom_point(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  geom_line(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
[…]

### 2022-09-20 inst/main/robustness_R100_ADBM_vs_observed.R

@@ -1,4 +1,4 @@
-# 2022.07.04
+# 2022.06.27
 # Robustness (R100) of ADBM predicted food webs VS robustness of observed food webs
 
 library(dplyr)
@@ -7,7 +7,144 @@ library(tidyr)
 library(ggpubr)
 library(latex2exp)
 
+##### Merging all the three simulations scenarios #####
 
-rob_all_raw1 <- readRDS("results/robustness_R100_leastconnected.RDS")
-rob_all_raw2 <- readRDS("results/robustness_R100_random.RDS")
+rob_all_raw1 <- readRDS("results/robustness_R100_leastconnected_uncertainty.RDS")
+rob_all_raw2 <- readRDS("results/robustness_R100_random_uncertainty_july14.RDS")
 rob_all_raw3 <- readRDS("results/robustness_R100_mostconnected_uncertainty.RDS")
+
+rob_all_raw1 <- rob_all_raw1 %>%
+  mutate(study = "(c) Least connected")
+
+rob_all_raw2 <- rob_all_raw2 %>%
+  mutate(study = "(b) Random")
+
+rob_all_raw3 <- rob_all_raw3 %>%
+  mutate(study = "(a) Most connected")
+
+rob_all_raw <- rbind(rob_all_raw1, rob_all_raw2, rob_all_raw3)
+
+
+rob_ADBM <- rob_all_raw %>%
+  filter(type == "ADBM_ABC") %>%
+  mutate(robustness_ADBM = robustness) %>%
+  select(-c(robustness, connectance, type))
+
+rob_obs <- rob_all_raw %>%
+  filter(type == "Empirical") %>%
+  mutate(robustness_emp = robustness) %>%
+  select(-c(robustness, connectance, type)) %>%
+  unique()
+
+rob_all_merged <- merge(x = rob_ADBM, rob_obs, by = c("fw_name", "study")) %>%
+  mutate(S = S.x, nsim = nsim.x) %>%
+  select(-c(S.x, S.y, nsim.x, nsim.y))
+
+
+rob_all_merged_mean <- rob_all_merged %>%
+  group_by(fw_name, robustness_emp, study) %>%
+  summarise(mean_robustness_ADBM = mean(robustness_ADBM), median_robustness_ADBM = median(robustness_ADBM))
+
+rob_all_merged_mean <- rob_all_merged_mean %>%
+  pivot_longer(!c(fw_name, robustness_emp, study), names_to = 'value_type', values_to = "values")
+
[…]

### 2022-09-20 inst/main/robustness_R50_ADBM_vs_observed.R

@@ -1,4 +1,4 @@
-# 2022.06.27
+# 2022.09.13
 # Robustness (R50) of ADBM predicted food webs VS robustness of observed food webs
 
 library(dplyr)
@@ -6,128 +6,8 @@ library(ggplot2)
 library(tidyr)
 library(ggpubr)
 library(latex2exp)
+library(HDInterval)
 
-rob_all_raw3 <- readRDS("results/robustness_R50_mostconnected_uncertainty.RDS")
-
-# rob_all_raw3 <- readRDS("results/robustness_random_uncertainty.RDS")
-
-
-rob_ADBM <- rob_all_raw3 %>%
-  filter(type == "ADBM_ABC") %>%
-  mutate(robustness_ADBM = robustness, connectance_ADBM = connectance) %>%
-  select(-c(robustness, connectance, type))
-
-rob_obs <- rob_all_raw3 %>%
-  filter(type == "Empirical") %>%
-  mutate(robustness_emp = robustness, connectance_emp = connectance) %>%
-  select(-c(robustness, connectance, type)) %>%
-  unique()
-  
-
-rob_all_merged <- merge(x = rob_ADBM, rob_obs, by = "fw_name") %>%
-  mutate(S = S.x, nsim = nsim.x) %>%
-  select(-c(S.x, S.y, nsim.x, nsim.y))
-
-
-ggplot(rob_all_merged) +
-  geom_point(aes(x = robustness_emp, y = robustness_ADBM))
-
-rob_all_merged <- rob_all_merged %>%
-  mutate(robustness_ADBM = ifelse(robustness_ADBM > 0.5, 0.5, robustness_ADBM),
-         robustness_emp = ifelse(robustness_emp > 0.5, 0.5, robustness_emp))
-
-rob_all_merged_mean <- rob_all_merged %>%
-  group_by(fw_name, robustness_emp) %>%
-  summarise(mean_robustness_ADBM = mean(robustness_ADBM))
-
-ggplot(rob_all_merged) +
-  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name, fill = fw_name), alpha = 0.5) +
-  geom_abline(slope = 1, intercept = 0, linetype = 3) +
-  # xlim(c(0.3, 0.55)) +
-  # ylim(c(0.3, 0.55)) +
-  geom_point(data = rob_all_merged_mean, aes(x = robustness_emp, y = mean_robustness_ADBM, color = fw_name), size = 3, shape = 2) +
-  theme_classic() +
[…]

### 2022-09-20 inst/main/robustness_R50_ADBM_vs_observed_median.R

@@ -1,0 +1,159 @@
+# 2022.09.08
+
+library(ggplot2)
+library(dplyr)
+library(latex2exp)
+
+fw_labs <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+             "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+             "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+             "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+             "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)")
+
+##### Most connected scenario #####
+
+rob_all_raw_mc <- readRDS("results/robustness_R50_mostconnected_uncertainty.RDS")
+
+rob_all_raw_mc <- rob_all_raw_mc %>%
+  group_by(fw_name, type, nsim_fw, connectance) %>%
+  summarise(robustness = median(robustness))
+
+rob_all_raw_mc <- data.frame(rob_all_raw_mc)
+
+rob_ADBM_mc <- rob_all_raw_mc %>%
+  filter(type == "ADBM_ABC") %>%
+  mutate(robustness_ADBM = robustness) %>%
+  select(-c(type, robustness))
+
+rob_obs_mc <- rob_all_raw_mc %>%
+  filter(type == "Empirical") %>%
+  mutate(robustness_emp = robustness) %>%
+  select(-c(type, robustness))
+
+rob_all_mc <- merge(x = rob_ADBM_mc, rob_obs_mc, by = c("fw_name")) 
+
+rob_all_mc_median <- rob_all_mc %>%
+  group_by(fw_name, robustness_emp) %>%
+  summarise(median_robustness_ADBM = median(robustness_ADBM))
+
+rob_all_mc %>%
+  ggplot() +
+  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name), alpha = 1, width = 0.0019, outlier.shape = 1,
+               outlier.alpha = 0.5, outlier.size = 0.3) +
+  geom_abline(slope = 1, intercept = 0, linetype = 3) +
+  xlim(c(0, 0.51)) +
+  ylim(c(0, 0.51)) +
[…]

### 2022-09-20 inst/main/robustness_R50_mostconnected_wo_basal_uncertainty.R

@@ -1,0 +1,90 @@
+# 2022.07.29
+
+# Compute robustness (R50) of 
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mc <- readRDS("results/most_connnected_wo_basal_uncertainty_new.RDS")
+
+fw_list <- unique(dd_mc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), S_wo_basal = integer(), nsim = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_mc_emp <- dd_mc %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_mc_emp <- dd_mc_emp %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S_wo_basal)
+  
+  robustness <- NA
+  
+  N_row <- dim(dd_mc_emp)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_mc_emp[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S_wo_basal
+      break
+    }
+  }
+  
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  S_wo_basal <- dd_mc_emp$S_wo_basal[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, S_wo_basal = S_wo_basal, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+    
+    #### ADBM ABC predicted food web second ####
[…]

### 2022-09-20 inst/main/robustness_R50_wo_basal_ADBM_vs_observed.R

@@ -1,0 +1,351 @@
+# 2022.07.29
+# Robustness (R50) (without basal) of ADBM predicted food webs VS robustness of observed food webs
+
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(ggpubr)
+library(latex2exp)
+
+##### Most connected scenario #####
+
+rob_all_raw_mc <- readRDS("results/robustness_R50_mostconnected_wo_basal_uncertainty.RDS")
+
+rob_ADBM_mc <- rob_all_raw_mc %>%
+  filter(type == "ADBM_ABC") %>%
+  mutate(robustness_ADBM = robustness, S_basal_ADBM = S - S_wo_basal) %>%
+  select(-c(robustness, connectance, type))
+
+rob_obs_mc <- rob_all_raw_mc %>%
+  filter(type == "Empirical") %>%
+  mutate(robustness_emp = robustness, S_basal_emp = S - S_wo_basal) %>%
+  select(-c(robustness, connectance, type)) %>%
+  unique()
+
+rob_all_mc <- merge(x = rob_ADBM_mc, rob_obs_mc, by = c("fw_name")) %>%
+  mutate(S = S.x, nsim = nsim.x) %>%
+  select(-c(S.x, S.y, nsim.x, nsim.y))
+
+rob_all_mc_mean <- rob_all_mc %>%
+  group_by(fw_name, robustness_emp) %>%
+  summarise(median_robustness_ADBM = median(robustness_ADBM))
+
+rob_all_mc_mean <- rob_all_mc_mean %>%
+  pivot_longer(!c(fw_name, robustness_emp), names_to = 'value_type', values_to = "values")
+
+fw_labs <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+             "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+             "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+             "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+             "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)")
+
+
+plot_MC_R50 <- rob_all_mc %>%
+  ggplot() +
[…]

### 2022-09-20 inst/main/robustness_largestbodymass_R50_uncertainty.R

@@ -1,0 +1,83 @@
+# 2022.08.02
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_la <- readRDS("results/largestbodymass_uncertainty.RDS")
+
+fw_list <- unique(dd_la$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_la_real <- dd_la %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_la_real <- dd_la_real %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- NA
+  N_row <- dim(dd_la_real)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_la_real[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  # intervality_emp <- intervality(pred_mat_emp)
+  S <- dim(pred_mat_emp)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+    
+    #### ADBM ABC predicted food web second ####
+    dd_la_ADBM_ABC <- dd_la %>%
+      filter(fw_name == foodweb, type == "ADBM", nsim == nsim_local) %>%
+      mutate(total_ext = (n_ext + acc_sec_ext)/S)
[…]

### 2022-09-20 inst/main/robustness_leastconnected_R50_uncertainty.R

@@ -1,11 +1,10 @@
-# 2022.02.27
+# 2022.08.02
 
 library(cheddar)
 library(R.utils)
 library(ggplot2)
 library(HDInterval)
 library(readxl)
-library(dplyr)
 
 sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
 sourceDirectory("R", modifiedOnly=FALSE)
@@ -14,19 +13,47 @@ dd_lc <- readRDS("results/least_connnected_uncertainty.RDS")
 
 fw_list <- unique(dd_lc$fw_name)
 rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
-                      S = integer(), nsim = integer())
+                      S = integer(), nsim_fw = integer())
 
 metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
 
 for(foodweb in fw_list){
   
-  for(nsim_local in 1:1000){
+  #### Emprirical food web first ####
+  dd_lc_real <- dd_lc %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim_fw == 1)
+  
+  dd_lc_real <- dd_lc_real %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- NA
+  N_row <- dim(dd_lc_real)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_lc_real[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  # intervality_emp <- intervality(pred_mat_emp)
+  S <- dim(pred_mat_emp)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim_fw = 1)
+  )
+  
+  for(nsim_fw_local in 1:1000){
     
-    #### ADBM ABC predicted food web first ####
[…]

### 2022-09-20 inst/main/robustness_leastconnected_R50_wo_basal_uncertainty.R

@@ -1,0 +1,90 @@
+# 2022.07.29
+
+# Compute robustness (R50) of ADBM predicted food webs for most connected scenario (without basal)
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_lc <- readRDS("results/least_connnected_wo_basal_uncertainty.RDS")
+
+fw_list <- unique(dd_lc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), S_wo_basal = integer(), nsim = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_lc_emp <- dd_lc %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_lc_emp <- dd_lc_emp %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S_wo_basal)
+  
+  robustness <- NA
+  
+  N_row <- dim(dd_lc_emp)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_lc_emp[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S_wo_basal
+      break
+    }
+  }
+  
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  S_wo_basal <- dd_lc_emp$S_wo_basal[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, S_wo_basal = S_wo_basal, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+    
[…]

### 2022-09-20 inst/main/robustness_maxgenerality_R50_uncertainty.R

@@ -1,0 +1,83 @@
+# 2022.08.02
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mg <- readRDS("results/maxgenerality_uncertainty.RDS")
+
+fw_list <- unique(dd_mg$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_mg_real <- dd_mg %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_mg_real <- dd_mg_real %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- NA
+  N_row <- dim(dd_mg_real)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_mg_real[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  # intervality_emp <- intervality(pred_mat_emp)
+  S <- dim(real_pred_mat)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+    
+    #### ADBM ABC predicted food web second ####
+    dd_mg_ADBM_ABC <- dd_mg %>%
+      filter(fw_name == foodweb, type == "ADBM", nsim == nsim_local) %>%
[…]

### 2022-09-20 inst/main/robustness_mostconnected_uncertainty.R

@@ -1,132 +1,0 @@
-# 2022.02.24
-
-library(cheddar)
-library(R.utils)
-library(ggplot2)
-library(HDInterval)
-library(readxl)
-
-sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
-sourceDirectory("R", modifiedOnly=FALSE)
-
-dd_mc <- readRDS("results/most_connnected_uncertainty.RDS")
-
-fw_list <- unique(dd_mc$fw_name)
-rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
-                      S = integer(), nsim = integer())
-
-metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
-
-for(foodweb in fw_list){
-  
-  for(nsim_local in 1:1000){
-    
-    #### ADBM ABC predicted food web first ####
-    dd_mc_ADBM_ABC <- dd_mc %>%
-      filter(fw_name == foodweb, type == "ADBM", nsim == nsim_local) %>%
-      mutate(total_ext = (n_ext + acc_sec_ext)/S)
-    
-    N_row <- dim(dd_mc_ADBM_ABC)[1]
-    for(i in 1:N_row){
-      ith_row <- dd_mc_ADBM_ABC[i,]
-      if(ith_row$total_ext >= 0.5){
-        robustness <- ith_row$n_ext/ith_row$S
-        break
-      }
-    }
-    
-    fw_tol <- metadata_fw_tol$dist_rej[which(metadata_fw_tol$foodweb == foodweb)]
-    pred_mat_ADBM_ABC <- ADBM_ABC_fw_all(fw_name = foodweb, fw_tol = fw_tol, nsim = nsim_local)$ADBM_pred_mat
-    S <- dim(pred_mat_ADBM_ABC)[1]
-    conn_ADBM_ABC <- sum(pred_mat_ADBM_ABC)/(dim(pred_mat_ADBM_ABC)[1]^2)
-    # intervality_ADBM_ABC <- intervality(pred_mat_ADBM_ABC)
-    rob_all <- rbind(rob_all,
-                     data.frame(robustness = robustness, fw_name = foodweb, type = "ADBM_ABC", connectance = conn_ADBM_ABC,
-                                S = S, nsim = nsim_local)
-    )
-    
-    
-    
-    #### Emprirical food web second ####
[…]

### 2022-09-20 inst/main/robustness_random_min_TSS.R

@@ -1,0 +1,158 @@
+# 2022.08.30
+
+library(cheddar)
+library(dplyr)
+library(R.utils)
+library(ggplot2)
+library(tidyr)
+library(HDInterval)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_rand_raw <- readRDS("results/random_raw_minTSS.RDS")
+
+fw_list <- unique(dd_rand_raw$fw_name)
+sim_ind <- unique(dd_rand_raw$nsim)
+list_all <- expand.grid(nsim = sim_ind, fw_name = fw_list)
+N <- dim(list_all)[1]
+
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double())
+
+Nsim <- 1000
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_rand_emp <- dd_rand_raw %>%
+    filter(fw_name == foodweb, type == "Empirical")
+  
+  dd_rand_emp <- dd_rand_emp %>%
+    mutate(total_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  
+  
+  for(k in 1:Nsim){
+    robustness <- NA
+    dd_rand_emp_local <- dd_rand_emp %>%
+      filter(nsim == k)
+    
+    N_row <- dim(dd_rand_emp_local)[1]
+    for(i in 1:N_row){
+      ith_row <- dd_rand_emp_local[i,]
+      if(ith_row$total_ext >= 0.5){
+        robustness <- ith_row$acc_pri_ext/ith_row$S
+        # print(robustness)
+        break
+      }
+    }
+    
+    robustness <- min(robustness, 0.5)
+    
+    rob_all <- rbind(rob_all,
+                     data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
[…]

### 2022-09-20 inst/main/robustness_random_wo_basal_R50_uncertainty.R

@@ -1,0 +1,97 @@
+# 2022.02.27
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+library(dplyr)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_rand <- readRDS("results/random_raw_uncertainty_july11.RDS")
+
+fw_list <- unique(dd_rand$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim = integer())
+Nsim <- 100
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_rand_emp <- dd_rand %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_rand_emp <- dd_rand_emp %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- 0
+  for(k in 1:Nsim){
+    dd_rand_emp_local <- dd_rand_emp %>%
+      filter(nsim_rand == k)
+    
+    N_row <- dim(dd_rand_emp_local)[1]
+    for(i in 1:N_row){
+      ith_row <- dd_rand_emp_local[i,]
+      if(ith_row$total_ext >= 0.5){
+        robustness <- robustness + ith_row$n_ext/ith_row$S
+        # print(robustness)
+        break
+      }
+    }
+  }
+  
+  robustness <- robustness/Nsim
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+    
[…]

### 2022-09-20 inst/main/sim_single_ext_v2.R

@@ -1,18 +1,0 @@
-# 2022.07.06
-# Simulating single primary extinction in a food web i.e removing given node from a given food web
-# Calculating secondary extinction 
-
-
-indeg <- rowSums(net)
-outdeg <- colSums(net)
-
-totdeg <- indeg + outdeg
-
-new_net <- net[!rownames(net) %in% node, !colnames(net) %in% node]
-
-if(length(new_net) == 1){
-  new_net <- as.matrix(new_net)
-  lost_node <- setdiff(rownames(net), node)
-  rownames(new_net) <- lost_node
-  colnames(new_net) <- lost_node
-}

### 2022-09-20 inst/main/slope_delta_R50_conn.R

@@ -1,0 +1,258 @@
+#  2022.09.13
+# delta R50 vs delta connectance
+
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(ggpubr)
+library(latex2exp)
+library(HDInterval)
+
+
+fw_labs <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+             "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+             "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+             "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+             "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)",
+                  "All food webs" = "All food webs")
+
+#### Most connected ####
+
+rob_all_raw_mc <- readRDS("results/robustness_R50_mostconnected_uncertainty.RDS")
+
+fw_all <- unique(rob_all_raw_mc$fw_name)
+
+## Observed food web
+rob_all_mc_emp <- rob_all_raw_mc %>%
+  filter(type == "Empirical")
+
+rob_all_mc_emp <- data.frame(rob_all_mc_emp)
+
+rob_all_mc_emp <- rob_all_mc_emp %>%
+  select(-c(S))
+
+#### ADBM predicted food webs
+rob_all_mc_ADBM <- rob_all_raw_mc %>%
+  filter(type == "ADBM_ABC")
+
[…]

### 2022-09-20 inst/main/slope_delta_rob50_basal.R

@@ -1,0 +1,132 @@
+# 2022.08.24
+# We investigate the difference in robustness (R50) between ADBM predicted food webs and observed food webs wrt the difference in their proportion of basal species
+
+library(HDInterval)
+library(readxl)
+library(latex2exp)
+library(facetscales)
+library(R.utils)
+library(cheddar)
+library(DirectedClustering)
+library(bipartite)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+
+dd_all_main <- data.frame(robustness = double(), fw_name = character(), type = character(), prop_basal = double(),
+                          S = integer(), nsim = integer(), slope = double(), study = character())
+
+dd_all_mean_main <- data.frame(fw_name = character(), mean_slope = double(), study = character())
+
+fw_labs <- c("Benguela Pelagic", "Broadstone Stream", "Broom", "Capinteria", "Caricaie Lakes", 
+             "Grasslands", "Mill Stream", "Skipwith Pond", "Small Reef", "Tuesday Lake",
+             "Ythan", "Broadstone Stream size_agg")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)",
+                  "All food webs" = "All food webs")
+
+
+#### Random ####
+
+dd <- readRDS("results/robustness_R50_random_uncertainty_july14.RDS")
+
+fw_tol_all <- read_excel("../C1_method_v2/data/parameter_values.xlsx")
+
+fw_all <- as.character(fw_tol_all$foodweb)
+
[…]

### 2022-09-20 inst/main/slope_delta_rob50_conn_median.R

@@ -1,0 +1,81 @@
+
+
+library(tidyr)
+library(HDInterval)
+#### Random ####
+
+fw_labs <- c("Benguela Pelagic", "Broadstone Stream", "Broom", "Capinteria", "Caricaie Lakes", 
+             "Grasslands", "Mill Stream", "Skipwith Pond", "Small Reef", "Tuesday Lake",
+             "Ythan", "Broadstone Stream size_agg")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)",
+                  "All food webs" = "All food webs")
+
+rob_all_raw_ra <- readRDS("results/OP_2022_08_10/robustness_R50_random_uncertainty_sep4.RDS")
+
+dd <- rob_all_raw_ra %>%
+  group_by(fw_name, type, nsim_fw, connectance) %>%
+  summarise(robustness = median(robustness))
+
+dd <- dd %>%
+  group_by(fw_name, type) %>%
+  summarise(connectance = connectance, robustness = robustness, l_conn = as.numeric(hdi(connectance)[1]), u_conn = as.numeric(hdi(connectance)[2])) %>%
+  filter(connectance >= l_conn & connectance <= u_conn) %>%
+  group_by(fw_name, type) %>%
+  select(-c(l_conn, u_conn))
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+fw_all <- metadata_fw_tol$foodweb
+
+dd_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                     S = integer(), nsim = integer(), slope = double())
+
+for(fw in fw_all){
+  
[…]

### 2022-09-20 inst/main/slope_delta_rob50_conn_old.R

@@ -1,0 +1,552 @@
+# 2022.06.29
+# We investigate the difference in robustness (R50) between ADBM predicted food webs and observed food webs wrt the difference in their connectance
+
+library(HDInterval)
+library(readxl)
+library(latex2exp)
+library(facetscales)
+
+
+dd_all_main <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                     S = integer(), nsim = integer(), slope = double(), study = character())
+
+dd_all_mean_main <- data.frame(fw_name = character(), mean_slope = double(), study = character())
+
+#### Most connected ####
+fw_labs <- c("Benguela Pelagic", "Broadstone Stream", "Broom", "Capinteria", "Caricaie Lakes", 
+             "Grasslands", "Mill Stream", "Skipwith Pond", "Small Reef", "Tuesday Lake",
+             "Ythan", "Broadstone Stream size_agg")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)",
+                  "All food webs" = "All food webs")
+
+
+dd <- readRDS("results/robustness_R50_mostconnected_uncertainty_new.RDS")
+
+dd <- dd %>%
+  group_by(fw_name, type) %>%
+  summarise(connectance = connectance, robustness = robustness, l_conn = as.numeric(hdi(connectance)[1]), u_conn = as.numeric(hdi(connectance)[2])) %>%
+  filter(connectance >= l_conn & connectance <= u_conn) %>%
+  group_by(fw_name, type) %>%
+  select(-c(l_conn, u_conn))
+
[…]

### 2022-09-20 inst/main/slope_delta_rob50_conn_wo_basal.R

@@ -1,0 +1,156 @@
+# 2022.08.29
+# We investigate the difference in robustness (R50) between ADBM predicted food webs and observed food webs wrt the difference in their connectance (without basal species)
+
+library(HDInterval)
+library(readxl)
+library(latex2exp)
+library(facetscales)
+library(R.utils)
+library(ggplot2)
+library(dplyr)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+sourceDirectory("../C3_overestimation/R", modifiedOnly = FALSE)
+
+dd_all_main <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                          S = integer(), nsim = integer(), slope = double(), study = character())
+
+dd_all_mean_main <- data.frame(fw_name = character(), mean_slope = double(), study = character())
+
+
+fw_labs <- c("Benguela Pelagic", "Broadstone Stream", "Broom", "Capinteria", "Caricaie Lakes", 
+             "Grasslands", "Mill Stream", "Skipwith Pond", "Small Reef", "Tuesday Lake",
+             "Ythan", "Broadstone Stream size_agg")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)",
+                  "All food webs" = "All food webs")
+
+
+#### Random ####
+
+dd <- readRDS("results/robustness_R50_random_uncertainty_july14.RDS")
+
+dd_all <- data.frame(robustness = double(), fw_name = character(), type = character(),
[…]

### 2022-09-20 inst/main/slope_delta_rob50_wo_basal_conn.R

@@ -1,0 +1,298 @@
+# 2022.06.29
+# We investigate the difference in robustness (R50) between ADBM predicted food webs and observed food webs wrt the difference in their connectance
+
+library(HDInterval)
+library(readxl)
+library(latex2exp)
+library(facetscales)
+
+
+dd_all_main <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                          S = integer(), nsim = integer(), slope = double(), study = character())
+
+dd_all_mean_main <- data.frame(fw_name = character(), mean_slope = double(), study = character())
+
+#### Most connected ####
+fw_labs <- c("Benguela Pelagic", "Broadstone Stream", "Broom", "Capinteria", "Caricaie Lakes", 
+             "Grasslands", "Mill Stream", "Skipwith Pond", "Small Reef", "Tuesday Lake",
+             "Ythan", "Broadstone Stream size_agg")
+
+fw_labs_nice <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream (taxonomic aggregation)",
+                  "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+                  "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+                  "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+                  "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream (size aggregation)")
+
+dd <- readRDS("results/robustness_R50_mostconnected_wo_basal_uncertainty.RDS")
+
+dd <- dd %>%
+  group_by(fw_name, type) %>%
+  summarise(connectance = connectance, robustness = robustness, l_conn = as.numeric(hdi(connectance)[1]), u_conn = as.numeric(hdi(connectance)[2])) %>%
+  filter(connectance >= l_conn & connectance <= u_conn) %>%
+  group_by(fw_name, type) %>%
+  select(-c(l_conn, u_conn))
+
[…]

### 2023-02-10 manuscript/ms_C3_v2.Rmd
updated ms

--- 2022-09-20 manuscript/ms_C3_v2.Rmd
@@
 Simultaneously, models might predict links which cannot occur, i.e., false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occuring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
-Thus we expect that predicted food webs are more robust than observed ones.
-This expectation has never, to our knowledge, been tested, nor has the effect size been quantified.
-  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links, though which does not predict all links correctly.
+  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
+Thus, we expect that predicted food webs are more robust than observed ones.
+However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e.
+the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
+  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links but does not predict all links correctly.
 We did this for 12 different food webs from a wide variety of ecosystems.
 We used three extinction scenarios: random, most connected, and least connected.
-  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, and this can be attributed to the higher connectance of the predicted food webs.
-On average, for every one unit of increase in connectance, we found the food webs to be robust by 0.52 units and 0.04 units for the most connected and the random species extinction scenarios respectively while no effect in the least connected species extinction scenario.
+  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs.
+On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios.
+On the other hand, we saw no effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
   5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
-Nevertheless, increased connectance may contribute to lower dynamical stability, and so it would be interesting to compare the dynamical stability of observed and predicted food webs, as well as the topological stability that we have focused on.
+Nevertheless, increased connectance may contribute to lower dynamical stability, so it would be interesting to compare the dynamical stability of observed and predicted food webs and the topological stability that we have focused on.
 
@@
 bibliography: bibliography.bib
+csl: methods-in-ecology-and-evolution.csl
 biblio-style: biblatex
@@
 
-Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity, and can lead to food web collapse [@ullah2018].
-This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species, for example due to habitat destruction and climate change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
-An example of a secondary extinction is when a consumer goes extinction because its sole resource species goes extinct.
-Therefore, research focused on cascading secondary extinctions also known as 'community viability analysis' have been performed extensively in the past few decades to quantify how robust are food webs to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
-This research revealed that the rate of collapse of a food web is dependent on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity and can lead to food web collapse [@ullah2018].
+This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
+An example of a secondary extinction is when a consumer goes extinct because its sole resource species goes extinct.
+Therefore, research focused on cascading secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
+This research revealed that the rate of collapse of a food web depends on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
 
 Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-Primary species loss is considered to be extinction of a species due to causes external to the food web.
-In research with models, the specific cause or causes are usually not specified.
-Overharvesting of a population which causes extinction could be considered a driver of a primary extinction.
+Primary species loss is considered to be extinction of a species due to causes external to the food web, e.g.
+overharvesting [@koningGrassrootsReservesRescue2021], introduction of invasive species [@davidImpactsInvasiveSpecies2017].
 A secondary extinction is an extinction caused by a previous extinction (either primary or secondary).
-Numerous studies have used a topological criteria for assigning a secondary extinction to a species, i.e., if an extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction because it has no resources.
+Numerous studies have used topological criterion for assigning a secondary extinction to a species, i.e., if extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @soleComplexityFragilityEcological2001].
 
 When there are few primary extinctions, and these cause many secondary extinctions, a food web is said to be fragile or not robust.
-When there are few secondary extinctions, a food web is said to be robust.
-Several studies have shown that the robustness of the food webs increases with food web connectance.
-Also, the removal (primary extinction) of the most connected species cause considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
-Simulation studies like these, which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure, provide an alternate solution to canonical experiments in natural ecosystems which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
+In contrast, a food web is said to be robust when there are only a few secondary extinctions.
+Several studies have shown that the robustness of the food webs increases with food web connectance [@dunneNetworkStructureBiodiversity2002; @dunneCascadingExtinctionsCommunity2009].
+Additionally, these studies have demonstrated that the removal (primary extinction) of the most connected species causes considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
+Simulation studies like these, which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure, provide an alternate solution to canonical experiments in natural ecosystems, which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
 
-Along with quantifying food web robustness based on its topological structure, studies such as @williamsEffectsNetworkDynamical2008, @broseAllometricScalingEnhances2006 and @martinezDiversityComplexityPersistence have quantified robustness based on the abundance dynamics of a food web.
-The topological approach of quantifying a food web robustness only requires the food web structure whereas the dynamical approach not only requires the food web structure but also the temporal dynamics of abundance of species in that food web.
-For example: @williamsEffectsNetworkDynamical2008 combined models of network structure with models of bioenergetic dynamics to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
+Along with quantifying food web robustness based on its topological structure, studies such as @williamsEffectsNetworkDynamical2008, @broseAllometricScalingEnhances2006, and @martinezDiversityComplexityPersistence have quantified robustness based on the abundance dynamics of a food web.
+However, the topological approach of quantifying a food web's robustness only requires the food web structure, whereas the dynamical approach requires the food web structure and the temporal dynamics of the abundance of species in that food web.
+For example, @williamsEffectsNetworkDynamical2008 combined network structure models with bioenergetic dynamics models to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
 
@@
 
-A key assumption of the observed food webs is that they are very well sampled i.e.
+A key assumption of the observed food webs is that they are very well sampled, i.e.
 all the links that in reality can occur are represented.
-However, it is known that not all food webs are very well sampled and then do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
-Some rare trophic links require more sampling effort as compared to others, whereas some trophic links remain unobserved because of linkage constraints irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
+However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
+Some rare trophic links require more sampling effort than others, whereas some trophic links remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
 Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
-Therefore, one solution to compensate for undersampling is to use a food web model such as the Allometric Diet Breadth Model (ADBM) to predict the missing links, and to then measure the robustness of the predicted food web.
-The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator where trophic interactions satisfying those rules would be predicted by the model which are perhaps not observed because those interactions are rare.
-However, this solution is not infallible, as it is likely that the food web model might still miss some links, and also may predict some links that could not, in fact occur.
+One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] to predict the missing links and then measure the robustness of the predicted food web.
+The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare.
+However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.
 
@@
 In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs.
-We expect the ADBM predicted food webs to be more robust as compared to the observed food webs, and for the greater robustness to be related to the amount by which the ADBM overestimates connectance.
-We do this by simulating primary species loss in 12 food webs predicted from the ADBM to quantify the secondary loss of extinctions.
+We expect the ADBM predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the ADBM predicts greater connectance compared to that of the observed food webs.
+We do this by simulating primary species loss in 12 food webs predicted by the ADBM to quantify the secondary loss of extinctions and compare the robustness of food webs predicted by the ADBM to the robustness of the observed food webs.
 We use three different approaches of primary species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
@@
 
-<!-- [OP] ## Provide overview of the methods -->
-
-In the upcoming sections, we present a detailed account of the implementation of simulation of primary extinctions for three different extinction scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems and compute the resultant secondary extinctions.
-We then describe a robustness metric of those predicted food webs and how we compare to properties of the food webs.
+In the upcoming sections, we present a detailed account of the implementation of the simulation of primary extinctions for three different extinction scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems and compute the resultant secondary extinctions.
+We then describe a robustness metric of those predicted food webs and how we compare them to the properties of the food webs.
 
@@
 The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966].
-We chose this model because we have already used it to predict missing links in the predicted food webs, whereby it consistently overestimated connectance  @guptaSimultaneouslyEstimatingFood2022.
+We chose this model because it is known to predict greater connectance in the predicted food webs compared to the observed food webs [@guptaSimultaneouslyEstimatingFood2022].
 The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
-The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate i.e.
+The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate, i.e.
 how fast a predator searches space, and prey densities.
 Each of these variables is derived from the allometric scaling relationship using the body sizes of species.
-More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in @petchey2008.
+More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in open access @petchey2008.
 
@@
 The observed food webs that we fit the ADBM to belong to marine, freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}).
-These food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids and also contain various types of feeding interactions, including predation, herbivory, bacterivory, parasitism and pathogenic.
-The observed connectance of these food webs varies from 0.03 to 0.24 and the number of species varies from 29 to 239 species.
-
-**OP: reduce the width of the final column of table 1.**
-**OP: state how and why these set of 12 food webs were chosen to study by us.**
-
+We considered these food webs because they belong to diverse ecosystems and follow FAIR (Findable Accessible Interoperable Reusable) principles [@wilkinsonFAIRGuidingPrinciples2016].
+These food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids and various feeding interactions, including predation, herbivory, bacterivory, parasitism and pathogenic.
+The observed connectance of these food webs varies from 0.03 to 0.24 (Links/Species$^2$), and the number of species varies from 29 to 239.
 The goodness of fit of the ADBM's predictions depends on the interaction types in the food webs.
-Those with size-structured interactions, such as herbivory in aquatic ecosystems interactions being better predicted when compared to less size-structured ones such as parasitoids and terrestrial herbivory ones [@petchey2008].
+For example, those with size-structured interactions, such as herbivory in aquatic ecosystems, are better predicted compared to less size-structured ones, such as parasitoids and terrestrial herbivory ones [@petchey2008].
 
@@
   landscape(margin = "1cm") %>%
-  column_spec(1, width = "3cm") %>%
-  column_spec(2, width = "8em") %>%
-  column_spec(7, width = "8em") %>%
-  column_spec(8, width = "8em") %>%
-  column_spec(9, width = "8em")
+  column_spec(1, width = "4cm") %>%
+  column_spec(2, width = "3cm") %>%
+  column_spec(4, width = "2cm") %>%
+  column_spec(5, width = "2cm") %>%
+  column_spec(6, width = "3cm")
 
@@
 
-The ADBM was parameterised using approximate Bayesian computation (ABC) where a set of parameter values were sampled from the prior distributions.
-That set of parameter values was either accepted or rejected based on how close the predicted food web is to the observed food web using an accuracy metric -- true skill statistic (TSS).
-The accepted parameter values then formed a posterior distribution.
-Further, prediction intervals of the true skill statistic and connectance of the predicted food webs were computed.
-In our study, we considered food webs where the predicted connectance lay within the 95% prediction interval.
+The ADBM was parameterised using approximate Bayesian computation (ABC), where a set of parameter values were sampled from a prior distribution.
+Then, that set of parameter values was either accepted or rejected based on how close the predicted food web was to the observed food web using an accuracy metric -- true skill statistic (TSS).
+The accepted parameter values formed a posterior distribution (Fig.
+4 and S14-S25 in @guptaSimultaneouslyEstimatingFood2022).
+Further, prediction intervals of the true skill statistic and connectance of the predicted food webs were computed (Fig.
+5 (a, b) in @guptaSimultaneouslyEstimatingFood2022).
+In our study, we considered model predicted food webs where the predicted connectance lay within the 95% prediction interval of all model predicted food webs.
 A detailed explanation of the parameterisation method can be found in @guptaSimultaneouslyEstimatingFood2022.
@@
 
-We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of the three criteria: removal of (i) the most-connected species, (ii) the least-connected species and (iii) randomly chosen species.
-The most-connected and least-connected criteria are based on the degree (i.e.
-the total number of links to resources and from consumers) of species.
-We considered these three criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web and the extinction of most-connected species and least-connected species takes into account the two opposite extreme scenarios.
-These extinction scenarios have been widely used in studying species extinctions and collapse of food webs and other networks [@dunne2002network; @soleComplexityFragilityEcological2001; @dunne2004; @dunneCascadingExtinctionsCommunity2009; @albertStatisticalMechanicsComplex2002].
+We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of the three criteria: removal of (i) the most connected species, (ii) the least connected species and (iii) randomly chosen species.
+The most connected and least connected criteria are based on species' degree (i.e.
+the total number of links to resources and from consumers).
+We considered these three criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web, while the extinction of the most connected species and least connected species takes into account the two opposite extreme scenarios.
+These extinction scenarios have been widely used in studying species extinctions and the collapse of food webs and other networks [@dunne2002network; @soleComplexityFragilityEcological2001; @dunne2004; @dunneCascadingExtinctionsCommunity2009; @albertStatisticalMechanicsComplex2002].
 
-Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web and a secondary extinction was recorded.
+Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded.
 Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
-Once no more secondary extinctions occurred, then another primary extinction was made, of the next appropriate species depending on the extinction scenario.
+Once no more secondary extinctions occurred, then another primary extinction was made of the next appropriate species depending on the extinction scenario.
 This process was carried out until all the species were extinct from the food web.
 
-The robustness (R) of a food web was defined as the proportion of species subjected to primary removals that resulted in extinction (primary and secondary extinctions) of some specified proportion of the species.
+The robustness (R) of a food web was defined as the proportion of species subjected to primary removals resulting in extinction (primary and secondary extinctions) of some specified proportion of the species.
 In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, which results in at least 50% of total species loss [@dunne2002network; @dunne2004; @jonssonReliabilityR50Measure2015; @dunneCascadingExtinctionsCommunity2009].
 Therefore, if primary extinctions never cause any secondary extinctions, the food web is maximally robust and ($R_{50} = 0.50$).
-Whereas in a minimally robust community ($R_{50} = 1/S$), the first primary extinction causes a cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
+Whereas in a minimally robust community ($R_{50} = 1/S$, where $S$ is the number of species), the first primary extinction causes a cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
 at least $S/2 - 1$).
@@
 First, we simulated primary species loss in food webs predicted by the ADBM which had the maximum true skill statistics and compared it to primary species loss in observed food webs.
-Second, to take into account the uncertainty in robustness in the ADBM predicted food webs we simulated primary species loss and thereby computed robustness for all the ADBM predicted food webs corresponding to the 95% prediction interval of the predicted connectance.
+Second, to take into account the uncertainty in robustness in the ADBM predicted food webs, we simulated primary species loss and thereby computed robustness for all the ADBM predicted food webs corresponding to the 95% prediction interval of the predicted connectance.
 Furthermore, in the case of the random extinction scenario, we simulated 1000 random extinction sequences in a single ADBM predicted food web.
@@
 To quantify the effect of undersampling, i.e.
-overestimation of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (I.e 0.5 for $R_{50}$ and 1 for connectance).
-However, we did not perform any statistical significance test because we work with simulated food webs and therefore the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].
+greater connectance of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (i.e.
+0.5 for $R_{50}$ and 1 for connectance).
+However, we did not perform any statistical significance test because we work with simulated food webs and therefore, the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].
 
@@
 We then compare the robustness of all the ADBM predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
-Finally we quantify the effect of overestimation of connectance on the difference in their robustness estimates.
+Finally, we quantify the effect of the difference in their connectance on the difference in their robustness estimates.
 
@@
 
-In the most-connected extinction scenario, the cumulative secondary extinction curves started to rise steeply at a lower number of primary species removal in the observed food webs as compared to the ADBM predicted food webs for nine food webs (Fig.
+In the most connected extinction scenario, the cumulative secondary extinction curves started to rise steeply in the observed food webs at a lower number of primary species removal as compared to the ADBM predicted food webs for nine food webs (Fig.
 \ref{fig:fig_r1} (a, c, d, e, f, g, h, j, l)).
-However there were higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal in five food webs (Fig.
+However, there was a higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal in five food webs (Fig.
 \ref{fig:fig_r1} (a, f, g, h, k)).
@@
 \ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show example variation caused by different random primary extinction orders.
-The secondary extinctions in the ADBM predicted food webs were more abrupt than that in the observed food webs.
+The secondary extinction curves of the ADBM predicted food webs were steeper than that of the observed food webs, i.e.
+primary removal of some species in an extinction sequence can lead to the complete collapse of the remaining food web in the ADBM predicted food webs.
 
-**OP: expand and clarify what is meant by abrupt... describe this in a sentence. (Abrupt could mean different things to different people, so clarification would be good.)
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
+```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
 S denotes the number of species in a food web.
@@
 
-Compared to the most-connected and random extinction scenarios, there were fewer secondary extinctions in the least-connected extinction scenario and therefore the secondary extinction curves were flat for many of the food webs (Fig.
+Compared to the most connected and random extinction scenarios, there were fewer secondary extinctions in the least connected extinction scenario, and therefore the secondary extinction curves were flat for many of the food webs (Fig.
 \ref{fig:fig_r3}).
@@
 \ref{fig:fig_r3} (b, c, g, h, i, k, l)}).
-In five of the food webs, a very high number of secondary extinctions occurred at very low number of primary species removal (Fig.
+In five of the food webs, a very high number of secondary extinctions occurred at a very low number of primary species removal (Fig.
 \ref{fig:fig_r3} (a, d, e, f, j)).
@@
 
-The ADBM predicted food webs were more robust than the observed food webs on average in the most-connected and random extinction scenarios (Fig.
+The ADBM predicted food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig.
 \ref{fig:fig_r4} (a, b)).
-However, there were large variations in the robustness within the ADBM predicted food webs in the most-connected extinction scenario (Fig.
+However, there were large variations in the robustness within the ADBM predicted food webs in the most connected extinction scenario (Fig.
 \ref{fig:fig_r4} (a)).
@@
 
-The food webs were more robust to the random extinction scenario than the most-connected scenario (Fig.
+The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
+\ref{fig:fig_r4} (a, b)).
+Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
+\ref{fig:fig_r4} (b)).
+Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
+Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
+The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
 \ref{fig:fig_r4} (a, b)).
@@
 
-In the least-connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig.
+In the least connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig.
 \ref{fig:fig_r4} (c)), however there were some exceptions.
@@
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
-Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.
+Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
 Some points are not visible due to perfect overlap in b and c.
 Refer to Fig.
-7 in the Supplementary Information for a faceted visualisation."}
+7 in the Supplementary Information for a faceted visualisation.
+The dashed black lines are the 1:1 relationships for reference."}
 knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
@@
 
-**OP: "Box" in the figure caption is stated, but it is not clear where boxes are in the figure.
-
-In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size of connectance on robustness was positive on average in the most-connected extinction scenario (Fig.
-\ref{fig:fig_r5} (a)) i.e.
-overestimation of connectance had a positive effect on the robustness.
-In the random extinction scenario, there was a positive effect of overestimation of connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig.
+In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig.
+\ref{fig:fig_r5} (a)), i.e.
+greater connectance had a positive effect on the robustness.
+In the random extinction scenario, there was a positive effect of greater connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig.
 \ref{fig:fig_r5} (b)).
 However, the effect size varied across the food webs.
-In the least-connected extinction scenario, the overestimation of connectance had little effect on average on the difference in the robustness (Fig.
+In the least connected extinction scenario, the median effect sizes were zero or very close to zero for all the food webs except Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig.
 \ref{fig:fig_r5} (c)).
+However, there were lots of outlier effect sizes less than zero.
 
-**OP: In figure 5c it looks like most of the data is less than zero, i.e. higher connectance is associated with lower robustness.**
-
-```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e ratio of difference in normalised robustness between ADBM predicted food webs and observed food webs to difference in their normalised connectance) shown for the 12 food webs.
-Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e.
+ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs.
+Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5."}
 knitr::include_graphics("../results/plot_R50_slope.png")
@@
 The considerable variation of the robustness of the ADBM predicted food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling.
-As was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average.
-A future development would be to understand how undersampling, i.e.
-overestimation of connectance, influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs, and compare it with the patterns in our study in which extinction occur only by topological criteria.
-**OP: what might one expect, based on previous work/evidence/results?*
-
-<!-- ## What does overestimation of connectance imply in terms of stability? -->
+Furthermore, as was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average.
+Future development would be to understand how undersampling, i.e.
+predicted greater connectance, influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria.
+However, one would expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].
 
@@
 \ref{fig:fig_r4}) for all of the 12 food web ecosystems (with some exceptions).
-This is likely due to the higher connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has on average more trophic links as compared to a food web with a lower connectance (Fig.
+This is likely due to the greater connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has, on average, more trophic links as compared to a food web with a lower connectance (Fig.
 \ref{fig:fig_r5}).
@@
 
-The findings from our study are similar to what had been documented for other food web models [@dunneCascadingExtinctionsCommunity2009], in terms of an increase in the robustness when the connectance of a food web is increased.
-However, contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig.
+## A paragraph on the implication of our study
+
+* On the uncertainty in the ADBM estimates 
+* On the limitation of a food web model 
+* On undersampling
+
+Contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig.
 \ref{fig:fig_r5}).
-**OP: the next sentence seems to be repeating the previous two, rather than adding some content.
-Please clarify what development is provided in the next sentence** The ADBM usually predicted higher connectance than that of the observed food webs however, in some cases an increase in connectance resulted in lower robustness (Fig.
-\ref{fig:fig_r5}) in the predicted food web.
-For example: the Benguela Pelagic and Small Reef food webs were surprisingly less robust to primary extinctions on average in the least-connected extinction scenario (Fig.
+For example, the Benguela Pelagic and Small Reef ADBM predicted food webs were surprisingly less robust to primary extinctions on average in the least connected extinction scenario compared to the observed food webs (Fig.
 \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
-**OP.
-next sentence is my suggestion, please check it is accurate** In these two food webs, extinction of the least connected species could cause an almost complete, or complete collapse of the food web.
-We suspect this is because the ADBM is underestimating the proportion of basal species in the predicted food webs when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
-As a result, these low degree basal species are the ones to be removed at an early stage in the deletion sequence thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
-This suggests that the overestimation of connectance by the ADBM resulted in a more robust food web on average but differences in the predicted food web properties such as underestimation of the proportion of basal species and overestimation of the maximum trophic level (Fig: \ref{fig:fig_a1}) counteracted that effect and led to reduced robustness.
-This suggests that food web properties other than connectance play an important role in determining the robustness of a food web and therefore should be also taken into account (**OP: add a citation to one or more of the published studies that have shown this.).
-
-<!-- ## Explain how ADBM predicts diet, that the ADBM can only predicts contiguous diets [OP] and the implications of this -->
-
-**OP: the next sentence does not add any value, which is not so good in a two sentence paragraph.
-You could delete the first sentence and replace it with some sentences along the lines of: One of the choices we made was to use the ADBM, whereas we could have chosed to use other models.
-Alternative include modelX, modelY,...
-And then describe those models in some detail and the continue what remains here.** The ADBM based on its size-based rules predicts the diet of a consumer and hence is able to predict some links in the predicted food webs which do in reality occur but are actually not observed in the observed food webs perhaps because of low sampling effort.
-<!-- This could also be possible because of rare prey-predator interactions even when sampling is extensive [@grayJoiningDotsAutomated2015; @woodwardChapterIndividualBasedFood2010; @jordanoSamplingNetworksEcological2016].
--->
-A future study could be to extend our study to use other food webs models based on size-based rules such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021 and compare them with our study.
-We expect, however, similar results because these food webs are also based on body size rules.
+In these two food webs, the extinction of the least connected species could cause an almost complete, or complete collapse of the food web.
+We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
+As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
+This suggests that the greater connectance predicted by the ADBM resulted in a more robust food web on average.
+However, differences in the predicted food web properties, such as a lower proportion of basal species and higher maximum trophic level (Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness.
+On average, a consumer in a food web with a higher maximum trophic level would have fewer resources and be more susceptible to extinction than a consumer in a food web with a lower maximum trophic level [@binzerSusceptibilitySpeciesExtinctions2011].
+This suggests that food web properties other than connectance play an important role in determining a food web's robustness and, therefore, should also be taken into account [@binzerSusceptibilitySpeciesExtinctions2011; @mendoncaRobustnessTemperateTropical2022; @riedeSizebasedFoodWeb2011].
 
@@
 Real false positive means that the food web model predicts a link between two species that can never interact.
-(The other type of false positive is when the model predicts a link that was not observed, but when it could have been observed.
-In this case, further sampling should result in the link being observed and a change from false positive to true positive.) Firstly this may be because the ADBM uses only body size as a trait.
+(The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
+In this case, further sampling should result in the link being observed and a change from false positive to true positive.) Firstly, this may be because the ADBM uses only body size as a trait.
 A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022].
@@
 However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall].
-Therefore a future study could extend our study with other food web models which are not based on body size such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008.
+Hence, it would be intriguing to extend our study to use other food web models based on size-based rules, such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021, to understand if the results are dependent on the decision of model selection.
+We expect to get a similar result in a size-based deterministic model but a different result, i.e.
+lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010].
+It would also be interesting to use food web models not based on body size, such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008.
 We expect to have a difference in results based on whether the trophic interactions in the food webs are governed by size-structured rules or not.
@@
 It would be intriguing to know if this difference in connectance has a similar influence on the dynamical stability of the food webs as well.
-Hence, a prospect could be to use a dynamical model (for example bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
-**OP: please try to clarify/futher explain the following sentence, as I don't quite understand it.** We expect that the difference in dynamical robustness of the ADBM predicted and the observed food webs would be similar to differences in their topological robustness because the dynamical robustness of the ADBM predicted and the observed food webs would be both underestimated when compared to their topological robustness [@curtsdotterRobustnessSecondaryExtinctions2011a].
-
-<!-- ## Incorporate trait-based deletions sequences -->
-
-<!-- Although our study takes into account all the theoretically possible extinction sequences of species in a food web, a future development could be to specifically consider extinction sequences which are more realistic based on species traits which are more realistic than the others [@bergEcologicalCommunitiesAre2015; @jacobRoleBodySize2011].
-This can help to understand which extinction sequences results in a greater difference in robustness of the ADBM predicted food webs and that of the observed food webs.
--->
+Hence, a prospect could be to use a dynamical model (for example, the bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
+We expect that the greater connectance will lead to reduced dynamical stability in the ADBM predicted food web compared to that of the predicted food web.
+The difference in stability will be linearly related to the difference in connectance because @martinezDiversityComplexityPersistence has shown that food web stability linearly decreases with connectance.
 
@@
 
-Since the ADBM underestimates the proportion of basal species and overestimates the maximum trophic level in the predicted food webs compared to that of the observed food webs **OP: you/ we must give evidence for this new assertion**, it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
-We would explain more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.
+Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig.
+\ref{fig:fig_a1} in Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
+We would expect a more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.
 
@@
 
-We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links i.e.
-overestimation of connectance on the topological robustness of 12 food webs from various ecosystems.
-We found that the overestimation of connectance can have large impacts on the robustness of the food webs, while at the same time producing large variation in robustness among the predicted food webs.
-Differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are responsible.
+We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e.
+greater connectance on the topological robustness of 12 food webs from various ecosystems.
+We found that the greater connectance can have a large impact on the robustness of the food webs while at the same time producing large variations in robustness among the predicted food webs.
+Furthermore, differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are also responsible.
 
@@
 This work was supported by the University Research Priority Program Global Change and Biodiversity (Grant number: U-704-04-11) of the University of Zurich.
+We thank the Petchey group members for their valuable suggestions in the manuscript.
 
@@
 **Owen L.
-Petchey:** Conceptualization, Funding acquisition, Resources, Supervision, Writing -- review & editing.
-**AG:** Owen, Could you please add your contributions here? **OP: done**
+Petchey:** Conceptualization; Funding acquisition; Resources; Supervision; Writing -- review & editing.
 
@@
 
-To be added
-<!-- All the data used in this study was collected in other studies and is openly available.
+All the data used in this study was collected in other studies and is openly available.
 We list those studies and the open access source in Table \ref{fig:tab_1}.
-The complete code used in the analysis is available in the repository <XXX>.
--->
+The complete code used in the analysis is available in the repository <https://doi.org/10.5281/zenodo.7180835>.
 
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_a1} Maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
-Box represent 25th and 75th percentile; bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
+Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
+The dashed black lines are the 1:1 relationships for reference."}
 knitr::include_graphics("../results/plot_max_tl_ADBM_vs_emp.png")
@@
 
-```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
+```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
-Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5."}
+Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
+The dashed black lines are the 1:1 relationships for reference."}
 knitr::include_graphics("../results/plot_R50_ADBM_vs_obs_ra_lc_facet.png")

### 2023-02-10 manuscript/ms_C3_v2.tex
updated ms

@@
 \usepackage{lineno}
+\linenumbers
 \usepackage {amsmath}
@@
   Previous research shows that (i) food web robustness (the inverse of
-  the number of secondary extinctions occuring due to primary
+  the number of secondary extinctions occurring due to primary
   extinctions) increases with connectance (the number of realised
   trophic links divided by the number of possible links), and (ii) that
-  predicted food webs usually have greater connectance than observed
-  ones. Thus we expect that predicted food webs are more robust than
-  observed ones. This expectation has never, to our knowledge, been
-  tested, nor has the effect size been quantified.
+  model predicted food webs usually have greater connectance than
+  observed ones. Thus, we expect that predicted food webs are more
+  robust than observed ones. However, this expectation has never, to our
+  knowledge, been tested, nor has the effect size, i.e.~the difference
+  in robustness of predicted and observed food web with respect to the
+  difference in their connectance, been quantified.
 \item
@@
   webs to the robustness of food webs predicted by a model (the ADBM)
-  that can account for missing links, though can also make false
-  positives. We did this for 12 different food webs from a wide variety
-  of ecosystems.
+  that can account for missing links but does not predict all links
+  correctly. We did this for 12 different food webs from a wide variety
+  of ecosystems. We used three extinction scenarios: random, most
+  connected, and least connected.
 \item
   We found, as expected, that the predicted food webs were more robust
-  than the observed food webs, and this can be attributed to the higher
+  than the observed food webs, which can be attributed to the higher
   connectance of the predicted food webs. On average, for every one unit
-  of increase in connectance, we found the food webs to be robust by
-  0.52 units and 0.04 units for the most connected and the random
-  species extinction scenarios respectively while no effect in the least
-  connected species extinction scenario.
+  of increase in connectance, we found that the food webs robustness
+  increased by 0.52 units for the most connected species extinction
+  scenario and by 0.04 units for the random species extinction
+  scenarios. On the other hand, we saw no effect, on average, of
+  increased connectance for the least connected species extinction
+  scenario for all except two of the 12 food webs.
 \item
@@
   missing links with food web models. Nevertheless, increased
-  connectance may contribute to lower dynamical stability, and so it
-  would be interesting to compare the dynamical stability of observed
-  and predicted food webs, as well as the topological stability that we
-  have focused on.
+  connectance may contribute to lower dynamical stability, so it would
+  be interesting to compare the dynamical stability of observed and
+  predicted food webs and the topological stability that we have focused
+  on.
 \end{enumerate}
@@
 Anthropogenic changes such as climate change and habitat destruction are
-a threat to biodiversity, and can lead to food web collapse (Ullah et
-al. 2018). This food web collapse is due to the cascades of secondary
-extinctions in a food web because of the primary loss of species, for
-example due to habitat destruction and climate change (Pimm et al. 2006;
-J. A. Thomas et al. 2004; C. D. Thomas et al. 2004). Therefore, research
-focused on cascading secondary extinctions also known as `community
-viability analysis' have been performed extensively in the past few
-decades to quantify how robust are food webs to species extinction
-(Jennifer A. Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and
-Williams 2009; Berg et al. 2011; Ebenman, Law, and Borrvall 2004;
-Ebenman and Jonsson 2005). And it has been shown that the rate of
-collapse of a food web is dependent on its structure and complexity
-(Jennifer A. Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and
-Williams 2009).
+a threat to biodiversity and can lead to food web collapse (Ullah et
+al., 2018). This food web collapse is due to the cascades of secondary
+extinctions in a food web because of the primary loss of species due to
+environmental change (Pimm et al., 2006; C. D. Thomas et al., 2004; J.
+A. Thomas et al., 2004). An example of a secondary extinction is when a
+consumer goes extinct because its sole resource species goes extinct.
+Therefore, research focused on cascading secondary extinctions, also
+known as `community viability analysis', has been performed extensively
+in the past few decades to quantify how robust food webs are to species
+extinction (Berg et al., 2011; Dunne et al., 2002a; Dunne \& Williams,
+2009; Ebenman et al., 2004; Ebenman \& Jonsson, 2005). This research
+revealed that the rate of collapse of a food web depends on its
+structure and complexity (Dunne et al., 2002a; Dunne \& Williams, 2009).
 
 Simulation of primary species loss has been conducted in observed food
-webs and model food webs from terrestrial and aquatic ecosystems where
-robustness was measured in terms of secondary extinctions (Jennifer A.
-Dunne, Williams, and Martinez 2002b; Jennifer A. Dunne and Williams
-2009). These studies have shown that the robustness of the food webs
-increases with food web connectance. Also, the removal of the most
-connected species cause considerably more secondary extinctions than the
-random removals of species (Jennifer A. Dunne, Williams, and Martinez
-2002a; Sol'e and Montoya 2001). Simulation studies like these which
-investigate the impact of primary extinctions in a food web to quantify
-robustness based on its topological structure provide an alternate
-solution to canonical experiments in natural ecosystems which are not
-possible or very difficult to conduct (Jennifer A. Dunne and Williams
-2009).
+webs and model food webs from terrestrial and aquatic ecosystems, where
+robustness was measured in terms of secondary extinctions (Dunne et al.,
+2002a; Dunne \& Williams, 2009). Primary species loss is considered to
+be extinction of a species due to causes external to the food web,
+e.g.~overharvesting (Koning \& McIntyre, 2021), introduction of invasive
+species (David et al., 2017). A secondary extinction is an extinction
+caused by a previous extinction (either primary or secondary). Numerous
+studies have used topological criterion for assigning a secondary
+extinction to a species, i.e., if extinction is of the last resource
+species of a consumer species, then the consumer species suffers
+secondary extinction (Dunne et al., 2002a; Dunne \& Williams, 2009;
+Sol'e \& Montoya, 2001).
+
+When there are few primary extinctions, and these cause many secondary
+extinctions, a food web is said to be fragile or not robust. In
+contrast, a food web is said to be robust when there are only a few
+secondary extinctions. Several studies have shown that the robustness of
+the food webs increases with food web connectance (Dunne et al., 2002b;
+Dunne \& Williams, 2009). Additionally, these studies have demonstrated
+that the removal (primary extinction) of the most connected species
+causes considerably more secondary extinctions than the random removals
+of species (Dunne et al., 2002b; Sol'e \& Montoya, 2001). Simulation
+studies like these, which investigate the impact of primary extinctions
+in a food web to quantify robustness based on its topological structure,
+provide an alternate solution to canonical experiments in natural
+ecosystems, which are not possible or very difficult to conduct (Dunne
+\& Williams, 2009).
 
 Along with quantifying food web robustness based on its topological
-structure, studies such as Williams (2008), Brose, Williams, and
-Martinez (2006) and Martinez, Williams, and Dunne (2006) have quantified
-robustness based on the abundance dynamics of a food web. The
-topological approach of quantifying a food web robustness only requires
-the food web structure whereas the dynamical approach not only requires
-the food web structure but also the temporal dynamics of abundance of
-species in that food web. For example: Williams (2008) combined models
-of network structure with models of bioenergetic dynamics to study the
-role of food web topology and nonlinear dynamics on species coexistence
-in complex ecological networks.
+structure, studies such as Williams (2008), Brose et al. (2006), and
+Martinez et al. (2006) have quantified robustness based on the abundance
+dynamics of a food web. However, the topological approach of quantifying
+a food web's robustness only requires the food web structure, whereas
+the dynamical approach requires the food web structure and the temporal
+dynamics of the abundance of species in that food web. For example,
+Williams (2008) combined network structure models with bioenergetic
+dynamics models to study the role of food web topology and nonlinear
+dynamics on species coexistence in complex ecological networks.
 
 A key assumption of the observed food webs is that they are very well
-sampled i.e.~all the links that in reality can occur are represented.
-However, it is known that not all food webs are very well sampled and
-then do not represent all of the feeding links that occur (Caron et al.
-2022; Patonai and Jord'an 2017; Jordano 2016). Some rare trophic links
-require more sampling effort as compared to others whereas some trophic
-links remain unobserved because of linkage constraints irrespective of
-sufficient sampling effort (Jordano 2016). Previous studies such as
-Caron et al. (2022) and Gupta, Furrer, and Petchey (2022) have shown
+sampled, i.e.~all the links that in reality can occur are represented.
+However, it is known that not all food webs are very well sampled and do
+not represent all of the feeding links that can occur (Caron et al.,
+2022; Jordano, 2016; Patonai \& Jord'an, 2017). Some rare trophic links
+require more sampling effort than others, whereas some trophic links
+remain unobserved because of biological constraints such as
+spatio-temporal uncoupling, size or reward mismatching, foraging
+constraints and physiological-biochemical constraints, which are
+irrespective of sufficient sampling effort (Jordano, 2016). Previous
+studies such as Caron et al. (2022) and Gupta et al. (2022) have shown
 that the predicted food webs from these models usually have greater
-connectance than the observed ones. Therefore, one solution to
-compensate for undersampling is to use a food web model such as the
-Allometric Diet Breadth Model (ADBM) to predict the missing links, and
-to then measure the robustness of the predicted food web. ADBM is a
+connectance than the observed ones. One solution to compensate for
+undersampling is using a food web model such as the Allometric Diet
+Breadth Model (ADBM) (Petchey et al., 2008) to predict the missing links
+and then measure the robustness of the predicted food web. The ADBM is a
 mechanistic model constructed using foraging rules based on the body
-sizes of prey and predator where trophic interactions satisfying those
-rules would be predicted by the model which are perhaps not observed
+sizes of prey and predator, where trophic interactions satisfying those
+rules would be predicted by the model, which are perhaps not observed
 because those interactions are rare. However, this solution is not
 infallible, as it is likely that the food web model might still miss
-some links, and also may predict some links that could not, in fact
+some links and also may predict some links that could not, in fact
 occur.
@@
 In our study, we investigate the topological robustness of the ADBM
-predicted food webs and compare it to that of the observed food webs,
-and quantify the effect of undersampling i.e overestimation of
-connectance on the robustness of these predicted food webs. We expect
-that the ADBM predicted food webs to be more robust as compared to the
-observed food webs, and for the greater robustness to be related to the
-amount by which the ADBM overestimates connectance. We do this by
-simulating primary species loss in 12 food webs predicted from the ADBM
-to quantify the secondary loss of extinctions. We use three different
-approaches of species removal: (i) most connected species, (ii) random
-species and (iii) least connected species to understand if the outcome
-varies among these approaches.
+predicted food webs and compare it to that of the observed food webs. We
+expect the ADBM predicted food webs to be more robust than the observed
+food webs, and for the greater robustness to be related to the amount by
+which the ADBM predicts greater connectance compared to that of the
+observed food webs. We do this by simulating primary species loss in 12
+food webs predicted by the ADBM to quantify the secondary loss of
+extinctions and compare the robustness of food webs predicted by the
+ADBM to the robustness of the observed food webs. We use three different
+approaches of primary species removal: (i) most connected species, (ii)
+random species and (iii) least connected species to understand if the
+outcome varies among these approaches.
 
@@
 In the upcoming sections, we present a detailed account of the
-implementation of simulation of primary extinctions for three different
-extinction scenarios on 12 food webs predicted by the ADBM from a wide
-variety of ecosystems and compute the resultant secondary extinctions.
-We then compute a robustness metric to quantify the robustness of those
-predicted food webs and compare them against that of the observed food
-webs.
+implementation of the simulation of primary extinctions for three
+different extinction scenarios on 12 food webs predicted by the ADBM
+from a wide variety of ecosystems and compute the resultant secondary
+extinctions. We then describe a robustness metric of those predicted
+food webs and how we compare them to the properties of the food webs.
 
@@
 The allometric diet breadth model (ADBM) is based on optimal foraging
-theory, specifically the contingency model (MacArthur and Pianka 1966).
-We chose this model because the ADBM can likely predict missing links in
-the predicted food webs because it consistently overestimated
-connectance in the predicted food webs as shown by our study in Gupta,
-Furrer, and Petchey (2022). The ADBM predicts the set of prey species a
-consumer should feed upon to maximise its rate of energy intake (Petchey
-et al. 2008). The foraging variables used in the model are the energy
-content of prey, handling times of the predator on prey, space clearance
-rate i.e.~how fast a predator searches space, and prey densities. All of
-these variables are derived from the allometric scaling relationship
-using the body sizes of species. More details on the foraging rules
-defined in the ADBM and ADBM's predictive power across different food
-webs can be found in Petchey et al. (2008).
+theory, specifically the contingency model (MacArthur \& Pianka, 1966).
+We chose this model because it is known to predict greater connectance
+in the predicted food webs compared to the observed food webs (Gupta et
+al., 2022). The ADBM predicts the set of prey species a consumer should
+feed upon to maximise its rate of energy intake (Petchey et al., 2008).
+The foraging variables used in the model are the energy content of prey,
+handling times of the predator on prey, space clearance rate, i.e.~how
+fast a predator searches space, and prey densities. Each of these
+variables is derived from the allometric scaling relationship using the
+body sizes of species. More details on the foraging rules defined in the
+ADBM and ADBM's predictive power across different food webs can be found
+in open access Petchey et al. (2008).
 
@@
 The observed food webs that we fit the ADBM to belong to marine,
-freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). These
-food webs contain primary producers, herbivores, carnivores, parasites,
-and parasitoids and also contain various types of feeding interactions,
-including predation, herbivory, bacterivory, parasitism and pathogenic.
-The observed connectance of these food webs varies from 0.03 to 0.24 and
-the number of species varies from 29 to 239 species.
-
-The goodness of fit of the ADBM's predictions depends on the interaction
-types in the food webs with predictions that are more size-structured
-such as aquatic and herbivory interactions being better predicted when
-compared to less size-structured ones such as parasitoid and terrestrial
-herbivory ones (Petchey et al. 2008).
+freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}). We
+considered these food webs because they belong to diverse ecosystems and
+follow FAIR (Findable Accessible Interoperable Reusable) principles
+(Wilkinson et al., 2016). These food webs contain primary producers,
+herbivores, carnivores, parasites, and parasitoids and various feeding
+interactions, including predation, herbivory, bacterivory, parasitism
+and pathogenic. The observed connectance of these food webs varies from
+0.03 to 0.24 (Links/Species\(^2\)), and the number of species varies
+from 29 to 239. The goodness of fit of the ADBM's predictions depends on
+the interaction types in the food webs. For example, those with
+size-structured interactions, such as herbivory in aquatic ecosystems,
+are better predicted compared to less size-structured ones, such as
+parasitoids and terrestrial herbivory ones (Petchey et al., 2008).
 
@@
 \fontsize{7}{9}\selectfont
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{3cm}|>{\raggedright\arraybackslash}p{8em}|l|l|l|l|>{}p{8em}|>{}p{8em}|>{}p{8em}}
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}|>{\raggedright\arraybackslash}p{3cm}|l|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{2cm}|>{\raggedright\arraybackslash}p{3cm}}
 \hline
-Common food web name (Original Publication) & Predation matrix source & General ecosystem & Number of species & Observed connectance & 95\% prediction interval of predicted connectance  (Gupta et al.
+Common food web name (Original Publication) & Predation matrix source & General ecosystem & Number of species & Observed connectance (Links/Species$^2$) & 95\% prediction interval of predicted connectance  of the ADBM  (Gupta et al.
 2022)\\
@@
 Broadstone Stream (size aggregation) (Woodward
-et al. 2010) & Guy Woodward. (2021) & Freshwater & 29 & 0.24 & 0.25 - 0.47\\
+et al. 2010) & Guy Woodward (2021) & Freshwater & 29 & 0.24 & 0.25 - 0.47\\
 \hline
@@
 
-The ADBM was parameterised using approximate Bayesian computation (ABC)
-where a set of parameter values were sampled from the prior
-distributions. That set of parameter values was either accepted or
-rejected based on how close the predicted food web is to the observed
-food web using an accuracy metric -- true skill statistic (TSS). The
-accepted parameter values then formed a posterior distribution. Further,
-prediction intervals of the true skill statistic and connectance of the
-predicted food webs were computed. In our study, we considered food webs
-where the predicted connectance lay within the 95\% prediction interval.
-A detailed explanation of the parameterisation method can be found in
-Gupta, Furrer, and Petchey (2022).
+The ADBM was parameterised using approximate Bayesian computation (ABC),
+where a set of parameter values were sampled from a prior distribution.
+Then, that set of parameter values was either accepted or rejected based
+on how close the predicted food web was to the observed food web using
+an accuracy metric -- true skill statistic (TSS). The accepted parameter
+values formed a posterior distribution (Fig. 4 and S14-S25 in Gupta et
+al. (2022)). Further, prediction intervals of the true skill statistic
+and connectance of the predicted food webs were computed (Fig. 5 (a, b)
+in Gupta et al. (2022)). In our study, we considered model predicted
+food webs where the predicted connectance lay within the 95\% prediction
+interval of all model predicted food webs. A detailed explanation of the
+parameterisation method can be found in Gupta et al. (2022).
 
@@
 
-We implemented the primary species removal method from Jennifer A. Dunne
-and Williams (2009) by sequentially removing species using one of the
-three criteria: removal of (i) the most-connected species, (ii) the
-least-connected species and (iii) randomly chosen species. The
-most-connected and least-connected criteria are based on the degree
-(i.e.~the total number of links to resources and from consumers) of
-species. We considered these mentioned criteria because the random
-extinction scenario takes into account all the theoretically possible
-extinction sequences of species that can occur in a food web and the
-extinction of most-connected species and least-connected species takes
-into account the two opposite extreme scenarios. These extinction
-scenarios have been widely used in studying species extinctions and
-collapse of food webs and other networks (Jennifer A. Dunne, Williams,
-and Martinez 2002b; Sol'e and Montoya 2001; J. Dunne, Williams, and
-Martinez 2004; Jennifer A. Dunne and Williams 2009; Albert and Barab'asi
-2002).
+We implemented the primary species removal method from Dunne \& Williams
+(2009) by sequentially removing species using one of the three criteria:
+removal of (i) the most connected species, (ii) the least connected
+species and (iii) randomly chosen species. The most connected and least
+connected criteria are based on species' degree (i.e.~the total number
+of links to resources and from consumers). We considered these three
+criteria because the random extinction scenario takes into account all
+the theoretically possible extinction sequences of species that can
+occur in a food web, while the extinction of the most connected species
+and least connected species takes into account the two opposite extreme
+scenarios. These extinction scenarios have been widely used in studying
+species extinctions and the collapse of food webs and other networks
+(Albert \& Barab'asi, 2002; J. Dunne et al., 2004; Dunne et al., 2002a;
+Dunne \& Williams, 2009; Sol'e \& Montoya, 2001).
 
-Given a primary removal of species in a food web if any remaining
+Given a primary removal of species in a food web, if any remaining
 species lost all of their resource species, or any cannibalistic species
 lost all of their resource species except the cannibalistic links, they
-are removed from the web and a secondary extinction was recorded.
+are removed from the web, and a secondary extinction was recorded.
 Secondary extinctions may cause further secondary extinctions, which
 were also checked for and recorded. Once no more secondary extinctions
-occurred, then another primary extinction was made, of the next
+occurred, then another primary extinction was made of the next
 appropriate species depending on the extinction scenario. This process
@@
 The robustness (R) of a food web was defined as the proportion of
-species subjected to primary removals that resulted in a set of
-extinction (i.e.~primary removals plus secondary extinctions) of some
-specified proportion of the species. In our study, we use \(R_{50}\),
-the number of primary extinctions divided by the total number of
-species, which results in at least 50\% of total species loss (Jennifer
-A. Dunne, Williams, and Martinez 2002b; J. Dunne, Williams, and Martinez
-2004; Jonsson et al. 2015; Jennifer A. Dunne and Williams 2009).
-Therefore, if primary extinctions never cause any secondary extinctions,
-the food web is maximally robust and (\(R_{50} = 0.50\)). Whereas in a
-minimally robust community (\(R_{50} = 1/S\)), the first primary
-extinction causes a cascade of secondary extinctions of at least nearly
-half of the species in the food web (i.e.~at least \(S/2 - 1\)).
+species subjected to primary removals resulting in extinction (primary
+and secondary extinctions) of some specified proportion of the species.
+In our study, we use \(R_{50}\), the number of primary extinctions
+divided by the total number of species, which results in at least 50\%
+of total species loss (J. Dunne et al., 2004; Dunne et al., 2002a; Dunne
+\& Williams, 2009; Jonsson et al., 2015). Therefore, if primary
+extinctions never cause any secondary extinctions, the food web is
+maximally robust and (\(R_{50} = 0.50\)). Whereas in a minimally robust
+community (\(R_{50} = 1/S\), where \(S\) is the number of species), the
+first primary extinction causes a cascade of secondary extinctions of at
+least nearly half of the species in the food web (i.e.~at least
+\(S/2 - 1\)).
 
@@
 primary species loss in observed food webs. Second, to take into account
-the uncertainty in robustness in the ADBM predicted food webs we
+the uncertainty in robustness in the ADBM predicted food webs, we
 simulated primary species loss and thereby computed robustness for all
 the ADBM predicted food webs corresponding to the 95\% prediction
-interval of the predicted connectance. In the case of the random
-extinction scenario, we simulated 1000 random extinction sequences in a
-single ADBM predicted food web.
+interval of the predicted connectance. Furthermore, in the case of the
+random extinction scenario, we simulated 1000 random extinction
+sequences in a single ADBM predicted food web.
 
-\hypertarget{statistical-analysis}{%
-\subsection{Statistical analysis}\label{statistical-analysis}}
+\hypertarget{analysis}{%
+\subsection{Analysis}\label{analysis}}
 
@@
 median as a summary statistics to quantify the average robustness of a
-single food web. To quantify the effect of undersampling
-i.e.~overestimation of connectance we compute the ratio of the
-difference in normalised robustness between the ADBM predicted food webs
-and observed food webs to the difference in their normalised
-connectance, where normalisation was performed by dividing the variables
-by their maximum possible values (I.e 0.5 for \(R_{50}\) and 1 for
-connectance). However, we did not perform any statistical significance
-test because we work with simulated food webs and therefore the p-values
-of these tests are influenced by the number of model simulations (White
-et al. 2014).
+single food web to random extinction. To quantify the effect of
+undersampling, i.e.~greater connectance of connectance, we compute the
+ratio of the difference in normalised robustness between the ADBM
+predicted food webs and observed food webs to the difference in their
+normalised connectance, where normalisation was performed by dividing
+the variables by their maximum possible values (i.e.~0.5 for \(R_{50}\)
+and 1 for connectance). However, we did not perform any statistical
+significance test because we work with simulated food webs and
+therefore, the p-values of these tests are influenced by the number of
+model simulations (White et al., 2014).
 
@@
 We first present the secondary extinction curves of the ADBM predicted
-food webs which had the maximum true skill statistics and the observed
-food webs for 12 food webs under three different extinction scenarios.
-We then compare the robustness of all the ADBM predicted food webs
-within the 95\% prediction interval against that of the observed food
-webs to take into account uncertainty in the robustness across food webs
-predictions. Finally we quantify the effect of overestimation of
-connectance on the difference in their robustness estimates.
+food webs which had the maximum true skill statistics and of the
+observed food webs for 12 food webs under three different extinction
+scenarios. We then compare the robustness of all the ADBM predicted food
+webs within the 95\% prediction interval against that of the observed
+food webs to take into account uncertainty in the robustness across food
+webs predictions. Finally, we quantify the effect of the difference in
+their connectance on the difference in their robustness estimates.
 
@@
 
-In the most-connected extinction scenario, the cumulative secondary
-extinction curves started to rise steeply at a lower number of primary
-species removal in the observed food webs as compared to the ADBM
+In the most connected extinction scenario, the cumulative secondary
+extinction curves started to rise steeply in the observed food webs at a
+lower number of primary species removal as compared to the ADBM
 predicted food webs for nine food webs (Fig. \ref{fig:fig_r1} (a, c, d,
-e, f, g, h, j, l)). However there were higher number of cumulative
+e, f, g, h, j, l)). However, there was a higher number of cumulative
 secondary extinctions occurring in the ADBM predicted food webs when
 compared to that of the observed food webs at a high number of primary
-species removal (Fig. \ref{fig:fig_r1} (a, f, g, h, k)). In the Skipwith
-Pond food web, there were no secondary extinctions for any number of
-primary removal of species (Fig. \ref{fig:fig_r1} (i)), whereas in the
-Broadstone Stream (taxonomic aggregation) food web the same was true
-only for the observed food web but in the ADBM predicted food web there
-was a steep rise in the cumulative secondary extinctions (Fig.
-\ref{fig:fig_r1} (b)).
+species removal in five food webs (Fig. \ref{fig:fig_r1} (a, f, g, h,
+k)). In the Skipwith Pond food web, there were no secondary extinctions
+for any number of primary removal of species (Fig. \ref{fig:fig_r1}
+(i)), whereas in the Broadstone Stream (taxonomic aggregation) food web
+the same was true only for the observed food web but in the ADBM
+predicted food web there was a steep rise in the cumulative secondary
+extinctions (Fig. \ref{fig:fig_r1} (b)).
 
@@
 
-\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of the most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 extinctions in the ADBM predicted and the observed food webs for five
-(out of 1000) independent random extinction sequences to show
-qualitative differences between their secondary extinction curves. The
-secondary extinctions in the ADBM predicted food webs were more abrupt
-than that in the observed food webs.
+(out of 1000) independent random extinction sequences to show example
+variation caused by different random primary extinction orders. The
+secondary extinction curves of the ADBM predicted food webs were steeper
+than that of the observed food webs, i.e.~primary removal of some
+species in an extinction sequence can lead to the complete collapse of
+the remaining food web in the ADBM predicted food webs.
 
@@
 
-\caption{\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five independent random extinction sequences.
+\caption{\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
 S denotes the number of species in a food web.
@@
 
-Compared to the most-connected and random extinction scenarios, there
-were fewer secondary extinctions in the least-connected extinction
-scenario and therefore the secondary extinction curves were flat for
-most of the food webs (Fig. \ref{fig:fig_r3}). In some of the food webs,
+Compared to the most connected and random extinction scenarios, there
+were fewer secondary extinctions in the least connected extinction
+scenario, and therefore the secondary extinction curves were flat for
+many of the food webs (Fig. \ref{fig:fig_r3}). In some of the food webs,
 the extinction curves of the ADBM predicted food webs overlapped with
 the observed food webs (Fig. \ref{fig:fig_r3} (b, c, g, h, i, k, l)\}).
-Contrary to the most-connected scenario, there was a very high number of
-secondary extinctions occurring at very low number of primary species
-removal (Fig. \ref{fig:fig_r3} (a, d, e, f, j)).
+In five of the food webs, a very high number of secondary extinctions
+occurred at a very low number of primary species removal (Fig.
+\ref{fig:fig_r3} (a, d, e, f, j)).
 
@@
 
-\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary \textbf{removals of the least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
@@
 The ADBM predicted food webs were more robust than the observed food
-webs on average in the most-connected and random extinction scenarios
+webs on average in the most connected and random extinction scenarios
 (Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in
-the robustness within the ADBM predicted food webs in the most-connected
+the robustness within the ADBM predicted food webs in the most connected
 extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the ADBM
@@
 The food webs were more robust to the random extinction scenario than
-the most-connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
+the most connected scenario (Fig. \ref{fig:fig_r4} (a, b)). Small Reef
 and Benguela Pelagic food webs had more variations in robustness within
@@
 food webs in the Broadstone Stream (size aggregation) as shown by the
-outliers.
+outliers. The food webs were more robust to the random extinction
+scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a,
+b)). Small Reef and Benguela Pelagic food webs had more variations in
+robustness within the ADBM predicted food webs as compared to the other
+food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream
+(taxonomic aggregation) and Broadstone Stream (size aggregation) food
+webs were the most robust (Median \(R_{50} = 0.5\)) for both ADBM
+predicted and observed food webs. Although there were few less robust
+ADBM predicted food webs in the Broadstone Stream (size aggregation) as
+shown by the outliers.
 
-In the least-connected extinction scenario, the food webs had a very
+In the least connected extinction scenario, the food webs had a very
 high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
@@
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).
-Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.
+Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
 Some points are not visible due to perfect overlap in b and c.
 Refer to Fig.
-7 in the Supplementary Information for a faceted visualisation.}\label{fig:unnamed-chunk-5}
+7 in the Supplementary Information for a faceted visualisation.
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 In all of the food webs except Small Reef and Broadstone Stream
-(taxonomic aggregation), the effect size was positive on average in the
-most-connected extinction scenario (Fig. \ref{fig:fig_r5} (a))
-i.e.~overestimation of connectance had a positive effect on the
-robustness. In the random extinction scenario, there was a positive
-effect of overestimation of connectance on the robustness for Ythan,
-Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom
-and Benguela Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect
-size varied across the food webs. In the least-connected extinction
-scenario, the overestimation of connectance had little effect on average
-on the difference in the robustness (Fig. \ref{fig:fig_r5} (c)).
+(taxonomic aggregation), the effect size of connectance on robustness
+was positive on average in the most connected extinction scenario (Fig.
+\ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
+the robustness. In the random extinction scenario, there was a positive
+effect of greater connectance on the robustness for Ythan, Small Reef,
+Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela
+Pelagic (Fig. \ref{fig:fig_r5} (b)). However, the effect size varied
+across the food webs. In the least connected extinction scenario, the
+median effect sizes were zero or very close to zero for all the food
+webs except Benguela Pelagic and Small Reef food webs where the median
+effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
+were lots of outlier effect sizes less than zero.
 
@@
 
-\caption{\label{fig:fig_r5} Effect size (i.e ratio of difference in normalised robustness between ADBM predicted food webs and observed food webs to difference in their normalised connectance) shown for the 12 food webs.
-Box represent 25th and 75th percentile; black bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-6}
+\caption{\label{fig:fig_r5} Effect size (i.e.
+ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs.
+Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-6}
 \end{figure}
@@
 
-The primary removal of species revealed that the ADBM predicted food
-webs are more robust than the observed food webs on average, with
-variation within the robustness of the ADBM predicted food webs in the
-12 food web ecosystems suggesting that undersampling in food webs can
-lead to differences in the estimates of food web robustness. The food
-webs are least robust to primary extinction of the most connected
-species scenario compared to that of least connected and random
-extinction scenarios on average. A future development would be to
-understand how undersampling i.e.~overestimation of connectance
-influences the stability of the dynamics of the ADBM predicted food webs
-against that of the observed food webs, and compare it with our study.
+As expected, the ADBM predicted food webs were more robust than the
+observed food webs on average. The considerable variation of the
+robustness of the ADBM predicted food webs suggests, however, that
+undersampling in food webs can lead to considerable uncertainty in the
+estimates of food web robustness, even when a model is used to
+compensate for undersampling. Furthermore, as was previously found, the
+food webs are least robust to primary extinction of the most connected
+species compared to that of least connected and random extinction
+scenarios on average. Future development would be to understand how
+undersampling, i.e.~predicted greater connectance, influences the
+stability of the dynamics of the ADBM predicted food webs against that
+of the observed food webs and compare it with the patterns in our study
+in which extinction occur only by topological criteria. However, one
+would expect a decrease in food web stability with greater connectance
+(Martinez et al., 2006; May, 1972).
 
-The robustness of the ADBM predicted food webs were higher than that of
-the observed food webs on average (Fig. \ref{fig:fig_r4}) for all of the
-12 food web ecosystems with some exceptions. This can be attributed to
-the higher connectance of the ADBM predicted food webs as compared to
-that of the observed food webs because a species in a food web with a
-higher connectance has on average more trophic links as compared to a
-food web with a lower connectance (Fig. \ref{fig:fig_r5}). Our study
-suggests that it is important to consider undersampling in observed food
-webs when computing their robustness.
+As mentioned, the robustness of the ADBM predicted food webs was higher
+than that of the observed food webs on average (Fig. \ref{fig:fig_r4})
+for all of the 12 food web ecosystems (with some exceptions). This is
+likely due to the greater connectance of the ADBM predicted food webs as
+compared to that of the observed food webs because a species in a food
+web with a higher connectance has, on average, more trophic links as
+compared to a food web with a lower connectance (Fig. \ref{fig:fig_r5}).
+Our study suggests that it is important to consider undersampling in
+observed food webs when computing their robustness.
 
-The findings from our study are similar to what had been documented for
-other food web models (Jennifer A. Dunne and Williams 2009), in terms of
-an increase in the robustness when the connectance of a food web is
-increased. However, contrary to general expectations (Jennifer A. Dunne,
-Williams, and Martinez 2002a), food web robustness did not always
-increase with the connectance (Fig. \ref{fig:fig_r5}). The ADBM
-consistently predicted higher connectance than that of the observed food
-webs however, in some cases an increase in connectance resulted in lower
-robustness (Fig. \ref{fig:fig_r5}) in the predicted food web. For
-example: the Benguela Pelagic and Small Reef food webs were surprisingly
-less robust to primary extinctions on average in the least-connected
-extinction scenario (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5}
-(c)). We suspect this is because the ADBM is underestimating the
-proportion of basal species in the predicted food webs when compared to
-that of the observed food webs (Fig: 6 (a) in Gupta, Furrer, and Petchey
-(2022)). As a result, these low degree basal species are the ones to be
-removed at an early stage in the deletion sequence thereby resulting in
-an earlier food web collapse in the ADBM predicted food web as compared
-to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
-This suggests that the overestimation of connectance by the ADBM
-resulted in a more robust food web on average but differences in the
-predicted food web properties such as underestimation of the proportion
-of basal species and overestimation of the maximum trophic level (Fig:
-\ref{fig:fig_a1}) counteracted that effect and led to reduced
-robustness. This suggests that food web properties other than
-connectance play an important role in determining the robustness of a
-food web and therefore should be also taken into account.
-
-The ADBM based on its size-based rules predicts the diet of a consumer
-and hence is able to predict some links in the predicted food webs which
-do in reality occur but are actually not observed in the observed food
-webs perhaps because of low sampling effort. A future study could be to
-extend our study to use other food webs models based on size-based rules
-such as Gravel et al. (2013) and Vagnon et al. (2021) and compare them
-with our study. We expect similar results because these food webs are
-also based on body size rules.
+Contrary to general expectations (Dunne et al., 2002b), food web
+robustness did not always increase with the connectance (Fig.
+\ref{fig:fig_r5}). For example, the Benguela Pelagic and Small Reef ADBM
+predicted food webs were surprisingly less robust to primary extinctions
+on average in the least connected extinction scenario compared to the
+observed food webs (Fig. \ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
+In these two food webs, the extinction of the least connected species
+could cause an almost complete, or complete collapse of the food web. We
+suspect this is because the ADBM predicted food webs have a lower
+proportion of basal species when compared to that of the observed food
+webs (Fig: 6 (a) in Gupta et al. (2022)). As a result, these low-degree
+basal species are the ones to be removed at an early stage in the
+deletion sequence, thereby resulting in an earlier food web collapse in
+the ADBM predicted food web as compared to that of the observed food web
+(Fig: \ref{fig:fig_r3} (a) and (j)). This suggests that the greater
+connectance predicted by the ADBM resulted in a more robust food web on
+average. However, differences in the predicted food web properties, such
+as a lower proportion of basal species and higher maximum trophic level
+(Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs
+counteracted that effect and led to reduced robustness. On average, a
+consumer in a food web with a higher maximum trophic level would have
+fewer resources and be more susceptible to extinction than a consumer in
+a food web with a lower maximum trophic level (Binzer et al., 2011).
+This suggests that food web properties other than connectance play an
+important role in determining a food web's robustness and, therefore,
+should also be taken into account (Binzer et al., 2011; Mendonça et al.,
+2022; Riede et al., 2011).
 
 As with any food web model, we expect that there are real false
-positives in the food webs predicted by the ADBM. Firstly this may be
-because the ADBM uses only body size as a trait. A trait uncorrelated
-with the body size may be influential in determining the interaction
-between two species (Gupta, Furrer, and Petchey 2022). Secondly, the
-ADBM can only predict diets that are contiguous with respect to the size
-of the prey. I.e. it cannot predict that the consumer will consume prey
-of size 1 and 3, and not consume prey of size 2. However, it is
-important to note that observed diets are not always contiguous when
-prey are ordered by their size due to some ecological differences in how
-predator species choose their prey (Caron et al. 2022). Therefore a
-future study could extend our study with other food web models which are
-not based on body size such as Cattin et al. (2004) and Allesina,
-Alonso, and Pascual (2008). We expect to have a difference in results
+positives in the food webs predicted by the ADBM. Real false positive
+means that the food web model predicts a link between two species that
+can never interact. (The other type of false positive is when the model
+predicts a link that was not observed but could have been observed if
+the food web was sampled enough. In this case, further sampling should
+result in the link being observed and a change from false positive to
+true positive.) Firstly, this may be because the ADBM uses only body
+size as a trait. A trait uncorrelated with the body size may be
+influential in determining the interaction between two species (Gupta et
+al., 2022). Secondly, the ADBM can only predict diets that are
+contiguous with respect to the size of the prey. I.e. it cannot predict
+that the consumer will consume prey of size 1 and 3, and not consume
+prey of size 2. However, it is important to note that observed diets are
+not always contiguous when prey are ordered by their size due to some
+ecological differences in how predator species choose their prey (Caron
+et al., 2022). Hence, it would be intriguing to extend our study to use
+other food web models based on size-based rules, such as Gravel et al.
+(2013) and Vagnon et al. (2021), to understand if the results are
+dependent on the decision of model selection. We expect to get a similar
+result in a size-based deterministic model but a different result,
+i.e.~lower robustness in a size-based stochastic model as compared to
+the ADBM because the latter can take into account non-contiguity in
+predator diets (Williams et al., 2010). It would also be interesting to
+use food web models not based on body size, such as Cattin et al. (2004)
+and Allesina et al. (2008). We expect to have a difference in results
 based on whether the trophic interactions in the food webs are governed
@@
 similar influence on the dynamical stability of the food webs as well.
-Hence, a prospect could be to use a dynamical model (for example
-bioenergetic food web model by Brose, Williams, and Martinez (2006)) to
-model the temporal dynamics of the ADBM predicted food webs. We expect
-that the difference in dynamical robustness of the ADBM predicted and
-the observed food webs would be similar to differences in their
-topological robustness because the dynamical robustness of the ADBM
-predicted and the observed food webs would be both underestimated when
-compared to their topological robustness (Curtsdotter et al. 2011).
+Hence, a prospect could be to use a dynamical model (for example, the
+bioenergetic food web model by Brose et al. (2006)) to model the
+temporal dynamics of the ADBM predicted food webs. We expect that the
+greater connectance will lead to reduced dynamical stability in the ADBM
+predicted food web compared to that of the predicted food web. The
+difference in stability will be linearly related to the difference in
+connectance because Martinez et al. (2006) has shown that food web
+stability linearly decreases with connectance.
 
-Since the ADBM underestimates the proportion of basal species and
-overestimates the maximum trophic level in the predicted food webs
-compared to that of the observed food webs, it would be interesting to
-use these properties as summary statistics to parameterise the ADBM and
-investigate how that influences the difference in the robustness between
-the ADBM predicted and the observed food webs.
+Since the ADBM predicted food webs have a lower proportion of basal
+species and a higher maximum trophic level as compared to that of the
+observed food webs (Fig: 6 (a) in Gupta et al. (2022) and Fig.
+\ref{fig:fig_a1} in Supplementary Information), it would be interesting
+to use these properties as summary statistics to parameterise the ADBM
+and investigate how that influences the difference in the robustness
+between the ADBM predicted and the observed food webs. We would expect a
+more highly constrained predicted food web structure, lower variation in
+robustness, and a greater apparent influence of connectance on
+robustness.
 
 We have used a food web model to compensate for undersampling in
-recorded food webs and thereby quantified the influence of missing links
-i.e.~overestimation of connectance on the topological robustness of 12
-food webs from various ecosystems. We found that the overestimation of
-connectance can have large impacts on the robustness of the food webs
-with variation in robustness among the predicted food webs which have
-also been influenced by differences in the structural food web
-properties between the ADBM predicted food webs and the observed food
-webs.
+recorded food webs and thereby quantified the influence of missing
+links, i.e.~greater connectance on the topological robustness of 12 food
+webs from various ecosystems. We found that the greater connectance can
+have a large impact on the robustness of the food webs while at the same
+time producing large variations in robustness among the predicted food
+webs. Furthermore, differences in other structural food web properties
+between the ADBM predicted food webs and the observed food webs are also
+responsible.
 
@@
 Global Change and Biodiversity (Grant number: U-704-04-11) of the
-University of Zurich.
+University of Zurich. We thank the Petchey group members for their
+valuable suggestions in the manuscript.
 
@@
 Validation; Writing -- original draft; Writing -- review and editing.
-\textbf{Owen L. Petchey:} \textbf{AG:} Owen, Could you please add your
-contributions here?
+\textbf{Owen L. Petchey:} Conceptualization; Funding acquisition;
+Resources; Supervision; Writing -- review \& editing.
 
@@
 
-To be added
+All the data used in this study was collected in other studies and is
+openly available. We list those studies and the open access source in
+Table \ref{fig:tab_1}. The complete code used in the analysis is
+available in the repository
+\url{https://doi.org/10.5281/zenodo.7180835}.
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 
@@
 
-\caption{\label{fig:fig_a1} Maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
-Box represent 25th and 75th percentile; bold midline represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-7}
+\caption{\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
+Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-7}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[H]
 
@@
 Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).
-Box represent 25th and 75th percentile; solid diamond represent median; whisker represent outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-8}
+Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-8}
 \end{figure}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-albertStatisticalMechanicsComplex2002}{}}%
-Albert, R'eka, and Albert-L'aszl'o Barab'asi. 2002. {``Statistical
-Mechanics of Complex Networks.''} \emph{Reviews of Modern Physics} 74
-(1): 47--97. \url{https://doi.org/10.1103/RevModPhys.74.47}.
+Albert, R., \& Barab'asi, A.-L. (2002). Statistical mechanics of complex
+networks. \emph{Reviews of Modern Physics}, \emph{74}(1), 47--97.
+\url{https://doi.org/10.1103/RevModPhys.74.47}
 
 \leavevmode\vadjust pre{\hypertarget{ref-allesinaGeneralModelFood2008}{}}%
-Allesina, Stefano, David Alonso, and Mercedes Pascual. 2008. {``A
-{General Model} for {Food Web Structure}.''} \emph{Science} 320 (5876):
-658--61. \url{https://doi.org/10.1126/science.1156269}.
+Allesina, S., Alonso, D., \& Pascual, M. (2008). A {General Model} for
+{Food Web Structure}. \emph{Science}, \emph{320}(5876), 658--661.
+\url{https://doi.org/10.1126/science.1156269}
 
 \leavevmode\vadjust pre{\hypertarget{ref-bergUsingSensitivityAnalysis2011}{}}%
-Berg, Sofia, Maria Christianou, Tomas Jonsson, and Bo Ebenman. 2011.
-{``Using Sensitivity Analysis to Identify Keystone Species and Keystone
-Links in Size-Based Food Webs.''} \emph{Oikos} 120 (4): 510--19.
-\url{https://doi.org/10.1111/j.1600-0706.2010.18864.x}.
+Berg, S., Christianou, M., Jonsson, T., \& Ebenman, B. (2011). Using
+sensitivity analysis to identify keystone species and keystone links in
+size-based food webs. \emph{Oikos}, \emph{120}(4), 510--519.
+\url{https://doi.org/10.1111/j.1600-0706.2010.18864.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-binzerSusceptibilitySpeciesExtinctions2011}{}}%
+Binzer, A., Brose, U., Curtsdotter, A., Eklöf, A., Rall, B. C., Riede,
+J. O., \& de Castro, F. (2011). The susceptibility of species to
+extinctions in model communities. \emph{Basic and Applied Ecology},
+\emph{12}(7), 590--599. \url{https://doi.org/10.1016/j.baae.2011.09.002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-broseAllometricScalingEnhances2006}{}}%
-Brose, Ulrich, Richard J. Williams, and Neo D. Martinez. 2006.
-{``Allometric Scaling Enhances Stability in Complex Food Webs.''}
-\emph{Ecology Letters} 9 (11): 1228--36.
-\url{https://doi.org/10.1111/j.1461-0248.2006.00978.x}.
+Brose, U., Williams, R. J., \& Martinez, N. D. (2006). Allometric
+scaling enhances stability in complex food webs. \emph{Ecology Letters},
+\emph{9}(11), 1228--1236.
+\url{https://doi.org/10.1111/j.1461-0248.2006.00978.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-caronAddressingEltonianShortfall}{}}%
-Caron, Dominique, Luigi Maiorano, Wilfried Thuiller, and Laura J.
-Pollock. 2022. {``Addressing the {Eltonian} Shortfall with Trait-Based
-Interaction Models.''} \emph{Ecology Letters} n/a (n/a).
-\url{https://doi.org/10.1111/ele.13966}.
+Caron, D., Maiorano, L., Thuiller, W., \& Pollock, L. J. (2022).
+Addressing the {Eltonian} shortfall with trait-based interaction models.
+\emph{Ecology Letters}, \emph{n/a}(n/a).
+\url{https://doi.org/10.1111/ele.13966}
 
 \leavevmode\vadjust pre{\hypertarget{ref-cattinPhylogeneticConstraintsAdaptation2004}{}}%
-Cattin, Marie-France, Louis-F'elix Bersier, Carolin Banašek-Richter,
-Richard Baltensperger, and Jean-Pierre Gabriel. 2004. {``Phylogenetic
-Constraints and Adaptation Explain Food-Web Structure.''} \emph{Nature}
-427 (6977, 6977): 835--39. \url{https://doi.org/10.1038/nature02327}.
+Cattin, M.-F., Bersier, L.-F., Banašek-Richter, C., Baltensperger, R.,
+\& Gabriel, J.-P. (2004). Phylogenetic constraints and adaptation
+explain food-web structure. \emph{Nature}, \emph{427}(6977, 6977),
+835--839. \url{https://doi.org/10.1038/nature02327}
 
-\leavevmode\vadjust pre{\hypertarget{ref-curtsdotterRobustnessSecondaryExtinctions2011a}{}}%
-Curtsdotter, Alva, Amrei Binzer, Ulrich Brose, Francisco de Castro, Bo
-Ebenman, Anna Eklöf, Jens O. Riede, Aaron Thierry, and Björn C. Rall.
-2011. {``Robustness to Secondary Extinctions: {Comparing} Trait-Based
-Sequential Deletions in Static and Dynamic Food Webs.''} \emph{Basic and
-Applied Ecology} 12 (7): 571--80.
-\url{https://doi.org/10.1016/j.baae.2011.09.008}.
+\leavevmode\vadjust pre{\hypertarget{ref-davidImpactsInvasiveSpecies2017}{}}%
+David, P., Th'ebault, E., Anneville, O., Duyck, P.-F., Chapuis, E., \&
+Loeuille, N. (2017). Impacts of {Invasive Species} on {Food Webs}. In
+\emph{Advances in {Ecological Research}} (Vol. 56, pp. 1--60).
+{Elsevier}. \url{https://doi.org/10.1016/bs.aecr.2016.10.001}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunneCascadingExtinctionsCommunity2009}{}}%
+Dunne, J. A., \& Williams, R. J. (2009). Cascading extinctions and
+community collapse in model food webs. \emph{Philosophical Transactions
+of the Royal Society B: Biological Sciences}, \emph{364}(1524),
+1711--1723. \url{https://doi.org/10.1098/rstb.2008.0219}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunne2002network}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002a). Network
+structure and biodiversity loss in food webs: Robustness increases with
+connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}}%
+Dunne, J. A., Williams, R. J., \& Martinez, N. D. (2002b). Network
+structure and biodiversity loss in food webs: Robustness increases with
+connectance. \emph{Ecology Letters}, \emph{5}(4), 558--567.
+\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-dunne2004}{}}%
-Dunne, Ja, Rj Williams, and Nd Martinez. 2004. {``Network Structure and
-Robustness of Marine Food Webs.''} \emph{Marine Ecology Progress Series}
-273: 291--302. \url{https://doi.org/10.3354/meps273291}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dunneCascadingExtinctionsCommunity2009}{}}%
-Dunne, Jennifer A., and Richard J. Williams. 2009. {``Cascading
-Extinctions and Community Collapse in Model Food Webs.''}
-\emph{Philosophical Transactions of the Royal Society B: Biological
-Sciences} 364 (1524): 1711--23.
-\url{https://doi.org/10.1098/rstb.2008.0219}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dunneNetworkStructureBiodiversity2002}{}}%
-Dunne, Jennifer A., Richard J. Williams, and Neo D. Martinez. 2002a.
-{``Network Structure and Biodiversity Loss in Food Webs: Robustness
-Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.
-\url{https://doi.org/10.1046/j.1461-0248.2002.00354.x}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-dunne2002network}{}}%
-Dunne, Jennifer A, Richard J Williams, and Neo D Martinez. 2002b.
-{``Network Structure and Biodiversity Loss in Food Webs: Robustness
-Increases with Connectance.''} \emph{Ecology Letters} 5 (4): 558--67.
+Dunne, J., Williams, R., \& Martinez, N. (2004). Network structure and
+robustness of marine food webs. \emph{Marine Ecology Progress Series},
+\emph{273}, 291--302. \url{https://doi.org/10.3354/meps273291}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ebenmanUsingCommunityViability2005}{}}%
-Ebenman, Bo, and Tomas Jonsson. 2005. {``Using Community Viability
-Analysis to Identify Fragile Systems and Keystone Species.''}
-\emph{Trends in Ecology \& Evolution} 20 (10): 568--75.
-\url{https://doi.org/10.1016/j.tree.2005.06.011}.
+Ebenman, B., \& Jonsson, T. (2005). Using community viability analysis
+to identify fragile systems and keystone species. \emph{Trends in
+Ecology \& Evolution}, \emph{20}(10), 568--575.
+\url{https://doi.org/10.1016/j.tree.2005.06.011}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ebenmanCOMMUNITYVIABILITYANALYSIS2004}{}}%
-Ebenman, Bo, Richard Law, and Charlotte Borrvall. 2004. {``{COMMUNITY
-VIABILITY ANALYSIS}: {THE RESPONSE OF ECOLOGICAL COMMUNITIES TO SPECIES
-LOSS}.''} \emph{Ecology} 85 (9): 2591--2600.
-\url{https://doi.org/10.1890/03-8018}.
+Ebenman, B., Law, R., \& Borrvall, C. (2004). {COMMUNITY VIABILITY
+ANALYSIS}: {THE RESPONSE OF ECOLOGICAL COMMUNITIES TO SPECIES LOSS}.
+\emph{Ecology}, \emph{85}(9), 2591--2600.
+\url{https://doi.org/10.1890/03-8018}
 
 \leavevmode\vadjust pre{\hypertarget{ref-gravelInferringFoodWeb2013a}{}}%
-Gravel, Dominique, Timoth'ee Poisot, Camille Albouy, Laure Velez, and
-David Mouillot. 2013. {``Inferring Food Web Structure from
-Predator--Prey Body Size Relationships.''} \emph{Methods in Ecology and
-Evolution} 4 (11): 1083--90.
-\url{https://doi.org/10.1111/2041-210X.12103}.
+Gravel, D., Poisot, T., Albouy, C., Velez, L., \& Mouillot, D. (2013).
+Inferring food web structure from predator--prey body size
+relationships. \emph{Methods in Ecology and Evolution}, \emph{4}(11),
+1083--1090. \url{https://doi.org/10.1111/2041-210X.12103}
 
 \leavevmode\vadjust pre{\hypertarget{ref-guptaSimultaneouslyEstimatingFood2022}{}}%
-Gupta, Anubhav, Reinhard Furrer, and Owen L. Petchey. 2022.
-{``Simultaneously Estimating Food Web Connectance and Structure with
-Uncertainty.''} \emph{Ecology and Evolution} 12 (3): e8643.
-\url{https://doi.org/10.1002/ece3.8643}.
+Gupta, A., Furrer, R., \& Petchey, O. L. (2022). Simultaneously
+estimating food web connectance and structure with uncertainty.
+\emph{Ecology and Evolution}, \emph{12}(3), e8643.
+\url{https://doi.org/10.1002/ece3.8643}
 
 \leavevmode\vadjust pre{\hypertarget{ref-jonssonReliabilityR50Measure2015}{}}%
-Jonsson, Tomas, Sofia Berg, Alexander Pimenov, Catherine Palmer, and
-Mark Emmerson. 2015. {``The Reliability of {R50} as a Measure of
-Vulnerability of Food Webs to Sequential Species Deletions.''}
-\emph{Oikos} 124 (4): 446--57. \url{https://doi.org/10.1111/oik.01588}.
+Jonsson, T., Berg, S., Pimenov, A., Palmer, C., \& Emmerson, M. (2015).
+The reliability of {R50} as a measure of vulnerability of food webs to
+sequential species deletions. \emph{Oikos}, \emph{124}(4), 446--457.
+\url{https://doi.org/10.1111/oik.01588}
 
 \leavevmode\vadjust pre{\hypertarget{ref-jordanoSamplingNetworksEcological2016}{}}%
-Jordano, Pedro. 2016. {``Sampling Networks of Ecological
-Interactions.''} \emph{Functional Ecology} 30 (12): 1883--93.
-\url{https://doi.org/10.1111/1365-2435.12763}.
+Jordano, P. (2016). Sampling networks of ecological interactions.
+\emph{Functional Ecology}, \emph{30}(12), 1883--1893.
+\url{https://doi.org/10.1111/1365-2435.12763}
+
+\leavevmode\vadjust pre{\hypertarget{ref-koningGrassrootsReservesRescue2021}{}}%
+Koning, A. A., \& McIntyre, P. B. (2021). Grassroots reserves rescue a
+river food web from cascading impacts of overharvest. \emph{Frontiers in
+Ecology and the Environment}, \emph{19}(3), 152--158.
+\url{https://doi.org/10.1002/fee.2293}
 
 \leavevmode\vadjust pre{\hypertarget{ref-macarthur1966}{}}%
-MacArthur, Robert H., and Eric R. Pianka. 1966. {``On Optimal Use of a
-Patchy Environment.''} \emph{The American Naturalist} 100 (916): 603--9.
-\url{https://www.jstor.org/stable/2459298}.
+MacArthur, R. H., \& Pianka, E. R. (1966). On optimal use of a patchy
+environment. \emph{The American Naturalist}, \emph{100}(916), 603--609.
+\url{https://www.jstor.org/stable/2459298}
 
 \leavevmode\vadjust pre{\hypertarget{ref-martinezDiversityComplexityPersistence}{}}%
-Martinez, Neo D, Richard J Williams, and Jennifer A Dunne. 2006.
-{``Diversity, {Complexity}, and {Persistence} in {Large Model
-Ecosystems},''} 24.
+Martinez, N. D., Williams, R. J., \& Dunne, J. A. (2006).
+\emph{Diversity, {Complexity}, and {Persistence} in {Large Model
+Ecosystems}}. 24.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mayWillLargeComplex1972}{}}%
+May, R. M. (1972). Will a {Large Complex System} be {Stable}?
+\emph{Nature}, \emph{238}(5364), 413.
+\url{https://doi.org/10.1038/238413a0}
+
+\leavevmode\vadjust pre{\hypertarget{ref-mendoncaRobustnessTemperateTropical2022}{}}%
+Mendonça, V., Madeira, C., Dias, M., Flores, A., \& Vinagre, C. (2022).
+Robustness of temperate versus tropical food webs: Comparing species
+trait-based sequential deletions. \emph{Marine Ecology Progress Series},
+\emph{691}, 19--28. \url{https://doi.org/10.3354/meps14062}
 
 \leavevmode\vadjust pre{\hypertarget{ref-patonaiAggregationIncompleteFood2017}{}}%
-Patonai, Katalin, and Ferenc Jord'an. 2017. {``Aggregation of Incomplete
-Food Web Data May Help to Suggest Sampling Strategies.''}
-\emph{Ecological Modelling} 352 (May): 77--89.
-\url{https://doi.org/10.1016/j.ecolmodel.2017.02.024}.
+Patonai, K., \& Jord'an, F. (2017). Aggregation of incomplete food web
+data may help to suggest sampling strategies. \emph{Ecological
+Modelling}, \emph{352}, 77--89.
+\url{https://doi.org/10.1016/j.ecolmodel.2017.02.024}
 
 \leavevmode\vadjust pre{\hypertarget{ref-petchey2008}{}}%
-Petchey, Owen L., A. P. Beckerman, J. O. Riede, and P. H. Warren. 2008.
-{``Size, Foraging, and Food Web Structure.''} \emph{Proceedings of the
-National Academy of Sciences} 105 (11): 4191--96.
-\url{https://doi.org/10.1073/pnas.0710672105}.
+Petchey, O. L., Beckerman, A. P., Riede, J. O., \& Warren, P. H. (2008).
+Size, foraging, and food web structure. \emph{Proceedings of the
+National Academy of Sciences}, \emph{105}(11), 4191--4196.
+\url{https://doi.org/10.1073/pnas.0710672105}
 
 \leavevmode\vadjust pre{\hypertarget{ref-pimmHumanImpactsRates2006}{}}%
-Pimm, Stuart, Peter Raven, Alan Peterson, Çağan H. Şekercioğlu, and Paul
-R. Ehrlich. 2006. {``Human Impacts on the Rates of Recent, Present, and
-Future Bird Extinctions.''} \emph{Proceedings of the National Academy of
-Sciences} 103 (29): 10941--46.
-\url{https://doi.org/10.1073/pnas.0604181103}.
+Pimm, S., Raven, P., Peterson, A., H. Şekercioğlu, Çağan, \& Ehrlich, P.
+R. (2006). Human impacts on the rates of recent, present, and future
+bird extinctions. \emph{Proceedings of the National Academy of
+Sciences}, \emph{103}(29), 10941--10946.
+\url{https://doi.org/10.1073/pnas.0604181103}
+
+\leavevmode\vadjust pre{\hypertarget{ref-riedeSizebasedFoodWeb2011}{}}%
+Riede, J. O., Binzer, A., Brose, U., de Castro, F., Curtsdotter, A.,
+Rall, B. C., \& Eklöf, A. (2011). Size-based food web characteristics
+govern the response to species extinctions. \emph{Basic and Applied
+Ecology}, \emph{12}(7), 581--589.
+\url{https://doi.org/10.1016/j.baae.2011.09.006}
 
 \leavevmode\vadjust pre{\hypertarget{ref-soleComplexityFragilityEcological2001}{}}%
-Sol'e, Ricard V., and M. Montoya. 2001. {``Complexity and Fragility in
-Ecological Networks.''} \emph{Proceedings of the Royal Society of
-London. Series B: Biological Sciences} 268 (1480): 2039--45.
-\url{https://doi.org/10.1098/rspb.2001.1767}.
+Sol'e, R. V., \& Montoya, M. (2001). Complexity and fragility in
+ecological networks. \emph{Proceedings of the Royal Society of London.
+Series B: Biological Sciences}, \emph{268}(1480), 2039--2045.
+\url{https://doi.org/10.1098/rspb.2001.1767}
 
 \leavevmode\vadjust pre{\hypertarget{ref-thomasExtinctionRiskClimate2004}{}}%
-Thomas, Chris D., Alison Cameron, Rhys E. Green, Michel Bakkenes, Linda
-J. Beaumont, Yvonne C. Collingham, Barend F. N. Erasmus, et al. 2004.
-{``Extinction Risk from Climate Change.''} \emph{Nature} 427 (6970,
-6970): 145--48. \url{https://doi.org/10.1038/nature02121}.
+Thomas, C. D., Cameron, A., Green, R. E., Bakkenes, M., Beaumont, L. J.,
+Collingham, Y. C., Erasmus, B. F. N., de Siqueira, M. F., Grainger, A.,
+Hannah, L., Hughes, L., Huntley, B., van Jaarsveld, A. S., Midgley, G.
+F., Miles, L., Ortega-Huerta, M. A., Townsend Peterson, A., Phillips, O.
+L., \& Williams, S. E. (2004). Extinction risk from climate change.
+\emph{Nature}, \emph{427}(6970, 6970), 145--148.
+\url{https://doi.org/10.1038/nature02121}
 
 \leavevmode\vadjust pre{\hypertarget{ref-thomasComparativeLossesBritish2004}{}}%
-Thomas, J. A., M. G. Telfer, D. B. Roy, C. D. Preston, J. J. D.
-Greenwood, J. Asher, R. Fox, R. T. Clarke, and J. H. Lawton. 2004.
-{``Comparative {Losses} of {British Butterflies}, {Birds}, and {Plants}
-and the {Global Extinction Crisis}.''} \emph{Science} 303 (5665):
-1879--81. \url{https://doi.org/10.1126/science.1095046}.
+Thomas, J. A., Telfer, M. G., Roy, D. B., Preston, C. D., Greenwood, J.
+J. D., Asher, J., Fox, R., Clarke, R. T., \& Lawton, J. H. (2004).
+Comparative {Losses} of {British Butterflies}, {Birds}, and {Plants} and
+the {Global Extinction Crisis}. \emph{Science}, \emph{303}(5665),
+1879--1881. \url{https://doi.org/10.1126/science.1095046}
 
 \leavevmode\vadjust pre{\hypertarget{ref-ullah2018}{}}%
-Ullah, Hadayet, Ivan Nagelkerken, Silvan U. Goldenberg, and Damien A.
-Fordham. 2018. {``Climate Change Could Drive Marine Food Web Collapse
-Through Altered Trophic Flows and Cyanobacterial Proliferation.''}
-Edited by Michel Loreau. \emph{PLOS Biology} 16 (1): e2003446.
-\url{https://doi.org/10.1371/journal.pbio.2003446}.
+Ullah, H., Nagelkerken, I., Goldenberg, S. U., \& Fordham, D. A. (2018).
+Climate change could drive marine food web collapse through altered
+trophic flows and cyanobacterial proliferation. \emph{PLOS Biology},
+\emph{16}(1), e2003446.
+\url{https://doi.org/10.1371/journal.pbio.2003446}
 
 \leavevmode\vadjust pre{\hypertarget{ref-vagnonAllometricNicheModel2021}{}}%
-Vagnon, Chlo'e, Franck Cattan'eo, Chlo'e Goulon, David Grimardias, Jean
-Guillard, and Victor Frossard. 2021. {``An Allometric Niche Model for
-Species Interactions in Temperate Freshwater Ecosystems.''}
-\emph{Ecosphere} 12 (3): e03420.
-\url{https://doi.org/10.1002/ecs2.3420}.
+Vagnon, C., Cattan'eo, F., Goulon, C., Grimardias, D., Guillard, J., \&
+Frossard, V. (2021). An allometric niche model for species interactions
+in temperate freshwater ecosystems. \emph{Ecosphere}, \emph{12}(3),
+e03420. \url{https://doi.org/10.1002/ecs2.3420}
 
 \leavevmode\vadjust pre{\hypertarget{ref-whiteEcologistsShouldNot2014}{}}%
-White, J. Wilson, Andrew Rassweiler, Jameal F. Samhouri, Adrian C.
-Stier, and Crow White. 2014. {``Ecologists Should Not Use Statistical
-Significance Tests to Interpret Simulation Model Results.''}
-\emph{Oikos} 123 (4): 385--88.
-\url{https://doi.org/10.1111/j.1600-0706.2013.01073.x}.
+White, J. W., Rassweiler, A., Samhouri, J. F., Stier, A. C., \& White,
+C. (2014). Ecologists should not use statistical significance tests to
+interpret simulation model results. \emph{Oikos}, \emph{123}(4),
+385--388. \url{https://doi.org/10.1111/j.1600-0706.2013.01073.x}
+
+\leavevmode\vadjust pre{\hypertarget{ref-wilkinsonFAIRGuidingPrinciples2016}{}}%
+Wilkinson, M. D., Dumontier, M., Aalbersberg, Ij. J., Appleton, G.,
+Axton, M., Baak, A., Blomberg, N., Boiten, J.-W., da Silva Santos, L.
+B., Bourne, P. E., Bouwman, J., Brookes, A. J., Clark, T., Crosas, M.,
+Dillo, I., Dumon, O., Edmunds, S., Evelo, C. T., Finkers, R., \ldots{}
+Mon, B. (2016). The {FAIR Guiding Principles} for scientific data
+management and stewardship. \emph{Scientific Data}, \emph{3}(1, 1),
+160018. \url{https://doi.org/10.1038/sdata.2016.18}
 
 \leavevmode\vadjust pre{\hypertarget{ref-williamsEffectsNetworkDynamical2008}{}}%
-Williams, Richard J. 2008. {``Effects of Network and Dynamical Model
-Structure on Species Persistence in Large Model Food Webs.''}
-\emph{Theoretical Ecology} 1 (3): 141--51.
-\url{https://doi.org/10.1007/s12080-008-0013-5}.
+Williams, R. J. (2008). Effects of network and dynamical model structure
+on species persistence in large model food webs. \emph{Theoretical
+Ecology}, \emph{1}(3), 141--151.
+\url{https://doi.org/10.1007/s12080-008-0013-5}
+
+\leavevmode\vadjust pre{\hypertarget{ref-williamsProbabilisticNicheModel2010}{}}%
+Williams, R. J., Anandanadesan, A., \& Purves, D. (2010). The
+{Probabilistic Niche Model Reveals} the {Niche Structure} and {Role} of
+{Body Size} in a {Complex Food Web}. \emph{PLoS ONE}, \emph{5}(8),
+e12092. \url{https://doi.org/10.1371/journal.pone.0012092}
 

### 2023-02-10 manuscript/ms_C3_v3.Rmd
updated ms

--- 2023-02-10 manuscript/ms_C3_v2.Rmd
@@
 Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links.
-Simultaneously, models might predict links which cannot occur, i.e., false positives.
+Simultaneously, models might predict links which cannot occur, i.e., real false positives.
   2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
-Thus, we expect that predicted food webs are more robust than observed ones.
+Thus, we expect that predicted food webs are more robust than the observed ones.
 However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e.
 the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
-  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links but does not predict all links correctly.
+  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links.
 We did this for 12 different food webs from a wide variety of ecosystems.
@@
 On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios.
-On the other hand, we saw no effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
+On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
   5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
-Nevertheless, increased connectance may contribute to lower dynamical stability, so it would be interesting to compare the dynamical stability of observed and predicted food webs and the topological stability that we have focused on.
+Also, the differences in the structural properties of the model predicted food webs and the observed food webs suggest structural properties of a food web could be used as summary statistics to fit models such as the ADBM to the observed data.
 
@@
 
+## Paragraph on how other structural food web properties are responsible as well
+
+Structural properties other than food web connectance such as the proportion of basal species and the maximum trophic level of species in a food web can influence the robustness of a food web [@mendoncaRobustnessTemperateTropical2022; @riedeSizebasedFoodWeb2011].
+For example, a food web with a higher proportion of basal species on average will be more robust as compared to otherwise [@mendoncaRobustnessTemperateTropical2022] because extinctions of all the basal species will lead to collapse of the complete food web.
+A food web with a lower maximum trophic level of species on average will be more robust as compared to otherwise [@riedeSizebasedFoodWeb2011].
+This is because a food web with a lower maximum trophic level will have higher number of species per trophic level on average as compared to otherwise.
+
 Along with quantifying food web robustness based on its topological structure, studies such as @williamsEffectsNetworkDynamical2008, @broseAllometricScalingEnhances2006, and @martinezDiversityComplexityPersistence have quantified robustness based on the abundance dynamics of a food web.
@@
 However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
-Some rare trophic links require more sampling effort than others, whereas some trophic links remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
+Some rare trophic links require more sampling effort than others, whereas some trophic links (sometimes referred to as forbidden links) remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
 Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
-One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] to predict the missing links and then measure the robustness of the predicted food web.
+One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] (reference (gut content paper)) to predict the missing links and then measure the robustness of the predicted food web.
 The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare.
@@
 In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs.
-We expect the ADBM predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the ADBM predicts greater connectance compared to that of the observed food webs.
-We do this by simulating primary species loss in 12 food webs predicted by the ADBM to quantify the secondary loss of extinctions and compare the robustness of food webs predicted by the ADBM to the robustness of the observed food webs.
+We achieved this by simulating primary species loss in 12 food webs predicted by the model to quantify secondary loss of extinctions and compare the robustness of food webs predicted by the model to the robustness of the observed food webs.
+We expect the model predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the model predicts greater connectance compared to that of the observed food webs.
+We also examined how different structural food web properties other than the connectance can influence this difference in the perceived robustness.
+In order to do that, we define our null hypothesis to be: (H1) The missing links that are filled in by the model increase robustness because they increase connectance; and our alternate hypothesis to be: (H2) Although the model fills in missing links, it also changes other structural properties and these outweigh the effects of connectance on robustness.
+
+<!-- We do this by simulating primary species loss in 12 food webs predicted by the ADBM to quantify the secondary loss of extinctions and compare the robustness of food webs predicted by the ADBM to the robustness of the observed food webs.
 We use three different approaches of primary species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
+-->
 
@@
 For example, those with size-structured interactions, such as herbivory in aquatic ecosystems, are better predicted compared to less size-structured ones, such as parasitoids and terrestrial herbivory ones [@petchey2008].
+
+All food webs with one exception (Broadstone Stream) was available only at the species level, i.e.
+with information about interactions between species and the body size of species.
+We use the term "species" in this study to indicate a "node" in a food web in which nodes are connected by trophic interactions, and nodes are a collection of individuals that share links.
+These species/nodes are not always taxonomic species, but can be broader taxonomic ranks.
+
+In contrast, the Broadstone Stream food web data contained interactions between individuals and the individual body sizes.
+Thus, the Broadstone Stream food web can be constructed by aggregating by either taxonomy or size [@woodwardChapterIndividualBasedFood2010].
 
@@
 
-We first present the secondary extinction curves of the ADBM predicted food webs which had the maximum true skill statistics and of the observed food webs for 12 food webs under three different extinction scenarios.
-We then compare the robustness of all the ADBM predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
+We first compare the robustness of the model food webs against that of the observed food webs.
+We then quantify the effect of difference in their connectance on the difference in their robustness estimates.
+
+<!-- We first compare the robustness of all the model predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
 Finally, we quantify the effect of the difference in their connectance on the difference in their robustness estimates.
+-->
 
-## Secondary extinctions
+<!-- ## Secondary extinctions -->
 
-In the most connected extinction scenario, the cumulative secondary extinction curves started to rise steeply in the observed food webs at a lower number of primary species removal as compared to the ADBM predicted food webs for nine food webs (Fig.
+<!-- In the most connected extinction scenario, the cumulative secondary extinction curves started to rise steeply in the observed food webs at a lower number of primary species removal as compared to the ADBM predicted food webs for nine food webs (Fig.
 \ref{fig:fig_r1} (a, c, d, e, f, g, h, j, l)).
@@
 \ref{fig:fig_r1} (b)).
+-->
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+<!-- ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_mostconnected_maxTSS.png")
-```
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."} -->
+<!-- knitr::include_graphics("../results/plot_mostconnected_maxTSS.png") -->
+<!-- ``` -->
 
-In Fig.
+<!-- In Fig.
 \ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show example variation caused by different random primary extinction orders.
@@
 primary removal of some species in an extinction sequence can lead to the complete collapse of the remaining food web in the ADBM predicted food webs.
+-->
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
+<!-- ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
 S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_ra_extlines_maxTSS.png")
-```
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."} -->
+<!-- knitr::include_graphics("../results/plot_ra_extlines_maxTSS.png") -->
+<!-- ``` -->
 
-Compared to the most connected and random extinction scenarios, there were fewer secondary extinctions in the least connected extinction scenario, and therefore the secondary extinction curves were flat for many of the food webs (Fig.
+<!-- Compared to the most connected and random extinction scenarios, there were fewer secondary extinctions in the least connected extinction scenario, and therefore the secondary extinction curves were flat for many of the food webs (Fig.
 \ref{fig:fig_r3}).
 In some of the food webs, the extinction curves of the ADBM predicted food webs overlapped with the observed food webs (Fig.
-\ref{fig:fig_r3} (b, c, g, h, i, k, l)}).
+\ref{fig:fig_r3} (b, c, g, h, i, k, l)).
 In five of the food webs, a very high number of secondary extinctions occurred at a very low number of primary species removal (Fig.
 \ref{fig:fig_r3} (a, d, e, f, j)).
+-->
 
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
+<!-- ```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
 S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_leastconnected_maxTSS.png")
-```
+The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."} -->
+<!-- knitr::include_graphics("../results/plot_leastconnected_maxTSS.png") -->
+<!-- ``` -->
 
-## Robustness
+<!-- ## Robustness  -->
 
-The ADBM predicted food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig.
+The model food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig.
 \ref{fig:fig_r4} (a, b)).
-However, there were large variations in the robustness within the ADBM predicted food webs in the most connected extinction scenario (Fig.
+However, there were large variations in the robustness within the model food webs in the most connected extinction scenario (Fig.
 \ref{fig:fig_r4} (a)).
-For example, the ADBM predicted Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the ADBM predicted food webs compared to other food webs.
+For example, the model food webs for the Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the model food webs compared to other food webs.
 
@@
 \ref{fig:fig_r4} (a, b)).
-Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
+Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig.
 \ref{fig:fig_r4} (b)).
-Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
-Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
+Skipwith Pond and Broadstone Stream (taxonomic aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs.
 The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
 \ref{fig:fig_r4} (a, b)).
-Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
+Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig.
 \ref{fig:fig_r4} (b)).
-Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
-Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
+Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs.
+Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
 
@@
 \ref{fig:fig_r4} (c)), however there were some exceptions.
-The ADBM predicted food webs for Small Reef and Benguela Pelagic had very low median robustness.
-Benguela Pelagic, Broom and Capinteria food webs from the ADBM had larger variations in robustness when compared to that of the others.
+The model food webs for Small Reef and Benguela Pelagic had very low median robustness.
+The model food webs for the Benguela Pelagic, Broom and Capinteria food webs had larger variations in robustness when compared to that of the others.
 
@@
 
-In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig.
+In all of the food webs except Broadstone Stream (taxonomic aggregation) and Skipwith Pond, the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig.
 \ref{fig:fig_r5} (a)), i.e.
@@
 However, the effect size varied across the food webs.
-In the least connected extinction scenario, the median effect sizes were zero or very close to zero for all the food webs except Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig.
+In the least connected extinction scenario, the median effect sizes were zero for all the food webs except for Caricaie Lakes and Capinteria food webs where the effect sizes were very close to zero and for Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig.
 \ref{fig:fig_r5} (c)).
-However, there were lots of outlier effect sizes less than zero.
+However, there were lots of outlier with effect sizes negative.
 
@@
 
-As expected, the ADBM predicted food webs were more robust than the observed food webs on average.
-The considerable variation of the robustness of the ADBM predicted food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling.
+As expected, the model food webs were more robust than the observed food webs on average.
+The considerable variation of the robustness of the model food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling.
 Furthermore, as was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average.
 Future development would be to understand how undersampling, i.e.
-predicted greater connectance, influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria.
+predicted greater connectance, influences the stability of the dynamics of the model food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria.
 However, one would expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].
@@
 
+Our study also depicts that the uncertainty in the model predictions can have a strong influence on the perceived robustness of the observed food webs.
+The large variations in the robustness of the model predicted food webs suggest why it is crucial to incorporate uncertainty in the food web predictions.
+At the same time, our study also quantifies the impact of undersampling on the perceived robustness of the observed food webs which then influences the perceived functioning and stability of the food webs (reference).
+This strongly suggest why it is crucial to incorporate the influence of undersampling.
+
 Contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig.
@@
 As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM.
-Real false positive means that the food web model predicts a link between two species that can never interact.
-(The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
-In this case, further sampling should result in the link being observed and a change from false positive to true positive.) Firstly, this may be because the ADBM uses only body size as a trait.
+Real false positive means that the food web model predicts a link between two species that can never interact (The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
+In this case, further sampling should result in the link being observed and a change from false positive to true positive.).
+Firstly, this may be because the ADBM uses only body size as a trait.
 A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022].

### 2023-02-10 manuscript/ms_C3_v3.tex
updated ms

--- 2023-02-10 manuscript/ms_C3_v2.tex
@@
   (ADBM) to predict missing links. Simultaneously, models might predict
-  links which cannot occur, i.e., false positives.
+  links which cannot occur, i.e., real false positives.
 \item
@@
   observed ones. Thus, we expect that predicted food webs are more
-  robust than observed ones. However, this expectation has never, to our
-  knowledge, been tested, nor has the effect size, i.e.~the difference
-  in robustness of predicted and observed food web with respect to the
-  difference in their connectance, been quantified.
+  robust than the observed ones. However, this expectation has never, to
+  our knowledge, been tested, nor has the effect size, i.e.~the
+  difference in robustness of predicted and observed food web with
+  respect to the difference in their connectance, been quantified.
 \item
@@
   webs to the robustness of food webs predicted by a model (the ADBM)
-  that can account for missing links but does not predict all links
-  correctly. We did this for 12 different food webs from a wide variety
-  of ecosystems. We used three extinction scenarios: random, most
-  connected, and least connected.
+  that can account for missing links. We did this for 12 different food
+  webs from a wide variety of ecosystems. We used three extinction
+  scenarios: random, most connected, and least connected.
 \item
@@
   scenario and by 0.04 units for the random species extinction
-  scenarios. On the other hand, we saw no effect, on average, of
-  increased connectance for the least connected species extinction
-  scenario for all except two of the 12 food webs.
+  scenarios. On the other hand, we saw no effect or very little effect,
+  on average, of increased connectance for the least connected species
+  extinction scenario for all except two of the 12 food webs.
 \item
@@
   of food web robustness that can be compensated for by filling in
-  missing links with food web models. Nevertheless, increased
-  connectance may contribute to lower dynamical stability, so it would
-  be interesting to compare the dynamical stability of observed and
-  predicted food webs and the topological stability that we have focused
-  on.
+  missing links with food web models. Also, the differences in the
+  structural properties of the model predicted food webs and the
+  observed food webs suggest structural properties of a food web could
+  be used as summary statistics to fit models such as the ADBM to the
+  observed data.
 \end{enumerate}
@@
 
+\hypertarget{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}{%
+\subsection{Paragraph on how other structural food web properties are
+responsible as
+well}\label{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}}
+
+Structural properties other than food web connectance such as the
+proportion of basal species and the maximum trophic level of species in
+a food web can influence the robustness of a food web (Mendonça et al.,
+2022; Riede et al., 2011). For example, a food web with a higher
+proportion of basal species on average will be more robust as compared
+to otherwise (Mendonça et al., 2022) because extinctions of all the
+basal species will lead to collapse of the complete food web. A food web
+with a lower maximum trophic level of species on average will be more
+robust as compared to otherwise (Riede et al., 2011). This is because a
+food web with a lower maximum trophic level will have higher number of
+species per trophic level on average as compared to otherwise.
+
 Along with quantifying food web robustness based on its topological
@@
 require more sampling effort than others, whereas some trophic links
-remain unobserved because of biological constraints such as
-spatio-temporal uncoupling, size or reward mismatching, foraging
-constraints and physiological-biochemical constraints, which are
-irrespective of sufficient sampling effort (Jordano, 2016). Previous
-studies such as Caron et al. (2022) and Gupta et al. (2022) have shown
-that the predicted food webs from these models usually have greater
-connectance than the observed ones. One solution to compensate for
-undersampling is using a food web model such as the Allometric Diet
-Breadth Model (ADBM) (Petchey et al., 2008) to predict the missing links
-and then measure the robustness of the predicted food web. The ADBM is a
-mechanistic model constructed using foraging rules based on the body
-sizes of prey and predator, where trophic interactions satisfying those
-rules would be predicted by the model, which are perhaps not observed
-because those interactions are rare. However, this solution is not
-infallible, as it is likely that the food web model might still miss
-some links and also may predict some links that could not, in fact
-occur.
+(sometimes referred to as forbidden links) remain unobserved because of
+biological constraints such as spatio-temporal uncoupling, size or
+reward mismatching, foraging constraints and physiological-biochemical
+constraints, which are irrespective of sufficient sampling effort
+(Jordano, 2016). Previous studies such as Caron et al. (2022) and Gupta
+et al. (2022) have shown that the predicted food webs from these models
+usually have greater connectance than the observed ones. One solution to
+compensate for undersampling is using a food web model such as the
+Allometric Diet Breadth Model (ADBM) (Petchey et al., 2008) (reference
+(gut content paper)) to predict the missing links and then measure the
+robustness of the predicted food web. The ADBM is a mechanistic model
+constructed using foraging rules based on the body sizes of prey and
+predator, where trophic interactions satisfying those rules would be
+predicted by the model, which are perhaps not observed because those
+interactions are rare. However, this solution is not infallible, as it
+is likely that the food web model might still miss some links and also
+may predict some links that could not, in fact occur.
 
@@
 predicted food webs and compare it to that of the observed food webs. We
-expect the ADBM predicted food webs to be more robust than the observed
-food webs, and for the greater robustness to be related to the amount by
-which the ADBM predicts greater connectance compared to that of the
-observed food webs. We do this by simulating primary species loss in 12
-food webs predicted by the ADBM to quantify the secondary loss of
-extinctions and compare the robustness of food webs predicted by the
-ADBM to the robustness of the observed food webs. We use three different
-approaches of primary species removal: (i) most connected species, (ii)
-random species and (iii) least connected species to understand if the
-outcome varies among these approaches.
+achieved this by simulating primary species loss in 12 food webs
+predicted by the model to quantify secondary loss of extinctions and
+compare the robustness of food webs predicted by the model to the
+robustness of the observed food webs. We expect the model predicted food
+webs to be more robust than the observed food webs, and for the greater
+robustness to be related to the amount by which the model predicts
+greater connectance compared to that of the observed food webs. We also
+examined how different structural food web properties other than the
+connectance can influence this difference in the perceived robustness.
+In order to do that, we define our null hypothesis to be: (H1) The
+missing links that are filled in by the model increase robustness
+because they increase connectance; and our alternate hypothesis to be:
+(H2) Although the model fills in missing links, it also changes other
+structural properties and these outweigh the effects of connectance on
+robustness.
 
@@
 parasitoids and terrestrial herbivory ones (Petchey et al., 2008).
+
+All food webs with one exception (Broadstone Stream) was available only
+at the species level, i.e.~with information about interactions between
+species and the body size of species. We use the term ``species'' in
+this study to indicate a ``node'' in a food web in which nodes are
+connected by trophic interactions, and nodes are a collection of
+individuals that share links. These species/nodes are not always
+taxonomic species, but can be broader taxonomic ranks.
+
+In contrast, the Broadstone Stream food web data contained interactions
+between individuals and the individual body sizes. Thus, the Broadstone
+Stream food web can be constructed by aggregating by either taxonomy or
+size (Woodward et al., 2010).
 
@@
 
-We first present the secondary extinction curves of the ADBM predicted
-food webs which had the maximum true skill statistics and of the
-observed food webs for 12 food webs under three different extinction
-scenarios. We then compare the robustness of all the ADBM predicted food
-webs within the 95\% prediction interval against that of the observed
-food webs to take into account uncertainty in the robustness across food
-webs predictions. Finally, we quantify the effect of the difference in
+We first compare the robustness of the model food webs against that of
+the observed food webs. We then quantify the effect of difference in
 their connectance on the difference in their robustness estimates.
 
-\hypertarget{secondary-extinctions}{%
-\subsection{Secondary extinctions}\label{secondary-extinctions}}
-
-In the most connected extinction scenario, the cumulative secondary
-extinction curves started to rise steeply in the observed food webs at a
-lower number of primary species removal as compared to the ADBM
-predicted food webs for nine food webs (Fig. \ref{fig:fig_r1} (a, c, d,
-e, f, g, h, j, l)). However, there was a higher number of cumulative
-secondary extinctions occurring in the ADBM predicted food webs when
-compared to that of the observed food webs at a high number of primary
-species removal in five food webs (Fig. \ref{fig:fig_r1} (a, f, g, h,
-k)). In the Skipwith Pond food web, there were no secondary extinctions
-for any number of primary removal of species (Fig. \ref{fig:fig_r1}
-(i)), whereas in the Broadstone Stream (taxonomic aggregation) food web
-the same was true only for the observed food web but in the ADBM
-predicted food web there was a steep rise in the cumulative secondary
-extinctions (Fig. \ref{fig:fig_r1} (b)).
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{../results/plot_mostconnected_maxTSS}
-
-}
-
-\caption{\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-2}
-\end{figure}
-
-In Fig. \ref{fig:fig_r2}, we present the cumulative secondary
-extinctions in the ADBM predicted and the observed food webs for five
-(out of 1000) independent random extinction sequences to show example
-variation caused by different random primary extinction orders. The
-secondary extinction curves of the ADBM predicted food webs were steeper
-than that of the observed food webs, i.e.~primary removal of some
-species in an extinction sequence can lead to the complete collapse of
-the remaining food web in the ADBM predicted food webs.
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{../results/plot_ra_extlines_maxTSS}
-
-}
-
-\caption{\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-3}
-\end{figure}
-
-Compared to the most connected and random extinction scenarios, there
-were fewer secondary extinctions in the least connected extinction
-scenario, and therefore the secondary extinction curves were flat for
-many of the food webs (Fig. \ref{fig:fig_r3}). In some of the food webs,
-the extinction curves of the ADBM predicted food webs overlapped with
-the observed food webs (Fig. \ref{fig:fig_r3} (b, c, g, h, i, k, l)\}).
-In five of the food webs, a very high number of secondary extinctions
-occurred at a very low number of primary species removal (Fig.
-\ref{fig:fig_r3} (a, d, e, f, j)).
-
-\begin{figure}
-
-{\centering \includegraphics[width=400px]{../results/plot_leastconnected_maxTSS}
-
-}
-
-\caption{\label{fig:fig_r3} Cumulative secondary extinctions of species resulting from the primary removals of the \textbf{least connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species.}\label{fig:unnamed-chunk-4}
-\end{figure}
-
-\hypertarget{robustness}{%
-\subsection{Robustness}\label{robustness}}
-
-The ADBM predicted food webs were more robust than the observed food
-webs on average in the most connected and random extinction scenarios
-(Fig. \ref{fig:fig_r4} (a, b)). However, there were large variations in
-the robustness within the ADBM predicted food webs in the most connected
-extinction scenario (Fig. \ref{fig:fig_r4} (a)). For example, the ADBM
-predicted Caricaie Lakes food web was more robust than the observed food
+The model food webs were more robust than the observed food webs on
+average in the most connected and random extinction scenarios (Fig.
+\ref{fig:fig_r4} (a, b)). However, there were large variations in the
+robustness within the model food webs in the most connected extinction
+scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs
+for the Caricaie Lakes food web was more robust than the observed food
 web on average but had a larger variation in the robustness within the
-ADBM predicted food webs compared to other food webs.
+model food webs compared to other food webs.
 
@@
 and Benguela Pelagic food webs had more variations in robustness within
-the ADBM predicted food webs as compared to the other food webs (Fig.
-\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
-aggregation) and Broadstone Stream (size aggregation) food webs were the
-most robust (Median \(R_{50} = 0.5\)) for both ADBM predicted and
-observed food webs. Although there were few less robust ADBM predicted
-food webs in the Broadstone Stream (size aggregation) as shown by the
-outliers. The food webs were more robust to the random extinction
-scenario than the most connected scenario (Fig. \ref{fig:fig_r4} (a,
-b)). Small Reef and Benguela Pelagic food webs had more variations in
-robustness within the ADBM predicted food webs as compared to the other
-food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream
-(taxonomic aggregation) and Broadstone Stream (size aggregation) food
-webs were the most robust (Median \(R_{50} = 0.5\)) for both ADBM
-predicted and observed food webs. Although there were few less robust
-ADBM predicted food webs in the Broadstone Stream (size aggregation) as
+the model food webs as compared to the other food webs (Fig.
+\ref{fig:fig_r4} (b)). Skipwith Pond and Broadstone Stream (taxonomic
+aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
+for both model and observed food webs. The food webs were more robust to
+the random extinction scenario than the most connected scenario (Fig.
+\ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had
+more variations in robustness within the model food webs as compared to
+the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond,
+Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size
+aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
+for both model and observed food webs. Although there were few less
+robust model food webs in the Broadstone Stream (size aggregation) as
 shown by the outliers.
@@
 (Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
-ADBM predicted food webs for Small Reef and Benguela Pelagic had very
-low median robustness. Benguela Pelagic, Broom and Capinteria food webs
-from the ADBM had larger variations in robustness when compared to that
-of the others.
+model food webs for Small Reef and Benguela Pelagic had very low median
+robustness. The model food webs for the Benguela Pelagic, Broom and
+Capinteria food webs had larger variations in robustness when compared
+to that of the others.
 
@@
 7 in the Supplementary Information for a faceted visualisation.
-The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-2}
 \end{figure}
 
-In all of the food webs except Small Reef and Broadstone Stream
-(taxonomic aggregation), the effect size of connectance on robustness
-was positive on average in the most connected extinction scenario (Fig.
+In all of the food webs except Broadstone Stream (taxonomic aggregation)
+and Skipwith Pond, the effect size of connectance on robustness was
+positive on average in the most connected extinction scenario (Fig.
 \ref{fig:fig_r5} (a)), i.e.~greater connectance had a positive effect on
@@
 across the food webs. In the least connected extinction scenario, the
-median effect sizes were zero or very close to zero for all the food
-webs except Benguela Pelagic and Small Reef food webs where the median
+median effect sizes were zero for all the food webs except for Caricaie
+Lakes and Capinteria food webs where the effect sizes were very close to
+zero and for Benguela Pelagic and Small Reef food webs where the median
 effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
-were lots of outlier effect sizes less than zero.
+were lots of outlier with effect sizes negative.
 
@@
 ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs.
-Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-6}
+Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.}\label{fig:unnamed-chunk-3}
 \end{figure}
@@
 
-As expected, the ADBM predicted food webs were more robust than the
-observed food webs on average. The considerable variation of the
-robustness of the ADBM predicted food webs suggests, however, that
-undersampling in food webs can lead to considerable uncertainty in the
-estimates of food web robustness, even when a model is used to
-compensate for undersampling. Furthermore, as was previously found, the
-food webs are least robust to primary extinction of the most connected
-species compared to that of least connected and random extinction
-scenarios on average. Future development would be to understand how
-undersampling, i.e.~predicted greater connectance, influences the
-stability of the dynamics of the ADBM predicted food webs against that
-of the observed food webs and compare it with the patterns in our study
-in which extinction occur only by topological criteria. However, one
-would expect a decrease in food web stability with greater connectance
-(Martinez et al., 2006; May, 1972).
+As expected, the model food webs were more robust than the observed food
+webs on average. The considerable variation of the robustness of the
+model food webs suggests, however, that undersampling in food webs can
+lead to considerable uncertainty in the estimates of food web
+robustness, even when a model is used to compensate for undersampling.
+Furthermore, as was previously found, the food webs are least robust to
+primary extinction of the most connected species compared to that of
+least connected and random extinction scenarios on average. Future
+development would be to understand how undersampling, i.e.~predicted
+greater connectance, influences the stability of the dynamics of the
+model food webs against that of the observed food webs and compare it
+with the patterns in our study in which extinction occur only by
+topological criteria. However, one would expect a decrease in food web
+stability with greater connectance (Martinez et al., 2006; May, 1972).
 
@@
 observed food webs when computing their robustness.
+
+\hypertarget{a-paragraph-on-the-implication-of-our-study}{%
+\subsection{A paragraph on the implication of our
+study}\label{a-paragraph-on-the-implication-of-our-study}}
+
+\begin{itemize}
+\tightlist
+\item
+  On the uncertainty in the ADBM estimates
+\item
+  On the limitation of a food web model
+\item
+  On undersampling
+\end{itemize}
+
+Our study also depicts that the uncertainty in the model predictions can
+have a strong influence on the perceived robustness of the observed food
+webs. The large variations in the robustness of the observed food webs
+suggest why it is crucial to incorporate uncertainty in the food web
+predictions. At the same time, our study also quantifies the impact of
+undersampling on the perceived robustness of the observed food webs and
+thus influencing the perceived functioning and stability of the food
+webs (reference). This strongly suggest why it is crucial to incorporate
+the influence of undersampling.
 
@@
 means that the food web model predicts a link between two species that
-can never interact. (The other type of false positive is when the model
+can never interact (The other type of false positive is when the model
 predicts a link that was not observed but could have been observed if
@@
 result in the link being observed and a change from false positive to
-true positive.) Firstly, this may be because the ADBM uses only body
+true positive.). Firstly, this may be because the ADBM uses only body
 size as a trait. A trait uncorrelated with the body size may be
@@
 Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-7}
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-4}
 \end{figure}
@@
 Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-8}
+The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
 \end{figure}
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-woodwardChapterIndividualBasedFood2010}{}}%
+Woodward, G., Blanchard, J., Lauridsen, R. B., Edwards, F. K., Jones, J.
+I., Figueroa, D., Warren, P. H., \& Petchey, O. L. (2010). Chapter 6 -
+{Individual-Based Food Webs}: {Species Identity}, {Body Size} and
+{Sampling Effects}. In G. Woodward (Ed.), \emph{Advances in {Ecological
+Research}} (Vol. 43, pp. 211--266). {Academic Press}.
+\url{https://doi.org/10.1016/B978-0-12-385005-8.00006-X}
+
 \end{CSLReferences}

### 2023-02-10 inst/main/calc_fw_prop.R

@@ -47,7 +47,7 @@ max_tl_emp_fun <- function(foodweb){
   metadata <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
   fw_tol_loc <- metadata$dist_rej[metadata$foodweb == fw]
   
-  for(nsim_loc in 1:10){
+  for(nsim_loc in 1:1){
     pred_mat <- ADBM_ABC_fw_all(fw_name = fw, fw_tol = fw_tol_loc, nsim = nsim_loc)
     
     pred_mat_emp <- pred_mat$real_pred_mat

### 2023-02-10 inst/main/calc_fw_prop_basal.R

@@ -1,0 +1,33 @@
+# 2022.11.28
+# Calculate proportion of basal species
+
+prop_basal_ADBM_fun <- function(foodweb){
+  
+  fw <- foodweb
+  prop_basal_ADBM_all <- c()
+  
+  library(R.utils)
+  library(readxl)
+  library(cheddar)
+  
+  sourceDirectory("R", modifiedOnly = FALSE)
+  sourceDirectory("../C1_method_v2/R", modifiedOnly = FALSE)
+  
+  metadata <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+  fw_tol_loc <- metadata$dist_rej[metadata$foodweb == fw]
+  
+  for(nsim_loc in 1:1000){
+    print(nsim_loc)
+    pred_mat <- ADBM_ABC_fw_all(fw_name = fw, fw_tol = fw_tol_loc, nsim = nsim_loc)
+    
+    pred_mat_ADBM <- pred_mat$ADBM_pred_mat
+    
+    comm_ADBM <- mat.to.comm(pred.mat = pred_mat_ADBM, fw_title = fw)
+    
+    prop_basal_ADBM <- FractionBasalNodes(comm_ADBM)
+    
+    prop_basal_ADBM_all <- c(prop_basal_ADBM_all, prop_basal_ADBM)
+  }
+  
+  return(prop_basal_ADBM_all)
+}

### 2023-02-10 inst/main/plot_max_tl_ADBM_vs_emp.R

@@ -21,9 +21,11 @@ plot_max_tl_ADBM_vs_emp <- ggplot(max_tl_df) +
   xlim(c(0, 10)) +
   ylim(c(0, 10)) +
   scale_color_brewer(palette = "Paired", labels = fw_labs, name = "Food web") +
-  geom_abline(slope = 1, intercept = 0) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2) +
   xlab("Maximum trophic level in observed food webs") +
   ylab("Maximum trophic level in ADBM predicted food webs") +
   theme_classic()
+
+# saveRDS(object = plot_max_tl_ADBM_vs_emp, file = "results/plot_max_tl_ADBM_vs_emp.RDS")
 
 # ggsave(plot = plot_max_tl_ADBM_vs_emp, filename = "results/plot_max_tl_ADBM_vs_emp.png", width = 8, height = 5)

### 2023-02-10 inst/main/plot_mostconnected_maxTSS.R

@@ -28,7 +28,9 @@ plot_dd_mc_mod <- ggplot(dd_mc_mod) +
   scale_color_manual(name = "Food web type", labels = c("ADBM" = "ADBM food web with maximum TSS", "Empirical" = "Observed food web"), 
                      values = c("ADBM" = "red", "Empirical" = "blue")) +
   theme(legend.position="bottom", legend.text = element_text(size = 15),
-        legend.title = element_text(size = 15))
+        legend.title = element_text(size = 15)) +
+  theme(text = element_text(size = 16)) +
+  scale_x_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), labels = c(0, 0.25, 0.5, 0.75, 1))
 
 
 # ggsave(plot = plot_dd_mc_mod, filename = "results/plot_mostconnected_maxTSS.png", width = 13, height = 6)

### 2023-02-10 inst/main/plot_multiple_random_ext_lines.R

@@ -9,11 +9,12 @@ dd_rand_raw <- readRDS("results/random_raw_uncertainty_maxTSS.RDS")
 dd_rand_mod <- dd_rand_raw %>%
   mutate(acc_pri_ext_by_S = n_ext/S, acc_sec_ext_by_S = acc_sec_ext/S)
 
-fw_labs <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream \n (taxonomic aggregation)",
-             "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
-             "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
-             "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
-             "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream \n (size aggregation)")
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
 
 plot_ra_ext_lines <- dd_rand_mod %>%
   filter(nsim_rand %in% c(36:40)) %>%
@@ -31,6 +32,8 @@ plot_ra_ext_lines <- dd_rand_mod %>%
     scale_color_manual(name = "Food web type", labels = c("ADBM_ABC" = "ADBM food web with maximum TSS", "Empirical" = "Observed food web"), 
                      values = c("ADBM_ABC" = "red", "Empirical" = "blue")) +
     theme(legend.position="bottom", legend.text = element_text(size = 15),
-          legend.title = element_text(size = 15))
+          legend.title = element_text(size = 15)) +
[…]

### 2023-02-10 inst/main/robustness_R50_ADBM_vs_observed.R

@@ -70,7 +70,7 @@ rob_both_median <- rob_both %>%
 #### Graph
 plot_R50_ra <- rob_both %>%
   ggplot() +
-  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name, fill = fw_name), alpha = 1, width = 0.0019, outlier.shape = 1,
+  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name, fill = fw_name), alpha = 0.5, width = 0.01, outlier.shape = 1,
                outlier.alpha = 0.5, outlier.size = 0.3) +
   geom_abline(slope = 1, intercept = 0, linetype = 3) +
   xlim(c(0.0, 0.51)) +
@@ -86,7 +86,8 @@ plot_R50_ra <- rob_both %>%
   scale_color_brewer(type = "qual", palette = "Paired", labels = fw_labs, name = "Food web") +
   scale_shape_manual(name  = "Summary statistics", labels = c("Median"), values = c(18)) +
   ggtitle("(b) Random") +
-  theme(legend.position = "right", plot.title = element_text(hjust = 0.5))
+  theme(legend.position = "right", plot.title = element_text(hjust = 0.5)) +
+  theme(text = element_text(size = 15))
 
 
 ##### Most Connected extinction ####
@@ -134,7 +135,7 @@ rob_both_mc_median <- rob_both_mc %>%
 #### Graph
 plot_R50_mc <- rob_both_mc %>%
   ggplot() +
-  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name, fill = fw_name), alpha = 1, width = 0.0019, outlier.shape = 1,
+  geom_boxplot(aes(x = robustness_emp, y = robustness_ADBM, color = fw_name, fill = fw_name), alpha = 0.5, width = 0.01, outlier.shape = 1,
                outlier.alpha = 0.5, outlier.size = 0.3) +
   geom_abline(slope = 1, intercept = 0, linetype = 3) +
   xlim(c(0.0, 0.51)) +
@@ -150,7 +151,8 @@ plot_R50_mc <- rob_both_mc %>%
   scale_color_brewer(type = "qual", palette = "Paired", labels = fw_labs, name = "Food web") +
   scale_shape_manual(name  = "Summary statistics", labels = c("Median"), values = c(18)) +
   ggtitle("(a) Most connected") +
[…]

### 2023-02-10 manuscript/C3_code/R/ADBM_2008_fw.R

@@ -1,0 +1,33 @@
+ADBM_2008_fw <- function(fw_name){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- read_excel("../C1_method_v2/data/parameter_values.xlsx")
+  
+  ADBM_fw_par <- ADBM_fw_all[ADBM_fw_all$foodweb == fw_name,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}

### 2023-02-10 manuscript/C3_code/R/ADBM_ABC_fw_all.R

@@ -1,0 +1,33 @@
+ADBM_ABC_fw_all <- function(fw_name, fw_tol, nsim){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".RDS"))
+  
+  ADBM_fw_par <- ADBM_fw_all$post_dists[nsim,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}

### 2023-02-10 manuscript/C3_code/R/ADBM_ABC_fw_maxTSS.R

@@ -1,0 +1,36 @@
+# Returns ADBM predicted food web with max TSS
+
+ADBM_ABC_fw_maxTSS <- function(fw_name, fw_tol){
+  
+  real_fw <- readRDS(paste("../C1_method_v2/data/", fw_name, ".web.RDS", sep = ""))
+  real_pred_mat <- real_fw$predation.matrix
+  
+  ADBM_fw_all <- readRDS(paste0("../C1_method_v2/results/rejection/", fw_name, "/rN=1000_tol=", fw_tol, "_TSS_lower_a/", fw_name, ".RDS"))
+  
+  sel_ind <- which.min(ADBM_fw_all$dist)
+  ADBM_fw_par <- ADBM_fw_all$post_dists[sel_ind,]
+  
+  ## Generating the ADBM predicted food web
+  fw_data <- real_fw
+  
+  n_species <- length(fw_data$species.sizes)
+  
+  M <- fw_data$species.sizes
+  M <- sort(M)
+  
+  sim_a <- 10^ADBM_fw_par$a
+  sim_ai <- ADBM_fw_par$ai
+  sim_aj <- ADBM_fw_par$aj
+  sim_r.b <- 10^ADBM_fw_par$r.b
+  
+  local_par <- data.frame(a = sim_a, ai = sim_ai, aj = sim_aj, r.b = sim_r.b)
+  sim_model_core_par <- list(e = 1, n = 1, ni = -3/4, r.a = 1, M  = M)
+  pred_mat <- ratio.power(opt=local_par, x = sim_model_core_par)
+  rownames(pred_mat) <- as.character(seq(1, n_species))
+  colnames(pred_mat) <- as.character(seq(1, n_species))
+  
+  ADBM_pred_mat <- pred_mat
+  
+  return(list(real_pred_mat = real_pred_mat,
+              ADBM_pred_mat = ADBM_pred_mat))
+}

### 2023-02-10 manuscript/C3_code/R/isolated_nodes_fun.R

@@ -1,0 +1,14 @@
+# 2022.07.07
+# Obtain isolated nodes if any (isolated nodes are the one that do not feed on any other nodes)
+
+isolated_nodes_fun <- function(net){
+  
+  indeg <- rowSums(net)
+  outdeg <- colSums(net)
+  
+  totdeg <- indeg + outdeg
+  
+  return(names(which(totdeg == 0)))
+  
+}
+

### 2023-02-10 manuscript/C3_code/R/most_connected_ext.R

@@ -1,0 +1,49 @@
+# 23.11.2021
+# Simulating extinction for most connected nodes
+
+most_connected_ext <- function(net){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  new_net <- net
+  k <- 1
+  ext_list <- list()
+  
+  # Stop when all the species is extinct
+  while(all(is.na(new_net)) == FALSE){
+    indeg <- rowSums(new_net)
+    outdeg <- colSums(new_net)
+    totdeg <- indeg + outdeg
+    
+    max_totdeg <- which.max(totdeg)
+    node <- names(max_totdeg)
+    
+    ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+    new_net <- ext_list[[k]]$net
+    
+    if(k != 1){
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]] + dd$acc_sec_ext[k-1])
+            )
+    }else{
+      dd <- rbind(dd, 
+                  data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                             acc_sec_ext = ext_list[[k]][[2]])
+                  )
+    }
+    
+    k <- k + 1
+    # print(k)
+ 
+    }
+  
+  return(dd)
+
+}

### 2023-02-10 manuscript/C3_code/R/random_ext.R

@@ -1,0 +1,50 @@
+# 24.11.2021
+# Simulating extinctions for random nodes
+
+random_ext <- function(net, nsim){
+  
+  dd <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+  basal_species <- basal_species_fun(net)
+  
+  ## Removing isolated nodes
+  isolated_nodes <- isolated_nodes_fun(net = net)
+  not_isolated_nodes <- setdiff(x = colnames(net), y = isolated_nodes)
+  net <- net[not_isolated_nodes, not_isolated_nodes]
+  
+  for(sim_ind in 1:nsim){
+      dd_temp <- data.frame(node = character(), acc_pri_ext = integer(), n_sec_ext = integer(), acc_sec_ext = integer(), nsim = integer())
+      new_net <- net
+      k <- 1
+      ext_list <- list()
+    
+    while(all(is.na(new_net)) == FALSE | sum(new_net) != 0){
+      pool_node <- rownames(new_net)
+      
+      node <- sample(x = pool_node, size = 1)
+      
+      ext_list[[k]] <- sim_single_ext_v2(net = new_net, node = node, basal_species = basal_species)
+      new_net <- ext_list[[k]]$net
+      
+      if(k != 1){
+        dd_temp <- rbind(dd_temp, 
+                    data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                               acc_sec_ext = ext_list[[k]][[2]] + dd_temp$acc_sec_ext[k-1], nsim = sim_ind)
+        )
+      } else {
+        dd_temp <- rbind(dd_temp, 
+                    data.frame(node = node, acc_pri_ext = k, n_sec_ext = ext_list[[k]][[2]],
+                               acc_sec_ext = ext_list[[k]][[2]], nsim = sim_ind)
+        )
+      }
+      
+      k <- k + 1
+      # print(k)
+    }
+    dd <- rbind(dd, dd_temp)
+  }
+  
+  
+  sim_ind <- sim_ind + 1
+  
+  return(dd)
+}

### 2023-02-10 manuscript/C3_code/R/sim_single_ext.R

@@ -1,0 +1,51 @@
+# 22.11.2021
+# Simulating single extinction in a network
+
+sim_single_ext <- function(net, node){
+  
+  indeg <- rowSums(net)
+  # print(length((indeg)))
+  outdeg <- colSums(net)
+  # print(length((outdeg)))
+  totdeg <- indeg + outdeg
+  
+
+  new_net <- net[!rownames(net) %in% node, !colnames(net) %in% node]
+  
+  if(length(new_net) == 1){
+    new_net <- as.matrix(new_net)
+    lost_node <- setdiff(rownames(net), node)
+    rownames(new_net) <- lost_node
+    colnames(new_net) <- lost_node
+  }
+  
+  ## Predators of node "node"
+  node_pred <- net[node,]
+  
+  node_to_sec_ext <- which(outdeg[as.logical(node_pred)] == 1)
+  
+  
+  if(length(node_to_sec_ext) != 0){
+    new_net_2 <- new_net[!rownames(new_net) %in% names(node_to_sec_ext), !colnames(new_net) %in% names(node_to_sec_ext)]
+    if(length(new_net_2) == 1){
+      new_net_2 <- as.matrix(new_net_2)
+      lost_node <- setdiff(rownames(new_net), names(node_to_sec_ext))
+      rownames(new_net_2) <- lost_node
+      colnames(new_net_2) <- lost_node
+    }
+  } else { ## If there are no predator of the primary node (the one which is removed)
+    new_net_2 <- new_net
+  }
+  
+  ## Setdiff to ensure cannibalistic extinction are not included again in secondary ext
+  n_sec_ext <- length(setdiff(names(node_to_sec_ext), node))
+  
+  list_ret <- list(net = new_net_2, n_sec_ext = n_sec_ext)
+  
+  return(list_ret)
+  
+  }
+  
+  
+  
+  

### 2023-02-10 manuscript/C3_code/R/sim_single_ext_v2.R

@@ -1,0 +1,58 @@
+# 2022.07.06
+# Simulating single primary extinction in a food web i.e removing given node from a given food web
+# Calculating secondary extinction 
+# Ensure that the input network "net" does not have any isolated nodes
+
+
+sim_single_ext_v2 <- function(net, node, basal_species){
+  
+  indeg <- rowSums(net)
+  outdeg <- colSums(net)
+  
+  totdeg <- indeg + outdeg
+  
+  new_net <- net[!rownames(net) %in% node, !colnames(net) %in% node]
+  
+  if(length(new_net) == 1){
+    new_net <- as.matrix(new_net)
+    lost_node <- setdiff(rownames(net), node)
+    rownames(new_net) <- lost_node
+    colnames(new_net) <- lost_node
+  }
+  
+  sp_outdeg_zero <- names(which(colSums(new_net) == 0))
+  sp_outdeg_zero_wo_basal <- setdiff(sp_outdeg_zero, basal_species)
+  
+  count <- 1
+  n_sec_ext <- length(sp_outdeg_zero_wo_basal)
+  while(length(sp_outdeg_zero_wo_basal) != 0){
+    
+    node_to_sec_ext <- sp_outdeg_zero_wo_basal
+    new_net_2 <- new_net[!rownames(new_net) %in% node_to_sec_ext, !colnames(new_net) %in% node_to_sec_ext]
+    
+    if(length(new_net_2) == 1){
+      new_net_2 <- as.matrix(new_net_2)
+      lost_node <- setdiff(rownames(new_net), node_to_sec_ext)
+      rownames(new_net_2) <- lost_node
+      colnames(new_net_2) <- lost_node
+    }
+    
+    sp_outdeg_zero <- names(which(colSums(new_net_2) == 0))
+    sp_outdeg_zero_wo_basal <- setdiff(sp_outdeg_zero, basal_species)
+    
+    n_sec_ext <- n_sec_ext + length(sp_outdeg_zero_wo_basal)
+    # print(count)
+    count <- count + 1
+    new_net <- new_net_2
+  }
+  
+  if(count > 1){
+    list_ret <- list(net = new_net_2, n_sec_ext = n_sec_ext)
+  } else {
+    new_net_2 <- new_net
+    list_ret <- list(net = new_net_2, n_sec_ext = n_sec_ext)
+  }
+  
+  return(list_ret)
+}
+

### 2023-02-10 manuscript/C3_code/main/extinction_leastconnected.R

@@ -1,0 +1,71 @@
+# 2022.02.09
+# We simulated primary extinction by removing least connected species in food web predicted by the ADBM which had the maximum TSS
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing least connected nodes
+dd_lc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  ADBM_ABC_fw_calc <- ADBM_ABC_fw(fw_name = fw_name, fw_tol = fw_tol)
+  
+  real_pred_mat <- ADBM_ABC_fw_calc$real_pred_mat
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  ADBM_ABC_pred_mat <- ADBM_ABC_fw_calc$ADBM_pred_mat
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  L_ADBM_ABC <- sum(ADBM_ABC_pred_mat)
+  
+  
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  ADBM_ABC_conn <- sum(ADBM_ABC_pred_mat)/(dim(ADBM_ABC_pred_mat)[1]^2)
+  
+  real_ext_mc <- least_connected_ext(net = real_pred_mat)
+  ADBM_ABC_ext_mc <- least_connected_ext(net = ADBM_ABC_pred_mat)
+  
[…]

### 2023-02-10 manuscript/C3_code/main/extinction_leastconnected_uncertainty.R

@@ -1,0 +1,74 @@
+# 2022.02.23
+# We simulated primary extinction by removing least connected species in all the 1000 food web predicted by the ADBM 
+
+library(R.utils)
+library(NetworkExtinction)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing most connected nodes
+dd_lc <- data.frame(n_ext = double(),
+                    acc_sec_ext = integer(),
+                    nsim_fw = integer(),
+                    type = character(),
+                    fw_name = character(),
+                    S = integer(),
+                    L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+
+
+for(i in fw_ind){
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  real_pred_mat <- readRDS(paste0("../C1_data/data/", fw_name, ".web.RDS"))$predation.matrix
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_lc <- least_connected_ext(net = real_pred_mat)
+  
+  dd_lc <- rbind(dd_lc, 
+                 data.frame(n_ext = real_ext_lc$acc_pri_ext,
+                            acc_sec_ext = real_ext_lc$acc_sec_ext,
+                            nsim_fw = 1,
+                            type = "Empirical",
+                            fw_name = fw_name,
+                            S = S,
+                            L = L_real))
+  
+  for(j in 1:1000){
[…]

### 2023-02-10 manuscript/C3_code/main/extinction_random_maxTSS.R

@@ -1,0 +1,79 @@
+# 2022.09.12
+# We simulated primary extinction by removing random species in all the food web predicted by the ADBM with max TSS
+
+library(R.utils)
+library(network)
+library(readxl)
+library(dplyr)
+library(ggplot2)
+library(doParallel)
+
+sourceDirectory("../C1_method_v2/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+# For removing random nodes
+dd_rand <- data.frame(n_ext = double(),
+                      acc_sec_ext = integer(),
+                      nsim_rand = integer(),
+                      type = character(),
+                      fw_name = character(),
+                      S = integer(),
+                      L = integer())
+
+# Getting the foodweb name and tolerance
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+n_fw <- length(metadata_fw_tol$foodweb)
+fw_ind <- 1:n_fw
+Nsim <- 100
+
+for(i in fw_ind){
+  
+  fw_name <- metadata_fw_tol$foodweb[i]
+  fw_tol <- metadata_fw_tol$dist_rej[i]
+  
+  ### Real food webs
+  real_pred_mat <- readRDS(paste0("../C1_method_v2/data/", fw_name, ".web.RDS"))$predation.matrix
+  
+  if(is.null(rownames(real_pred_mat))){
+    n_nodes <- dim(real_pred_mat)[1]
+    rownames(real_pred_mat) <- as.character(1:n_nodes)
+    colnames(real_pred_mat) <- as.character(1:n_nodes)
+  }
+  
+  S <- dim(real_pred_mat)[1]
+  L_real <- sum(real_pred_mat)
+  real_conn <- sum(real_pred_mat)/(dim(real_pred_mat)[1]^2)
+  real_ext_rand <- random_ext_parallel(net = real_pred_mat, nsim = Nsim, n_cores = 5)
+  
+  dd_rand <- rbind(dd_rand,
+                   data.frame(n_ext = real_ext_rand$acc_pri_ext,
+                              acc_sec_ext = real_ext_rand$acc_sec_ext,
+                              nsim_rand = real_ext_rand$nsim,
+                              type = "Empirical",
+                              fw_name = fw_name,
[…]

### 2023-02-10 manuscript/C3_code/main/plot_multiple_random_ext_lines.R

@@ -1,0 +1,36 @@
+# 2022.08.30
+# Plot multiple cumulative secondary extinctions for random extinction scenario for independent simulations
+
+library(dplyr)
+library(ggplot2)
+
+dd_rand_raw <- readRDS("results/random_raw_uncertainty_maxTSS.RDS")
+
+dd_rand_mod <- dd_rand_raw %>%
+  mutate(acc_pri_ext_by_S = n_ext/S, acc_sec_ext_by_S = acc_sec_ext/S)
+
+fw_labs <- c("Benguela Pelagic" = "Benguela Pelagic", "Broadstone Stream" = "Broadstone Stream \n (taxonomic aggregation)",
+             "Broom" = "Broom", "Capinteria" = "Capinteria", "Caricaie Lakes" = "Caricaie Lakes",
+             "Grasslands" = "Grasslands", "Mill Stream" = "Mill Stream",
+             "Skipwith Pond" = "Skipwith Pond", "Small Reef" = "Small Reef", "Tuesday Lake" = "Tuesday Lake",
+             "Ythan" = "Ythan", "Broadstone Stream size_agg" = "Broadstone Stream \n (size aggregation)")
+
+plot_ra_ext_lines <- dd_rand_mod %>%
+  filter(nsim_rand %in% c(36:40)) %>%
+  ggplot() +
+    geom_point(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type, color = as.factor(nsim_rand))) +
+    geom_line(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type, color = as.factor(nsim_rand))) +
+    facet_wrap(~fw_name, labeller = labeller(fw_name = fw_labs), nrow = 2) +
+    theme_classic() +
+    xlab("Species removed/S") +
+    ylab("Cumulative secondary extinctions/S") +
+    # scale_color_manual(name = "Food web type", labels = c("ADBM" = "ADBM food web", "Empirical" = "Observed food web"), 
+    #                    values = c("ADBM" = "red", "Empirical" = "blue")) +
+    scale_shape_discrete(name = "Type") +
+    scale_linetype_discrete(name = "Type") +
+    scale_color_manual(name = "Food web type", labels = c("ADBM_ABC" = "ADBM food web with maximum TSS", "Empirical" = "Observed food web"), 
+                     values = c("ADBM_ABC" = "red", "Empirical" = "blue")) +
[…]

### 2023-02-10 manuscript/C3_code/main/plot_random.R

@@ -1,0 +1,58 @@
+# 2022.02.13
+
+# Plot how secondary extinctions vary when number of species removed is increased
+
+library(dplyr)
+library(ggplot2)
+
+dd_rand_raw <- readRDS("results/random_raw_wo_basal_maxTSS.RDS")
+
+dd_rand_mod <- dd_rand_raw %>%
+  group_by(fw_name, type, nsim, S) %>%
+  mutate(max_pri = max(acc_pri_ext)) %>%
+  group_by(fw_name, type, S) %>%
+  mutate(max_min_pri = min(max_pri)) %>%
+  filter(acc_pri_ext <= max_min_pri) %>%
+  group_by(fw_name, acc_pri_ext, type, S) %>%
+  summarise(mean_acc_sec_ext = mean(acc_sec_ext), l_acc_sec_ext = min(acc_sec_ext), u_acc_sec_ext = max(acc_sec_ext)) %>%
+  mutate(acc_pri_ext_by_S = acc_pri_ext/S, acc_sec_ext_by_S = mean_acc_sec_ext/S, l_acc_sec_ext_by_S = l_acc_sec_ext/S,
+         u_acc_sec_ext_by_S = u_acc_sec_ext/S)
+
+
+
+
+fw_labs <- c("Benguela Pelagic" = "(a) Benguela Pelagic", "Broadstone Stream" = "(b) Broadstone Stream \n(taxonomic aggregation)",
+             "Broadstone Stream size_agg" = "(c) Broadstone Stream \n(size aggregation)",
+             "Broom" = "(d) Broom", "Capinteria" = "(e) Capinteria", "Caricaie Lakes" = "(f) Caricaie Lakes",
+             "Grasslands" = "(g) Grasslands", "Mill Stream" = "(h) Mill Stream",
+             "Skipwith Pond" = "(i) Skipwith Pond", "Small Reef" = "(j) Small Reef", "Tuesday Lake" = "(k) Tuesday Lake",
+             "Ythan" = "(l) Ythan")
+
+
+plot_dd_random_mod <- ggplot(dd_rand_mod) +
+  geom_point(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  geom_line(aes(x = acc_pri_ext_by_S, y = acc_sec_ext_by_S, color = type)) +
+  facet_wrap(~fw_name, labeller = labeller(fw_name = fw_labs), nrow = 2) +
+  theme_classic() +
+  xlab("Species removed/S") +
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_leastconnected_R50_uncertainty.R

@@ -1,0 +1,83 @@
+# 2022.08.02
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_lc <- readRDS("results/least_connnected_uncertainty.RDS")
+
+fw_list <- unique(dd_lc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim_fw = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_lc_real <- dd_lc %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim_fw == 1)
+  
+  dd_lc_real <- dd_lc_real %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- NA
+  N_row <- dim(dd_lc_real)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_lc_real[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  # intervality_emp <- intervality(pred_mat_emp)
+  S <- dim(pred_mat_emp)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim_fw = 1)
+  )
+  
+  for(nsim_fw_local in 1:1000){
+    
+    #### ADBM ABC predicted food web second ####
+    dd_lc_ADBM_ABC <- dd_lc %>%
+      filter(fw_name == foodweb, type == "ADBM_ABC", nsim_fw == nsim_fw_local) %>%
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_mostconnected.R

@@ -1,0 +1,104 @@
+# 2022.09.02
+# We investigate how the robustness vary across food webs
+
+library(cheddar)
+library(dplyr)
+library(R.utils)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mc <- readRDS("results/most_connected.RDS")
+
+fw_list <- unique(dd_mc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double(), intervality = double())
+
+for(foodweb in fw_list){
+  
+  #### ADBM ABC predicted food web ####
+  dd_mc_ADBM_ABC <- dd_mc %>%
+    filter(fw_name == foodweb, type == "ADBM_ABC") %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  N_row <- dim(dd_mc_ADBM_ABC)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_mc_ADBM_ABC[i,]
+    if(ith_row$total_ext >= 0.5){
+      robustness <- ith_row$n_ext/ith_row$S
+      break
+    }
+  }
+  
+  pred_mat_ADBM_ABC <- readRDS(paste0("data/ADBM_predicted_foodwebs/", foodweb, ".pred_mat.RDS"))
+  S <- dim(pred_mat_ADBM_ABC)[1]
+  conn_ADBM_ABC <- sum(pred_mat_ADBM_ABC)/(dim(pred_mat_ADBM_ABC)[1]^2)
+  intervality_ADBM_ABC <- intervality(pred_mat_ADBM_ABC)
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "ADBM", connectance = conn_ADBM_ABC,
+                              S = S, intervality = intervality_ADBM_ABC)
+  )
+  
+  #### Empirical food web ####
+  dd_mc_ADBM <- dd_mc %>%
+    filter(fw_name == foodweb, type == "Empirical")
+  
+  dd_mc_ADBM <- dd_mc_ADBM %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  N_row <- dim(dd_mc_ADBM)[1]
+  for(i in 1:N_row){
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_mostconnected_R100_uncertainty.R

@@ -1,0 +1,135 @@
+# 2022.07.04
+# We investigate how the robustness (R100: the number of species required to achieve a total loss of all the species) vary across food webs for most connected extinction scenario
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+library(dplyr)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_mc <- readRDS("results/most_connnected_uncertainty_new.RDS")
+
+fw_list <- unique(dd_mc$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim = integer())
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  for(nsim_local in 1:1000){
+    
+    #### ADBM ABC predicted food web first ####
+    dd_mc_ADBM_ABC <- dd_mc %>%
+      filter(fw_name == foodweb, type == "ADBM", nsim == nsim_local) %>%
+      mutate(total_ext = (n_ext + acc_sec_ext)/S)
+    
+    N_row <- dim(dd_mc_ADBM_ABC)[1]
+    for(i in 1:N_row){
+      ith_row <- dd_mc_ADBM_ABC[i,]
+      if(ith_row$total_ext >= 1){
+        robustness <- ith_row$n_ext/ith_row$S
+        break
+      }
+    }
+    
+    fw_tol <- metadata_fw_tol$dist_rej[which(metadata_fw_tol$foodweb == foodweb)]
+    pred_mat_ADBM_ABC <- ADBM_ABC_fw_all(fw_name = foodweb, fw_tol = fw_tol, nsim = nsim_local)$ADBM_pred_mat
+    S <- dim(pred_mat_ADBM_ABC)[1]
+    conn_ADBM_ABC <- sum(pred_mat_ADBM_ABC)/(dim(pred_mat_ADBM_ABC)[1]^2)
+    # intervality_ADBM_ABC <- intervality(pred_mat_ADBM_ABC)
+    rob_all <- rbind(rob_all,
+                     data.frame(robustness = robustness, fw_name = foodweb, type = "ADBM_ABC", connectance = conn_ADBM_ABC,
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_random.R

@@ -1,0 +1,116 @@
+# 2022.15.02
+
+library(cheddar)
+library(dplyr)
+library(R.utils)
+library(ggplot2)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_rand_raw <- readRDS("results/random_raw.RDS")
+
+fw_list <- unique(dd_rand_raw$fw_name)
+sim_ind <- unique(dd_rand_raw$nsim)
+list_all <- expand.grid(nsim = sim_ind, fw_name = fw_list)
+N <- dim(list_all)[1]
+
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double())
+
+for(i in 1:N){
+  
+  row_sel <- list_all[i,]
+  foodweb <- as.character(row_sel$fw_name)
+  
+  
+  ###### ADBM_ABC #######
+  type_fw = "ADBM"
+  dd_fil <- dd_rand_raw %>%
+    filter(fw_name == row_sel$fw_name, nsim == row_sel$nsim, type == type_fw) %>%
+    mutate(acc_tot_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  
+  N_row <- dim(dd_fil)[1]
+  for(i in 1:N_row){
+    ith_row <- dd_fil[i,]
+    if(ith_row$acc_tot_ext >= 0.5){
+      robustness <- ith_row$acc_pri_ext/ith_row$S
+      break
+    }
+  }
+  
+  pred_mat <- readRDS(paste0("data/", type_fw, "_predicted_foodwebs/", foodweb, ".pred_mat.RDS"))
+  S <- dim(pred_mat)[1]
+  conn <- sum(pred_mat)/(dim(pred_mat)[1]^2)
+  
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = type_fw, connectance = conn,
+                              S = S)
+  )
+  
+  ###### Empirical #######
+  type_fw = "Empirical"
+  dd_fil <- dd_rand_raw %>%
+    filter(fw_name == row_sel$fw_name, nsim == row_sel$nsim, type == type_fw) %>%
+    mutate(acc_tot_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_random_R50_uncertainty.R

@@ -1,0 +1,97 @@
+# 2022.02.27
+
+library(cheddar)
+library(R.utils)
+library(ggplot2)
+library(HDInterval)
+library(readxl)
+library(dplyr)
+
+sourceDirectory("../C1_method/R", modifiedOnly=FALSE)
+sourceDirectory("R", modifiedOnly=FALSE)
+
+dd_rand <- readRDS("results/random_raw_uncertainty_july11.RDS")
+
+fw_list <- unique(dd_rand$fw_name)
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = integer(), nsim = integer())
+Nsim <- 100
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_rand_emp <- dd_rand %>%
+    filter(fw_name == foodweb, type == "Empirical", nsim == 1)
+  
+  dd_rand_emp <- dd_rand_emp %>%
+    mutate(total_ext = (n_ext + acc_sec_ext)/S)
+  
+  robustness <- 0
+  for(k in 1:Nsim){
+    dd_rand_emp_local <- dd_rand_emp %>%
+      filter(nsim_rand == k)
+    
+    N_row <- dim(dd_rand_emp_local)[1]
+    for(i in 1:N_row){
+      ith_row <- dd_rand_emp_local[i,]
+      if(ith_row$total_ext >= 0.5){
+        robustness <- robustness + ith_row$n_ext/ith_row$S
+        # print(robustness)
+        break
+      }
+    }
+  }
+  
+  robustness <- robustness/Nsim
+  robustness <- min(robustness, 0.5)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  rob_all <- rbind(rob_all,
+                   data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
+                              S = S, nsim = 1)
+  )
+  
+  for(nsim_local in 1:1000){
+
[…]

### 2023-02-10 manuscript/C3_code/main/robustness_random_max_TSS.R

@@ -1,0 +1,166 @@
+# 2022.08.30
+
+library(cheddar)
+library(dplyr)
+library(R.utils)
+library(ggplot2)
+library(tidyr)
+library(HDInterval)
+
+sourceDirectory("../C1_method/R", modifiedOnly = FALSE)
+sourceDirectory("R", modifiedOnly = FALSE)
+
+dd_rand_raw <- readRDS("results/random_raw_maxTSS.RDS")
+
+fw_list <- unique(dd_rand_raw$fw_name)
+sim_ind <- unique(dd_rand_raw$nsim)
+list_all <- expand.grid(nsim = sim_ind, fw_name = fw_list)
+N <- dim(list_all)[1]
+
+rob_all <- data.frame(robustness = double(), fw_name = character(), type = character(), connectance = double(),
+                      S = double())
+
+Nsim <- 1000
+
+metadata_fw_tol <- read_excel("~/Google Drive/GitHub/C1_method_v2/data/parameter_values.xlsx")
+
+for(foodweb in fw_list){
+  
+  #### Emprirical food web first ####
+  dd_rand_emp <- dd_rand_raw %>%
+    filter(fw_name == foodweb, type == "Empirical")
+  
+  dd_rand_emp <- dd_rand_emp %>%
+    mutate(total_ext = (acc_pri_ext + acc_sec_ext)/S)
+  
+  pred_mat_emp <- readRDS(paste0("../C1_method_v2/data/", foodweb, ".web.RDS"))$predation.matrix
+  conn_emp <- sum(pred_mat_emp)/(dim(pred_mat_emp)[1]^2)
+  S <- dim(pred_mat_emp)[1]
+  
+
+  for(k in 1:Nsim){
+    robustness <- NA
+    dd_rand_emp_local <- dd_rand_emp %>%
+      filter(nsim == k)
+    
+    N_row <- dim(dd_rand_emp_local)[1]
+    for(i in 1:N_row){
+      ith_row <- dd_rand_emp_local[i,]
+      if(ith_row$total_ext >= 0.5){
+        robustness <- ith_row$acc_pri_ext/ith_row$S
+        # print(robustness)
+        break
+      }
+    }
+    
+    robustness <- min(robustness, 0.5)
+    
+    rob_all <- rbind(rob_all,
+                     data.frame(robustness = robustness, fw_name = foodweb, type = "Empirical", connectance = conn_emp,
[…]

### 2023-05-26 manuscript/SI.Rmd
Updated ms, SI

--- 2023-02-10 manuscript/ms_C3_v2.Rmd
@@
 ---
-title: Missing links and the topological robustness of food webs
-authors:
-- affiliation: University of Zurich
-  department: Department of Evolutionary Biology and Environmental Studies
-  email: anubhav.gupta@ieu.uzh.ch
-  location: 8057 Zurich, Switzerland
-  name: Anubhav Gupta
-  thanks: Corresponding author
-- affiliation: University of Zurich
-  department: Department of Evolutionary Biology and Environmental Studies
-  email: owen.petchey@ieu.uzh.ch
-  location: 8057 Zurich, Switzerland
-  name: Owen L. Petchey
-geometry: margin=1in
-abstract: |
-
- 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs.
-Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links.
-Simultaneously, models might predict links which cannot occur, i.e., false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
-Thus, we expect that predicted food webs are more robust than observed ones.
-However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e.
-the difference in robustness of predicted and observed food web with respect to the difference in their connectance, been quantified.
-  3) We fill this research gap by comparing the robustness of observed food webs to the robustness of food webs predicted by a model (the ADBM) that can account for missing links but does not predict all links correctly.
-We did this for 12 different food webs from a wide variety of ecosystems.
-We used three extinction scenarios: random, most connected, and least connected.
-  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs.
-On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios.
-On the other hand, we saw no effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
-  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
-Nevertheless, increased connectance may contribute to lower dynamical stability, so it would be interesting to compare the dynamical stability of observed and predicted food webs and the topological stability that we have focused on.
-
-keywords:
-  - connectance
-  - ABC
-  - ADBM
-  - food web
-  - extinction
-  - uncertainty
+title: "Supplementary Information:  \nMissing links and the topological robustness of food webs"
+author:
+  - Anubhav Gupta
+  - Owen L. Petchey
+date: "`r format(Sys.time(), '%d %B %Y')`"
 header-includes:
    - \usepackage{lineno}
-  - \linenumbers
-  - \usepackage {amsmath}
-  - \setlength\parindent{24pt}
+   #- \linenumbers
+   - \renewcommand{\thefigure}{S\arabic{figure}}
+   - \setcounter{figure}{0}
    - \usepackage{setspace}\doublespacing
-# indent: true
-mainfont: Times New Roman
-bibliography: bibliography.bib
-csl: methods-in-ecology-and-evolution.csl
-biblio-style: biblatex
+   - \usepackage{float}
 output:
-  rticles::arxiv_article:
-    keep_tex: true
+  pdf_document: 
+    number_sections: yes
+    latex_engine: pdflatex
 ---
 
-# Introduction
-
-<!-- ## Background on anthropogenic changes and its impact on food web -->
-
-Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity and can lead to food web collapse [@ullah2018].
-This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
-An example of a secondary extinction is when a consumer goes extinct because its sole resource species goes extinct.
-Therefore, research focused on cascading secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
-This research revealed that the rate of collapse of a food web depends on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-
-Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
-Primary species loss is considered to be extinction of a species due to causes external to the food web, e.g.
-overharvesting [@koningGrassrootsReservesRescue2021], introduction of invasive species [@davidImpactsInvasiveSpecies2017].
-A secondary extinction is an extinction caused by a previous extinction (either primary or secondary).
-Numerous studies have used topological criterion for assigning a secondary extinction to a species, i.e., if extinction is of the last resource species of a consumer species, then the consumer species suffers secondary extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @soleComplexityFragilityEcological2001].
-
-When there are few primary extinctions, and these cause many secondary extinctions, a food web is said to be fragile or not robust.
-In contrast, a food web is said to be robust when there are only a few secondary extinctions.
-Several studies have shown that the robustness of the food webs increases with food web connectance [@dunneNetworkStructureBiodiversity2002; @dunneCascadingExtinctionsCommunity2009].
-Additionally, these studies have demonstrated that the removal (primary extinction) of the most connected species causes considerably more secondary extinctions than the random removals of species [@dunneNetworkStructureBiodiversity2002; @soleComplexityFragilityEcological2001].
-Simulation studies like these, which investigate the impact of primary extinctions in a food web to quantify robustness based on its topological structure, provide an alternate solution to canonical experiments in natural ecosystems, which are not possible or very difficult to conduct [@dunneCascadingExtinctionsCommunity2009].
-
-Along with quantifying food web robustness based on its topological structure, studies such as @williamsEffectsNetworkDynamical2008, @broseAllometricScalingEnhances2006, and @martinezDiversityComplexityPersistence have quantified robustness based on the abundance dynamics of a food web.
-However, the topological approach of quantifying a food web's robustness only requires the food web structure, whereas the dynamical approach requires the food web structure and the temporal dynamics of the abundance of species in that food web.
-For example, @williamsEffectsNetworkDynamical2008 combined network structure models with bioenergetic dynamics models to study the role of food web topology and nonlinear dynamics on species coexistence in complex ecological networks.
-
-<!-- ## [OP] State what is the problem... -->
-
-A key assumption of the observed food webs is that they are very well sampled, i.e.
-all the links that in reality can occur are represented.
-However, it is known that not all food webs are very well sampled and do not represent all of the feeding links that can occur [@caronAddressingEltonianShortfall; @patonaiAggregationIncompleteFood2017; @jordanoSamplingNetworksEcological2016].
-Some rare trophic links require more sampling effort than others, whereas some trophic links remain unobserved because of biological constraints such as spatio-temporal uncoupling, size or reward mismatching, foraging constraints and physiological-biochemical constraints, which are irrespective of sufficient sampling effort [@jordanoSamplingNetworksEcological2016].
-Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
-One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] to predict the missing links and then measure the robustness of the predicted food web.
-The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare.
-However, this solution is not infallible, as it is likely that the food web model might still miss some links and also may predict some links that could not, in fact occur.
-
-<!-- ## What we do in this study -->
-
-In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs.
-We expect the ADBM predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the ADBM predicts greater connectance compared to that of the observed food webs.
-We do this by simulating primary species loss in 12 food webs predicted by the ADBM to quantify the secondary loss of extinctions and compare the robustness of food webs predicted by the ADBM to the robustness of the observed food webs.
-We use three different approaches of primary species removal: (i) most connected species, (ii) random species and (iii) least connected species to understand if the outcome varies among these approaches.
-
-# Materials and methods
-
-In the upcoming sections, we present a detailed account of the implementation of the simulation of primary extinctions for three different extinction scenarios on 12 food webs predicted by the ADBM from a wide variety of ecosystems and compute the resultant secondary extinctions.
-We then describe a robustness metric of those predicted food webs and how we compare them to the properties of the food webs.
-
-## Allometric Diet Breadth Model (ADBM)
-
-The allometric diet breadth model (ADBM) is based on optimal foraging theory, specifically the contingency model [@macarthur1966].
-We chose this model because it is known to predict greater connectance in the predicted food webs compared to the observed food webs [@guptaSimultaneouslyEstimatingFood2022].
-The ADBM predicts the set of prey species a consumer should feed upon to maximise its rate of energy intake [@petchey2008].
-The foraging variables used in the model are the energy content of prey, handling times of the predator on prey, space clearance rate, i.e.
-how fast a predator searches space, and prey densities.
-Each of these variables is derived from the allometric scaling relationship using the body sizes of species.
-More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in open access @petchey2008.
-
-## Food web data
-
-The observed food webs that we fit the ADBM to belong to marine, freshwater and terrestrial ecosystems (Table \ref{fig:tab_1}).
-We considered these food webs because they belong to diverse ecosystems and follow FAIR (Findable Accessible Interoperable Reusable) principles [@wilkinsonFAIRGuidingPrinciples2016].
-These food webs contain primary producers, herbivores, carnivores, parasites, and parasitoids and various feeding interactions, including predation, herbivory, bacterivory, parasitism and pathogenic.
-The observed connectance of these food webs varies from 0.03 to 0.24 (Links/Species$^2$), and the number of species varies from 29 to 239.
-The goodness of fit of the ADBM's predictions depends on the interaction types in the food webs.
-For example, those with size-structured interactions, such as herbivory in aquatic ecosystems, are better predicted compared to less size-structured ones, such as parasitoids and terrestrial herbivory ones [@petchey2008].
-
-```{r echo=FALSE, warning=FALSE}
-library(readxl)
-library(knitr)
-library(kableExtra)
-fw_table <- read_excel("table/fw_table.xlsx")
-kable(fw_table, format = "latex",
-      caption = "\\label{fig:tab_1}Information about the food webs predicted using the ADBM.", escape = FALSE, align = "l") %>%
-  kable_styling(font_size = 7, latex_options="scale_down", row_label_position = 1) %>%
-  landscape(margin = "1cm") %>%
-  column_spec(1, width = "4cm") %>%
-  column_spec(2, width = "3cm") %>%
-  column_spec(4, width = "2cm") %>%
-  column_spec(5, width = "2cm") %>%
-  column_spec(6, width = "3cm")
-
-```
-
-<!-- ## \*\*OP: need a section on how the food web model was fit to the data. Also should state how we deal with / use the uncertainty contained in the posterior joint distribution. -->
-
-## Model parameterisation using approximate Bayesian computation
-
-The ADBM was parameterised using approximate Bayesian computation (ABC), where a set of parameter values were sampled from a prior distribution.
-Then, that set of parameter values was either accepted or rejected based on how close the predicted food web was to the observed food web using an accuracy metric -- true skill statistic (TSS).
-The accepted parameter values formed a posterior distribution (Fig.
-4 and S14-S25 in @guptaSimultaneouslyEstimatingFood2022).
-Further, prediction intervals of the true skill statistic and connectance of the predicted food webs were computed (Fig.
-5 (a, b) in @guptaSimultaneouslyEstimatingFood2022).
-In our study, we considered model predicted food webs where the predicted connectance lay within the 95% prediction interval of all model predicted food webs.
-A detailed explanation of the parameterisation method can be found in @guptaSimultaneouslyEstimatingFood2022.
-
-## Extinction scenarios and robustness
-
-We implemented the primary species removal method from @dunneCascadingExtinctionsCommunity2009 by sequentially removing species using one of the three criteria: removal of (i) the most connected species, (ii) the least connected species and (iii) randomly chosen species.
-The most connected and least connected criteria are based on species' degree (i.e.
-the total number of links to resources and from consumers).
-We considered these three criteria because the random extinction scenario takes into account all the theoretically possible extinction sequences of species that can occur in a food web, while the extinction of the most connected species and least connected species takes into account the two opposite extreme scenarios.
-These extinction scenarios have been widely used in studying species extinctions and the collapse of food webs and other networks [@dunne2002network; @soleComplexityFragilityEcological2001; @dunne2004; @dunneCascadingExtinctionsCommunity2009; @albertStatisticalMechanicsComplex2002].
-
-Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded.
-Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
-Once no more secondary extinctions occurred, then another primary extinction was made of the next appropriate species depending on the extinction scenario.
-This process was carried out until all the species were extinct from the food web.
-
-The robustness (R) of a food web was defined as the proportion of species subjected to primary removals resulting in extinction (primary and secondary extinctions) of some specified proportion of the species.
-In our study, we use $R_{50}$, the number of primary extinctions divided by the total number of species, which results in at least 50% of total species loss [@dunne2002network; @dunne2004; @jonssonReliabilityR50Measure2015; @dunneCascadingExtinctionsCommunity2009].
-Therefore, if primary extinctions never cause any secondary extinctions, the food web is maximally robust and ($R_{50} = 0.50$).
-Whereas in a minimally robust community ($R_{50} = 1/S$, where $S$ is the number of species), the first primary extinction causes a cascade of secondary extinctions of at least nearly half of the species in the food web (i.e.
-at least $S/2 - 1$).
-
-## Simulating species extinctions
-
-First, we simulated primary species loss in food webs predicted by the ADBM which had the maximum true skill statistics and compared it to primary species loss in observed food webs.
-Second, to take into account the uncertainty in robustness in the ADBM predicted food webs, we simulated primary species loss and thereby computed robustness for all the ADBM predicted food webs corresponding to the 95% prediction interval of the predicted connectance.
-Furthermore, in the case of the random extinction scenario, we simulated 1000 random extinction sequences in a single ADBM predicted food web.
-
-## Analysis
-
-In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web to random extinction.
-To quantify the effect of undersampling, i.e.
-greater connectance of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (i.e.
-0.5 for $R_{50}$ and 1 for connectance).
-However, we did not perform any statistical significance test because we work with simulated food webs and therefore, the p-values of these tests are influenced by the number of model simulations [@whiteEcologistsShouldNot2014].
-
-# Results
-
-We first present the secondary extinction curves of the ADBM predicted food webs which had the maximum true skill statistics and of the observed food webs for 12 food webs under three different extinction scenarios.
-We then compare the robustness of all the ADBM predicted food webs within the 95% prediction interval against that of the observed food webs to take into account uncertainty in the robustness across food webs predictions.
-Finally, we quantify the effect of the difference in their connectance on the difference in their robustness estimates.
-
-## Secondary extinctions
-
-In the most connected extinction scenario, the cumulative secondary extinction curves started to rise steeply in the observed food webs at a lower number of primary species removal as compared to the ADBM predicted food webs for nine food webs (Fig.
-\ref{fig:fig_r1} (a, c, d, e, f, g, h, j, l)).
-However, there was a higher number of cumulative secondary extinctions occurring in the ADBM predicted food webs when compared to that of the observed food webs at a high number of primary species removal in five food webs (Fig.
-\ref{fig:fig_r1} (a, f, g, h, k)).
-In the Skipwith Pond food web, there were no secondary extinctions for any number of primary removal of species (Fig.
-\ref{fig:fig_r1} (i)), whereas in the Broadstone Stream (taxonomic aggregation) food web the same was true only for the observed food web but in the ADBM predicted food web there was a steep rise in the cumulative secondary extinctions (Fig.
-\ref{fig:fig_r1} (b)).
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r1} Cumulative secondary extinctions of species resulting from the primary removals of the \\textbf{most connected species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_mostconnected_maxTSS.png")
-```
-
-In Fig.
-\ref{fig:fig_r2}, we present the cumulative secondary extinctions in the ADBM predicted and the observed food webs for five (out of 1000) independent random extinction sequences to show example variation caused by different random primary extinction orders.
-The secondary extinction curves of the ADBM predicted food webs were steeper than that of the observed food webs, i.e.
-primary removal of some species in an extinction sequence can lead to the complete collapse of the remaining food web in the ADBM predicted food webs.
-
-```{r, echo=FALSE, fig.align='center', out.width="400px", fig.cap="\\label{fig:fig_r2} Cumulative secondary extinctions of species resulting from the primary removals of \\textbf{random species} in the ADBM predicted food webs corresponding to the maximum TSS and observed food webs for five (out ot 1000) independent random extinction sequences.
-S denotes the number of species in a food web.
-The cumulative secondary extinctions of species and the number of species removed have been normalised by the number of species."}
-knitr::include_graphics("../results/plot_ra_extlines_maxTSS.png")
-```
-
-Compared to the most connected and random extinction scenarios, there were fewer secondary extinctions in the least connected extinction scenario, and therefore the secondary extinction curves were flat for many of the food webs (Fig.
-\ref{fig:fig_r3}).
-In some of the food webs, the extinction curves of the ADBM predicted food webs overlapped with the observed food webs (Fig.
-\ref{fig:fig_r3} (b, c, g, h, i, k, l)}).
-In five of the food webs, a very high number of secondary extinctions occurred at a very low number of primary species removal (Fig.
-\ref{fig:fig_r3} (a, d, e, f, j)).
+# Supplementary Information
 
@@
 ```
-
-## Robustness
-
-The ADBM predicted food webs were more robust than the observed food webs on average in the most connected and random extinction scenarios (Fig.
-\ref{fig:fig_r4} (a, b)).
-However, there were large variations in the robustness within the ADBM predicted food webs in the most connected extinction scenario (Fig.
-\ref{fig:fig_r4} (a)).
-For example, the ADBM predicted Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the ADBM predicted food webs compared to other food webs.
-
-The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
-\ref{fig:fig_r4} (a, b)).
-Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
-\ref{fig:fig_r4} (b)).
-Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
-Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
-The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
-\ref{fig:fig_r4} (a, b)).
-Small Reef and Benguela Pelagic food webs had more variations in robustness within the ADBM predicted food webs as compared to the other food webs (Fig.
-\ref{fig:fig_r4} (b)).
-Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both ADBM predicted and observed food webs.
-Although there were few less robust ADBM predicted food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
-
-In the least connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig.
-\ref{fig:fig_r4} (c)), however there were some exceptions.
-The ADBM predicted food webs for Small Reef and Benguela Pelagic had very low median robustness.
-Benguela Pelagic, Broom and Capinteria food webs from the ADBM had larger variations in robustness when compared to that of the others.
-
-```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r4} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
-Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-Some points are not visible due to perfect overlap in b and c.
-Refer to Fig.
-7 in the Supplementary Information for a faceted visualisation.
-The dashed black lines are the 1:1 relationships for reference."}
-knitr::include_graphics("../results/plot_R50_ADBM_vs_obs.png")
-```
-
-In all of the food webs except Small Reef and Broadstone Stream (taxonomic aggregation), the effect size of connectance on robustness was positive on average in the most connected extinction scenario (Fig.
-\ref{fig:fig_r5} (a)), i.e.
-greater connectance had a positive effect on the robustness.
-In the random extinction scenario, there was a positive effect of greater connectance on the robustness for Ythan, Small Reef, Mill Stream, Grasslands, Caricaie Lakes, Capinteria, Broom and Benguela Pelagic (Fig.
-\ref{fig:fig_r5} (b)).
-However, the effect size varied across the food webs.
-In the least connected extinction scenario, the median effect sizes were zero or very close to zero for all the food webs except Benguela Pelagic and Small Reef food webs where the median effect sizes were negative (Fig.
-\ref{fig:fig_r5} (c)).
-However, there were lots of outlier effect sizes less than zero.
-
-```{r, echo=FALSE, fig.align='center', out.width="450px", fig.cap="\\label{fig:fig_r5} Effect size (i.e.
-ratio of the difference in normalised robustness between ADBM predicted food webs and observed food webs to the difference in their normalised connectance) shown for the 12 food webs.
-Box represent the 25th and 75th percentile; bold black midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5."}
-knitr::include_graphics("../results/plot_R50_slope.png")
-```
-
-# Discussion
-
-As expected, the ADBM predicted food webs were more robust than the observed food webs on average.
-The considerable variation of the robustness of the ADBM predicted food webs suggests, however, that undersampling in food webs can lead to considerable uncertainty in the estimates of food web robustness, even when a model is used to compensate for undersampling.
-Furthermore, as was previously found, the food webs are least robust to primary extinction of the most connected species compared to that of least connected and random extinction scenarios on average.
-Future development would be to understand how undersampling, i.e.
-predicted greater connectance, influences the stability of the dynamics of the ADBM predicted food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria.
-However, one would expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].
-
-As mentioned, the robustness of the ADBM predicted food webs was higher than that of the observed food webs on average (Fig.
-\ref{fig:fig_r4}) for all of the 12 food web ecosystems (with some exceptions).
-This is likely due to the greater connectance of the ADBM predicted food webs as compared to that of the observed food webs because a species in a food web with a higher connectance has, on average, more trophic links as compared to a food web with a lower connectance (Fig.
-\ref{fig:fig_r5}).
-Our study suggests that it is important to consider undersampling in observed food webs when computing their robustness.
-
-## A paragraph on the implication of our study
-
-* On the uncertainty in the ADBM estimates 
-* On the limitation of a food web model 
-* On undersampling
-
-Contrary to general expectations [@dunneNetworkStructureBiodiversity2002], food web robustness did not always increase with the connectance (Fig.
-\ref{fig:fig_r5}).
-For example, the Benguela Pelagic and Small Reef ADBM predicted food webs were surprisingly less robust to primary extinctions on average in the least connected extinction scenario compared to the observed food webs (Fig.
-\ref{fig:fig_r4} (c) and \ref{fig:fig_r5} (c)).
-In these two food webs, the extinction of the least connected species could cause an almost complete, or complete collapse of the food web.
-We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
-As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
-This suggests that the greater connectance predicted by the ADBM resulted in a more robust food web on average.
-However, differences in the predicted food web properties, such as a lower proportion of basal species and higher maximum trophic level (Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness.
-On average, a consumer in a food web with a higher maximum trophic level would have fewer resources and be more susceptible to extinction than a consumer in a food web with a lower maximum trophic level [@binzerSusceptibilitySpeciesExtinctions2011].
-This suggests that food web properties other than connectance play an important role in determining a food web's robustness and, therefore, should also be taken into account [@binzerSusceptibilitySpeciesExtinctions2011; @mendoncaRobustnessTemperateTropical2022; @riedeSizebasedFoodWeb2011].
-
-As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM.
-Real false positive means that the food web model predicts a link between two species that can never interact.
-(The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
-In this case, further sampling should result in the link being observed and a change from false positive to true positive.) Firstly, this may be because the ADBM uses only body size as a trait.
-A trait uncorrelated with the body size may be influential in determining the interaction between two species [@guptaSimultaneouslyEstimatingFood2022].
-Secondly, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
-I.e.
-it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2.
-However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall].
-Hence, it would be intriguing to extend our study to use other food web models based on size-based rules, such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021, to understand if the results are dependent on the decision of model selection.
-We expect to get a similar result in a size-based deterministic model but a different result, i.e.
-lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010].
-It would also be interesting to use food web models not based on body size, such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008.
-We expect to have a difference in results based on whether the trophic interactions in the food webs are governed by size-structured rules or not.
-
-It would be intriguing to know if this difference in connectance has a similar influence on the dynamical stability of the food webs as well.
-Hence, a prospect could be to use a dynamical model (for example, the bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
-We expect that the greater connectance will lead to reduced dynamical stability in the ADBM predicted food web compared to that of the predicted food web.
-The difference in stability will be linearly related to the difference in connectance because @martinezDiversityComplexityPersistence has shown that food web stability linearly decreases with connectance.
-
-<!-- ## Use food web properties to parameterise the ADBM via ABC -->
-
-Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig.
-\ref{fig:fig_a1} in Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
-We would expect a more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.
-
-<!-- ## Conclusion -->
-
-We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e.
-greater connectance on the topological robustness of 12 food webs from various ecosystems.
-We found that the greater connectance can have a large impact on the robustness of the food webs while at the same time producing large variations in robustness among the predicted food webs.
-Furthermore, differences in other structural food web properties between the ADBM predicted food webs and the observed food webs are also responsible.
-
-# Acknowledgements
-
-This work was supported by the University Research Priority Program Global Change and Biodiversity (Grant number: U-704-04-11) of the University of Zurich.
-We thank the Petchey group members for their valuable suggestions in the manuscript.
-
-# Conflict of interest
-
-None declared
-
-# Author contributions
-
-**Anubhav Gupta:** Conceptualisation; Data curation; Formal analysis; Investigation; Methodology; Project administration; Software; Validation; Writing -- original draft; Writing -- review and editing.
-**Owen L.
-Petchey:** Conceptualization; Funding acquisition; Resources; Supervision; Writing -- review & editing.
-
-# Data Accessibility Statement
-
-All the data used in this study was collected in other studies and is openly available.
-We list those studies and the open access source in Table \ref{fig:tab_1}.
-The complete code used in the analysis is available in the repository <https://doi.org/10.5281/zenodo.7180835>.
-
-# Supplementary Information
 
@@
 ```
-
-# References

### 2023-05-26 manuscript/ms_C3_v3.Rmd
Updated ms, SI

@@
 Simultaneously, models might predict links which cannot occur, i.e., real false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than observed ones.
+  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones.
 Thus, we expect that predicted food webs are more robust than the observed ones.
@@
 
-## Paragraph on how other structural food web properties are responsible as well
+<!-- ## Paragraph on how other structural food web properties are responsible as well -->
 
@@
 Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
-One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008] (reference (gut content paper)) to predict the missing links and then measure the robustness of the predicted food web.
+One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web.
 The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare.
@@
 \ref{fig:fig_r4} (b)).
-Skipwith Pond and Broadstone Stream (taxonomic aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs.
-The food webs were more robust to the random extinction scenario than the most connected scenario (Fig.
-\ref{fig:fig_r4} (a, b)).
-Small Reef and Benguela Pelagic food webs had more variations in robustness within the model food webs as compared to the other food webs (Fig.
+Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs (Fig.
 \ref{fig:fig_r4} (b)).
-Skipwith Pond, Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size aggregation) food webs were the most robust (Median $R_{50} = 0.5$) for both model and observed food webs.
 Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
@@
 Refer to Fig.
-7 in the Supplementary Information for a faceted visualisation.
+S3 in the Supplementary Information for a faceted visualisation.
 The dashed black lines are the 1:1 relationships for reference."}
@@
 
-## A paragraph on the implication of our study
-
-* On the uncertainty in the ADBM estimates 
-* On the limitation of a food web model 
-* On undersampling
-
 Our study also depicts that the uncertainty in the model predictions can have a strong influence on the perceived robustness of the observed food webs.
 The large variations in the robustness of the model predicted food webs suggest why it is crucial to incorporate uncertainty in the food web predictions.
-At the same time, our study also quantifies the impact of undersampling on the perceived robustness of the observed food webs which then influences the perceived functioning and stability of the food webs (reference).
+At the same time, our study also quantifies the impact of undersampling on the perceived robustness of the observed food webs which then influences the perceived functioning and stability of the food webs [@thompson2012food; @dunne2002network].
 This strongly suggest why it is crucial to incorporate the influence of undersampling.
@@
 In these two food webs, the extinction of the least connected species could cause an almost complete, or complete collapse of the food web.
-We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022).
-As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig: \ref{fig:fig_r3} (a) and (j)).
+We suspect this is because the ADBM predicted food webs have a lower proportion of basal species when compared to that of the observed food webs (Fig.
+6 (a) in @guptaSimultaneouslyEstimatingFood2022).
+As a result, these low-degree basal species are the ones to be removed at an early stage in the deletion sequence, thereby resulting in an earlier food web collapse in the ADBM predicted food web as compared to that of the observed food web (Fig.
+S1 (a) and (j) in the Supplementary Information).
 This suggests that the greater connectance predicted by the ADBM resulted in a more robust food web on average.
-However, differences in the predicted food web properties, such as a lower proportion of basal species and higher maximum trophic level (Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness.
+However, differences in the predicted food web properties, such as a lower proportion of basal species (Fig.
+6 (a) in @guptaSimultaneouslyEstimatingFood2022) and higher maximum trophic level (Fig.
+S2 in the Supplementary Information) when compared to that of the predicted food webs counteracted that effect and led to reduced robustness.
 On average, a consumer in a food web with a higher maximum trophic level would have fewer resources and be more susceptible to extinction than a consumer in a food web with a lower maximum trophic level [@binzerSusceptibilitySpeciesExtinctions2011].
@@
 
-Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig: 6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig.
-\ref{fig:fig_a1} in Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
+Since the ADBM predicted food webs have a lower proportion of basal species and a higher maximum trophic level as compared to that of the observed food webs (Fig.
+6 (a) in @guptaSimultaneouslyEstimatingFood2022 and Fig.
+S2 in the Supplementary Information), it would be interesting to use these properties as summary statistics to parameterise the ADBM and investigate how that influences the difference in the robustness between the ADBM predicted and the observed food webs.
 We would expect a more highly constrained predicted food web structure, lower variation in robustness, and a greater apparent influence of connectance on robustness.
@@
 
-# Supplementary Information
-
-```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
-Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference."}
-knitr::include_graphics("../results/plot_max_tl_ADBM_vs_emp.png")
-```
-
-```{r, echo=FALSE, fig.align='center', fig.pos="H", out.width="450px", fig.cap="\\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\\% of total species (primary removals and secondary extinctions).
-Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference."}
-knitr::include_graphics("../results/plot_R50_ADBM_vs_obs_ra_lc_facet.png")
-```
-
 # References

### 2023-05-26 manuscript/ms_C3_v3.tex
Updated ms, SI

@@
   trophic links divided by the number of possible links), and (ii) that
-  model predicted food webs usually have greater connectance than
+  model predicted food webs usually have greater connectance than the
   observed ones. Thus, we expect that predicted food webs are more
@@
 
-\hypertarget{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}{%
-\subsection{Paragraph on how other structural food web properties are
-responsible as
-well}\label{paragraph-on-how-other-structural-food-web-properties-are-responsible-as-well}}
-
 Structural properties other than food web connectance such as the
@@
 compensate for undersampling is using a food web model such as the
-Allometric Diet Breadth Model (ADBM) (Petchey et al., 2008) (reference
-(gut content paper)) to predict the missing links and then measure the
-robustness of the predicted food web. The ADBM is a mechanistic model
-constructed using foraging rules based on the body sizes of prey and
-predator, where trophic interactions satisfying those rules would be
-predicted by the model, which are perhaps not observed because those
-interactions are rare. However, this solution is not infallible, as it
-is likely that the food web model might still miss some links and also
-may predict some links that could not, in fact occur.
+Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey et
+al., 2008) to predict the missing links and then measure the robustness
+of the predicted food web. The ADBM is a mechanistic model constructed
+using foraging rules based on the body sizes of prey and predator, where
+trophic interactions satisfying those rules would be predicted by the
+model, which are perhaps not observed because those interactions are
+rare. However, this solution is not infallible, as it is likely that the
+food web model might still miss some links and also may predict some
+links that could not, in fact occur.
 
@@
 the model food webs as compared to the other food webs (Fig.
-\ref{fig:fig_r4} (b)). Skipwith Pond and Broadstone Stream (taxonomic
-aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
-for both model and observed food webs. The food webs were more robust to
-the random extinction scenario than the most connected scenario (Fig.
-\ref{fig:fig_r4} (a, b)). Small Reef and Benguela Pelagic food webs had
-more variations in robustness within the model food webs as compared to
-the other food webs (Fig. \ref{fig:fig_r4} (b)). Skipwith Pond,
-Broadstone Stream (taxonomic aggregation) and Broadstone Stream (size
-aggregation) food webs were the most robust (Median \(R_{50} = 0.5\))
-for both model and observed food webs. Although there were few less
-robust model food webs in the Broadstone Stream (size aggregation) as
-shown by the outliers.
+\ref{fig:fig_r4} (b)). Skipwith Pond, Broadstone Stream (taxonomic
+aggregation) and Broadstone Stream (size aggregation) food webs were the
+most robust (Median \(R_{50} = 0.5\)) for both model and observed food
+webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust
+model food webs in the Broadstone Stream (size aggregation) as shown by
+the outliers.
 
@@
 Refer to Fig.
-7 in the Supplementary Information for a faceted visualisation.
+S3 in the Supplementary Information for a faceted visualisation.
 The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-2}
@@
 
-\hypertarget{a-paragraph-on-the-implication-of-our-study}{%
-\subsection{A paragraph on the implication of our
-study}\label{a-paragraph-on-the-implication-of-our-study}}
-
-\begin{itemize}
-\tightlist
-\item
-  On the uncertainty in the ADBM estimates
-\item
-  On the limitation of a food web model
-\item
-  On undersampling
-\end{itemize}
-
 Our study also depicts that the uncertainty in the model predictions can
 have a strong influence on the perceived robustness of the observed food
-webs. The large variations in the robustness of the observed food webs
-suggest why it is crucial to incorporate uncertainty in the food web
-predictions. At the same time, our study also quantifies the impact of
-undersampling on the perceived robustness of the observed food webs and
-thus influencing the perceived functioning and stability of the food
-webs (reference). This strongly suggest why it is crucial to incorporate
-the influence of undersampling.
+webs. The large variations in the robustness of the model predicted food
+webs suggest why it is crucial to incorporate uncertainty in the food
+web predictions. At the same time, our study also quantifies the impact
+of undersampling on the perceived robustness of the observed food webs
+which then influences the perceived functioning and stability of the
+food webs (Dunne et al., 2002a; Thompson et al., 2012). This strongly
+suggest why it is crucial to incorporate the influence of undersampling.
 
@@
 proportion of basal species when compared to that of the observed food
-webs (Fig: 6 (a) in Gupta et al. (2022)). As a result, these low-degree
+webs (Fig. 6 (a) in Gupta et al. (2022)). As a result, these low-degree
 basal species are the ones to be removed at an early stage in the
@@
 the ADBM predicted food web as compared to that of the observed food web
-(Fig: \ref{fig:fig_r3} (a) and (j)). This suggests that the greater
-connectance predicted by the ADBM resulted in a more robust food web on
-average. However, differences in the predicted food web properties, such
-as a lower proportion of basal species and higher maximum trophic level
-(Fig: \ref{fig:fig_a1}) when compared to that of the predicted food webs
-counteracted that effect and led to reduced robustness. On average, a
-consumer in a food web with a higher maximum trophic level would have
+(Fig. S1 (a) and (j) in the Supplementary Information). This suggests
+that the greater connectance predicted by the ADBM resulted in a more
+robust food web on average. However, differences in the predicted food
+web properties, such as a lower proportion of basal species (Fig. 6 (a)
+in Gupta et al. (2022)) and higher maximum trophic level (Fig. S2 in the
+Supplementary Information) when compared to that of the predicted food
+webs counteracted that effect and led to reduced robustness. On average,
+a consumer in a food web with a higher maximum trophic level would have
 fewer resources and be more susceptible to extinction than a consumer in
@@
 species and a higher maximum trophic level as compared to that of the
-observed food webs (Fig: 6 (a) in Gupta et al. (2022) and Fig.
-\ref{fig:fig_a1} in Supplementary Information), it would be interesting
-to use these properties as summary statistics to parameterise the ADBM
-and investigate how that influences the difference in the robustness
-between the ADBM predicted and the observed food webs. We would expect a
-more highly constrained predicted food web structure, lower variation in
+observed food webs (Fig. 6 (a) in Gupta et al. (2022) and Fig. S2 in the
+Supplementary Information), it would be interesting to use these
+properties as summary statistics to parameterise the ADBM and
+investigate how that influences the difference in the robustness between
+the ADBM predicted and the observed food webs. We would expect a more
+highly constrained predicted food web structure, lower variation in
 robustness, and a greater apparent influence of connectance on
@@
 \url{https://doi.org/10.5281/zenodo.7180835}.
-
-\hypertarget{supplementary-information}{%
-\section{Supplementary Information}\label{supplementary-information}}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=450px]{../results/plot_max_tl_ADBM_vs_emp}
-
-}
-
-\caption{\label{fig:fig_a1} The maximum trophic level of ADBM predicted food webs plotted against that of the observed food webs.
-Box represent the 25th and 75th percentile; bold midline represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-4}
-\end{figure}
-
-\begin{figure}[H]
-
-{\centering \includegraphics[width=450px]{../results/plot_R50_ADBM_vs_obs_ra_lc_facet}
-
-}
-
-\caption{\label{fig:fig_a2} Robustness comparison between the ADBM predicted food webs and the observed food webs for 12 food webs across different ecosystems for random and least connected extinction scenarios.
-Here, $R_{50}$ is the proportion of species that have to be removed to achieve a total loss of at least 50\% of total species (primary removals and secondary extinctions).
-Box represent the 25th and 75th percentile; solid diamond represents the median; whisker represents outlier limits; the outlier coefficient used was 1.5.
-The dashed black lines are the 1:1 relationships for reference.}\label{fig:unnamed-chunk-5}
-\end{figure}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gupta2023many}{}}%
+Gupta, A., Figueroa, D., O'Gorman, E., Jones, I., Woodward, G., \&
+Petchey, O. L. (2023). How many predator guts are required to predict
+trophic interactions? \emph{Food Webs}, \emph{34}, e00269.
+
 \leavevmode\vadjust pre{\hypertarget{ref-guptaSimultaneouslyEstimatingFood2022}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-thompson2012food}{}}%
+Thompson, R. M., Brose, U., Dunne, J. A., Hall, R. O., Hladyz, S.,
+Kitching, R. L., Martinez, N. D., Rantala, H., Romanuk, T. N., Stouffer,
+D. B., et al. (2012). Food webs: Reconciling the structure and function
+of biodiversity. \emph{Trends in Ecology \& Evolution}, \emph{27}(12),
+689--697.
+
 \leavevmode\vadjust pre{\hypertarget{ref-ullah2018}{}}%

### 2023-06-26 manuscript/ms_C3_v3.Rmd
Update ms_C3_v3.Rmd

@@
   2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones.
-Thus, we expect that predicted food webs are more robust than the observed ones.
+Thus, we expect that predicted food webs with fewer missing links are more robust than the observed ones.
 However, this expectation has never, to our knowledge, been tested, nor has the effect size, i.e.
@@
 We did this for 12 different food webs from a wide variety of ecosystems.
-We used three extinction scenarios: random, most connected, and least connected.
+We used three extinction scenarios: random, most connected first, and least connected first.
   4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs.
@@
   5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
-Also, the differences in the structural properties of the model predicted food webs and the observed food webs suggest structural properties of a food web could be used as summary statistics to fit models such as the ADBM to the observed data.
+Moreover, differences in the structural properties of the model predicted food webs, such as proportion of basal species and maximum trophich height can have large effects on robustness and therefore could be used to further constrain predicted food webs and perhaps produce more constrained predictions of food web robustness.
 
@@
 Anthropogenic changes such as climate change and habitat destruction are a threat to biodiversity and can lead to food web collapse [@ullah2018].
-This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
+This food web collapse is due to the cascades of secondary extinctions in a food web because of the primary loss of species due to environmental change and anthropogenic impacts [@pimmHumanImpactsRates2006; @thomasComparativeLossesBritish2004; @thomasExtinctionRiskClimate2004].
 An example of a secondary extinction is when a consumer goes extinct because its sole resource species goes extinct.
-Therefore, research focused on cascading secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
+Therefore, research about cascades of secondary extinctions, also known as 'community viability analysis', has been performed extensively in the past few decades to quantify how robust food webs are to species extinction [@dunne2002network; @dunneCascadingExtinctionsCommunity2009; @bergUsingSensitivityAnalysis2011; @ebenmanCOMMUNITYVIABILITYANALYSIS2004; @ebenmanUsingCommunityViability2005].
 This research revealed that the rate of collapse of a food web depends on its structure and complexity [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
 
-Simulation of primary species loss has been conducted in observed food webs and model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
+Simulation of the effects of primary species loss has been conducted in observed food webs and in model food webs from terrestrial and aquatic ecosystems, where robustness was measured in terms of secondary extinctions [@dunne2002network; @dunneCascadingExtinctionsCommunity2009].
 Primary species loss is considered to be extinction of a species due to causes external to the food web, e.g.
@@
 Previous studies such as @caronAddressingEltonianShortfall and @guptaSimultaneouslyEstimatingFood2022 have shown that the predicted food webs from these models usually have greater connectance than the observed ones.
-One solution to compensate for undersampling is using a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web.
+One solution to compensate for undersampling is, therefore, to  use a food web model such as the Allometric Diet Breadth Model (ADBM) [@petchey2008; @gupta2023many] to predict the missing links and then measure the robustness of the predicted food web.
 The ADBM is a mechanistic model constructed using foraging rules based on the body sizes of prey and predator, where trophic interactions satisfying those rules would be predicted by the model, which are perhaps not observed because those interactions are rare.
@@
 In our study, we investigate the topological robustness of the ADBM predicted food webs and compare it to that of the observed food webs.
-We achieved this by simulating primary species loss in 12 food webs predicted by the model to quantify secondary loss of extinctions and compare the robustness of food webs predicted by the model to the robustness of the observed food webs.
+We achieved this by simulating primary species loss in 12 food webs predicted by the model to quantify secondary loss of extinctions and comparing the robustness of food webs predicted by the model to the robustness of the observed food webs.
 We expect the model predicted food webs to be more robust than the observed food webs, and for the greater robustness to be related to the amount by which the model predicts greater connectance compared to that of the observed food webs.
-We also examined how different structural food web properties other than the connectance can influence this difference in the perceived robustness.
+We also examined how structural food web properties other than the connectance can influence this difference in the perceived robustness.
 In order to do that, we define our null hypothesis to be: (H1) The missing links that are filled in by the model increase robustness because they increase connectance; and our alternate hypothesis to be: (H2) Although the model fills in missing links, it also changes other structural properties and these outweigh the effects of connectance on robustness.
@@
 Each of these variables is derived from the allometric scaling relationship using the body sizes of species.
-More details on the foraging rules defined in the ADBM and ADBM's predictive power across different food webs can be found in open access @petchey2008.
+More details on the foraging rules defined in the ADBM and it's predictive power across different food webs can be found in open access @petchey2008.
 
@@
 
-Given a primary removal of species in a food web, if any remaining species lost all of their resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded.
+Given a primary removal of species in a food web, if any remaining species no longer have any resource species, or any cannibalistic species lost all of their resource species except the cannibalistic links, they are removed from the web, and a secondary extinction was recorded.
 Secondary extinctions may cause further secondary extinctions, which were also checked for and recorded.
@@
 In the random extinction scenario, we computed robustness $R_{50}$ for all 1000 independent random extinction sequences and calculated the median as a summary statistics to quantify the average robustness of a single food web to random extinction.
-To quantify the effect of undersampling, i.e.
-greater connectance of connectance, we compute the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance, where normalisation was performed by dividing the variables by their maximum possible values (i.e.
+To quantify the effect of undersampling, we computed the ratio of the difference in normalised robustness between the ADBM predicted food webs and observed food webs to the difference in their normalised connectance.
+Normalisation was performed by dividing the variables by their maximum possible values (i.e.
 0.5 for $R_{50}$ and 1 for connectance).
@@
 \ref{fig:fig_r4} (a)).
-For example, the model food webs for the Caricaie Lakes food web was more robust than the observed food web on average but had a larger variation in the robustness within the model food webs compared to other food webs.
+For example, the model food webs for the Caricaie Lakes food web were more robust than the observed food web on average but had a larger variation in the robustness within the model food webs compared to other food webs.
 
@@
 \ref{fig:fig_r4} (b)).
-Although there were few less robust model food webs in the Broadstone Stream (size aggregation) as shown by the outliers.
 
 In the least connected extinction scenario, the food webs had a very high robustness (Median $R_{50} = 0.5$) for most of the food webs (Fig.
-\ref{fig:fig_r4} (c)), however there were some exceptions.
+\ref{fig:fig_r4} (c)).
+However there were some exceptions.
 The model food webs for Small Reef and Benguela Pelagic had very low median robustness.
@@
 \ref{fig:fig_r5} (c)).
-However, there were lots of outlier with effect sizes negative.
+However, there were many outliers with effect sizes negative.
 
@@
 predicted greater connectance, influences the stability of the dynamics of the model food webs against that of the observed food webs and compare it with the patterns in our study in which extinction occur only by topological criteria.
-However, one would expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].
+One would at least expect a decrease in food web stability with greater connectance [@martinezDiversityComplexityPersistence; @mayWillLargeComplex1972].
 
@@
 As with any food web model, we expect that there are real false positives in the food webs predicted by the ADBM.
-Real false positive means that the food web model predicts a link between two species that can never interact (The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
+Real false positive means that the food web model predicts a link between two species that can never interact.
+(The other type of false positive is when the model predicts a link that was not observed but could have been observed if the food web was sampled enough.
 In this case, further sampling should result in the link being observed and a change from false positive to true positive.).
@@
 Secondly, the ADBM can only predict diets that are contiguous with respect to the size of the prey.
-I.e.
-it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2.
+I.e., it cannot predict that the consumer will consume prey of size 1 and 3, and not consume prey of size 2.
 However, it is important to note that observed diets are not always contiguous when prey are ordered by their size due to some ecological differences in how predator species choose their prey [@caronAddressingEltonianShortfall].
 Hence, it would be intriguing to extend our study to use other food web models based on size-based rules, such as @gravelInferringFoodWeb2013a and @vagnonAllometricNicheModel2021, to understand if the results are dependent on the decision of model selection.
-We expect to get a similar result in a size-based deterministic model but a different result, i.e.
-lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010].
+We expect to get a similar result in a size-based deterministic model but a different result, i.e., lower robustness in a size-based stochastic model as compared to the ADBM because the latter can take into account non-contiguity in predator diets [@williamsProbabilisticNicheModel2010].
 It would also be interesting to use food web models not based on body size, such as @cattinPhylogeneticConstraintsAdaptation2004 and @allesinaGeneralModelFood2008.
@@
 
-It would be intriguing to know if this difference in connectance has a similar influence on the dynamical stability of the food webs as well.
+It would be intriguing to know if the difference in connectance has a similar influence on the dynamical stability of the food webs as well.
 Hence, a prospect could be to use a dynamical model (for example, the bioenergetic food web model by @broseAllometricScalingEnhances2006) to model the temporal dynamics of the ADBM predicted food webs.
@@
 
-We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e.
-greater connectance on the topological robustness of 12 food webs from various ecosystems.
+We have used a food web model to compensate for undersampling in recorded food webs and thereby quantified the influence of missing links, i.e., greater connectance on the topological robustness of 12 food webs from various ecosystems.
 We found that the greater connectance can have a large impact on the robustness of the food webs while at the same time producing large variations in robustness among the predicted food webs.

### 2023-12-18 manuscript/ms_C3_v3.tex
abstract shortened

@@
   Undersampling can lead to missing trophic interactions in recorded
-  food webs, with potential consequences for the perceived functioning
-  and stability of the food webs. Undersampling can be compensated for
-  by using food web models such as the allometric diet breadth model
-  (ADBM) to predict missing links. Simultaneously, models might predict
-  links which cannot occur, i.e., real false positives.
+  food webs, impacting the perceived functioning and stability of the
+  food webs. Undersampling can be compensated for by using food web
+  models such as the allometric diet breadth model (ADBM) to predict
+  missing links. Simultaneously, models might predict links which cannot
+  occur, i.e., real false positives.
 \item
-  Previous research shows that (i) food web robustness (the inverse of
-  the number of secondary extinctions occurring due to primary
-  extinctions) increases with connectance (the number of realised
-  trophic links divided by the number of possible links), and (ii) that
-  model predicted food webs usually have greater connectance than the
-  observed ones. Thus, we expect that predicted food webs are more
-  robust than the observed ones. However, this expectation has never, to
-  our knowledge, been tested, nor has the effect size, i.e.~the
-  difference in robustness of predicted and observed food web with
-  respect to the difference in their connectance, been quantified.
+  Previous research shows that (i) food web robustness increases with
+  connectance, and (ii) that model predicted food webs usually have
+  greater connectance than the observed ones. Thus, we expect that
+  predicted food webs with fewer missing links are more robust than the
+  observed ones. However, this expectation has never, to our knowledge,
+  been tested, nor has the effect size, i.e.~the difference in
+  robustness of predicted and observed food web with respect to the
+  difference in their connectance, been quantified.
 \item
@@
   webs from a wide variety of ecosystems. We used three extinction
-  scenarios: random, most connected, and least connected.
+  scenarios: random, most connected first, and least connected first.
 \item
-  We found, as expected, that the predicted food webs were more robust
-  than the observed food webs, which can be attributed to the higher
-  connectance of the predicted food webs. On average, for every one unit
-  of increase in connectance, we found that the food webs robustness
-  increased by 0.52 units for the most connected species extinction
-  scenario and by 0.04 units for the random species extinction
-  scenarios. On the other hand, we saw no effect or very little effect,
-  on average, of increased connectance for the least connected species
-  extinction scenario for all except two of the 12 food webs.
+  We found, as expected, that predicted food webs were more robust than
+  observed food webs, which can be attributed to the higher connectance
+  of the predicted food webs. On average, a one-unit rise in connectance
+  corresponded to a 0.52-unit increase in robustness for the most
+  connected species extinction scenario and a 0.04-unit increase for
+  random species extinction scenarios. Interestingly, the least
+  connected species extinction scenario showed minimal or no effect on
+  increased connectance, on average, for most food webs, except for two.
 \item
-  These results show that undersampling can lead to large underestimates
-  of food web robustness that can be compensated for by filling in
-  missing links with food web models. Also, the differences in the
-  structural properties of the model predicted food webs and the
-  observed food webs suggest structural properties of a food web could
-  be used as summary statistics to fit models such as the ADBM to the
-  observed data.
+  These results emphasize the significant underestimation of food web
+  robustness caused by undersampling, mitigated by filling in missing
+  links using models. Moreover, differences in the structural properties
+  of the model predicted food webs, such as proportion of basal species
+  and maximum trophic height can have large effects on robustness and
+  therefore could be used to further constrain predicted food webs and
+  perhaps produce more constrained predictions of food web robustness.
 \end{enumerate}
@@
 extinctions in a food web because of the primary loss of species due to
-environmental change (Pimm et al., 2006; C. D. Thomas et al., 2004; J.
-A. Thomas et al., 2004). An example of a secondary extinction is when a
-consumer goes extinct because its sole resource species goes extinct.
-Therefore, research focused on cascading secondary extinctions, also
-known as `community viability analysis', has been performed extensively
-in the past few decades to quantify how robust food webs are to species
-extinction (Berg et al., 2011; Dunne et al., 2002a; Dunne \& Williams,
-2009; Ebenman et al., 2004; Ebenman \& Jonsson, 2005). This research
-revealed that the rate of collapse of a food web depends on its
-structure and complexity (Dunne et al., 2002a; Dunne \& Williams, 2009).
+environmental change and anthropogenic impacts (Pimm et al., 2006; C. D.
+Thomas et al., 2004; J. A. Thomas et al., 2004). An example of a
+secondary extinction is when a consumer goes extinct because its sole
+resource species goes extinct. Therefore, research about cascades of
+secondary extinctions, also known as `community viability analysis', has
+been performed extensively in the past few decades to quantify how
+robust food webs are to species extinction (Berg et al., 2011; Dunne et
+al., 2002a; Dunne \& Williams, 2009; Ebenman et al., 2004; Ebenman \&
+Jonsson, 2005). This research revealed that the rate of collapse of a
+food web depends on its structure and complexity (Dunne et al., 2002a;
+Dunne \& Williams, 2009).
 
-Simulation of primary species loss has been conducted in observed food
-webs and model food webs from terrestrial and aquatic ecosystems, where
-robustness was measured in terms of secondary extinctions (Dunne et al.,
-2002a; Dunne \& Williams, 2009). Primary species loss is considered to
-be extinction of a species due to causes external to the food web,
-e.g.~overharvesting (Koning \& McIntyre, 2021), introduction of invasive
-species (David et al., 2017). A secondary extinction is an extinction
-caused by a previous extinction (either primary or secondary). Numerous
-studies have used topological criterion for assigning a secondary
-extinction to a species, i.e., if extinction is of the last resource
-species of a consumer species, then the consumer species suffers
-secondary extinction (Dunne et al., 2002a; Dunne \& Williams, 2009;
-Sol'e \& Montoya, 2001).
+Simulation of the effects of primary species loss has been conducted in
+observed food webs and in model food webs from terrestrial and aquatic
+ecosystems, where robustness was measured in terms of secondary
+extinctions (Dunne et al., 2002a; Dunne \& Williams, 2009). Primary
+species loss is considered to be extinction of a species due to causes
+external to the food web, e.g.~overharvesting (Koning \& McIntyre,
+2021), introduction of invasive species (David et al., 2017). A
+secondary extinction is an extinction caused by a previous extinction
+(either primary or secondary). Numerous studies have used topological
+criterion for assigning a secondary extinction to a species, i.e., if
+extinction is of the last resource species of a consumer species, then
+the consumer species suffers secondary extinction (Dunne et al., 2002a;
+Dunne \& Williams, 2009; Sol'e \& Montoya, 2001).
 
@@
 usually have greater connectance than the observed ones. One solution to
-compensate for undersampling is using a food web model such as the
-Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey et
-al., 2008) to predict the missing links and then measure the robustness
-of the predicted food web. The ADBM is a mechanistic model constructed
-using foraging rules based on the body sizes of prey and predator, where
-trophic interactions satisfying those rules would be predicted by the
-model, which are perhaps not observed because those interactions are
-rare. However, this solution is not infallible, as it is likely that the
-food web model might still miss some links and also may predict some
-links that could not, in fact occur.
+compensate for undersampling is, therefore, to use a food web model such
+as the Allometric Diet Breadth Model (ADBM) (Gupta et al., 2023; Petchey
+et al., 2008) to predict the missing links and then measure the
+robustness of the predicted food web. The ADBM is a mechanistic model
+constructed using foraging rules based on the body sizes of prey and
+predator, where trophic interactions satisfying those rules would be
+predicted by the model, which are perhaps not observed because those
+interactions are rare. However, this solution is not infallible, as it
+is likely that the food web model might still miss some links and also
+may predict some links that could not, in fact occur.
 
@@
 predicted by the model to quantify secondary loss of extinctions and
-compare the robustness of food webs predicted by the model to the
+comparing the robustness of food webs predicted by the model to the
 robustness of the observed food webs. We expect the model predicted food
@@
 greater connectance compared to that of the observed food webs. We also
-examined how different structural food web properties other than the
-connectance can influence this difference in the perceived robustness.
-In order to do that, we define our null hypothesis to be: (H1) The
-missing links that are filled in by the model increase robustness
-because they increase connectance; and our alternate hypothesis to be:
-(H2) Although the model fills in missing links, it also changes other
-structural properties and these outweigh the effects of connectance on
-robustness.
+examined how structural food web properties other than the connectance
+can influence this difference in the perceived robustness. In order to
+do that, we define our null hypothesis to be: (H1) The missing links
+that are filled in by the model increase robustness because they
+increase connectance; and our alternate hypothesis to be: (H2) Although
+the model fills in missing links, it also changes other structural
+properties and these outweigh the effects of connectance on robustness.
 
@@
 body sizes of species. More details on the foraging rules defined in the
-ADBM and ADBM's predictive power across different food webs can be found
+ADBM and it's predictive power across different food webs can be found
 in open access Petchey et al. (2008).
@@
 Given a primary removal of species in a food web, if any remaining
-species lost all of their resource species, or any cannibalistic species
-lost all of their resource species except the cannibalistic links, they
-are removed from the web, and a secondary extinction was recorded.
-Secondary extinctions may cause further secondary extinctions, which
-were also checked for and recorded. Once no more secondary extinctions
-occurred, then another primary extinction was made of the next
-appropriate species depending on the extinction scenario. This process
-was carried out until all the species were extinct from the food web.
+species no longer have any resource species, or any cannibalistic
+species lost all of their resource species except the cannibalistic
+links, they are removed from the web, and a secondary extinction was
+recorded. Secondary extinctions may cause further secondary extinctions,
+which were also checked for and recorded. Once no more secondary
+extinctions occurred, then another primary extinction was made of the
+next appropriate species depending on the extinction scenario. This
+process was carried out until all the species were extinct from the food
+web.
 
@@
 single food web to random extinction. To quantify the effect of
-undersampling, i.e.~greater connectance of connectance, we compute the
-ratio of the difference in normalised robustness between the ADBM
-predicted food webs and observed food webs to the difference in their
-normalised connectance, where normalisation was performed by dividing
-the variables by their maximum possible values (i.e.~0.5 for \(R_{50}\)
-and 1 for connectance). However, we did not perform any statistical
-significance test because we work with simulated food webs and
-therefore, the p-values of these tests are influenced by the number of
-model simulations (White et al., 2014).
+undersampling, we computed the ratio of the difference in normalised
+robustness between the ADBM predicted food webs and observed food webs
+to the difference in their normalised connectance. Normalisation was
+performed by dividing the variables by their maximum possible values
+(i.e.~0.5 for \(R_{50}\) and 1 for connectance). However, we did not
+perform any statistical significance test because we work with simulated
+food webs and therefore, the p-values of these tests are influenced by
+the number of model simulations (White et al., 2014).
 
@@
 scenario (Fig. \ref{fig:fig_r4} (a)). For example, the model food webs
-for the Caricaie Lakes food web was more robust than the observed food
+for the Caricaie Lakes food web were more robust than the observed food
 web on average but had a larger variation in the robustness within the
@@
 most robust (Median \(R_{50} = 0.5\)) for both model and observed food
-webs (Fig. \ref{fig:fig_r4} (b)). Although there were few less robust
-model food webs in the Broadstone Stream (size aggregation) as shown by
-the outliers.
+webs (Fig. \ref{fig:fig_r4} (b)).
 
@@
 high robustness (Median \(R_{50} = 0.5\)) for most of the food webs
-(Fig. \ref{fig:fig_r4} (c)), however there were some exceptions. The
+(Fig. \ref{fig:fig_r4} (c)). However there were some exceptions. The
 model food webs for Small Reef and Benguela Pelagic had very low median
@@
 effect sizes were negative (Fig. \ref{fig:fig_r5} (c)). However, there
-were lots of outlier with effect sizes negative.
+were many outliers with effect sizes negative.
 
@@
 with the patterns in our study in which extinction occur only by
-topological criteria. However, one would expect a decrease in food web
+topological criteria. One would at least expect a decrease in food web
 stability with greater connectance (Martinez et al., 2006; May, 1972).
@@
 means that the food web model predicts a link between two species that
-can never interact (The other type of false positive is when the model
+can never interact. (The other type of false positive is when the model
 predicts a link that was not observed but could have been observed if
@@
 al., 2022). Secondly, the ADBM can only predict diets that are
-contiguous with respect to the size of the prey. I.e. it cannot predict
+contiguous with respect to the size of the prey. I.e., it cannot predict
 that the consumer will consume prey of size 1 and 3, and not consume
@@
 dependent on the decision of model selection. We expect to get a similar
-result in a size-based deterministic model but a different result,
-i.e.~lower robustness in a size-based stochastic model as compared to
-the ADBM because the latter can take into account non-contiguity in
-predator diets (Williams et al., 2010). It would also be interesting to
-use food web models not based on body size, such as Cattin et al. (2004)
-and Allesina et al. (2008). We expect to have a difference in results
-based on whether the trophic interactions in the food webs are governed
-by size-structured rules or not.
+result in a size-based deterministic model but a different result, i.e.,
+lower robustness in a size-based stochastic model as compared to the
+ADBM because the latter can take into account non-contiguity in predator
+diets (Williams et al., 2010). It would also be interesting to use food
+web models not based on body size, such as Cattin et al. (2004) and
+Allesina et al. (2008). We expect to have a difference in results based
+on whether the trophic interactions in the food webs are governed by
+size-structured rules or not.
 
-It would be intriguing to know if this difference in connectance has a
+It would be intriguing to know if the difference in connectance has a
 similar influence on the dynamical stability of the food webs as well.
@@
 recorded food webs and thereby quantified the influence of missing
-links, i.e.~greater connectance on the topological robustness of 12 food
-webs from various ecosystems. We found that the greater connectance can
-have a large impact on the robustness of the food webs while at the same
-time producing large variations in robustness among the predicted food
-webs. Furthermore, differences in other structural food web properties
-between the ADBM predicted food webs and the observed food webs are also
-responsible.
+links, i.e., greater connectance on the topological robustness of 12
+food webs from various ecosystems. We found that the greater connectance
+can have a large impact on the robustness of the food webs while at the
+same time producing large variations in robustness among the predicted
+food webs. Furthermore, differences in other structural food web
+properties between the ADBM predicted food webs and the observed food
+webs are also responsible.
 

### 2023-12-18 manuscript/ms_C3_v3.Rmd
Abstract shortened

@@
 
- 1)  Undersampling can lead to missing trophic interactions in recorded food webs, with potential consequences for the perceived functioning and stability of the food webs.
+ 1)  Undersampling can lead to missing trophic interactions in recorded food webs, impacting the perceived functioning and stability of the food webs.
 Undersampling can be compensated for by using food web models such as the allometric diet breadth model (ADBM) to predict missing links.
 Simultaneously, models might predict links which cannot occur, i.e., real false positives.
-  2) Previous research shows that (i) food web robustness (the inverse of the number of secondary extinctions occurring due to primary extinctions) increases with connectance (the number of realised trophic links divided by the number of possible links), and (ii) that model predicted food webs usually have greater connectance than the observed ones.
+  2) Previous research shows that (i) food web robustness increases with connectance, and (ii) that model predicted food webs usually have greater connectance than the observed ones.
 Thus, we expect that predicted food webs with fewer missing links are more robust than the observed ones.
@@
 We used three extinction scenarios: random, most connected first, and least connected first.
-  4)  We found, as expected, that the predicted food webs were more robust than the observed food webs, which can be attributed to the higher connectance of the predicted food webs.
-On average, for every one unit of increase in connectance, we found that the food webs robustness increased by 0.52 units for the most connected species extinction scenario and by 0.04 units for the random species extinction scenarios.
-On the other hand, we saw no effect or very little effect, on average, of increased connectance for the least connected species extinction scenario for all except two of the 12 food webs.
-  5) These results show that undersampling can lead to large underestimates of food web robustness that can be compensated for by filling in missing links with food web models.
-Moreover, differences in the structural properties of the model predicted food webs, such as proportion of basal species and maximum trophich height can have large effects on robustness and therefore could be used to further constrain predicted food webs and perhaps produce more constrained predictions of food web robustness.
+  4)  We found, as expected, that predicted food webs were more robust than observed food webs, which can be attributed to the higher connectance of the predicted food webs.
+On average, a one-unit rise in connectance corresponded to a 0.52-unit increase in robustness for the most connected species extinction scenario and a 0.04-unit increase for random species extinction scenarios.
+Interestingly, the least connected species extinction scenario showed minimal or no effect on increased connectance, on average, for most food webs, except for two.
+  5) These results emphasize the significant underestimation of food web robustness caused by undersampling, mitigated by filling in missing links using models.
+Moreover, differences in the structural properties of the model predicted food webs, such as proportion of basal species and maximum trophic height can have large effects on robustness and therefore could be used to further constrain predicted food webs and perhaps produce more constrained predictions of food web robustness.
 
